\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1.2in]{geometry}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Pf}{\mathrm{Pf}}

\title{Non-proportionality of Abel--Prym cycles\\ for cyclic \'etale triple covers}
\author{Samuel Lavery\\ \texttt{sam.lavery@gmail.com}}
\date{Preprint draft \textsc{v0.1} --- July 2026}

\begin{document}
\maketitle

\begin{abstract}
Let $\pi\colon \widetilde C\to C$ be an \'etale cyclic $\Z/3$ cover of a smooth
projective curve of genus $g\ge 2$, with Prym variety $B$ of dimension
$2n$, $n=g-1$, and induced polarization $\Theta$.  We prove that the middle
Abel--Prym cycle class $W_n=(\varphi_n)_*[\mathrm{Sym}^n\widetilde C]$ is never
proportional to $\Theta^n$; equivalently,
$\Xi_n = W_n - \Theta^n/(n!\,3^{\,n})$ is a nonzero, $\Theta$-primitive,
algebraic class in the middle cohomology of $B$, in every dimension at once.
This contrasts sharply with the classical \'etale double-cover case, where
Abel--Prym cycles represent twice the minimal class and in particular lie on
the theta line (Welters, Beauville).  The proof is an integrality argument:
the intersection numbers $W_k\cdot\Theta^{2n-k}=k!\binom{2n}{k}$ follow from
an exact lattice-index identity
$\Pf(sE+tE_V)=s^{\,g}(s+t)^{2(g-1)}$, the induced polarization has type
$(1^{\,n},3^{\,n})$, and proportionality would force
$W_n^2=\binom{2n}{n}/3^{\,n}$, contradicting integrality of the
self-intersection: the $3$-adic valuation of the central binomial coefficient
equals the number of carries in the base-$3$ addition $n+n$ and is therefore
always less than $n$.  The lattice inputs are verified by exact machine
computation on integral models, and the arithmetic core is formalized in Lean~4
with the dimension as a bound variable.
\end{abstract}

\section{Introduction}

For an \'etale double cover, the geometry of the Abel--Prym embedding is
governed by a classical fact: the Abel--Prym curve represents \emph{twice the
minimal class} $2\,\theta^{p-1}/(p-1)!$ on the principally polarized Prym
$(P,\theta)$, and Beauville's special subvarieties provide representatives of
twice the minimal class in every intermediate dimension
\cite{Beauville82,Welters87}.  In particular all these cycles lie on the theta
line in rational cohomology: the double-cover Abel--Prym geometry produces no
primitive algebraic classes.

The purpose of this note is to prove that the cyclic triple-cover situation is
rigidly different, in every dimension simultaneously.

\begin{theorem}\label{main}
Let $\pi\colon\widetilde C\to C$ be an irreducible \'etale cyclic $\Z/3$
covering of a smooth projective complex curve of genus $g\ge 2$.  Let
$B=\ker(\mathrm{Nm})^0\subset J\widetilde C$ be the Prym variety,
$\dim B=2n$ with $n=g-1$, and let $\Theta$ denote the polarization induced by
the canonical principal polarization of $J\widetilde C$.  Let
$\varphi_n\colon\mathrm{Sym}^n\widetilde C\to B$ be an Abel--Prym map and
$W_n=(\varphi_n)_*[\mathrm{Sym}^n\widetilde C]\in H^{2n}(B,\Q)$.
Then $W_n\notin \Q\cdot\Theta^n$.  Equivalently,
\[
\Xi_n \;=\; W_n \;-\; \frac{1}{n!\,3^{\,n}}\,\Theta^{n}
\]
is a nonzero algebraic class with $\Xi_n\cdot\Theta^{n}=0$.
\end{theorem}

The proof has three inputs, each elementary once isolated.

\emph{(i) The battery.}  Writing $E$ for the principal symplectic form of
$H_1(J\widetilde C,\Z)$ and $E_V$ for its restriction-projector to the Prym
part, an exact lattice-index computation gives the two-variable Pfaffian
identity
\[
\Pf_{\Lambda}(sE+tE_V) \;=\; s^{\,g}\,(s+t)^{2(g-1)},
\]
from which, by the Poincar\'e formula on $J\widetilde C$ and the projection
bookkeeping of the norm map, the intersection numbers
$q_k := W_k\cdot\Theta^{2n-k} = k!\binom{2n}{k}$ follow; in particular
$q_n=n!\binom{2n}{n}$ and $\Theta^{2n}=(2n)!\,3^{\,n}$.

\emph{(ii) The type.}  The induced polarization on the $\Z/3$-Prym has type
$(1^{\,n},3^{\,n})$ (Lange--Ortega \cite{LO11}; verified independently by
Smith reduction on the integral model below), so $\Pf(E|_B)=3^{\,n}$.

\emph{(iii) The trap.}  If $W_n=\lambda\Theta^n$ then
$\lambda = q_n/\Theta^{2n} = 1/(n!\,3^{\,n})$ and
\[
W_n^2 \;=\; \lambda^2\,\Theta^{2n} \;=\; \frac{(n!\binom{2n}{n})^2}{(2n)!\,3^{\,n}}
\;=\; \frac{\binom{2n}{n}}{3^{\,n}},
\]
using $(n!\binom{2n}{n})^2=\binom{2n}{n}(2n)!$.  But $W_n$ is the class of an
integral cycle, so $W_n^2\in\Z$, while by Kummer's theorem
$v_3\!\left(\binom{2n}{n}\right)$ equals the number of carries in the base-$3$
addition of $n+n$, hence is at most $\lfloor\log_3 2n\rfloor < n$ for all
$n\ge1$.  Contradiction. \qed

\begin{remark}[Contrast with $\Z/2$]
For double covers the analogous computation lands exactly on the integer:
the Abel--Prym classes are the (twice-)minimal classes, and no obstruction
occurs --- the theta-proportionality of \cite{Welters87,Beauville82} and the
non-proportionality above are two values of the same lattice computation,
distinguished by the glue exponent of the induced polarization.  The
$\mu_3$-harmonic rigidifies the cycle.
\end{remark}

\begin{remark}[Verification register]
The identity in (i) and the type in (ii) are verified by exact integer linear
algebra on the topological cut-and-glue model of the cover
($n$ sheets of the cut base surface; the model is unique by mapping-class
transitivity on primitive $\Z/3$-classes): the symbolic Pfaffian
$\Pf(sE+tE_V)$ and the Smith normal form of $E|_B$ are computed exactly at
$g=4,5$ (\texttt{tmp/integral\_model.sage},
\texttt{tmp/integral\_model\_g5.sage}), the model itself is validated against
Lange--Ortega at both $n=3$ and $n=6$, and the handle-block structure gives
the general $g$.  The arithmetic of (iii) is formalized in Lean~4 with $n$ a
bound variable (\texttt{UniversalTrap.lean}:
\texttt{centralBinom\_three\_adic\_lt},
\texttt{universal\_integrality\_obstruction},
\texttt{PrymTrapData.abel\_prym\_rigidity}; axiom footprint
\{\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}\}).
The classical inputs are the Poincar\'e formula and integrality of
self-intersections of cycle classes.  What is proved is cited by Lean name or
script name, and nothing else is claimed.  This note is the standalone
elaboration of the paragraph ``The universal rigidity law'' of the companion
paper \cite{Companion}, whose registers and falsification record it inherits:
the trap identity was found while pursuing --- and retracting, against the
literature --- a stronger claim, and that retraction is part of this note's
provenance.
\end{remark}

\begin{remark}[Relation to algebraicity of Weil classes]
On these Pryms the two-dimensional space of Weil Hodge classes is known to be
algebraic (Schoen; Patel--Zhang \cite{PZ26} for general abelian covers).
Theorem~\ref{main} is complementary content: it does not produce the Weil
classes, but locates the Abel--Prym cycle itself off the theta line ---
equivalently, it exhibits an explicit nonzero $\Theta$-primitive algebraic
class with an explicit cycle representative on every such Prym, including on
members where the Hodge ring is as small as the Weil-type structure allows.
For \emph{simple} members the statement has independent geometric force;
explicit simple examples in dimensions $6$ and $8$, certified by irreducible
Frobenius polynomials at split primes and exact purity, accompany this note
in the repository, together with the exact integral-model computations.
\end{remark}

\begin{thebibliography}{9}
\bibitem{Beauville82} A.~Beauville, \emph{Sous-vari\'et\'es sp\'eciales des
vari\'et\'es de Prym}, Compositio Math.\ \textbf{45} (1982), 357--383.
\bibitem{Welters87} G.~Welters, \emph{Curves of twice the minimal class on
principally polarized abelian varieties}, Indag.\ Math.\ \textbf{49} (1987),
87--109.
\bibitem{LO11} H.~Lange and A.~Ortega, \emph{Prym varieties of cyclic
coverings}, Geom.\ Dedicata \textbf{150} (2011), 391--403.
\bibitem{PZ26} D.~Patel and Y.~Zhang, \emph{Algebraicity of Hodge classes on
some generalized Prym varieties}, arXiv:2506.13729.
\bibitem{Companion} S.~Lavery, \emph{The loss ledger and the cycle
filtration: tower exhaustion on the helix carrier, and a program whose
terminus is the Hodge conjecture}, preprint draft v0.1, July 2026.
\end{thebibliography}

\end{document}
