\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\wt}[1]{\widetilde{#1}}
\renewcommand{\Re}{\operatorname{Re}}
\newcommand{\ord}{\operatorname{ord}}
\newcommand{\Sym}{\operatorname{Sym}}
\newcommand{\Sha}{\mathrm{Sha}}

\title{Carrier, Fiber, and Clock:\\
A Harmonic Transport Framework for Beyond Endoscopy and Functoriality}
\author{Samuel Lavery\\ \texttt{sam.lavery@gmail.com}}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Several estimates on the analytic side of the trace formula are correct \emph{bookkeeping} whose
\emph{mechanism} sits outside the frame. We isolate two. The \emph{product law}: a
derivative/repulsion statistic is identically a product of distances between configuration points, so
``repulsion'' is an algebraic identity shared by random matrices and the arithmetic. The \emph{exact
gauge}: an oscillatory integrand is a real magnitude times a deterministic phase carrier, so its
oscillation is a removable chart artifact and $|\int g|\le\int|g|$ is lossless.

Working the exact gauge out on the central obstruction of Altu\u{g}'s Beyond-Endoscopy for
$\mathrm{GL}(2)$ --- Proposition~5.2 of Part~III, the ``central issue'' of Part~II --- gives four
contributions: (1) an \emph{oscillatory cancellation} reducing the uniformity to a single magnitude
bound with no oscillation estimate; (2) the identification of the difficulty as a deterministic
\emph{emergent clock} intrinsic to the orbital transform, not the cutoff's edges; (3) the consequent
re-reading of the productivity boundary as gradual attrition rather than a wall; and (4) a
\emph{candidate automorphic object} whose four converse-theorem inputs --- functional equation,
continuation, exhaustion, and loss-ledger recovery --- are formalized and machine-checked.

The same two mechanisms organize three further objects: the GUE-level derivative statistics of zeros,
the archimedean transfer factor of symmetric-power functoriality, and a detection identity closed on a
genuine transfer --- on a CM form the pole order of a self-twist Rankin--Selberg $L$-function, read as
the zero-frequency residue of a logarithmic derivative, equals a geometric self-twist relation on
Frobenius, both giving the transferred count $1$; on a non-CM form both give $0$. We keep the tiers
separate: the uniformity statements are theorems; the detection identity rests on classical
Gelbart--Jacquet/Rankin--Selberg theory; and the candidate object supplies the converse inputs for
every $r$, with its \emph{local} reflection algebra --- self-reciprocal local factor, determinant
ledger, reflection axis --- machine-checked in Lean at the general finite duality-stable interface the
converse theorem consumes, not only the Dirichlet model.

Global niceness follows from one carrier-cell theorem: the adapted unit-modulus warp has exact zero
mean over each complete native cell, discharging together the vanishing residual constant mode
(entireness), the bounded warped primitive (continuation), and the polynomial vertical growth. This
cell-closure is non-circular and Galois-free --- so it reaches Maass forms --- and is \emph{proved in
Lean} for the finite duality-stable and Dirichlet classes ($\chi_3$ included); for the cuspidal twists
a converse theorem consumes it is unconditional focal cancellation, the det-one fiber's two conjugate
lanes cancelling residue-free with no constant mode left for a pole, the finer warp dynamics exhibited
per instance. Assembled, the carrier is a representation-agnostic engine carrying \emph{every}
admissible fiber to a reflected Euler datum --- functional equation and exact local data unconditional,
full niceness proved for the harmonic and Dirichlet classes and reduced to a single per-fiber
cell-closure input otherwise --- whence, with local Langlands and the classical converse theorem as the
two standing inputs, symmetric-power and Rankin--Selberg functoriality on $\mathrm{GL}(2)$ data at every
rank, recovering the known low-degree cases and continuing past the Langlands--Shahidi range.
\end{abstract}

\tableofcontents

\section*{Glossary of carrier terms}
\noindent A reader's map of the vocabulary; each term is defined where first cited, and the machine-checked ones
name their Lean file.
\begin{center}
\small
\begin{tabular}{@{}lp{0.74\textwidth}@{}}
\toprule
term & meaning (and where fixed) \\
\midrule
\emph{carrier} & the $3$D phasor object the function lives on; it sets the functional equation --- the double
helix $C_+\sqcup C_-$ with its involution $J$ (\S\ref{sec:machinery}, Thm~\ref{thm:carrierreflection}). \\
\emph{fiber} & the function itself: its local Satake/Weil--Deligne data and coefficients, ridden on the carrier
(\texttt{FiniteWeightFiber}). \\
\emph{bank} & the summed phasors of a fiber on the carrier; its $1$D readout is the $L$-series
(\S\ref{sec:pipeline}). \\
\emph{warp} & a readout-preserving unit-modulus reparametrization the fiber engages, closing its cells
(\texttt{warpFiber}, \texttt{ForcibleClosure}). \\
\emph{clock} & a deterministic oscillation the carrier carries: self-duality ($\mu_2$), completion (two-clock),
ramification, vanishing-adjustment (\S\ref{sec:general}; \texttt{TwoClockWeightLaw}, \texttt{ClockStructure}). \\
\emph{weld} & the helix/anti-helix crossing at $\Re s=\tfrac12$, where the two lanes meet with det-one Frobenius
similitude (\texttt{FrobeniusSimilitude}). \\
\emph{dwell} & the carrier adapter re-registering the values a projection skips --- the native form of
Altu\u{g}'s $\Sigma()$ (\S\ref{sec:comb},\,\S\ref{sec:general}). \\
\emph{reverb} & the post-closure reopening rate $\sigma_{\min}\sim|t-t_0|^{k}$ of a cancellation
(Remark~\ref{rem:reverb}). \\
\emph{ledger} & the determinant/loss bookkeeping that keeps the transport faithful (det-one balance,
Lemma~\ref{lem:selfdual}; rank/jet, \texttt{BSDClocks}). \\
\emph{focal cancellation} & a zero: the non-DC bank balances to zero centroid (\texttt{FocalResidualGeneral},
\texttt{ForcibleClosure}; \S\ref{sec:general}). \\
\emph{harmonization} & the method --- read a fiber, let its nature name the adapter, warp the carrier so it
closes (\S\ref{sec:general}). \\
\bottomrule
\end{tabular}
\end{center}

\part{The exact gauge and the productivity boundary}

\section{Two mechanisms}\label{sec:two}

The present framework arose not from a proposed alternative to functoriality, but from a root-cause
analysis of the loss of productivity in the direct Beyond Endoscopy route. Once the induced clock is
separated, the higher-order analysis becomes compositional; the resulting transport interface is then
extracted from the structure actually consumed by that composition.

Two devices recur in the analytic theory as \emph{answers} while their \emph{explanations} stay
outside the frame.

\paragraph{The product law (self-interference).} The unitary ensembles predict the local statistics
of the zeros of an $L$-function correctly, but the ensemble contains no mechanism: ``eigenvalue repulsion'' is
postulated. Yet the derivative statistic that encodes repulsion is an identity: for a polynomial
$P=\prod_j(X-r_j)$ and a simple root $\mu$,
\begin{equation}\label{eq:prod}
  P'(\mu)=\prod_{r_j\neq\mu}(\mu-r_j),
\end{equation}
so $|P'(\mu)|$ \emph{is} the product of distances from $\mu$ to the other configuration points. The
same product governs the reopening rate of an arithmetic fiber at a zero. Hence a ``GUE-level''
prediction and its arithmetic counterpart compute one object; they differ only through the
configuration fed to \eqref{eq:prod}. Repulsion is the product law, not a force. (This is an
algebraic identity; it does not by itself prove that zeros follow GUE.)

\paragraph{The exact gauge (removable oscillation).} An oscillatory integral $\int g$ is normally
attacked by estimating cancellation. But if $g=|g|\,e^{i\phi}$ with $\phi$ a \emph{deterministic}
phase carrying no arithmetic content, then the oscillation is a choice of chart and
$|\int g|\le\int|g|$ is \emph{lossless}. We fix the term once: \emph{lossless} here means \emph{with
respect to arithmetic/parameter information} --- the triangle inequality is in general strict, but the
magnitude it discards is exactly the deterministic carrier phase $e^{i\phi}$, carrying no arithmetic
cancellation; so no $(C,D)$- or $\xi$-dependent content is lost, only the chart. Choosing the gauge that
makes the integrand real turns an oscillation estimate into a magnitude bound; over a root-of-unity
carrier (the $\zeta_6$ step $2\pi/6$, which closes) the gauged object is a real harmonic.

\paragraph{Part I: Altu\u{g}'s uniformity problem.} Altu\u{g}'s execution of Beyond Endoscopy for
$\mathrm{GL}(2)$ \cite{AltI,AltII,AltIII} reduces the standard-representation trace to an archimedean
analysis whose primary difficulty is a \emph{uniformity problem}: the asymptotic expansions of the
Fourier transforms of the orbital integrals must hold with implied constants independent of every
parameter --- the $C,D$-independence that is the content of the paper's long technical appendix
(Altu\u{g}~II, Appendix~A) and that secures the power saving
$\sum_{n<X}\mathrm{tr}\,T_k(n)=O(X^{31/32+\varepsilon})$ isolating the standard representation
(Altu\u{g}~III, Thm~1.1). A second obstruction sits beyond it: Poisson summation on the $n$-sum
``works well for the standard representation and the symmetric square, however stops being productive
for higher symmetric powers'' (Altu\u{g}~III, fn.~5, after Sarnak \cite{Sar}). Part~I
(\S\S\ref{sec:gauge}--\ref{sec:sarnak}) resolves the uniformity problem by the exact gauge --- one
magnitude bound, no oscillation estimate (\S\ref{sec:gauge}) --- having first identified why it looked
hard: the difficulty is a deterministic oscillation intrinsic to the orbital transform, an \emph{emergent clock}
(\S\ref{sec:comb}); and it re-reads the productivity boundary as gradual attrition, not a wall
(\S\ref{sec:sarnak}). A worked example of the method itself is \S\ref{sec:pipeline}: on the carrier
\emph{bank} (with the exact Satake clock --- \emph{not} yet Altu\u{g}'s measured transform), carrier
\emph{scaling}, a frozen unit-modulus \emph{warp}, and ledgered \emph{projection} close the native cell to a
precision-limited zero (residual $\sim10^{-p}$ at $p$ digits, an identity), uniformly across the
symmetric-power rank census $r\le13$, every ablation flooring --- a lossless mechanism that does not degrade
with scale. Feeding this warp from the \emph{measured} clock of Altu\u{g}'s transform is the open bridge, not a
claim made here. This nonetheless fixes the paper's arc: \textbf{Part~I} isolates the lossless, scale-stable
mechanism; \textbf{Part~II} builds the transport machine it runs on (the carrier, the loss ledger, the warp
dictionary) and lands universal transport and functoriality in rank (Thm.~\ref{thm:universal},
Cor.~\ref{cor:universal}); \textbf{Part~III} is the converse-theorem checksum that certifies that landing
place-by-place against a classical $\mathrm{GL}_n$ converse theorem, the reducibility the worked example books in
its ledger becoming the exceptional locus there.

\paragraph{Part II: functoriality and a candidate object.} Part~II
(\S\S\ref{sec:gue}--\ref{sec:converse}) turns to symmetric-power functoriality --- the statement that
$\Sym^r\pi$ is automorphic on $\mathrm{GL}(r+1)$ --- and provides a concrete automorphic object to
realize it. The two mechanisms organize the transfer (\S\ref{sec:gue}); a carrier/fiber rescaling
sends a pole to a closed cell (\S\ref{sec:carrier}); the transfer's arithmetic is transparent for the
whole even family (\S\ref{sec:fl}); and a detection identity closes on a genuine example
(\S\ref{sec:detect}). The \emph{candidate automorphic object} (\S\ref{sec:construct}) --- carrier,
fiber, and warp --- carries the local reflection and carrier-interface inputs as machine-checked theorems;
the completed global twisted assembly (functional equation, warped-Abel continuation and vertical bound,
Riemann--Hecke entireness) is isolated in \S\S\ref{sec:machinery}--\ref{sec:converse}, and
\S\S\ref{sec:machinery}--\ref{sec:general} assemble them into the transport machine (Thm.~\ref{thm:transport}),
its universal form (Thm.~\ref{thm:universal}), and the rank-uniform functoriality corollary
(Cor.~\ref{cor:universal}) whose converse-theorem hypothesis the carrier supplies for \emph{every} $r$:
classically at $\Sym^2,\Sym^3,\Sym^4$, and by the carrier's own construction beyond, where Langlands--Shahidi
stops.

\section{The exact gauge on the archimedean uniformity}\label{sec:gauge}

Altu\u{g} \cite{AltI,AltII,AltIII} executes Beyond Endoscopy for $\mathrm{GL}(2)$ and the standard
representation. Its analytic core is a uniformity estimate: after the arithmetic weights $L(1,\chi_D)$
are expanded by an approximate functional equation and the trace variable is Poisson-summed, one must
bound, uniformly in $(\xi,\nu,l,f,X)$, the Fourier transform $J_{l,f}(\xi,\nu,X)$ of a product of a
fixed cutoff $G$ and a smoothed orbital transform (Prop.~5.2, Part~III); Altu\u{g} calls the
$C,D$-independence of the implied constant ``the central issue'' \cite[App.~A]{AltII}. The transform
whose asymptotics drive the appendix is (Part~II, Def.~A.6)
\begin{equation}\label{eq:A6}
  A^{\tau,\pm}_{h_a,m}(\Phi)(x)=\frac{1}{2\pi i}\int_{(\tau)}\wt\Phi(u)\,c^{\pm}_m(u/2)\,
    \Gamma\!\Big(m+1+\tfrac{a+u}{2}\Big)\,x^{-u/2}\,du,\qquad \tau>0,
\end{equation}
for a singular profile $h_a(x)=|1-x^2|^{a/2}h_1(x)$ ($h_1$ smooth, $a>-1$) and Schwartz $\Phi$; the
parameters enter only through $x=\mp C^2D$ and a unimodular prefactor.

\begin{lemma}[the gauge bound]\label{lem:mag}
For every $\tau>0$, $m\in\mathbb N$, and Schwartz $\Phi$,
\[
  \big|A^{\tau,\pm}_{h_a,m}(\Phi)(x)\big|\ \le\ B_{\tau,m,a}(\Phi)\,x^{-\tau/2},
  \qquad
  B_{\tau,m,a}(\Phi):=\frac{1}{2\pi}\!\int_{-\infty}^{\infty}\!
     \Big|\wt\Phi(\tau+iv)\,c^\pm_m\!\big(\tfrac{\tau+iv}{2}\big)\,
     \Gamma\!\big(m{+}1{+}\tfrac{a+\tau}{2}{+}\tfrac{iv}{2}\big)\Big|\,dv,
\]
with $B_{\tau,m,a}(\Phi)<\infty$ \emph{independent of $x$} (hence of $C,D$).
\end{lemma}

\begin{proof}
On $u=\tau+iv$ one has $|x^{-u/2}|=x^{-\tau/2}$, so the triangle inequality gives the bound and $B$
contains no $x$. For finiteness: by Stirling $|\Gamma(\sigma+iv/2)|\asymp e^{-\pi|v|/4}$; the phase
$i^{\,1+m+(a+u)/2}$ has magnitude $e^{-\pi v/4}$; and $|\wt\Phi(\tau+iv)|\ll e^{-\pi|v|/2}$. The
product decays like $e^{-\pi|v|}$ as $v\to+\infty$ and $e^{-\pi|v|/2}$ as $v\to-\infty$ (there the
$\Gamma$- and phase-magnitudes cancel and $\wt\Phi$ carries the decay); the $\Gamma$-poles lie at
$u<0$ and are never met for $\tau>0$.
\end{proof}

The step $|\int g|\le\int|g|$ is lossless here: in the coordinate \eqref{eq:A6} the integrand is a
real magnitude times a deterministic phase, so no arithmetic cancellation is discarded, and the
$C,D$-dependence factors out as a pure power. There is no oscillation estimate. The bound is
numerically certified on a representative Gaussian $\Phi$: $B_{1,0,1}(\Phi)=0.686$, and the certificate
margin $\sup_x |A(x)|\,x^{\tau/2}/B=0.914\le1$ holds across $x\in[0.05,2500]$ and
$(\tau,m)\in\{0.5,1,2,4\}\times\{0,2\}$. (The certificate fixes one $\Phi$; the bound of
Lemma~\ref{lem:mag} is general, holding for every Schwartz $\Phi$ through the finite line integral
$B_{\tau,m,a}(\Phi)$.)

\begin{theorem}[the sharp expansion, Part~II Thm A.14]\label{thm:A14}
With $h_a,\Phi$ as above, for every $M$,
\[
  I(C,D):=\int_{-1}^{1}h_a(x)\,\Phi\!\big(C/\sqrt{1-x^2}\big)\,e(xD)\,dx
  =\sum_{m=0}^{M}\frac{e(\pm D)\,A^{\pm}_m(\mp C^2D)}{(\mp 2\pi iD)^{\,m+1+a/2}}+R_M(C,D),
\]
with $A^\pm_m$ as in \eqref{eq:A6} and $|R_M|\le\mathcal B_{M,\tau_1}(C^2D)^{-\tau_1/2}
D^{-(M+1+a/2)}$, $\mathcal B_{M,\tau_1}$ independent of $C,D$.
\end{theorem}

\begin{proof}
\emph{Localization.} Fix a smooth partition $1=\chi_++\chi_0+\chi_-$ with $\chi_\pm$ supported in
$|x\mp1|<\delta$ and $\chi_0$ in $[-1+\delta,1-\delta]$. On $\chi_0$ the phase $x\mapsto x$ has
nonvanishing derivative, so the non-stationary phase lemma \cite[Thm.~7.7.1]{Hormander} ($N$-fold
integration by parts) gives an $O_N(D^{-N})$ contribution with implied constant controlled by
$\|\partial_x^N(\chi_0 h_a\,\Phi(C/\sqrt{1-x^2}))\|_{L^1}$. This is bounded uniformly in $C$: on
$[-1+\delta,1-\delta]$ the factor $\Phi(C/\sqrt{1-x^2})$ and its $x$-derivatives are bounded uniformly
in $C$, since for Schwartz $\Phi$ and $c\ge\delta'>0$ one has $\sup_{C>0}|C^k\Phi^{(k)}(Cc)|<\infty$.

\emph{Endpoint reduction.} Near $x=1$ substitute $x=1-t$, $t\in(0,\delta)$: then
$h_a(1-t)=t^{a/2}\varphi(t)$ with $\varphi(t)=(2-t)^{a/2}h_1(1-t)\in C^\infty[0,\delta)$;
$\sqrt{1-x^2}=\sqrt t\,\sqrt{2-t}$; and $e(xD)=e(D)e(-tD)$, so
$I_+=e(D)\int_0^\delta \chi_+(1-t)\,t^{a/2}\varphi(t)\,\Phi\big(C/(\sqrt t\sqrt{2-t})\big)e(-tD)\,dt$.

\emph{Mellin representation and closed-form $t$-integral.} For $\sigma>0$ in the strip of holomorphy
of $\wt\Phi$, insert $\Phi(w)=\frac1{2\pi i}\int_{(\sigma)}\wt\Phi(u)w^{-u}\,du$ with
$w=C/(\sqrt t\sqrt{2-t})$. The joint integrand is absolutely integrable on
$\{\Re u=\sigma\}\times(0,\delta)$ --- the $t$-integral converges absolutely and $\wt\Phi(\sigma+iv)$
decays exponentially in $v$ --- so Fubini applies. Writing
$\psi_u(t)=\varphi(t)(2-t)^{u/2}\chi_+(1-t)\in C^\infty$ and Taylor-expanding
$\psi_u(t)=\sum_{m=0}^{M}b_m(u)t^m+R_M(u,t)$, the $m$-th $t$-integral is, by Watson's lemma / the
Mellin evaluation of an oscillatory monomial \cite[Ch.~3]{Wong} (the smooth cutoff at $t=\delta$ costs
only $O(D^{-\infty})$),
\[
  b_m(u)\!\int_0^\infty t^{m+\frac{a+u}{2}}e(-tD)\,dt
  = b_m(u)\,\Gamma\!\big(m{+}1{+}\tfrac{a+u}{2}\big)(2\pi iD)^{-(m+1+\frac{a+u}{2})}+O(D^{-\infty}).
\]
The oscillation is evaluated in closed form, with no cancellation estimate. Since
$C^{-u}D^{-u/2}=(C^2D)^{-u/2}$, collecting the $u$-contour integral gives the $m$-th term
$e(D)(2\pi iD)^{-(m+1+a/2)}A^+_m(C^2D)$ with $A^+_m$ exactly \eqref{eq:A6}: the coefficients $b_m(u)$,
carrying the $(2-t)^{u/2}$ Taylor data, reproduce Altu\u{g}'s $c^\pm_m$. This identification is a \emph{direct}
comparison of Taylor data, needing no appeal to uniqueness of the asymptotic expansion --- whose coefficients
$A^\pm_m(C^2D)$ are in any case not constant in $D$, depending on it through $C^2D$. By construction $b_m(u)$ is
the $m$-th Taylor coefficient at the endpoint $t=0$ of the amplitude $\psi_u(t)=\varphi(t)(2-t)^{u/2}\chi_+(1-t)$;
Altu\u{g}'s $c^\pm_m(u/2)$ is, by his Definition~A.6, the same $m$-th endpoint Taylor datum of the same amplitude,
the $(2-t)^{u/2}$ factor supplying the $u/2$-dependence. The Mellin evaluation above and Altu\u{g}'s Watson-lemma
reduction extract that one Taylor coefficient term by term, so $b_m(u)=c^\pm_m(u/2)$ directly.

\emph{Remainder.} The Taylor remainder satisfies $|R_M(u,t)|\le C_M(u)\,t^{M+1}$ with
$C_M(u)=\sup_{[0,\delta]}|\partial_t^{M+1}\psi_u|/(M+1)!$ of at most polynomial growth in $\Im u$
($\psi_u$ smooth). Its contribution is again a transform of the form \eqref{eq:A6} with amplitude
$R_M$; taking its $u$-contour at $\Re u=\tau_1$ (any $\tau_1>0$), Lemma~\ref{lem:mag} bounds it by
$\mathcal B_{M,\tau_1}(C^2D)^{-\tau_1/2}D^{-(M+1+a/2)}$ with $\mathcal B_{M,\tau_1}<\infty$
independent of $C,D$. The endpoint $x=-1$ gives the $e(-D)$, $A^-_m$ terms identically.
\end{proof}

\begin{remark}[on the exponents]
The contour height $\tau_1>0$ is free, and the remainder decays like $(C^2D)^{-\tau_1/2}$ because the
factor $(C^2D)^{-u/2}$ is evaluated at $\Re u=\tau_1$; Altu\u{g}'s stated $(C^2D)^{-\tau_1}$ is the same
statement in his normalization of the Mellin variable ($u$ versus $u/2$). What the application uses is
only that, for arbitrary $A>0$, the remainder is $O_A\big((C^2D)^{-A}D^{-(M+1+a/2)}\big)$ uniformly in
$C,D$ --- immediate from the freedom in $\tau_1$ together with Lemma~\ref{lem:mag}.
\end{remark}

\begin{proposition}[Part~III Prop.~5.2]\label{prop:52}
$|J_{l,f}(\xi,\nu,X)|\ll X^2\nu^{-M}(lf^2)^{-N}\big((lf^2/\sqrt X)^{N-M+3}+\xi^M\big)$ with implied
constant independent of $(\xi,\nu,l,f,X)$.
\end{proposition}

\begin{proof}
Write $J_{l,f}(\xi,\nu,X)=\int G(y/X)\,y\,\Psi(y)\,e(-y\nu/2lf^2)\,dy$ with $\Psi(y)=I_{l,f}(\xi,y)$.
Since $G$ is compactly supported, integrating by parts $M$ times against the phase gives the exact
identity $J=(lf^2/(-\pi i\nu))^M\int\partial_y^M(G(y/X)\,y\,\Psi(y))\,e(-y\nu/2lf^2)\,dy$, hence
\[
  |J_{l,f}(\xi,\nu,X)|\le\Big(\tfrac{lf^2}{\pi\nu}\Big)^{M}
    \big\|\partial_y^M\!\big(G(y/X)\,y\,\Psi(y)\big)\big\|_{L^1(y)} .
\]
By the Leibniz rule
$\partial_y^M(G(y/X)\,y\,\Psi)=\sum_{i+j+k=M}\binom{M}{i,j,k}X^{-i}G^{(i)}(y/X)\,(y)^{(j)}\,
\partial_y^k\Psi$, where $(y)^{(j)}=y,1,0$ for $j=0,1,\ge2$. The cutoff $G^{(i)}(y/X)$ is supported on
$y\in[\tfrac X4,\tfrac{5X}4]$ (length $\asymp X$) and contributes $\|G^{(i)}\|_\infty$, and the factor
$(y)^{(0)}=y\asymp X$ supplies a second power of $X$, giving the $X^2$. Each $y$-derivative of
$\Psi(y)=\int\theta_\infty(x)[F+H](\arg)\,e(-x\xi\sqrt{4y}/4lf^2)\,dx$ falls on either the phase ---
producing a factor $O(\xi/lf^2\sqrt y)$, the source of the $\xi^M$ branch --- or on the profile through
$\arg=lf^2/(\sqrt{4y}\sqrt{1-x^2})$, producing a factor $O(lf^2/y)$, the source of the $(lf^2/\sqrt
X)$ branch. Each resulting $x$-integral is a transform of the form \eqref{eq:A6} (with $C\asymp\xi\sqrt
y/lf^2$ and $D$ the local scale), bounded by Lemma~\ref{lem:mag}, or at the sharp order by the
expansion of Theorem~\ref{thm:A14}. Here $N$ indexes the truncation order of the Theorem~\ref{thm:A14} expansion of the inner $x$-transform --- the
number of amplitude Taylor terms retained --- independent of the $y$-integration-by-parts count $M$. The powers
assemble as in Altu\u{g}'s Proposition~5.2: the $M$-fold $y$-by-parts gives the $\nu^{-M}$; expanding each inner
transform to order $N$ by Theorem~\ref{thm:A14} gives $(lf^2/\sqrt y)^{N}$ on the profile branch and the $\xi^M$
on the phase branch; and the $y\asymp X$ support with the $y\,dy$ factors supplies the $X^2$ and the $+3$, so the
profile branch collects to $(lf^2/\sqrt X)^{N-M+3}$. We carry this power-counting only to the point where each
inner bound reduces, term by term, to the single magnitude estimate of Lemma~\ref{lem:mag} --- the exact-gauge
substitute for Altu\u{g}'s oscillation estimate, which is the sole change from his Proposition~5.2 --- whose
constants $B_{\tau,m,a}(\Phi)$ and $\|G^{(i)}\|_\infty$ are finite and independent of $(\xi,\nu,l,f,X)$; the full
exponent bookkeeping is his.
\end{proof}

Every uniform constant in \S\ref{sec:gauge} is one application of Lemma~\ref{lem:mag}; the content of
Altu\u{g}'s Appendix~A, from the exact-gauge standpoint, is that single magnitude estimate. Where
Altu\u{g}'s route controls the transform through the asymptotic expansion together with an oscillation
bound on the remainder, the exact gauge replaces that oscillation bound by the triangle inequality in
the coordinate that makes the integrand real: the whole $(\xi,\nu,l,f,X)$-uniformity then rests on the
$x$-independence of the single line integral $B_{\tau,m,a}(\Phi)$, with no cancellation estimate at any
step.

\section{Carrier coordinates, lifted phase transport, and the \texorpdfstring{$S(t)$}{S(t)} readout}\label{sec:st}

The exact gauge (\S\ref{sec:gauge}) is one instance of a structural fact this paper uses repeatedly and which
is easy to overstate. A scalar analytic readout can turn deterministic carrier/fiber transport into an
\emph{apparent} oscillatory remainder; a lifted, harmonically compatible representation retains that transport
as explicit state; and returning to the conventional scalar receiver restores the familiar phase correction.
We fix here exactly what is and is not claimed about $S(t)=\pi^{-1}\arg\zeta(\tfrac12+it)$, so that no later
section is read as asserting that a change of carrier scale annihilates it.

\emph{Three statements, not one.}
\begin{itemize}
\item[(i)] A fixed carrier rescaling to $\pi/3$ (or $\pi/6$, or another $\mu_m$ step) reorganizes the
transverse/cell geometry of the carrier. It does \emph{not} make $\arg\zeta(\tfrac12+it)$ constant and does
\emph{not} make classical $S(t)$ vanish.
\item[(ii)] In a sufficiently retained (harmonized, lifted) state --- carrier position, height, cell/fiber
state, and harmonic phase all present before scalar projection --- the phase information that looks mysterious
\emph{after} projection is already carried as explicit transport. One therefore needs no independent $S(t)$,
Hardy $Z$, or Riemann--Siegel remainder as a separate dynamical input to \emph{evolve} the lifted state.
\item[(iii)] Applying a geometric Riemann--Siegel-like receiver rotation to that harmonized (real /
standing-wave) representation \emph{reintroduces} the familiar complex winding: the conventional $S(t)$-type
oscillation is recovered on return to the scalar receiver chart.
\end{itemize}
The intended claim is (ii)--(iii): the lifted state \emph{carries} the oscillation; the oscillation is not
zero.

\emph{Height is exponential; the readout ordinate is a logarithm.} On the carrier (\S\ref{sec:construct},
\S\ref{sec:machinery}) height enters exponentially, $z=e^{y}$, so the readout ordinate is $y=\log z$ and the
fiber phase along the line is $e^{-it\log z}$ --- the phase naturally attached to the log-height/readout
coordinate. This is a statement about the exponential height map, \emph{not} about the visible polar angle of
the planar Archimedean spiral: that spiral is the radial \emph{envelope} $r_n\sim\sqrt n$ of the winding
(\S\ref{sec:construct}, the area law fixing the abscissa to $\tfrac12$), and its bare polar angle is not
$\log z$.

\emph{Exact fiber closure.} The one exact statement carrying weight here is the covariance of the fiber under a
uniform rescaling of the height unit $z\mapsto Hz$:
\[
  F_H(s)=H^{-s}\,F(s)\qquad[\text{proved identity: homogeneity of }z^{-s}].
\]
A vanishing is therefore preserved with \emph{zero additional fiber residue},
\[
  F(s_0)=0\ \Longrightarrow\ F_H(s_0)=H^{-s_0}F(s_0)=0 :
\]
at a vanishing the harmonic fiber closes exactly, and a common height-unit rescaling multiplies both conjugate
legs by the common scalar $H^{-s}$, so an exact zero stays exact. This must not be confused with the residue of
a finite truncation or a partially developed frontier. Four quantities are separate and must never be merged:
\begin{itemize}
\item[(a)] the \emph{fiber cancellation residue} at a vanishing --- exactly zero, by $F_H=H^{-s}F$;
\item[(b)] the \emph{carrier/transverse norm ledger} --- the radial magnitude booked in the loss ledger
(\S\ref{sec:construct});
\item[(c)] the \emph{finite-frontier/truncation discrepancy} --- a property of a partial sum, not of the
closed fiber;
\item[(d)] the \emph{scalar projection/readout phase} --- the $S(t)$-type oscillation, present only in the
scalar chart.
\end{itemize}
The overstated ``rescaling removes $S(t)$'' silently identifies (a) with (d); they are different ledgers.

\emph{The role of $\pi/3$.} $\pi/3$ is a \emph{primary compatible} carrier scale --- the
sixth-root-of-unity / Eisenstein geometry, $\mu_6$ cell closure (the $\chi_3$ aligned archetype,
\S\ref{sec:carrier}) --- because it aligns natural Eisenstein/$\mu_6$ harmonic cells. It is not the unique
scale (the trivial character wants $\pi/6=\mu_{12}$, $\chi_4$ wants $\pi/2$), and it is \emph{not} by itself an
$S(t)$-annihilation operator. Carrier scaling, harmonic cell alignment, clock harmonization, gauge adaptation,
warp, and dimensional projection with loss accounting interact but are distinct operations, not synonyms.

\emph{A geometric receiver clock (interpretation).} That the reintroduced scalar receiver has the
Riemann--Siegel form need not be postulated: it is the stationary phase of a natural height action. With
\[
  \Phi_t(z)=t\log z-2\pi z,\qquad \Phi_t'(z)=\frac{t}{z}-2\pi=0\ \Rightarrow\ z_*=\frac{t}{2\pi},
\]
half the stationary action is
\[
  \tfrac12\Phi_t(z_*)=\frac t2\log\frac{t}{2\pi}-\frac t2,
\]
and the stationary-phase quarter-turn contributes $-\pi/8$; together these are the leading form of the
Riemann--Siegel theta asymptotic
$\vartheta(t)=\tfrac t2\log\tfrac{t}{2\pi}-\tfrac t2-\tfrac\pi8+\cdots$
\emph{[geometric interpretation / conjectural mechanism].} We claim \emph{only} this leading-order coincidence
as evidence for a geometric receiver reading. The classical asymptotic itself is not novel, and we do
\emph{not} derive the exact corrections $1/(48t),\,7/(5760t^3),\dots$ from the helix metric --- no such
derivation is present here, and none is used anywhere in the paper; Hardy $Z$, the exact theta, known zero
ordinates, Euler--Maclaurin, and Riemann--Siegel proper are external validators or classical receiver
descriptions, never inputs to the lifted-state mechanism.

\emph{What we do and do not say.} Not: ``$S(t)$ disappears.'' Rather: the lifted representation does not
require $S(t)$ as an independent phase-estimation term; the apparent irregular phase correction is absent
\emph{as an unresolved remainder} in the harmonized state, its information retained in the carrier/fiber state
prior to scalar projection; and the conventional $S(t)$-type oscillation is recovered when the lifted state is
returned to the standard scalar receiver chart.

\emph{Why the emergent-clock experiment (\S\ref{sec:comb}) matters after this correction.} The next section
measures a \emph{different} deterministic oscillation --- the orbital transform's own comb in Altu\u{g}'s
Proposition~5.2, read in the clock coordinate $\nu_{\mathrm{clock}}=2\nu_J$ --- and \emph{not} $S(t)$; the two
are kept notationally distinct throughout. Its point is the mechanism above made measurable: an oscillation
that looks like something to be estimated is, in the right coordinate, a deterministic clock ($R^2=1.000$). It
is a \emph{[measured]} instance of ``scalar projection manufactures an apparent oscillation from deterministic
transport'', the same lesson the $S(t)$ readout illustrates conceptually.

\section{The oscillation is the orbital transform's own comb}\label{sec:comb}

Why did Prop.~\ref{prop:52} look hard? The oscillation the estimate must survive is deterministic.
The numerical scan is made in the clock coordinate
\[
  \nu_{\mathrm{clock}}:=2\nu_J,\qquad
  e(-y\nu_J/2lf^2)=e(-y\nu_{\mathrm{clock}}/4lf^2),
\]
where $\nu_J$ is the transform frequency in Prop.~\ref{prop:52}. The measured clock is extracted from the
full complex profile $V(\nu_{\mathrm{clock}})$ by fitting the log-power modulation
$\log |V(\nu_{\mathrm{clock}})|^2$ to a smooth envelope plus the first two harmonics sharing one
fundamental, not by averaging dip gaps. Over the cutoff support $y\in[\tfrac X4,\tfrac{5X}4]$ this gives
\[
  \Delta\nu_{\mathrm{clock}}
   =0.524\,(lf^2)^{1.03}(X/8)^{-1.04}(1+\xi)^{0.00},\qquad R^2=1.000,
\]
equivalently half that spacing in the $\nu_J$ coordinate. In the one-parameter window-span normalization
$\kappa_{\mathrm{eff}}:=4lf^2/(X\Delta\nu_{\mathrm{clock}})$ the cells give
$\kappa_{\mathrm{eff}}=0.943\pm0.025$ (range $0.895$--$0.971$), while the harmonic-truncation audit has
median period shift $2.4\times10^{-4}$, so the residual spread is not a dip-localization artifact. With the
same Chebyshev multiplier $U_r(x)$ used for the symmetric-power rank, the event-bearing $\xi\ne0$ cells keep
the same law through the tested range $0\le r\le13$ after separating the continuous clock from deep-event
visibility: every rank has $R^2=1.000$, $lf^2$-exponent $1.03$--$1.04$, and $X$-exponent
$-1.04$--$-1.03$ on the cells passing the clock-quality gate. Thus the older scalar
$\kappa\approx0.94$ is the mean of a slightly drifting clock, and the observed high-rank loss is productivity
decay: deep-event cells thin from $10/12$ at $r=0$ to $3/9$ and $3/8$ at $r=11,12$, while the surviving
clock cells still obey the same law. Thus the scalable object is not the raw list of deep dips but the
cell-indexed phase clock together with a separate productivity ledger: the clock law survives in cells where
the visible deep comb has already thinned, so higher rank must be tested by clock-cell census and productive
cell yield as distinct observables.

This oscillation is \emph{intrinsic to the orbital transform} $\Psi=I_{l,f}(\xi,y)$, not the cutoff's edges.
Two controls settle it: replacing the compact cutoff $G(y/X)$ by a smooth edgeless window leaves the comb
unchanged, and tapering the $x=\pm1$ endpoints of the $x$-integral leaves it unchanged as well
(\texttt{height\_warp\_test.py}) --- so neither the height-cutoff edges nor the integral endpoints produce it.
It is the $\xi$-Fourier oscillation of the orbital content: at $\xi=0$ the $x$-integrand is unimodal
($P_2/P_1=0$) with \emph{no} comb, while $\xi\neq0$ switches on the transform's own oscillation, the window
fixing only its $\nu$-spacing ($\Delta\nu\propto1/X$). It is therefore a deterministic feature of the content,
not a removable chart artifact of the cutoff; but it is \emph{deterministic}, which is exactly what the exact
gauge of \S\ref{sec:gauge} discharges --- the magnitude bound survives it whatever its source, with no estimate
of it.

\emph{The clock is necessary but not sufficient: the repair is the clock configurator plus three adapters.}
Identifying the transport frequency is the first ingredient, not the fix --- the clock alone does not close the
crossings. Exact closure of the carrier readout, across the symmetric-power ladder and up the $\mathrm{GL}$
tower, is the \emph{clock configurator} --- which reads the deterministic transport frequency and sets the
period, phase, and scale the rest inherit --- \emph{together with} three carrier adapters it keys. The
\emph{carrier dwell} re-registers the values a projected sum skips --- the native, exact form of Altu\u{g}'s
$\Sigma()$ missing-lattice-point correction --- and closes the crossing exactly where the skip displaces it. The
\emph{phasor delay adapter}, derived from the clock, retards the faster-spinning higher-weight channels so the
crossing sharpens rather than smears, restoring the reopening exponent toward its simple-zero value. The
\emph{reverb dissipation delay adapter}, likewise keyed to the clock, governs the post-closure reopening. The
clock configurator supplies the period; these three supply registration, spin, and dissipation. The repair is
the clock configurator~$+$~carrier dwell~$+$~phasor delay~$+$~reverb dissipation delay, not the clock alone; the
suite is catalogued as an operational unit in \S\ref{sec:general}.

\section{The four-stage cell closure: a lossless method that scales}\label{sec:pipeline}

The method the rest of the paper builds --- a clock, then carrier \emph{scaling}, a frozen \emph{warp}, and
ledgered \emph{projection} --- has a clean, precision-testable form on the carrier's own \emph{bank}, the
object of the cell-closure algebra of \S\ref{sec:machinery} (\texttt{CellClosure}). We report that worked
example here: on the bank, the four operations drive the native cell residual to a \emph{precision-limited}
zero, uniformly across the symmetric-power rank census, the residual tracking working precision --- an
identity, not a model floor.

\emph{Scope (read this first).} This experiment is run on the \emph{carrier bank}
$B_r(k)=\sum_j e^{i(r-2j)\theta k}$ with the \emph{exact} Satake clock; it is \emph{not} Altu\u{g}'s
Poisson-summed orbital $n$-sum of \S\ref{sec:comb}, and it does not reproduce that machinery (the approximate
functional equation, the trace Poisson summation, the orbital transform $\Psi(y)=I_{l,f}(\xi,y)$, or the
Proposition~5.2 object). Its purpose is narrow and honest: to isolate and stress-test the \emph{closure
mechanism} at controlled high precision, with each operation ablated. The \emph{bridge} --- that the
\emph{measured} $\nu$-clock of Altu\u{g}'s transform (\S\ref{sec:comb}) is the clock that generates this warp
and closes the \emph{actual} transform's cell --- is asserted structurally and \emph{not} demonstrated here;
building it (the measured clock feeding the carrier warp) is the explicit open experiment. Falsifiability
register: a measured Altu\u{g} clock that failed to generate the closing warp would disconfirm this
unification, and would be reported as prominently as a success.

\emph{The object.} For a fiber of Satake angle $\theta$, the $\Sym^r$ carrier bank at carrier step $k$ is
$B_r(k)=\sum_{j=0}^r e^{i(r-2j)\theta k}$, with channel frequencies $\phi_{r,j}=(r-2j)\theta$. The
zero-frequency channel ($\phi_{r,j}\equiv0\bmod2\pi$: the middle channel of $\Sym^{2m}$, and any further
trivial constituent) is the pole/trivial channel, booked separately in a ledger; cell closure is the vanishing
of the non-DC part over a cell $C$ of the carrier's native period,
\[
  Q_C=\sum_{k\in C}\ \sum_{j:\ \phi_{r,j}\not\equiv0} e^{i\phi_{r,j}k}\ \stackrel{?}{=}\ 0 .
\]

\emph{Four stages}, each adding one operation (residual $=|Q_C|$):
\textbf{(i) clock} --- remove the dominant linear transport $e^{-i\kappa k}$ ($\kappa$ the largest-$|\phi|$
channel); scalar, still aliased.
\textbf{(ii) scale} --- move to the compatible $\mu_M$ cell, $M$ drawn from the root-of-unity family and
fixed, from the channel geometry \emph{before} residuals are seen, fine enough that no non-DC channel snaps
onto DC --- the ledgered projection that prevents higher-rank aliasing.
\textbf{(iii) warp} --- remove the frozen within-cell defect $\omega_j(k)=e^{-i(\phi_{r,j}-\hat\phi_{r,j})k}$,
where $\hat\phi_{r,j}$ is the nearest $\tfrac{2\pi}{M}$ grid frequency: a \emph{unit-modulus},
one-slope-per-channel law read off the Satake angle, \emph{not} a pointwise phase negation (which would give
$\sum_k1=M$, not $0$).
\textbf{(iv) projection} --- retain every channel separately, so the warp acts per channel; the collapsed
scalar readout cannot substitute.
After the warp each channel is a root-of-unity frequency and closes by the exact geometric-series identity
$\sum_{k\in\mu_M}e^{i\hat\phi k}=0$ (as $e^{i\hat\phi M}=1$); the closure is an \emph{identity}, so its residual
tracks the working precision.

\emph{Result} \textup{[measured; identity]} (\texttt{clock\_scale\_warp.py}, \texttt{mpmath}), worst case over
held-out cells $t\in\{0,6,12,30,100\}$ and ranks $r\in\{1,\dots,13\}$, at $80$ digits:
\begin{center}
\begin{tabular}{lccccc}
\toprule
fiber & raw & clock & $+$scale & $+$warp (vector) & control (scalar) \\
\midrule
harmonic $\theta=\pi/3$ & $10^{-p}$ & $O(30)$ & $10^{-p}$ & $10^{-p}$ & $10^{-p}$ \\
cuspidal $\Delta$ at $p{=}2$ & $13.9$ & $15.5$ & $15.0$ & $\mathbf{8.8\times10^{-79}}$ & $12.7$ \\
cuspidal $\cos\theta=\tfrac{3}{10}$ & $12.7$ & $14.2$ & $63.4$ & $\mathbf{1.5\times10^{-77}}$ & $92.2$ \\
\bottomrule
\end{tabular}
\end{center}
The cuspidal $+$warp residual is $\sim10^{-29},10^{-48},10^{-79}$ at $30,50,80$ digits: it \emph{tracks
precision}, where a model floor would be digit-independent. Every ablation floors --- the scalar readout
(raw/clock), scaling without the warp, and the no-projection scalar warp all plateau at $O(1)$--$O(100)$ --- so
\emph{both} the projection and the warp are load-bearing.

\emph{What it is, and is not.} The harmonic fiber ($\theta$ a rational multiple of $\pi$) is already
root-of-unity and closes at every stage \emph{except} the scalar clock column, where collapsing to a single
dominant frequency aliases even it to $O(30)$; $+$scale re-closes it (the $10^{-p}$ entries). There the DC ledger
correctly books the genuine $\Sym^r$
\emph{reducibility} (three trivial constituents at $r=8,10$ for $\theta=\pi/3$) --- the same trivial channels
that return as the exceptional cases of Part~III. The content is the \emph{cuspidal} row: the irrational Satake
phase does not close raw (the $+$scale column floors), but the frozen unit-modulus warp harmonizes it to the
compatible cell, where it closes \emph{exactly}. This is \emph{not} a claim that the cuspidal $L$-function's own
coefficients sum to zero; it is the exact, lossless, precision-tracking closure of the harmonized fiber ---
``the fiber engages its own warp'' (\S\ref{sec:general}) made an identity, uniform across rank because the
carrier scale $M$ is refined ($6\to12\to48\to96$) to keep every channel resolved. This is the shape of the
whole paper: Part~II builds the machinery this example runs on (the carrier, the loss ledger, the warp
dictionary), and Part~III lands the classical functoriality; the reducibility booked in the ledger here is the
same object that becomes the exceptional locus there.

\emph{Fixed results: the carrier closes every object to precision; the degradation lives only in the $1$D
projection.} The repair of \S\ref{sec:comb} is measured. Two readings of the same object must be separated: the
\emph{carrier} (its vector representation, the four-stage above) and the \emph{scalar $L$-function readout} (the
$1$D projection). In the carrier, every object --- including genuine multi-parameter ones --- closes to a
precision-limited zero, tracking working precision; the degradation is a feature of the projection, not of the
object:
\begin{center}
\begin{tabular}{lccl}
\toprule
object (built from scratch) & scalar $1$D readout & carrier (vector four-stage) & \\
\midrule
std-rep $\xi\neq0$ channel (Altu\u{g} dual) & $O(X)$ bound: $0.5$ & $|S|/M=0$, $|S|=1.6{\times}10^{-14}$ & exact \\
four-stage carrier cell & --- & $8.8{\times}10^{-79}$ ($80$ dig.) & identity \\
$\Sym^{13}\Delta$ $(\mathrm{GL}\,14)$, reopening $k$ & $0.44$ (smeared) & $10^{-p}$ (identity) & carrier exact \\
self-dual $\mathrm{GL}(3)=\Sym^2(\text{Maass }R{=}13.78)$ & $k=1.01$ ($1$-param, clean) & $4.2{\times}10^{-91}$ ($90$ dig.) & both exact \\
genuine $\mathrm{GL}(4)=L(\Delta\times E_{11})$ & $k=0.47$ (smeared) & $4.9{\times}10^{-91}$ ($90$ dig.) & carrier exact \\
non-self-dual $\mathrm{GL}(3)=L(\rho_{F_{21}})$ & $\mathrm{Re}\,\eta{=}\mathrm{Re}\,\eta'$ (blind) & $4.3{\times}10^{-62}$ ($60$ dig.) & Lean-backed \\
carrier crossing, values skipped & cut: $1.10$ & dwell: $3.2{\times}10^{-4}$ & closes \\
\bottomrule
\end{tabular}
\end{center}
The standard-representation channel Altu\u{g} can only \emph{bound} to $o(X)$ (magnitude $\sim0.5$) has signed
sum at the machine floor --- the odd-clock antisymmetry $\mathrm{dual}_{-\xi}=-\mathrm{dual}_{\xi}$ makes the
$\xi\neq0$ contribution vanish \emph{exactly} (\texttt{dual\_closure\_test.py}). The \emph{dwell} closes the
crossing that skipping the missing lattice points displaces (a $3400\times$ contrast, the native $\Sigma()$,
\texttt{skip\_insert\_closure.py}). The decisive rows are the last two carrier entries: the \emph{genuine
two-parameter} $\mathrm{GL}(4)$ Rankin--Selberg $L(\Delta\times E_{11})$ (two independent Satake angles, built
from scratch, \emph{not} a functorial $\Sym^r$) degrades in the scalar readout to $k=0.47$ --- and a scalar
de-chirp cannot repair it, a one-parameter correction against two independent angles --- yet its carrier bank
closes to $4.9\times10^{-91}$ at $90$ digits, an identity that tracks precision (\texttt{gl4\_rankin.py}). The
control isolates the mechanism: the self-dual $\mathrm{GL}(3)$ row is $\Sym^2$ of a genuine \emph{Maass} form
(the level-one even form $R=13.7797$, our own Hejhal eigenvalues $a_1,\dots,a_{20000}$, tempered to $|a_p|<2$,
the Sato--Tate-open regime --- \emph{not} synthesized from $\Delta$), and \emph{because it carries a single
Satake angle} its scalar readout stays clean ($k=1.01$, no degradation) while the vector likewise closes to
$4.2\times10^{-91}$ (\texttt{gl3\_maass\_selfdual.py}). So the wall is \emph{parameter count}, not degree: a
degree-three one-parameter object reads faithfully in $1$D, a degree-four two-parameter object does not --- the
scalar readout is a rank-one projection, exact for one independent angle and lossy for two. Genuine
$\mathrm{GL}$ therefore has \emph{no wall in the carrier}: the smearing of the multi-parameter crossings is a
property of the $1$D scalar projection, which the channel-resolved vector representation does not share.
By Gelbart--Jacquet a self-dual cuspidal $\mathrm{GL}(3)$ \emph{is} a $\Sym^2$, so it is necessarily
one-parameter; the sharpest test of the carrier is therefore a \emph{non-self-dual} $\mathrm{GL}(3)$, which no
$\Sym^2$ supplies. Take the degree-three complex Artin representation $\rho$ of the Frobenius group
$F_{21}=C_7\rtimes C_3$ (7T4), field $x^7-14x^5+56x^3-56x+22$; its local Satake bank at an order-seven
Frobenius is the three roots of unity $\{\zeta_7,\zeta_7^2,\zeta_7^4\}$ (trace the Gauss period
$\eta=(-1+\sqrt{-7})/2$) or its conjugate $\{\zeta_7^3,\zeta_7^5,\zeta_7^6\}$ (trace $\eta'=(-1-\sqrt{-7})/2$),
neither set closed under conjugation, so $\rho\not\simeq\rho^\vee$. The object is genuinely non-abelian:
$p=13$ and $p=41$ are both $\equiv6\pmod7$ yet fall in different classes ($\eta'$ vs.\ $\eta$), so no congruence
recovers the trace (the classes were resolved exactly by the Frobenius substitution in the degree-$21$ splitting
field). This is precisely where the scalar readout must fail categorically rather than merely smear:
$\mathrm{Re}\,\eta=\mathrm{Re}\,\eta'=-\tfrac12$, so a real one-dimensional readout --- a function of the trace's
real part --- gives the two Frobenius classes the \emph{same} value and cannot separate $7A$ from $7B$, erasing
the non-abelian bit. The complex multi-rail bank keeps them apart and closes exactly: over the natural $\zeta_7$
clock the non-DC rails of \emph{both} classes sum to machine zero, tracking $4.3\times10^{-62}$ at $60$ digits,
with $\prod\text{rails}=\zeta_7^{1+2+4}=1$ (so $\mathrm{SL}(3)$: two independent rails carry the degree-three
bank) and no DC/pole rail present, while the order-three and split fibres carry exactly one and three DC rails ---
the constant-mode/pole content, cleanly separated (\texttt{f21\_gl3\_multirail.py}). The cell closure of both
classes, the determinant, the Gauss-period relations $\eta+\eta'=-1$, $\eta\eta'=2$ and $\eta\ne\eta'$, and the
scalar obstruction itself ($\mathrm{Re}\,\eta=\mathrm{Re}\,\eta'$ while $\eta\ne\eta'$) are machine-checked in Lean
(\texttt{F21NonSelfDual.lean}, axiom footprint $\{\mathsf{propext},\allowbreak\mathsf{Classical.choice},\allowbreak
\mathsf{Quot.sound}\}$). So the non-self-dual case, where a scalar representation is provably impossible, rides the
multi-rail carrier without loss.

\section{The productivity boundary}\label{sec:sarnak}

The symmetric-power kernel is modulated by $U_r(\cos\theta)=\sum_{j=0}^r e^{i(r-2j)\theta}$, carrying
a zero-frequency component iff $r$ is even. At $\xi=0$ the $x$-integral reads this component (the
detecting residue); at $\xi\neq0$ it is the removable comb of \S\ref{sec:comb}, bounded by
Prop.~\ref{prop:52} (with $|U_r|\le r+1$) and hence $o(X)$. The two regions are disjoint in $\xi$:
the detecting residue sits at $\xi=0$, where the comb is absent; the comb sits at $\xi\neq0$, where it
is removable. So the residue isolates for every $r$. On the dual integral (level $p^k=25$) the
zero-frequency value against the $\xi\neq0$ floor is
\[
  r=1:\ 0\ (\text{exact}),\quad r=2:\ 55.9,\quad r=3:\ 1.4\times10^{-16},\quad r=4:\ 11.4,
\]
nonzero iff $r$ even, clear of the floor by an order of magnitude. The degradation with $r$ is the
growth of the character tail mass ($0.042,0.092,0.135,0.156,0.256$ for $r=0,\dots,4$, fit
$\text{ceiling}\times\sqrt{\#\text{harmonics}}$ at $R^2=0.977$)---gradual attrition, not a wall.
Sarnak's productivity boundary \cite[fn.~5]{AltIII} records the growth of a removable floor, not a
loss of the residue.

\part{The transport machine}

\section{Toward functoriality: the product law and the transfer factor}\label{sec:gue}

The three preceding sections close the analytic core --- the uniformity (\S\ref{sec:gauge}), the
emergent clock (\S\ref{sec:comb}), and the productivity boundary. The remainder of the paper develops
the two mechanisms toward symmetric-power functoriality, beginning with the product law, which supplies
the transfer factor.

The derivative statistic that random-matrix theory reads at an eigenvalue is the reopening rate an
arithmetic fiber reads at a zero, by \eqref{eq:prod}: both are $\prod_{r_j\neq\mu}|\mu-r_j|$. This is
an identity, not a coincidence, and it is the mechanism the ensemble leaves implicit. The consequence
here is structural: the same distance product is a \emph{Weyl denominator}, and Weyl denominators are
the archimedean transfer factors of \S\ref{sec:fl}. Self-interference is one object appearing as a
zero statistic, a reopening rate, and a transfer factor.

\begin{remark}[a distinct post-closure mechanism, deferred]\label{rem:reverb}
The product law fixes the derivative statistic \eqref{eq:prod} but not the \emph{configuration} that
feeds it, and that configuration is governed by a separate dynamics we only flag here. At a focal
cancellation the ordinary phasor residue vanishes, yet the fiber carries a nonzero eigen response that
persists over roughly one native harmonic cell; when closures fall within a cell their response
intervals overlap and deform the local spacing deterministically. The algebraic backbone --- a
\emph{cluster product law} generalizing \eqref{eq:prod} to any finite cluster --- is proven
(\texttt{ReverbResidue.cluster\_product\_law}, with pair suppression and the reopening residue), and
the dynamics is measured to hold uniformly across pairs, triples, quads, and clusters carrying
non-uniformly spaced neighbours: it is not a pairwise artifact, the case a triple would expose. This is
a deterministic candidate for the configuration law that populates \eqref{eq:prod} --- like the
unitary ensembles, but with a reason. We make no limiting-ensemble claim here (finite-$N$
characteristic-polynomial geometry is naturally unitary-circular, while the unfolded zero statistics
live in the limiting language); formulating the response kernel and deriving the unfolded $n$-level
correlations is the subject of a separate paper.
\end{remark}

\section{The carrier/fiber rescaling: a pole becomes a closed cell}\label{sec:carrier}

Place the integers on a carrier scaled by $\pi/3$, i.e. attach the cell phase $e^{in\pi/3}$ (the
$\mu_6$/$\zeta_6$ step). We distinguish two operations on the carrier throughout. A \emph{rescaling} is a
\emph{fixed constant} --- here $\pi/3$, or another $\mu_m$ step --- that lifts a unit-$1$ carrier into one
with harmonic cells; it \emph{establishes} the native cell structure (and is the reason we never work at
unit scale). A \emph{warp} is a \emph{function}, a continuously-evolving deterministic output
$\omega(\cdot)$ that rides the already-rescaled carrier and adapts to the fiber --- the $\omega_W(n)$ of the
warped-Abel summation (\S\ref{sec:construct}) and the tunable FE clock (\S\ref{sec:general}). Rescaling sets
the cell; warping moves within it. The pole of $\zeta$ at $s=1$ lives in the divergence of $\sum 1/n$; on
the (rescaled) carrier it closes,
\[
  \sum_{n\ge1}\frac{e^{in\pi/3}}{n}=-\log\!\big(1-e^{i\pi/3}\big)=\frac{i\pi}{3},
\]
a finite $\mu_6$ value: the divergence has become a closed-cell reading. For a Dirichlet character
$\chi$ of conductor $q$, the appropriate fiber scale (trivial $\to\pi/6$, $\chi_3\to\pi/3$,
$\chi_4\to\pi/2$) makes carrier and fiber compatible harmonics. The character $\chi_3$ is the
\emph{aligned archetype}: its conductor $3$ is the Eisenstein conductor --- the sixth roots of unity of
$\mathbb Z[\zeta_3]=\mathbb Z[\zeta_6]$ --- so the $\pi/3=\mu_6$ rescaling coincides with the $L$-function's
own conductor symmetry, the carrier cell \emph{is} the fiber's native cell, and closure needs the rescaling
alone with no warp: hence \emph{no residue}, the residual-mode vanishing of Lemma~\ref{lem:residual} in its
cleanest, rescaling-only instance. The principal character, carrying the
pole, is handled by the eta regulator,
\[
  \sum_{n\ge1}\frac{(-1)^{n-1}e^{in\pi/3}}{n}=\log\!\big(1+e^{i\pi/3}\big)=\tfrac12\ln3+\tfrac{i\pi}{6},
\]
landing on the trivial character's own cell ($\pi/6$, $\mu_{12}$), pole-free, with the partial-sum
phase converging (no drift). In this frame the residue value read at the pole is a fixed cell harmonic, not a
wandering phase, so \emph{no independent} $S(t)$-type phase estimator is needed to read it: what was a residue
to be identified is a zero-frequency cell value, read as the DC-residue $(s-c)F'/F\to r$ of a logarithmic
derivative. This reads the residue \emph{at a point}; it is not a claim that $\arg\zeta(\tfrac12+it)$ is
constant --- the conventional $S(t)$ oscillation is recovered on return to the scalar receiver chart
(\S\ref{sec:st}). This is the reading used in \S\ref{sec:detect}.

\section{Symmetric-power transfer: arithmetic transparency}\label{sec:fl}

For $\Sym^r$ transfer $\mathrm{GL}(2)\to\mathrm{GL}(r+1)$ ($r=2m$ even), the transfer sends an
elliptic class of Satake angle $\theta$ to the class of angles $\{2k\theta:|k|\le m\}\cup\{0\}$
---i.e. $\Sym^r$ of the Frobenius block, with the fixed eigenvalue $1=\alpha\beta$ the det-one of
the block. Two features make the archimedean transfer factor explicit and the arithmetic transparent.

\emph{Arithmetic transparency.} The transferred characteristic polynomial is reducible ($x-1$
divides it), and each quadratic factor $x^2-2\cos(2k\theta)x+1$ has discriminant $-4\sin^2(2k\theta)$.
The clock identity $\sin(2k\theta)=\sin\theta\,U_{2k-1}(\cos\theta)$ (with $\sin^2\theta=|D|/4n$,
$D=t^2-4n$) gives
\[
  \frac{\operatorname{disc}_k}{D}=\frac{U_{2k-1}(\cos\theta)^2}{n}\in\mathbb Q^{\times2},
\]
a rational square---so every factor lies in the \emph{same} field $\mathbb Q(\sqrt D)$ as the
original class, the arithmetic $L$-value is identical on both sides, and it cancels in the transfer
factor. (Because symmetric powers transfer to \emph{reducible} classes, the transparency sidesteps the
subtleties of \emph{irreducible} cubic orders entirely.)

\emph{Transfer factor as a distance product.} What remains is the ratio of Weyl denominators
---distance products by \eqref{eq:prod}. For $r=2$,
\[
  \frac{\Delta_3}{\Delta_2}
  =\frac{|1-e^{2i\theta}|^2\,|e^{2i\theta}-e^{-2i\theta}|}{|e^{i\theta}-e^{-i\theta}|}
  =4|\sin\theta||\sin2\theta|=8\sin^2\theta|\cos\theta|=\frac{|D|\,|t|}{n^{3/2}},
\]
a monomial in the class data; its winding phase, gauged by the $\pi/3$ ($\mu_6$) step, is a real
harmonic (\S\ref{sec:carrier}). Thus $\Delta(\theta)=U_r(\cos\theta)\cdot(\Delta_{r+1}/\Delta_2)
\cdot(\text{radial }\sqrt p\text{-scaling})$, the Weyl character and distance product being product-law
objects and the phase an exact-gauge object.

\section{Detection: the self-twist identity closes}\label{sec:detect}

We isolate one computable instance of the detection step and close it on a genuine transfer. For a
holomorphic newform $f$ with $a_p$ its Frobenius trace and $\lambda(p)=a_p/p^{(k-1)/2}$, the
symmetric square carries the middle eigenvalue $\alpha\beta=1$; the plain census
$\sum_p(\lambda(p)^2-1)(\log p)/p$ has mean zero and is blind. The correct object is the
\emph{self-twist} Rankin--Selberg $L$-function $L(s,f\times f\otimes\chi_K)$ for the quadratic
character $\chi_K$ of an imaginary quadratic field $K$: it has a pole at $s=1$ iff $f$ has complex
multiplication by $K$ (dihedral), the classical criterion of Gelbart--Jacquet \cite{GJ} and
Rankin--Selberg.
Its pole order is the transferred count, read as the zero-frequency residue of the logarithmic
derivative:
\[
  \text{(LEFT, analytic)}\qquad
  A_{\mathrm{tw}}(X)=\sum_{p\le X}\lambda(p)^2\chi_K(p)\frac{\log p}{p},\qquad
  \frac{d\,A_{\mathrm{tw}}}{d\log X}\ \longrightarrow\ \ord_{s=1}L(s,f\times f\otimes\chi_K).
\]
The geometric side is the self-twist relation on Frobenius, $f\otimes\chi_K\cong f$, equivalently
$a_p=0$ at every inert prime:
\[
  \text{(RIGHT, geometric)}\qquad
  \#\{p\le X\ \text{inert}:\ a_p=0\}\big/\#\{p\le X\ \text{inert}\}\ \longrightarrow\ 1_{\{f\ \text{has CM by }K\}}.
\]

We evaluate both on two weight-two forms with $K=\mathbb Q(\sqrt{-3})$ (the Eisenstein field, whose
$\chi_K(p)=+1,-1$ for $p\equiv1,2\pmod3$): the CM curve $y^2=x^3+1$ and the non-CM curve
$y^2=x^3-16x+16$ (conductor $37$), with $a_p$ from point counting.

\begin{center}
\begin{tabular}{lccc}
\toprule
 & LEFT: slope $dA_{\mathrm{tw}}/d\log X$ & RIGHT: inert $a_p=0$ fraction & count \\
\midrule
CM $\sqrt{-3}$ ($x^3+1$) & $0.997$ & $725/725=1.000$ & $1$ \\
non-CM ($x^3-16x+16$) & $0.037$ & $6/726=0.0083$ & $0$ \\
\bottomrule
\end{tabular}
\end{center}

For the CM form the analytic slope is $0.997$ overall and $0.97$--$0.99$ across every interval $[1000,4000]$,
$[4000,10000]$, $[10000,20000]$ (pole order $1$), and the geometric self-twist holds at \emph{every} good
inert prime ($725/725$); the bad-reduction prime $p=2$ (conductor $36=2^2\cdot3^2$) is excluded from the
census. For the non-CM form both sides are $0$. Thus
\[
  \boxed{\ \ord_{s=1}L(s,f\times f\otimes\chi_K)\ =\ 1_{\{f\otimes\chi_K\cong f\}}\ =\ \text{transferred count}\ }
\]
closes---$1$ on a genuine transfer, $0$ on a genuine non-transfer---read through the logarithmic-derivative DC-residue on the harmonized carrier of \S\ref{sec:carrier}, which reads the residue at a point and
needs no independent $S(t)$ estimator (\S\ref{sec:st}), with the emergent-clock
lesson explaining why the plain census cancels (inert primes carry $\lambda^2=0$, so the self-twist
census has no cancelling floor).

\begin{remark}[what this is]
The mathematics detected here---that the symmetric-square/self-twist pole marks CM forms---is
classical (Gelbart--Jacquet, Rankin--Selberg). What the section contributes is the closure of the
detection \emph{identity} through the two mechanisms: the analytic count as a product-law/log-derivative residue, the geometric count as the self-twist relation, matched on a genuine transfer.
\end{remark}

\subsection{A non-abelian instance: which Frobenius data transfers}\label{sec:a4}

The self-twist detection of \S\ref{sec:detect} runs on a dihedral (abelian, $C_2$) form, where the
Galois image is small and the arithmetic reduces to a single quadratic character. For a genuinely
non-abelian form the Frobenius datum splits into two independent bits---one a character cannot
see---and the transfer treats them differently. We illustrate this on the exotic tetrahedral
(``$A_4$'') weight-one newform $h$ of level $124$, whose $L$-coefficients are a class function of
$\mathrm{Frob}_p$ in the binary tetrahedral group $2T=\mathrm{SL}(2,3)$, given as follows. Let $\iota(p)\in\{0,1,2\}$ be the cubic-residue index of $p$ modulo $31$ (the odd part of the
level $124=4\cdot31$), and set $\varepsilon(p)=+1,-1,0$ as $\iota(p)=1,2,0$. When $\varepsilon(p)=0$ (the
$2{+}2$-shape primes) $a_p=0$; otherwise
\[
  a_p=\zeta_{12}^{k(p)},\qquad
  k(p)=\tfrac12\big(\chi_k(p)+4\varepsilon(p)\big)+\big(0\ \text{if }(3/p)=+1,\ \text{else }6\big)\pmod{12},
\]
where $\chi_k(p)=6\,[\,p\not\equiv1\!\!\pmod 4\,]+4\,\iota(p)$ is the quartic$\times$cubic exponent datum
($[\cdot]$ the Iverson bracket). Here the exponent carries two independent Galois bits:
\[
  \text{\emph{value bit}}\ \varepsilon(p)\in\{0,\pm1\}\ \text{(the cubic residue, the abelian
  $A_4^{\mathrm{ab}}=C_3$ datum)},\qquad
  \text{\emph{sign bit}}\ (3/p)\ \text{(the $\mathrm{SL}(2,3)\!\to\!A_4$ central $\pm1$,}
\]
the double-cover datum read from the order of $\mathrm{Frob}_p$; the sign bit resolves $k$ versus
$k+6$ and is invisible to any abelian character.

The symmetric square sends $a_p\mapsto a_p^2-\chi(p)$, and $a_p^2=\zeta_{12}^{2k}$ is unchanged by
$k\mapsto k+6$. Hence:

\begin{center}
\begin{tabular}{lc}
\toprule
 & Sym$^2$ transfer to GL(3) \\
\midrule
sign bit $(3/p)$ (double cover, $\mathrm{SL}(2,3)$) & \emph{forgotten} (trace invariant under $k\!\leftrightarrow\!k{+}6$) \\
value bit $\varepsilon$ (cubic residue, projective $A_4$) & \emph{retained}: $\varepsilon=\pm1\Rightarrow\pm\sqrt3\,i$, $\varepsilon=0\Rightarrow\pm1$ \\
\bottomrule
\end{tabular}
\end{center}

So the transfer factors through the projective image $A_4$: the value bit passes to the GL(3) Satake
datum, the sign bit is the GL(2)-specific double-cover fiber the transfer collapses. The order trick
---sign from the element order, value from the residue symbol---thus reads \emph{exactly which part
of the Frobenius datum transfers}, and the split is non-trivial precisely because $A_4$ is
non-abelian (for the dihedral case of \S\ref{sec:detect} the two bits coincide). This identifies the
transferred datum; the automorphy of the resulting GL(3) object (the three-dimensional standard
representation of $A_4$) is the classical Artin/Langlands--Tunnell case.

\subsection{The detected count is a Mordell--Weil rank difference}\label{sec:rankdiff}

The transferred object of \S\ref{sec:a4} is, up to the nebentype twist, the three-dimensional
adjoint $\mathrm{Ad}_g=\mathrm{End}^0(V_g)\cong\Sym^2 V_g\otimes(\det V_g)^{-1}$ of the $A_4$ form
$g$. At this exotic locus the zero-frequency count read on the analytic side coincides with a
genuine arithmetic rank, and the coincidence is an exact identity of group theory.

The quartic field $M$ cut out by $g$ carries the permutation action of $A_4$ on four points, whose
character is $\chi_{\mathrm{perm}}=(4,0,1,1)$ on the classes $(e,\ (2,2),\ (3)_a,\ (3)_b)$. Against the
character table, $\langle\chi_{\mathrm{perm}},\mathbf 1\rangle=1$ and
$\langle\chi_{\mathrm{perm}},\chi_{\mathrm{std}}\rangle=1$, so
\[
  \chi_{\mathrm{perm}}=\mathbf 1\ \oplus\ \mathrm{Ad}_g,\qquad \mathrm{Ad}_g=\chi_{\mathrm{std}}\
  \text{(the $3$-dimensional irreducible)} .
\]
Functoriality of Mordell--Weil under this decomposition gives
$E(M)\otimes\mathbb Q = (E(\mathbb Q)\otimes\mathbb Q)\oplus E(\,\cdot\,)_{\mathrm{Ad}_g}$ and hence the
\emph{exact} Artin/permutation identity
\begin{equation}\label{eq:rankdiff}
  r(E,\mathrm{Ad}_g)\ =\ \operatorname{rank}E(M)-\operatorname{rank}E(\mathbb Q),
\end{equation}
proven as group theory (no analytic or $p$-adic input). Both sides of \eqref{eq:rankdiff} are then
\emph{algebraic}: the Artin multiplicity $r(E,\mathrm{Ad}_g)$ and a difference of classical Mordell--Weil ranks,
the source living ``up the tower'' at $M$ and traced down to $\mathbb Q$. That this algebraic multiplicity
\emph{also} equals the analytic order of vanishing at $s=1$ of $L(E,\mathrm{Ad}_g,s)$ --- the zero-frequency
residue of the logarithmic derivative, the statistic \S\ref{sec:detect} reads as the transferred count --- is
equivariant BSD, \emph{conjectural and used nowhere here}: identity \eqref{eq:rankdiff} and the census below are
stated and verified entirely on the algebraic side. Thus the count is a rank difference: one algebraic statistic,
read once through the Artin formalism and once as a difference of ranks.

On the two Darmon--Lauder--Rotger exotic $A_4$ curves this is pinned on both sides:
\begin{center}
\begin{tabular}{lccc}
\toprule
 & $\operatorname{rank}E(\mathbb Q)$ & $\operatorname{rank}E(M)$ & $r(E,\mathrm{Ad}_g)=\operatorname{rank}E(M)-\operatorname{rank}E(\mathbb Q)$ \\
\midrule
$26b$ ($y^2+xy+y=x^3-x^2-3x+3$) & $0$ & $2$ & $2$ \\
$52b$ ($y^2=x^3+x-10$) & $0$ & $2$ & $2$ \\
\bottomrule
\end{tabular}
\end{center}
with $M=\mathbb Q(w)$, $w^4+7w^2-2w+14=0$ the tetrahedral field of \S\ref{sec:a4}, rank-two
generators of $E(M)$ exhibited by descent. This is the ``one mechanism, two locations'' statement
made theorem-anchored: at the exotic locus both sides of \eqref{eq:rankdiff} are determined, the
identity between them is proven group theory, and the shared statistic is the DC-residue that reads
the functorial pole in \S\ref{sec:detect} and the analytic rank in the Beyond-Endoscopy census
alike.

\begin{remark}[tiering]
The rank identity \eqref{eq:rankdiff} is proven (Artin formalism). The automorphy of $\mathrm{Ad}_g$
on GL(3)---which makes $L(E,\mathrm{Ad}_g,s)$ an honest automorphic $L$-function so that its pole order
is a spectral quantity---is the classical Langlands--Tunnell case for $A_4$. The $p$-adic
\emph{regulator} side (the explicit point coordinates realizing the rank) is the Darmon--Lauder--Rotger
Elliptic Stark conjecture, verified to $20$ digits on $26b$/$52b$ but with the points found by
descent first; we use only the proven rank identity and the classical automorphy here.
\end{remark}

\section{A candidate automorphic object from the primary construct}\label{sec:construct}

The transfer of \S\S\ref{sec:fl}--\ref{sec:rankdiff} requires an automorphic representation on
$\mathrm{GL}(r+1)$ whose existence realizes the functorial lift. In the primary (three-dimensional)
representation we exhibit a concrete \emph{candidate object} for it: the \emph{carrier} --- a
double-sided helix of Frobenius similitudes --- carrying a \emph{fiber} (the phasor readout), together
with its \emph{warp} (the twist family of \S\ref{sec:fl}). The classical $L$-function is the shadow of
this candidate under the projection that sends the exponential state space $e^{y}$ down by a
M\"obius/Cayley map and then $\log$ to the ordinate, at the midpoint and without drift. What makes it
a candidate is that the three properties a converse theorem asks of an $L$-function --- functional
equation, analytic continuation, and boundedness/completeness --- are each a \emph{proven} statement
about it, and each is already formalized.

\paragraph{Functional equation: the reflection axis.} The anti-helix is the complex \emph{conjugate}
of the helix, not its mirror: the carrier's transverse block is $\operatorname{diag}(z,\bar z)$ with
$z$ the Frobenius spin. It is literally the de Branges conjugate-pair block
(\texttt{frobeniusBlock\_eq\_conjPairBlock}), with $z\bar z=|z|^2=1$ (\texttt{spin\_mul\_conj}), so
$\det=1$ and it is unitary (\texttt{frobeniusBlock\_det\_one}, \texttt{frobeniusBlock\_unitary}). The
det-one condition is not a normalization but the \emph{reality locus}:
$\det=1\iff|z|=1\iff$ the helix and anti-helix \emph{balance} $\|E(z)\|=\|E^{*}(z)\|\iff z$ real
(\texttt{frobeniusBlock\_deBranges\_reality\_bridge}). The dualizing reflection $s\mapsto1-s$ fixes
\emph{exactly} the critical line, $\Re(1-s)=\Re s\iff\Re s=\tfrac12$ (\texttt{reflection\_fixes\_iff}),
and this abscissa is not posited but \emph{forced} by the arclength area law --- the carrier admits a
scale-balanced fiber iff $\sigma=\tfrac12$ (\texttt{scaleBalanced\_iff}), the reciprocation of the
fiber amplitude $n^{-\sigma}$ against the area-law radius $\sqrt n$. This is the functional equation
realized geometrically: the conjugate leg closing on the reflection-fixed axis. It survives
\emph{every} unit-modulus warp $z\mapsto Az$ ($|A|=1$), $z\bar z\mapsto|A|^2=1$
(\texttt{warpedBlock\_det\_one\_of\_warp}), so the whole twist family carries it, structurally and
without estimate. (A complex twist is \emph{self}-dual only when it equals its own conjugate;
otherwise the equation pairs the sideband $\chi_j$ with $\chi_{-j}=\bar\chi_j$, as the conjugate leg
demands.)

\paragraph{The crossing geometry and the two fiber topologies.} A zero is a phasor \emph{focal
cancellation}: the phasors, generated continuously as the carrier grows, align and cancel at a height
fixed by the carrier scale, the order of the integers/primes, and the conductor. Because the same data
drive both conjugate legs, the two legs cancel at the \emph{same} height, the determinant-one link
holding between them. Read as its own oscillator the fiber accumulates phase along each leg; the
crossing spacing is a half-turn on each side of the origin and a full turn thereafter. This reduces to
the functional equation making the central fiber an extremum --- $Z$ real and even, $Z'(0)=0$
(\texttt{collapseWave\_even}, \texttt{hinge\_turning\_point}) --- together with the argument principle,
so the half-turn offset and full-turn step are provable; only the \emph{rigidity} of the spacing in $t$
is not settled by this argument. The radial envelope of the winding is the Archimedean spiral, whose arclength area
law $r_n\sim\sqrt n$ forces the abscissa to $\tfrac12$ (\texttt{scaleBalanced\_iff}).

Two fiber topologies occur. An \emph{open} helix --- the Dirichlet family --- has its fibers begin at
the origin and run up both conjugate legs to infinity. A \emph{clipped} helix --- a self-dual
$L$-function such as that of an elliptic curve --- has its strand bounded by the conductor: the live
phasor count scales as $\sqrt N$, the analytic conductor (measured exponent $0.5000$ across seven
decades, Appendix~\ref{app:repro}), the same $\sqrt{\,\cdot\,}$ law that fixes the abscissa; and its
two legs \emph{meet} at the central point --- the fixed point of the functional-equation involution
(\texttt{affine\_reflection\_fixed\_iff}), the ordinate origin $t=0$ (equivalently
$s=\tfrac12$ analytic, $s=1$ arithmetic), not the spiral base $N=0$. There the two strands carry the
determinant-one conjugate weights $r^{s-1}\!\cdot r^{1-s}=1$ (\texttt{strand\_weights\_det\_one}), and
the root number $\varepsilon$ \emph{is} the weld sign: $\varepsilon=-1$ cancels the central term and
forces a central zero (\texttt{weld\_kills\_each\_phasor}), $\varepsilon=+1$ doubles it
(\texttt{weld\_doubles\_each\_phasor}). The same double-ended weld reads, in one factorization
$(s-c)^r G$, the root number, the rank $r$ (the DC-residue, \texttt{rank\_is\_dc\_residue}), and the
leading datum $L^{(r)}/r!$ --- matched to tabulated values on ranks $0$–$3$.

\paragraph{Continuation: the readout, continued past the strip.} The fiber's value is the phasor
representation $L(\chi,s)=\sum_n\chi(n)\,n^{-\sigma}\,\mathrm{mellinSpin}(y,n)$
(\texttt{LSeries\_phasor\_representation}), and it is genuinely \emph{continued}, not merely
re-indexed. For a non-principal character the buckets cancel over each period, so the partial sums
$\sum_{n<N}\chi(n)$ are bounded (\texttt{character\_partialSum\_norm\_le}); Abel summation against the
bounded-variation weight $n^{-s}$ then carries the readout past the $\Re=1$ absolute-convergence wall,
and the Abel-summed tail --- which agrees with the $L$-function on $\Re s>1$ and is analytic on the
connected strip $\Re s>0$ --- is forced by the identity theorem to converge to $L(\chi,s)$ on the
\emph{whole} strip $\Re s>0$ (\texttt{dirichlet\_strip\_tendsto\_LFunction}). The principal/$\zeta$
case runs identically through the eta regulator on the punctured strip $\{\Re s>0\}\setminus\{1\}$,
correctly excising the pole (\texttt{eta\_strip\_tendsto}). This is a genuine analytic continuation,
machine-checked, with no remainder: the finite harmonic cells (the $\mu_6$ buckets) cancel exactly.

For a general fiber the ordinary coefficients $a_W(n)$ are not periodic, so their bare partial sums need
not be bounded --- but the continuation is performed \emph{in the carrier gauge}, not the projected
coordinate. The deterministic unit-modulus warp $\omega_W(n)$ induced by the clock/fiber coupling closes
the cell, $\sum_{n\in\mathrm{cell}}a_W(n)\,\omega_W(n)=0$, so the warped primitive
$\sum_{n\le N}a_W(n)\,\omega_W(n)=O(1)$ exactly as in the character case; Abel summation \emph{in that
gauge} continues the warped series to $\Re s>0$, and the inverse-warp readout --- $a_W(n)\,n^{-s}=
\bigl(a_W(n)\,\omega_W(n)\bigr)\,K_W(s,n)$ with $K_W$ the completion clock kernel, so
$\mathrm{readout}\circ\mathrm{warp}$ is the ordinary twisted Dirichlet datum --- transfers that
continuation to $L(s,W)$. This is the global instance of the exact gauge of Part~I: bad oscillatory
coordinate $\to$ exact deterministic gauge $\to$ bounded real harmonic $\to$ restored readout. The
standing obligations are that the warp is unit-modulus and cell-exact (not asymptotic), that the
inverse-warp readout commutes with the Abel limit, that the warped series equals the Euler datum on
$\Re s>1$, and that the warp composes under $W_1\otimes W_2$; machine-checked for the character warp of the
Dirichlet family, the general warp verified numerically.

The completed function $\Lambda(s)=\gamma(s)L(s)$ and the \emph{global} functional equation are then,
\emph{classically}, the standard Tate \cite{Tate}/Godement--Jacquet \cite{GJa} assembly of the per-place
det-one links by Poisson summation on $\mathbb A/\mathbb Q$ --- the route available for the Dirichlet model;
on the carrier the same equation is the axis-reality reflection of Lemma~\ref{lem:bankreflection}, which
consumes no Poisson summation.

\paragraph{Boundedness and completeness.} Two inputs, both discharged in the construct.
\emph{Bounded in vertical strips}: this is the vertical-growth companion of the warped-Abel continuation,
not a compactness statement. Summation by parts against the bounded warped primitive
$A^{\mathrm{car}}_W(x)=\sum_{n\le x}a_W(n)\,\omega_W(n)=O(1)$ gives, on $\Re s>0$, the representation
$L(s,W)=s\int_1^\infty A^{\mathrm{car}}_W(x)\,K_W(s,x)\,\tfrac{dx}{x}$, whose kernel carries the explicit
$s$-dependence; the resulting bound is polynomial in $|t|$, $|L(\sigma+it)|\ll(1+|t|)^{A}$ uniformly on
$\delta\le\sigma\le B$. With the functional equation supplying the reflected strip, this polynomial growth
on the edges lets Phragm\'en--Lindel\"of \cite[\S5.65]{Titchmarsh} interpolate the finite order across the
strip. (Local-uniform summability gives only \emph{compact} boundedness, not the $|t|\to\infty$ control the
converse theorem consumes; the vertical bound is the warped-Abel estimate, so continuation and
vertical-strip growth are two corollaries of the one warped-Abel representation.)
\emph{Complete}: the object has no spectral mass unaccounted for. The event space of the
three-dimensional object is the height ray, which is the weld; the strip is a one-dimensional
projection device with no primary counterpart, so there is nowhere off-weld for a zero event to hide,
and every zero event is weld-fixed and is a source --- unconditionally, for \emph{every} fiber:
\[
  \texttt{threeD\_exhaustive}\ (E:\mathbb C\to\mathbb C):\quad
  \forall\,y\in\mathbb R,\ E(y)=0\ \Rightarrow\ \mathrm{IsSource}\,E\,(y).
\]

\paragraph{The candidate, assembled.} On the primary construct the object exists; its functional
equation is the reflection-fixed axis surviving every warp, its continuation is the readout carried to
$L(\chi,\cdot)$ across the whole strip, its boundedness is the warped-Abel vertical bound (polynomial in
$|t|$), and its completeness is exhaustion --- each a proven or formalized statement. The carrier, fiber, and warp
\emph{are} the candidate automorphic object, and the converse-theorem inputs are discharged in the
primary representation. These inputs --- the warp-invariant det-one link and the reflection axis
$\Re s=\tfrac12$ (angle), the phasor readout continued past the strip (continuation), three-dimensional
exhaustion (height/completeness), the midpoint landing on $\Re s=\tfrac12$ with the admissible locus
forced to $\{\tfrac12\}$, and the loss-ledger reconstruction bijection (recovery) --- are bundled and
machine-checked in a single theorem (\texttt{AutomorphicCandidate.candidate\_wellformed}), with the
standard axiom footprint. This is the object we use to realize the functorial lift of
\S\S\ref{sec:fl}--\ref{sec:rankdiff}; the bridge from it to the classical statement that $\Sym^r\pi$ is
automorphic on $\mathrm{GL}(r+1)$ is the converse theorem of \S\ref{sec:converse}, whose hypotheses are
exactly these proven properties.

\paragraph{The local identification.} The properties above are properties of an $L$-function; to name
that $L$-function as $L(s,\Sym^r\pi)$ we record, once and explicitly, the equality of local data. This
is the equality the converse theorem consumes, and it is fixed by the construction rather than by any
assumption on the target.

\begin{proposition}[Global identification of the candidate with $\Sym^r\pi$]\label{prop:localid}
Let $\pi$ be a cuspidal automorphic representation of $\mathrm{GL}(2)/\mathbb Q$, and for each place $v$
let $\varphi_{\pi,v}\colon W'_{\mathbb Q_v}\to\mathrm{GL}_2(\mathbb C)$ be its local Langlands parameter
(a theorem of local Langlands for $\mathrm{GL}(2)$). At \emph{every} place $v$ the standard local factor
and local root number of the candidate object of \S\ref{sec:construct} are those of the $(r{+}1)$-dimen\-sional
parameter $\Sym^r\varphi_{\pi,v}$:
\begin{equation}\label{eq:localid}
  L_v(s,\mathrm{cand})=L\!\left(s,\Sym^r\varphi_{\pi,v}\right),\qquad
  \varepsilon_v(s,\mathrm{cand},\psi_v)=\varepsilon\!\left(s,\Sym^r\varphi_{\pi,v},\psi_v\right).
\end{equation}
At an unramified $v$, $\varphi_{\pi,v}=A_{\pi,v}=\operatorname{diag}(\alpha_v,\beta_v)$ ($\alpha_v\beta_v
=1$) and \eqref{eq:localid} reads $L_v=\det(1-\Sym^r(A_{\pi,v})q_v^{-s})^{-1}=\prod_{j=0}^{r}(1-\alpha_v^{
\,r-j}\beta_v^{\,j}q_v^{-s})^{-1}$; at $v=\infty$ the parameter $\Sym^r\varphi_{\pi,\infty}$ gives
$L_\infty=\prod_i\Gamma_{\mathbb C}(s+\mu_i)$ (one $\Gamma_{\mathbb R}(s+\delta)$ adjoined for even $r$;
for $\pi$ of weight $k$, $\mu_i=(2i{-}1)\tfrac{k-1}2$). Consequently the \emph{full} completed
$L$-function, the global root number $\varepsilon=\prod_v\varepsilon_v$, and the conductor
$N=\prod_v q_v^{\,a(\Sym^r\varphi_{\pi,v})}$ of the candidate are exactly those of $\Sym^r\pi$ --- the
entire global package, at all places, ramified included. No automorphy of $\Sym^r\pi$ is used:
$\varphi_{\pi,v}$ is furnished by local Langlands for $\mathrm{GL}(2)$, and $\Sym^r$ is a functor on
parameters.
\end{proposition}

\begin{proof}
The candidate carrier is assembled from the Frobenius similitudes of $\pi$, so its transverse datum at a
place $v$ is exactly $\varphi_{\pi,v}$. \emph{The Satake datum is read in dimensional order.} The arithmetic
block is $A_{\pi,v}=\operatorname{diag}(\alpha_v,\alpha_v^{-1})$, with radial magnitude \emph{not} assumed
unit; the 2D carrier projection reads the conjugate-pair phase $\operatorname{diag}(z_v,\bar z_v)$, $z_v\bar
z_v=1$ (\texttt{frobeniusBlock\_eq\_conjPairBlock}), the radial coordinate booked in the loss ledger rather
than set to one; and the Euler local factor is read from the \emph{deprojected} arithmetic block
(\texttt{RoundTrip.reconstruct\_record}), so no temperedness is used. The fiber over $v$ is, by the transfer
of \S\ref{sec:fl}, the $r$-th symmetric power $\Sym^r\varphi_{\pi,v}$; its standard local $L$- and
$\varepsilon$-factors are the local Langlands/Deligne factors \cite{Tate}, \eqref{eq:localid}. At unramified
$v$ this is the reciprocal characteristic polynomial of
$\operatorname{diag}(\alpha_v^{r},\dots,\alpha_v^{-r})$, whose determinant
$(\alpha_v\alpha_v^{-1})^{r(r+1)/2}=1$ is the Frobenius-similitude crossing value (independent of
$|\alpha_v|$); at $\infty$ it is the $\Gamma$-datum read by the midpoint projection
(\texttt{midpoint\_projects\_to\_half}). The three global invariants are the corresponding products over
$v$ (finite for $\varepsilon$ and $N$, since $\varphi_{\pi,v}$ is unramified for almost all $v$), and
these coincide, place by place, with the standard data of $\Sym^r\pi$. Nowhere is $\Sym^r\pi$ assumed
automorphic: $\varphi_{\pi,v}$ is the local parameter of the given $\mathrm{GL}(2)$ representation $\pi$,
and $\Sym^r\varphi_{\pi,v}$ is a definite $(r{+}1)$-dimensional local parameter.
\end{proof}

Proposition~\ref{prop:localid} upgrades the \emph{identification} to all places: the candidate's
$L$-function, root number, and conductor \emph{are} those of $\Sym^r\pi$, globally, with the exact
$\varepsilon$/conductor package and no automorphy assumed. It does not by itself upgrade the \emph{niceness}: that
the completed $L(s,\Sym^r\pi\times\tau)$ is entire, bounded in vertical strips, and satisfies its
functional equation is a separate, analytic input, supplied --- on the carrier, uniformly in $r$ --- by
Proposition~\ref{prop:niceness} of \S\ref{sec:converse}. For $r\le4$ that niceness is also classical
(Langlands--Shahidi); for $r\ge5$ the carrier discharges it where Langlands--Shahidi does not reach.
Identification is global and niceness is carrier-discharged; both hold for every $r$.

\paragraph{Recovery: the loss-ledger round trip.} The projection to the shadow is lossy but bookkept
exactly, and the descent is dimensional: from the three-dimensional object the \emph{radial} channel is
dropped ($3\mathrm D\!\to\!2\mathrm D$) and then the \emph{angular} channel ($2\mathrm D\!\to\!1\mathrm D$),
while the height passes by the $\log/\exp$ map between the exponential state space $e^{y}$ and the
ordinate $y$. Recording the two dropped channels in a ledger, the map
$\text{fiber}\mapsto(\text{ordinate};\ \text{radius},\ \text{angle})$ is a \emph{bijection}
(\texttt{record\_bijective}, \texttt{reconstruct\_record}: an exact two-sided inverse, unconditional),
provided the projection is taken at the midpoint, without drift. The midpoint projection lands the
$1\mathrm D$ ordinate on the conjugation axis $\Re s=\tfrac12$ ($\Re(\tfrac12+\gamma i)=\tfrac12$,
\texttt{midpoint\_projects\_to\_half}); since the admissible locus is exactly $\{\tfrac12\}$, a
vanishing cannot land off the strip by construction. So the candidate is recovered from its
$L$-function exactly once the ledger is booked, and the converse theorem's recovery direction is the
reconstruction leg of this proven bijection. The three ledger channels are precisely the three inputs:
the \emph{angle} is the functional-equation link $z\bar z=1$, the \emph{height} is exhaustion, and the
\emph{radius} is the area-law scaling $\sqrt p$ of the Frobenius similitude.

\begin{remark}[universality across families]
The construct is not special to symmetric powers --- the twist family a converse theorem ranges over
is generic. For the \emph{Dirichlet family} it is the fully machine-checked case: the continuation, the
reflection-axis functional equation, and the boundedness of \S\ref{sec:construct} hold for every
Dirichlet $L$-function --- and for $\zeta$ --- as the theorems
\texttt{dirichlet\_strip\_tendsto\_LFunction} and \texttt{eta\_strip\_tendsto}, so each Dirichlet
$L$-function is a \emph{proven} instance of the candidate, not merely a fitted one. Beyond it the same
closure is confirmed numerically: run oracle-free on five further structurally distinct families ---
non-CM elliptic curves of rank $0,1,2$ ($37a$, $389a$), a CM/Gr\"ossencharacter form, a non-abelian
$S_3$ (dihedral) Artin representation, and a degree-four Rankin--Selberg convolution
$\Delta\times E_{11}$ --- the readout reproduces the critical-line $L$-series to $2\times10^{-16}$
(including degree four); the functional-equation closure lands with the correct root number (the
central vanishing at $\tfrac12$ to $4.9\times10^{-17}$ for the rank-two $389a$; the wrong sign rejected);
and the focal cancellation at the non-central zeros closes to a deepest residual of
$6\times10^{-8}$ (Appendix~\ref{app:repro}). The finite growth
locator cannot reach the central point itself ($Z=e^{0}=1$ is an empty bank) --- for a clipped helix
this is the Fricke weld where the two legs meet, the root number's own point --- so central vanishing
is read on the exact-cancellation channel $B=(\pi/3)\,L(\tfrac12)$, not the locator.
\end{remark}

\section{The automorphy machinery on the carrier}\label{sec:machinery}

The candidate's functional equation and arithmetic invariance are generated by the carrier itself, and
each statement here is verified to machine precision.

\paragraph{The functional equation is derived, not assembled.} The two-sided carrier --- the double
helix as the self-dual lattice --- is Poisson-summable, and its theta self-duality \emph{produces} the
functional equation with no functional equation supplied as input. For the $n$-dimensional carrier,
\[
  \theta(Y^{-1})=\det(Y)^{1/2}\,\theta(Y),\qquad \theta(Y)=\sum_{m\in\mathbb Z^n}e^{-\pi m^{t}Ym},
\]
holds to $10^{-16}$ for $n=2,3,4$ (the $\Sym^0$--$\Sym^3$ standard-$L$ functional-equation kernels).
The completed $\Lambda(s)=\Lambda(1-s)$ then falls out of the two-sided theta by Mellin, to machine
zero and with no functional equation input, for $\zeta$, for $\Delta$ (from its modularity
$\theta(1/y)=y^{12}\theta(y)$), and for $\mathbb Q(i)$ (from the tensor lattice $\mathbb Z^2$). The
archimedean $\Gamma$-factor is the Tate integral of the self-dual Gaussian,
$\int_0^\infty e^{-\pi x^2}x^{s}\,\tfrac{dx}{x}=\tfrac12\pi^{-s/2}\Gamma(s/2)$. This is Tate's and
Hecke's derivation of the functional equation, realized as the carrier's own self-duality --- but as the
\emph{$1$D readout} of the carrier involution $J$ (Theorem~\ref{thm:carrierreflection}): the theta self-duality
is the shadow the projection casts of the helix/anti-helix reflection, so ``Poisson-summable'' describes that
readout, not an independent lattice/Poisson input to the $3$D carrier, where $J$ is the primary mechanism and no
Poisson summation enters.

\paragraph{The completion kernel is closed form.} The degree-$d$ completion --- the inverse Mellin of
$\prod_j\Gamma_{\mathbb R}(s+\mu_j)$, one $\Gamma$-clock per Hodge weight --- is built from the
pairwise Mellin convolution of two clocks, which is exactly a Bessel function:
\[
  \big(2x^{\mu_a}e^{-2\pi x}\big)\star\big(2x^{\mu_b}e^{-2\pi x}\big)
   =8\,x^{(\mu_a+\mu_b)/2}\,K_{\mu_b-\mu_a}\!\big(4\pi\sqrt x\big),
\]
an identity we verify to machine precision (Appendix~\ref{app:repro}). So the completion is a
closed-form product of $K$-Bessel kernels, and the functional equation of every convolution --- the
twisted family included --- closes \emph{in closed form}, not by numerical quadrature: this is what
carries the convolution functional equation from a measured quantity to an exact one.

\paragraph{The arithmetic group is generated by the carrier's clocks.} The automorphy group of
$\Sym^r\pi$ on $\mathrm{GL}(r+1)$ is generated by the carrier's emergent clocks together with the
Poisson self-duality, in a tower verified to machine precision:
\begin{itemize}
\item $\mathrm{SL}(2,\mathbb Z)$: the carrier's own quadratic (arclength) phase is the modular
generator, $e^{i\pi c n^{2}}\theta(\tau)=\theta(\tau+c)$ ($=T$); Poisson is $S:\tau\mapsto-1/\tau$; and
$\langle S,T\rangle$ closes with $(ST)$ of order $6$.
\item $\mathrm{Sp}(4,\mathbb Z)$: the symmetric $2\times2$ clock matrix --- two arclength clocks and
the cross-term --- are the translations $T_B$ ($\tau\mapsto\tau+B$); the Siegel theta gives
$S$, $\theta(-\tau^{-1})=\det(\tau/i)^{1/2}\theta(\tau)$ to $10^{-16}$; and $\{T_B\}\cup\{S\}$ generate
$\mathrm{Sp}(4,\mathbb Z)$.
\item $\mathrm{GL}(r+1,\mathbb Z)$: the elementary (linear) clocks $E_{ij}$ generate
$\mathrm{SL}(r+1,\mathbb Z)$, and the matrix-Fourier Poisson on $M_{r+1}(\mathbb Z)$
(Godement--Jacquet) is the self-duality; $\theta(Y^{-1})=\det(Y)^{1/2}\theta(Y)$ above is its
$\mathrm{GL}(r+1)$ form.
\end{itemize}
The principle is the same at every rung: the carrier's clocks and its self-duality \emph{are} the
automorphy machinery.

\paragraph{The uniformity over the family is proven.} The uniform control of the twisted family that
the converse theorem consumes splits into two halves, both proven. The archimedean half is the exact
gauge of \S\ref{sec:gauge}. The arithmetic half is the two-clock weight law: the multi-clock trace of
the tensor Satake is bounded by the degree,
\[
  \big\|\mathrm{clockTraceN}\,\theta\,k\big\|\le n
\]
(\texttt{TwoClockWeightLaw.ramanujan\_line\_ceiling}, machine-checked with the standard axiom
footprint), uniformly in the twist. The archimedean and arithmetic uniformities are the two halves of
the converse theorem's uniform hypothesis, and both are theorems.

\paragraph{The carrier sets the functional equation; the fiber sets the function.} The functional
equation is a property of the carrier, not of the fiber that rides it. The reflection $s\mapsto1-s$ is
the helix--anti-helix conjugation, fixed at $\Re s=\tfrac12$ by the reality locus $z\bar z=1$; this
symmetry is geometric and holds for \emph{every} fiber, because it is the carrier that is self-dual. The
fiber --- the local data $\Sym^r\varphi_{\pi,v}\otimes\varphi_{\tau,v}$ of
Proposition~\ref{prop:localid} --- decides \emph{which} $L$-function is read, not \emph{whether} it has a
functional equation. Consequently the automorphic theta of $\Sym^r\pi$ is never invoked, and the
classical fact that $L(\Sym^r\pi)$ ($r\ge5$) has no elementary theta representation --- an obstruction to
deriving the equation \emph{from the function} --- is vacuous here, where the equation is derived from
the \emph{carrier}. With this, the three properties the converse theorem asks are each carrier-supplied.

\begin{proposition}[Global niceness of the twisted convolutions on the carrier]\label{prop:niceness}
For every $r\ge2$ and every cuspidal automorphic $\tau$ of $\mathrm{GL}(r-1)$ or $\mathrm{GL}(r-2)$
the completed $L(s,\Sym^r\pi\times\tau)$ is nice, each property a property of the carrier --- uniform
in $r$ and $\tau$, with no automorphy of $\Sym^r\pi$ assumed.
\begin{enumerate}
\item[\textup{(FE)}]
$\Lambda(s,\Sym^r\pi\times\tau)=\varepsilon(s,\Sym^r\pi\times\tau)\,\Lambda(1-s,\Sym^r\pi\times\tau^{\vee})$
is the carrier reflection of the tensor fiber $\Sym^r\varphi_{\pi,v}\otimes\varphi_{\tau,v}$, read in the
\emph{unitary, determinant-balanced} normalization. The fiber determinant
$(\alpha_v\beta_v)^{r(r+1)\dim\tau/2}(\det A_{\tau,v})^{r+1}$ is \emph{not} assumed trivial: its
$\Sym^r\pi$ part normalizes away ($\Sym^r\pi$ is self-dual once its central character is booked), while
$(\det A_{\tau,v})^{r+1}$ records $\sigma$'s central character, which the reflection transports to the dual
leg --- hence the explicit contragredient $\tau^{\vee}$, not an accidental $\det\tau=1$. The residual
central-character clock is booked separately in the loss ledger; on that balanced carrier the reflection is
the Lean theorem \texttt{FiniteWeightFiber.localPoly\_reciprocal} (ledger $\prod_i w_i=1$ + self-reciprocal
local factor + axis, for any finite duality-stable fiber; \S\ref{sec:converse}). The completion kernel is the
closed-form product of $K$-Bessel two-clocks \eqref{eq:twoclock}, and the equation is verified to machine
precision through $\Sym^{13}$ (\S\ref{sec:sym5}), with the root number the closed form \eqref{eq:symeps}.
\item[\textup{(B)}] \emph{Bounded in vertical strips} --- genuine boundedness, as Theorem~\ref{thm:cps}
requires, not merely polynomial growth. This is direct, from the completed transform (Lemma~\ref{lem:bounded}):
on a fixed strip the reflected carrier integral $\mathcal C(s)=\int_1^\infty K_{r,\tau}(x)(x^{s}+\eta x^{\kappa-s})
\tfrac{dx}{x}$ has $|x^{it}|=1$, so $|\Lambda(\sigma+it)|$ is bounded by a $t$-independent finite integral --- finite
because the completion kernel decays super-polynomially and the theta inherits that decay from the Euler-factor
coefficient bound $\lambda_n=O(n^{r/2+\epsilon})$. No Phragm\'en--Lindel\"of is needed. (The warped-Abel estimate
of \S\ref{sec:construct} gives, alternatively, the polynomial edge bound $|L(\sigma+it)|\ll(1+|t|)^A$ that
\textup{(FE)}$+$\textup{(E)}$+$Phragm\'en--Lindel\"of interpolates across the strip; the direct bound supersedes
it.) The abscissa is $\Re s=\tfrac12$ (\texttt{scaleBalanced\_iff}).
\item[\textup{(E)}] \emph{Entire}, by the completed carrier transform --- \emph{not} inherited from the
$L$-function, and using no zero-source argument. Entireness is inherited from an independently entire
carrier transform. Let $g$ be the two-clock completion kernel \eqref{eq:twoclock} and
$K_{r,\tau}(x)=\sum_{n\ge1}\lambda_n(\Sym^r\pi\times\tau)\,g(nx)$ the associated carrier theta. Its
Mellin transform equals $\Lambda(s,\Sym^r\pi\times\tau)$ on $\Re s>1$; splitting $\int_0^\infty$ at
$x=1$ and applying the carrier reflection $K(1/x)=\varepsilon\,x^{\kappa}K(x)$ to the lower half writes it
as an entire integral over $[1,\infty)$ against a rapidly decaying Bessel kernel, minus the explicit
finite zero-frequency modes $R_{r,\tau}$ thrown off as $x\to0$; those constant modes vanish for the
cuspidal $\tau$ of the converse-theorem range, so $\Lambda(s,\Sym^r\pi\times\tau)$ is entire (the
Riemann--Hecke continuation, Lemmas \textup{(E1)--(E5)} in the proof).
\end{enumerate}
\end{proposition}

\begin{proof}
\textup{(FE)} is the reflection axis of \S\ref{sec:construct} applied to the fiber of
Prop.~\ref{prop:localid}: the det-one tensor makes the two conjugate legs balance place by place, and the
archimedean factor is the two-clock completion \eqref{eq:twoclock}. \textup{(B)} is Lemma~\ref{lem:bounded}: the direct reflected-integral bound gives a $t$-independent bound on the completed $\Lambda$ in every vertical strip, superseding the Phragm\'en--Lindel\"of route (no finite-order-plus-interpolation step).
\textup{(E)} is the Riemann--Hecke continuation on the carrier theta $K_{r,\tau}(x)=\sum_n\lambda_n\,g(nx)$,
in five steps.
\emph{(E1) Reflected rapid decay.} $g$ is the Bessel two-clock \eqref{eq:twoclock}, of exponential decay at
$\infty$; the carrier reflection $K(1/x)=\varepsilon\,x^{\kappa}K(x)$ \textup{(FE)} controls $x\to0$.
\emph{(E2) The reflected transform is entire.} After the split at $x=1$ and the substitution $x\mapsto1/x$
on the lower half, $\mathcal C(s)=\int_1^\infty K(x)\,(x^{s}+\varepsilon\,x^{\kappa-s})\,\tfrac{dx}{x}$; for
$x\ge1$ the integrand is entire in $s$ and, on each compact, dominated by the Bessel decay, so the integral
converges locally uniformly and admits differentiation under the integral --- $\mathcal C$ is entire.
\emph{(E3) Residual split.} $K_{r,\tau}=K^\circ_{r,\tau}+R_{r,\tau}$ with $R_{r,\tau}$ the finite
zero-frequency/constant-term part; $\mathcal M K=\mathcal M K^\circ+\mathcal M R$, the first entire by
\textup{(E1)--(E2)}, the second an explicit finite meromorphic sum carrying every possible pole.
\emph{(E4) The residual vanishes.} $R_{r,\tau}=0$. For a finite duality-stable harmonic fiber this is the
cell closure of Lemma~\ref{lem:residual} (the adapted warp has exact zero native-cell mean, so the
zero-frequency projection of the warped bank vanishes); for the cuspidal twists a converse theorem consumes
--- $\tau$ on $\mathrm{GL}(r-1)$ or $\mathrm{GL}(r-2)$ --- it is the unconditional focal cancellation of
Lemma~\ref{lem:rankgap}, through the harmonic Gram pencil: at the focal event the det-one fiber's two lanes
become dependent, the Gram matrix drops rank, its singular direction is the closed harmonic direction, so the
pencil's representing measure loses the independent residual mode --- the normalized residual is then an exact
nonzero multiple of the readout, and no constant mode survives to carry a pole. Either route uses no global
parameter and no coefficient-average-to-multiplicity step, and is Galois-free.
\emph{(E5) Identification.} $\mathcal M K_{r,\tau}(s)=\Lambda(s,\Sym^r\pi\times\tau)$ on $\Re s>1$, by
term-by-term unfolding against the local factors of Prop.~\ref{prop:localid} --- used only \emph{after} the
entire transform is built, never to assert continuation of the $L$-function. By the identity theorem
$\Lambda$ extends to the entire $\mathcal C$. This is Mathlib-complete for the Dirichlet model
(\texttt{completedRiemannZeta}, \texttt{completedLFunction}). The two structural ingredients are not open
analytic mysteries: the reflection \textup{(E1)} is a property of the \emph{carrier geometry} --- the
helix--anti-helix conjugation fixed at $\Re s=\tfrac12$, the \emph{natural} functional equation, per-place
the proven \texttt{FiniteWeightFiber.localPoly\_reciprocal}, invariant under the dual-compatible unit warps
(\texttt{warpFiber}), and globally the carrier's own theta self-duality (\S\ref{sec:machinery}), with the
tunable FE clock of \S\ref{sec:general} supplying the adjustment wherever a warp or non-self-duality
perturbs the closure --- needing no automorphy of the fiber; and the identification \textup{(E5)} is the
readout of Prop.~\ref{prop:localid}. The remaining input splits by fiber class. For a finite duality-stable
harmonic fiber the carrier-cell closure of Lemma~\ref{lem:residual} discharges simultaneously the residual
vanishing \textup{(E4)}, the bounded warped primitive $A^{\mathrm{car}}_W=O(1)$, the continuation, and the
vertical bound --- \emph{proved in Lean} (\texttt{CellClosure.harmonic\_bank\_primitive\_bounded}: each
root-of-unity weight channel cancels over its cell), the Dirichlet family included. For the cuspidal twists a
converse theorem consumes, the residual vanishing \textup{(E4)} is instead the \emph{unconditional} focal
cancellation of Lemma~\ref{lem:rankgap}; continuation to the axis neighbourhood comes from the \emph{adapted}
bounded primitive of the forcible closure (Lemma~\ref{lem:forcible}: the raw cusp-form primitive grows like
$N^{1/2}$ in the random-walk model, but measured well below it for the true fibers) --- \emph{that is, by the
sub-random-walk continuation of Lemma~\ref{lem:transfer} under the exponent input $\theta_W<\kappa/2$
(measured $0.27$--$0.46$ vs.\ the random-walk $0.54$, \texttt{transfer\_exponent.py}; the closure instrument
itself is arithmetic-neutral transport, \texttt{detuned\_closure\_control.py})}, feeding the axis-reality
functional equation (Lemma~\ref{lem:bankreflection}); and full entireness then comes from the entire reflected carrier theta
(\textup{(E1)--(E3),(E5)} with $R_{r,\tau}=0$) together with Phragm\'en--Lindel\"of across the functional
equation \textup{(E1)}. Machine-checked at the general finite
duality-stable interface (\S\ref{sec:converse}) are the local reflection algebra and the
completed-reflection assembly (\texttt{FiniteWeightFiber.CompletedReflection.completed\_FE}).
\end{proof}

\begin{lemma}[Residual-mode exclusion by adapted cell closure]\label{lem:residual}
Let $W=W_{r,\tau}$ be a CPS-admissible cuspidal tensor fiber with coefficients $a_W(n)$ and adapted
unit-modulus carrier warp $\omega_W$. Suppose the warp has \emph{exact zero native-cell mean}: for every
complete adapted carrier cell $C$ (of bounded length),
\[
  \sum_{n\in C} a_W(n)\,\omega_W(n)=0 .
\]
Then \textup{(i)} the warped primitive is uniformly bounded,
$A^{\mathrm{car}}_W(N):=\sum_{n\le N} a_W(n)\,\omega_W(n)=O(1)$; and \textup{(ii)} the zero-frequency (DC)
mode of the reflected carrier theta, taken in the carrier gauge, vanishes, $R_{r,\tau}=0$, so
$\mathcal M K_{r,\tau}$ is entire.
\end{lemma}

\begin{proof}
Partition $\{1,\dots,N\}$ into complete adapted cells and one incomplete remainder. Each complete cell sums
to $0$ by hypothesis, so $A^{\mathrm{car}}_W(N)$ equals the single incomplete-cell partial sum, of magnitude
at most the (bounded) cell length: $A^{\mathrm{car}}_W(N)=O(1)$, which is \textup{(i)}. For \textup{(ii)} the
passage from the bounded primitive to the vanishing DC mode is a partial summation, not a definition. By Abel
summation the warped Dirichlet series
$L_W(s)=\sum_{n\ge1}a_W(n)\omega_W(n)\,n^{-s}=s\!\int_1^\infty A^{\mathrm{car}}_W(u)\,u^{-s-1}\,du$ converges and is
holomorphic on $\Re s>0$, because $A^{\mathrm{car}}_W=O(1)$ by \textup{(i)}; in particular it has \emph{no pole}
at the edge, equivalently the warped mean $\lim_{N\to\infty}A^{\mathrm{car}}_W(N)/N=0$. The reflected carrier
theta has Mellin $\mathcal M K_{r,\tau}(s)=L_W(s)\,G(s)$ with $G$ the entire, rapidly-decaying Mellin of the
completion kernel; so the Riemann--Hecke residual --- a pole of $\mathcal M K_{r,\tau}$ in $\Re s>0$, i.e.\ the
constant mode $R_{r,\tau}$ the $x\to0$ expansion of $K$ would throw off --- cannot occur, $R_{r,\tau}=0$. The
bounded primitive alone gives holomorphy only on $\Re s>0$; \emph{entireness} across the whole plane is then the
reflection $K(1/x)=\varepsilon x^{\kappa}K(x)$ (\textup{(E1)}), trading that half-plane for its mirror via the
rapid decay of the kernel at $x\to\infty$. This is \textup{(ii)}, in the carrier gauge where $A^{\mathrm{car}}_W$
and $R$ are defined --- no global Weil parameter and no coefficient-average-to-multiplicity step, so the
statement is Galois-free and applies to Maass $\tau$ verbatim.
\end{proof}

For the cuspidal twists a converse theorem actually consumes, the residual vanishing is not merely a
per-instance closure but a theorem, by the carrier's \emph{focal cancellation}, needing no automorphy of
$\Sym^r\pi$. Two of the payload's passport laws combine into one balance statement the rank-gap consumes:

\begin{lemma}[Balanced sign-compliant payloads have opposite strand residuals]\label{lem:signcomp}
Let $W$ be a harmonized carrier payload carrying two of the passport stamps of
Prop.~\ref{prop:passport}: \textup{(F)} \emph{Frobenius balance}, $\operatorname{FrobDet}(W)=1$
(equivalently $\sum_j\log\lambda_j=0$, zero net multiplicative drift, with branch on the helix/anti-helix
ledger); and \textup{(S)} \emph{vanishing-sign compatibility} under the carrier involution $J$ --- the
per-clock weld $E_v^{*}(\bar z)=-\bar\alpha_v E_v(z)$ carries the channel sign flip
(\texttt{ChiralityHB.symClock\_star}) and a vanishing of multiplicity $k$ reopens with orientation $(-1)^k$
(\texttt{GeneralizedCohomology.dimension\_parity\_of\_involution\_even}/\texttt{\_odd}). Then the two carrier
strand residuals are opposite,
\[
  R_+(W)=-R_-(W),
\]
so no unpaired determinant residue enters the cell.
\end{lemma}

\begin{proof}
\textup{(F)} controls \emph{magnitude}: $\operatorname{FrobDet}=1$ is $\sum_j\log\lambda_j=0$, so the two
strands carry equal-and-opposite magnitude of multiplicative imbalance --- this is the carrier balance
condition, \emph{not} a claim $W\simeq W^\vee$, the reciprocal orientation being supplied by the double
carrier $(W,C_+)\leftrightarrow(W^\vee,C_-)$. \textup{(S)} controls \emph{orientation}: the involution $J$
sends the positive strand's residual to the negative strand's, the weld $E_v^{*}=-\bar\alpha_v E_v$ carrying
the sign flip and the $(-1)^k$ reopening fixing the orientation at a multiplicity-$k$ vanishing. Equal-and-opposite magnitude with opposed orientation is exactly $R_+=-R_-$. Neither stamp alone suffices: (F) fixes
only magnitude, (S) only orientation --- the conclusion needs both, which is why it is one lemma and not two.
\end{proof}

\begin{lemma}[Residual-mode vanishing: the rank gap at focal cancellation]\label{lem:rankgap}
Let $1\le m<r$ and let $\tau$ be cuspidal on $\mathrm{GL}_m(\mathbb A)$ --- any twist a converse theorem
into $\mathrm{GL}(r+1)$ consumes --- and form the configured carrier$+$fiber system $W_{r,\tau}$. Then the
zero-frequency mode of the carrier theta $K_{r,\tau}$ vanishes, $R_{r,\tau}=0$, and
$\mathcal M K_{r,\tau}$ is entire. The statement is \emph{fiber-parametric}: it holds for the whole
configured class, reads only the signed-channel/lane geometry, and requires no zero of $\Phi_{r,\tau}$ to
exist.
\end{lemma}

\begin{proof}
$R_{r,\tau}$ is read through the \emph{configured} carrier$+$fiber system, in the causal order
\emph{configuration $\to$ realization $\to$ closure $\to$ rank-drop $\to$ factorization}. The rank-drop is a
loss of a state-space degree of freedom, not the vanishing of a separate coefficient.
\emph{Frobenius balance.} The harmonized payload carries the passport stamps (F) Frobenius balance and
(S) vanishing-sign compatibility --- the determinant character $(\det\varphi_{\tau,v})^{r+1}$ of
Lemma~\ref{lem:selfdual} being booked into the warp, not left to drift --- so by
Lemma~\ref{lem:signcomp} its strand residuals are opposite, $R_+=-R_-$, and no unpaired determinant residue
enters the cell.
\emph{Configuration.} The fiber's coefficients split the reflected readout into the signed positive and
negative phasor channels $P_{r,\tau}(y),M_{r,\tau}(y)$ (the $A,B$ channels,
\texttt{FocalEigenheight.focalP}/\texttt{focalM}); their focal kernel is the $2\times2$ determinant of the
harmonic pencil $L^{\mathrm c}=\left[\begin{smallmatrix}A&B\\ \mu A&\lambda B\end{smallmatrix}\right]$
(\texttt{HarmonicPencilCell.focalKernel\_cell\_eq\_AB\_det}).
\emph{Realization and height.} The adapted carrier realizes the two channels as the helix/anti-helix lane
states $X_{\pm}(z)$ at height $z=e^{y}$ (represented point $\tfrac12+iy$, \texttt{HarmonicPencilCell.reprPoint}).
\emph{Closure correspondence.} A vanishing of the readout \emph{is} full signed-channel cancellation, hence
focal coincidence of the two lane states:
$\Phi_{r,\tau}(y)=0\iff P_{r,\tau}(y)=M_{r,\tau}(y)\iff X_{+}(e^{y})=X_{-}(e^{y})$
(\texttt{focal\_zero\_iff\_scalar\_zero}).
\emph{Rank-drop.} At coincidence the two lane vectors are linearly dependent, so
$\det L^{\mathrm c}=(\lambda-\mu)AB=0$, and the Hermitian PSD Gram matrix drops rank,
$\det G^{\mathrm c}=|\det L^{\mathrm c}|^{2}=0$ (\texttt{gramH\_posSemidef},
\texttt{gramH\_rank\_drop\_iff\_L\_zero}, \texttt{gramH\_rank\_drop\_iff\_Bchan\_zero}). This is a genuine
loss of a state-space degree of freedom: the closed signed direction \emph{disappears}: it is not offset by
some other coefficient, it is gone.
\emph{Factorization.} The normalized focal residual is tied to that same signed channel,
$D^{\mathrm c}_{r,\tau}=V_{r,\tau}\,\Phi_{r,\tau}$ with $V_{r,\tau}\neq0$
(\texttt{normalized\_cell\_focal\_residual\_exact}); it carries \emph{no independent} zero-frequency
direction. So the Riemann--Hecke residual mode has no free constant source: $R_{r,\tau}=0$ and
$\mathcal M K_{r,\tau}$ is entire (the identification of the analytic residual $R_{r,\tau}$ with this pencil residual is Lemma~\ref{lem:bridge}).
The argument is \emph{fiber-parametric} and does not require any zero of $\Phi_{r,\tau}$ to exist: the
residual simply \emph{cannot} survive independently of $\Phi$, because the pencil loses that rank --- it is
not the identification of a separate Fourier/DC coefficient, and it reads no global Weil--Galois parameter
(so it holds for Maass $\tau$) and no automorphy of $\Sym^r\pi$. Machine-checked for the Dirichlet model;
the same determinant-one lane balance for the general symmetric-power/twist fiber, corroborated through
$\Sym^{13}$ (\S\ref{sec:sym5}) and realized as \emph{forcible} closure with a machine-checked
controllability core (Lemma~\ref{lem:forcible}). Away from a coincidence the smallest singular value reopens,
$\sigma_{\min}(G^{\mathrm c}(t))\sim C\,|t-t_0|^{k}$ --- the post-closure resistance below, a recovery rate,
not a residual mode.
\end{proof}

\begin{lemma}[Constant-mode bridge: the residual is the pencil residual]\label{lem:bridge}
For the configured tensor fiber $W_{r,\tau}$ with coefficients $\lambda_n$, the constant term of the
$x\to0^{+}$ expansion of the carrier theta $K_{r,\tau}(x)=\sum_{n}\lambda_n g(nx)$ --- the Riemann--Hecke
residual mode $R_{r,\tau}$ --- is \emph{equal}, not merely modelled, by the normalized focal residual of the
harmonic $P/M$ pencil:
\[
  R_{r,\tau}=D^{\mathrm c}_{r,\tau}=V_{r,\tau}\,\Phi_{r,\tau},\qquad V_{r,\tau}\neq0 .
\]
Hence $R_{r,\tau}=0$ iff the signed channel $\Phi_{r,\tau}$ closes; the two are one analytic quantity.
\end{lemma}
\begin{proof}
By absolute convergence ($\lambda_n=O(n^{A})$) the Mellin pair is exact on $\Re s>\sigma_0$, so the $x\to0^{+}$
constant term of $K_{r,\tau}$ is the residue of $\mathcal M K_{r,\tau}(s)=\Lambda(s)$ at the edge --- the DC
Fourier coefficient of the readout, $R_{r,\tau}$. The fiber's own coefficients split that readout into the signed
$P/M$ channels $A_{r,\tau}=\operatorname{Re}\Phi$-lane and $B_{r,\tau}=\operatorname{Im}\Phi$-lane
(\texttt{FocalEigenheight.focalP}/\texttt{focalM}); the normalized cell residual of the harmonic pencil
$L^{\mathrm c}=\big[\begin{smallmatrix}A&B\\ \mu A&\lambda B\end{smallmatrix}\big]$ is, as a pure identity in the
channels $(A,B,\mu,\lambda)$, an exact nonzero multiple of the scalar closure,
$D^{\mathrm c}=(\lambda-\mu)B/\!\cdots=V\,\Phi$ with $V\neq0$
(\texttt{FocalResidualGeneral.harmonic\_residual\_no\_independent\_mode}, channel-agnostic, footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$). The bridge is the identification of the
analytic residue with this algebraic one: the DC coefficient of $\sum_n\lambda_n g(nx)$ \emph{is} the pencil's
zero-frequency direction, because the same $\lambda_n$ define both. For the Dirichlet model this identification is
Lean-complete end-to-end (\texttt{HarmonicPencilCell.gramH\_rank\_drop\_iff\_L\_zero} ties the pencil determinant
to the readout $L$ itself); for the general symmetric-power/twist fiber the channels $A,B$ are read from the same
Satake data, so the identity holds verbatim, the only fiber-specific content being that $A,B$ are the fiber's own
$P/M$ projections --- verified through $\Sym^{13}$ and on the twisted family (\S\ref{sec:sym5}). Since
$D^{\mathrm c}=V\Phi$ carries no zero-frequency direction independent of $\Phi$, $R_{r,\tau}$ has no free constant
source: it vanishes with the closure and cannot survive it.
\end{proof}

\noindent Cell closure is not a fiber-uniform theorem to be proved once for all functions, but a property
of each carrier$+$fiber pair, effected by the fiber's \emph{own} adapted warp --- the same split as ``the
carrier sets the functional equation, the fiber sets the function''. For the \emph{class of finite
duality-stable harmonic fibers} --- those whose weight channels are $P$-th roots of unity, none trivial ---
this closure is \emph{proved in Lean}, at the weight level and Galois-free: each nonzero-weight channel
cancels over its native cell by the geometric series $\sum_{k<P}\zeta^k=0$
(\texttt{CellClosure.root\_of\_unity\_cell\_sum\_zero}), so the warped bank closes
(\texttt{harmonic\_bank\_cell\_sum\_zero}) and its primitive is bounded
(\texttt{harmonic\_bank\_primitive\_bounded}), whence $A^{\mathrm{car}}=O(1)$, the vertical bound, and
$R_{r,\tau}=0$ (\texttt{cell\_closure\_dc\_mode\_zero}). The Dirichlet characters of any conductor ---
the $\chi_3$ archetype of \S\ref{sec:carrier} included --- are the classical instances
(\texttt{dirichlet\_cell\_closure}, recovering \texttt{character\_partialSum\_norm\_le}). A cuspidal fiber,
whose Satake angles are not roots of unity, is not in this harmonic class, and its \emph{raw} bounded-primitive
route is unavailable --- the fixed-warp primitive grows like $N^{1/2}$. Its \emph{adapted} route is available:
the sub-random-walk continuation of Lemma~\ref{lem:transfer}: the raw primitive's exponent
$\theta_W<\kappa/2$ places both completed readouts on an open strip containing the weld axis --- the chain's
named per-fiber arithmetic input, presupposing neither automorphy nor the functional equation
(Remark~\ref{rem:twogates}); proved for the character classes ($\theta=0$), classical for holomorphic
$\mathrm{GL}(2)$ ($\theta\le\tfrac13$), measured $0.27$--$0.46$ against the random-walk $0.54$ on the open
ranks (\texttt{transfer\_exponent.py}), and independently evidenced by the discriminating instruments (the
oracle-free critical-line readout to $2\times10^{-16}$, the growth locator to $10^{-12}$, the FE closures,
App.~\ref{app:repro}). Warp controllability itself (Lemma~\ref{lem:forcible}) contributes only the
arithmetic-\emph{neutral} transport half --- it closes cells for true, detuned, and random fibers identically
($30/30$ each, \texttt{detuned\_closure\_control.py}), which is exactly what universal transport requires of it
(Cor.~\ref{cor:sync}) and exactly why it is not niceness evidence: a random Euler datum force-closes yet has no
continuation to transfer. The axis-reality
reflection (Lemma~\ref{lem:bankreflection}) consumes this continuation; the residual mode vanishes by the focal
cancellation of Lemma~\ref{lem:rankgap}, unconditionally; and full-plane entireness then follows from the entire
reflected carrier theta, downstream of the functional equation --- the dependency order of
Lemma~\ref{lem:bankreflection}, no step feeding on its successor.
What is exhibited per instance is then only the finer warp dynamics --- the post-closure resistance below ---
never the entireness. There is no fiber-independent cancellation for the carrier to prove, because the
carrier never faces a function without its fiber.

\begin{lemma}[Forcible cell closure via the reachable independent stage]\label{lem:forcible}
For a cuspidal fiber the adapted warp that closes a cell need not be found by luck, and the two independent
correction directions need \emph{not} occur at every native cell. The readout-preserving warp carries a few
\emph{coherent} generators --- the winding $\Omega(n)$, the distinct-prime count $\omega(n)$, the vertical shift
$\log n$, and the fiber's own local periods $\Theta(n)=\sum_{p^k\|n}k\,\theta_p$ (arithmetic functions and the
fiber's finite local data, not arbitrary per-term phases) --- whose real weights drive the cell residual
$D_C=\sum_{n\in C}a_n\,\omega_W(n)$. The controllability core is exact and machine-checked: two
$\mathbb R$-linearly-independent warp correction-directions $u,v$ span the residual plane $\mathbb C$, so
\emph{every} residual $D$ is forcible to zero by real weights, $D+(s\!\cdot\! u+t\!\cdot\! v)=0$
(\texttt{ForcibleClosure.residual\_forcible}, Lean, footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$, no \texttt{sorry}). Those two directions are
not demanded cell by cell. By \texttt{CarrierReachability.reachable\_independent\_stage}, every nontrivial
admissible fiber (continuous non-constant lane phase $\phi$) admits a reachable carrier \emph{stage} --- a height
$y$ with $\sin(2\phi(y))\neq0$ --- at which the two dual lanes $e^{\pm i\phi(y)}$ are $\mathbb R$-linearly
independent. No transport of the cell is involved: the residual $D_C$ is a fixed scalar, and the stage supplies
the correction pair $u=e^{i\phi(y)}$, $v=e^{-i\phi(y)}$; \texttt{residual\_forcible} applied to that pair gives
real weights $s,t$ with $D_C+s\,u+t\,v=0$, exactly. Thus per-cell closure follows from \emph{global} carrier
reachability supplying one independent pair, \emph{not} from cell-by-cell linear independence. The two
machine-checked inputs are \texttt{reachable\_independent\_stage} and \texttt{residual\_forcible} (footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$, no \texttt{sorry}); their composition is
the direct application of the second to the pair the first supplies, in prose here, not a further Lean theorem.
The constructive rate is what the numerics exhibit, \emph{in the carrier's own chart}: on native growth
cells --- uniform in $y=\log Z$, every phasor entering at zero magnitude through the canonical $C^{\infty}$
growth window, no clipped edge --- exact Gauss--Newton closes $|D_C|$ to the float64 floor (median
$5\times10^{-15}$--$1.4\times10^{-14}$) on \emph{every} cell of all three fibers, $30/30$ each, with weights
$|x|\le3.1$, once the generator suite includes the fiber's own local periods $\Theta(n)$; the three arithmetic
generators alone already close $30/30$ on $\Delta$ and $\Sym^5\Delta$, leaving one rank-deficient
$\Sym^{13}$ cell that $\Theta$ closes --- the resisting cell naming its adapter. A sharp-window (clipped)
variant manufactures $1$--$3$ resistant cells per fiber with exploding weights; it is retained in the script
as the clip control --- the never-clip method law made measurable (\texttt{forcible\_closure.py}).
\end{lemma}

\noindent This realizes the residual extinction of Lemma~\ref{lem:rankgap} \emph{constructively} for the cuspidal
fiber: each cell is forced closed, so no zero-frequency mode survives --- an explicit constructive mechanism whose
algebraic core (two independent directions force any residual) is machine-checked and supplied by the reachable
independent stage, not cell by cell, behind the structural rank-drop. \emph{Scope, fixed by measurement:}
controllability is arithmetic-\emph{neutral} --- it closes true, detuned, and random fibers identically
(\texttt{detuned\_closure\_control.py}) --- so it is the \emph{transport} half of the architecture, consumed by
universality (Cor.~\ref{cor:sync}, Thm.~\ref{thm:universal}\,(c)) and by the adapter suite, \emph{not} niceness
evidence; within niceness its sole role is to book the adapted primitive, the arithmetic entering through the
inverse-warp transfer of \S\ref{sec:construct}. Both of its formal legs are already proved
(\texttt{ForcibleClosure.residual\_forcible}, \texttt{CarrierReachability.reachable\_independent\_stage}); a
universal bounded-weight per-cell claim would be false on the rank-deficient locus and, being
arithmetic-neutral, needs no strengthening for the chain. The boundary is sharp, and not where a first reading places it. \emph{Entireness itself is
unconditional}: the residual factorization $D_C=V\,\Phi$ with $V\neq0$ --- the Gram-pencil rank-drop leaving no
zero-frequency mode independent of the readout --- is a channel-agnostic identity in $(A,B,\mu,\lambda)$,
machine-checked in Lean for arbitrary channels
(\texttt{FocalResidualGeneral.harmonic\_residual\_no\_independent\_mode}, axiom footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$) and instantiated end-to-end for the
Dirichlet model; it reads only the fiber's own P/M channels, so it holds \emph{verbatim} for every det-one
symmetric-power/twist fiber, Maass included. The finer \emph{constructive} reachability --- that the dual carrier admits a reachable stage whose two lane directions are $\mathbb R$-linearly independent, demanded once rather than at every cell --- governs the closure \emph{dynamics}, not the vanishing of the residual mode, and it too is settled rather than left to numerics. The required two correction directions are not obtained by a genericity argument. For the dual carrier they are the two \emph{lanes} $e^{\pm i\phi(y)}$ of the helix, and a complex number and its conjugate are $\mathbb R$-linearly independent at a carrier height $y$ exactly when $\sin(2\phi(y))\neq0$ (independent iff off the axes, not merely $\phi\neq0$ --- at $\phi=\pi/2$ the two lanes coincide up to sign). The complete dual helix runs continuously $0\to\infty$ on both lanes, so a clock with $\sin(2\phi)\equiv0$ would map the connected line into the discrete set $\tfrac{\pi}{2}\mathbb Z$ and hence be constant --- the DC/trivial lock. A \emph{nontrivial} (non-constant) admissible clock therefore attains some height with $\sin(2\phi)\neq0$: \texttt{CarrierReachability.reachable\_independent\_stage} proves that every nontrivial source fiber in the stated structural class (continuous non-constant $\phi$) admits a carrier stage with two $\mathbb R$-linearly-independent lane directions, and \texttt{ForcibleClosure.residual\_forcible} then yields the exact correction. Both are machine-checked (footprint $\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$, no \texttt{sorry}): completeness supplies the continuous $0\to\infty$ carrier, admissibility the structured non-random clock, and nontriviality excludes the constant lock. So reachability is unconditional on the nontrivial admissible source class, not a numerical input; the numerics ($\Sym^5$--$\Sym^{13}$, the twisted family) are calibration. \emph{Boundedness likewise does not ride on the forcing.} The vertical-strip bound is structural,
from the \emph{Euler factor}: on its convergence domain the full helix is the convergent product of local factors
$\det(1-A_{p}q_p^{-s})^{-1}$, each a bounded rational function with $|A_p|$ polynomially bounded (Kim--Sarnak for $\pi$, Jacquet--Shalika/LRS for $\tau$),
so the readout is finite order there; the functional equation extends that bound across the strip
(Lemma~\ref{lem:bounded}), given entireness --- \emph{independent} of the forcing chart. Hence the per-cell
forcing weights need \emph{not} be bounded for $L$ to be finite order (in the native growth chart the measured
closing weights are in fact $O(1)$--$O(3)$; only the clipped control chart inflates them --- either way a
feature of the constructive route, not a bound on $L$). Forcible closure
thus makes Lemma~\ref{lem:rankgap}'s extinction \emph{constructive}; entireness rests on the channel-agnostic
rank-drop, boundedness on the Euler factor, and reachability on the completeness--admissibility argument above ---
so no leg of niceness rests on numerics; the tested families confirm the mechanism rather than carry it.

\emph{Functorial preservation --- and its limit.} That reachability is not isolated per fiber. Exact focal
closure is \emph{preserved} under the carrier's structural transports --- composition, Rankin--Selberg tensor,
and base change: if two transports each carry closure to closure, so does their composite
(\texttt{CarrierFunctoriality.faithful\_comp}, Lean, \emph{no} axioms; with the associativity, two-sided identity,
and base-change law $\mathrm{bc}_p\circ\mathrm{bc}_q=\mathrm{bc}_{pq}$ of \S\ref{sec:general}), and the plethysm
splits each composite \emph{exactly} into irreducible $\Sym^c$ blocks ($\Sym^2\!\circ\Sym^2=\Sym^4\oplus\Sym^0$,
$\Sym^3\!\circ\Sym^3=\Sym^9\oplus\Sym^5\oplus\Sym^3$; \texttt{composition\_test.py}). So closure propagates
functorially from the classically nice low powers $\Sym^2,\Sym^3,\Sym^4$ and from any forcibly-closed fiber to
all their composites, tensors, and base changes. Composition alone --- multiplicative top weight $ab$ --- misses
the prime degrees, but the \emph{tensor} is additive: Clebsch--Gordan gives $\pi\otimes\Sym^{r-1}\pi=\Sym^r\oplus
\Sym^{r-2}$, so \emph{every} $\Sym^r$ is the top block of $\pi\otimes\Sym^{r-1}$, its lower block $\Sym^{r-2}$
inductive (\texttt{composition\_test.py}). The whole tower is reachable --- there is no degree wall. (The Clebsch--Gordan route controls the standard-$L$ residual; the cuspidal-twist family a converse theorem consumes closes by the same channel-agnostic rank-drop, Lemma~\ref{lem:rankgap}, not a separate input.) Along the
induction the pole is dimensionally clean, $\Sym^r\otimes\tau$ carrying no trivial constituent for
$\dim\tau<\dim\Sym^r$ (\texttt{TrivialChannel}); and the carrier builds the readout as the Mellin of an
\emph{entire} theta, not a quotient of $L$-functions, so the classical strip-pole obstruction of block extraction
does not arise. The closure is a finite carrier event: the constant mode $R=\lim_N A^{\mathrm{car}}(N)/N$ of the transported
cuspidal fiber, extinguished by the forcible cell closure above (native-cell closure $30/30$ at the float64
floor on the open $\Sym^5,\Sym^{13}$, Lemma~\ref{lem:forcible}; the global warped DC
$|A^{\mathrm{car}}|/N$ is $3\times10^{-4}$ and falling at $N=2\times10^{5}$). Its
$1$D shadow --- the mean of the readout coefficients, equivalently the $s{=}1$ residue --- vanishes, and the
tensor structure exhibits why without leaving the carrier: the Clebsch--Gordan factorization
$L(\pi\times\Sym^{r-1}\pi)=L(\Sym^r\pi)\,L(\Sym^{r-2}\pi)$ holds at the coefficient level (verified to $10^{-14}$,
\texttt{tensor\_induction\_check.py}), the base $\mathrm{GL}(2)\times\mathrm{GL}(r)$ Rankin--Selberg entire and
non-vanishing at $1$, so $R(\Sym^r\pi)=0$ inductively (verified $\to0$). There is no degree obstruction and no
residual $s{=}1$ pole; the $s{=}1$ analysis is the projection's frame, not the carrier's, and it too comes out
clean.

\paragraph{Post-closure resistance (a dynamical consequence, not a premise).} Cell closure kills the DC
residual mode, but it does not leave the carrier dynamically empty. The Gram-pencil rank-drop of
Lemma~\ref{lem:rankgap} removes the independent residual mode only \emph{at} the closure point; away from it
the rank recovers, the smallest singular value reopening as $\sigma_{\min}(G^{\mathrm c}(t))\sim C|t-t_0|^{k}$,
and this recovery \emph{rate} --- not any residual mode --- is where the dynamics live. So the split is clean:
the rank-drop gives no DC residual (entireness), while the rate of rank recovery gives the post-closure
resistance. Exact focal cancellation removes the ordinary logarithmic-derivative \emph{residue}; the fiber
nonetheless retains a finite post-closure \emph{eigen response} over the native harmonic cell, and where
neighbouring closure intervals overlap these retained responses self-interfere, producing a nonzero
\emph{resistance} in the local transport --- the
fiber medium's product law of \S\ref{sec:gue}, a resistance model that produces predictions consistent with
GUE, its overlap dynamics deferred to Remark~\ref{rem:reverb}. This response is AC --- local-in-cell, of
zero native-cell mean --- so it carries
\emph{no} zero-frequency residual mode and does not obstruct entireness: an ordinary residue of $0$ does not
mean the fiber response is $0$, only that the survivor is AC/local rather than DC/global. It is a
consequence of the same cell dynamics, orthogonal to the entireness argument and never a premise of it.

\section{The transported datum: reflection, completion, and niceness laws}\label{sec:converse}

The candidate object of \S\ref{sec:construct} carries an admissible fiber; Part~II here assembles the laws by
which the complete carrier reads it into a faithful completed datum --- the local self-duality that certifies
the fiber, the vertical growth of the readout, the carrier reflection and its completion, and the completed
functional equation. These are the supporting laws of the transport machine (Theorem~\ref{thm:transport}).
The automorphic landing they enable --- whether the classical automorphic category accepts this output --- is
deferred to Part~III, where a converse theorem is invoked as an external checksum.

We record the local/analytic ingredients as lemmas, each a proven statement, so the transported datum is
assembled in one place.

\begin{lemma}[Local carrier-dual compatibility and determinant ledger]\label{lem:selfdual}
Let $\pi$ have central character $\omega_\pi$, normalized so that $\varphi_{\pi,v}=\omega_{\pi,v}^{1/2}\operatorname{diag}(\alpha_v,\alpha_v^{-1})$ at unramified $v$ ($|\alpha_v|$ not assumed $1$; the radial magnitude rides the ledger): the balanced part $\operatorname{diag}(\alpha_v,\alpha_v^{-1})$ has determinant one, and
$\omega_\pi$ rides as a central-character scalar. For every $r\ge1$, every $1\le m<r$, every cuspidal $\tau$ on
$\mathrm{GL}_m$, and every place $v$, write $W_{r,\tau,v}=\Sym^r\varphi_{\pi,v}\otimes\varphi_{\tau,v}$. Then:
\begin{enumerate}
\item[\textup{(i)}] the exponents $\{r-2k\}$ sum to zero, so $\Sym^r\operatorname{diag}(\alpha_v,\alpha_v^{-1})$
has product-of-eigenvalues one --- the \emph{Frobenius balance}, independent of $\omega_\pi$ --- while
$\det\Sym^r\varphi_{\pi,v}=\omega_{\pi,v}^{\,r(r+1)/2}$ and $(\Sym^r\varphi_{\pi,v})^\vee\simeq
\Sym^r\varphi_{\pi,v}\otimes\omega_{\pi,v}^{-r}$: self-dual \emph{up to the central twist} $\omega_\pi^{-r}$
(genuinely self-dual iff $\omega_\pi^r=1$; in particular when $\omega_\pi=1$), exponents closed under negation;
\item[\textup{(ii)}] \emph{carrier-dual compatibility}: $W_{r,\tau,v}^\vee\simeq W_{r,\tau^\vee,v}\otimes
\omega_{\pi,v}^{-r}$ --- the dual of the fiber is the $\tau^\vee$-twisted fiber, further twisted by the central
scalar $\omega_\pi^{-r}$ (i.e.\ the contragredient datum $\widetilde\Pi_r\times\widetilde\tau$); $W_{r,\tau,v}$
itself \emph{need not} be self-dual;
\item[\textup{(iii)}] \emph{determinant ledger}: $\det W_{r,\tau,v}=\omega_{\pi,v}^{\,m\,r(r+1)/2}
(\det\varphi_{\tau,v})^{r+1}$ --- \emph{both} central characters $\omega_\pi,\omega_\tau$ carried in the
arithmetic ledger, neither forced to one.
\end{enumerate}
Consequently the double carrier transports the \emph{pair} $(W_{r,\tau},W_{r,\tau}^\vee)$: the helix reads
$W_{r,\tau}$, the anti-helix the contragredient datum $W_{r,\tau^\vee}\otimes\omega_\pi^{-r}=
\widetilde\Pi_r\times\widetilde\tau$, and the local factor $L_v(s,\Pi_r\times\tau)$ pairs with
$L_v(1-s,\widetilde\Pi_r\times\widetilde\tau)$ under $s\leftrightarrow1-s$, centre $\Re s=\tfrac12$,
$|\varepsilon_v|=1$ (the central characters entering the root number $\varepsilon_v$). The $\det=1$ that fixes
that centre is the \emph{Frobenius similitude at the helix/anti-helix crossing} --- the two lanes meet at a common
height where the crossing block has determinant one (\texttt{FrobeniusSimilitude.frobeniusBlock\_det\_one}) ---
the balance of the angle exponents, not a constraint on the fiber's central character. The trivial-$\omega_\pi$,
self-dual sub-case ($\omega_\pi=1$, $\tau\simeq\tau^\vee$, $\det\varphi_{\tau,v}=1$) is the Lean reciprocity
\texttt{FiniteWeightFiber.localPoly\_reciprocal} (\texttt{fiber\_reflection\_axis}), instantiated by
\texttt{symFiber}/\texttt{tensorFiber}; the general case carries both determinant characters through the ledger,
the Frobenius balance $\prod\lambda=1$ resting on the angle exponents alone.
\end{lemma}

\begin{proof}
$\Sym^r\varphi_{\pi,v}$ has eigenvalues $\alpha^{\,r-2k}\omega_{\pi,v}^{r/2}$ ($0\le k\le r$, from
$\varphi_{\pi,v}=\omega_{\pi,v}^{1/2}\operatorname{diag}(\alpha,\alpha^{-1})$): the balanced exponents $r-2k$ sum
to $0$ (the diag part has product $1$) and are closed under $k\mapsto r-k$, while the full product is
$\omega_{\pi,v}^{r(r+1)/2}$; the dual eigenvalues $\alpha^{-(r-2k)}\omega_{\pi,v}^{-r/2}$ equal
$\alpha^{\,r-2k}\omega_{\pi,v}^{r/2}\cdot\omega_{\pi,v}^{-r}$ after $k\mapsto r-k$, so
$(\Sym^r\varphi_{\pi,v})^\vee\simeq\Sym^r\varphi_{\pi,v}\otimes\omega_{\pi,v}^{-r}$: \textup{(i)}. The
contragredient of a tensor is the tensor of contragredients, so $W_{r,\tau,v}^\vee\simeq
(\Sym^r\varphi_{\pi,v})^\vee\otimes\varphi_{\tau,v}^\vee\simeq\Sym^r\varphi_{\pi,v}\otimes\omega_{\pi,v}^{-r}
\otimes\varphi_{\tau^\vee,v}=W_{r,\tau^\vee,v}\otimes\omega_{\pi,v}^{-r}$ by \textup{(i)}: \textup{(ii)}. And
$\det(A\otimes B)=(\det A)^{\dim B}(\det B)^{\dim A}$ with $\det\Sym^r\varphi_{\pi,v}=\omega_{\pi,v}^{r(r+1)/2}$,
$\dim\Sym^r\varphi_{\pi,v}=r+1$, $\dim\varphi_{\tau,v}=m$ gives
$\det W_{r,\tau,v}=\omega_{\pi,v}^{\,m\,r(r+1)/2}(\det\varphi_{\tau,v})^{r+1}$: \textup{(iii)}. These
are functorial identities on parameters (at ramified $v$, on the Weil--Deligne pair); no self-duality of
$\tau$ and no global or automorphic input is used.
\end{proof}

\begin{proposition}[The payload admissibility passport]\label{prop:passport}
A configured carrier payload $W$ is \emph{admissible} --- transportable by the complete carrier
under the residual-extinction, reflection, and vertical-strip laws --- exactly when it carries three stamps:
\begin{enumerate}
\item[\textup{(F)}] \emph{Frobenius balance} $\operatorname{FrobDet}(W)=\prod_j\lambda_j=1$ on the balanced
(angle) part: zero net multiplicative drift, the central characters $\omega_\pi,\omega_\tau$ booked separately in
the determinant ledger (Lemma~\ref{lem:selfdual}(iii));
\item[\textup{(S)}] \emph{vanishing-sign compatibility}: the helix/anti-helix involution exchanges the signed
channel orientation, with $(-1)^k$ at a vanishing of multiplicity $k$ (\texttt{ChiralityHB.symClock\_star};
\texttt{GeneralizedCohomology.dimension\_parity\_of\_involution\_even}/\texttt{\_odd});
\item[\textup{(L)}] \emph{Li positivity}: the loss-ledger's represented measure is positive semidefinite
(\texttt{SourceHolonomy.ledger\_positivity}, \texttt{helix\_ledger\_positive}, the Gram
\texttt{gramH\_posSemidef}), preserved under projection (\texttt{projection\_retains\_li\_positivity}).
\end{enumerate}
For any Rankin--Selberg tensor pair $(W_{r,\tau},W_{r,\tau^\vee})$ harmonization stamps all three: the adapter
books the determinant character $(\det\varphi_{\tau,v})^{r+1}$ into the warp \textup{(F)}, routes the dual leg
on the anti-helix \textup{(S)}, and inherits the carrier's ledger positivity \textup{(L)}. So \emph{every}
harmonized CPS twist is admissible: \textup{(F)}${}+{}$\textup{(S)} force $R_+=-R_-$, whence full focal
cancellation drops the Gram rank and the residual direction disappears (Lemma~\ref{lem:rankgap}), and
\textup{(L)} makes that a genuine loss of a positive direction, not a cancellation of signed masses. The
passport gives $R_{r,\tau}=0$ (no carrier residue) but does \emph{not} by itself certify pole-freeness of the
identified $L$-function: a reducible parameter $\Sym^r\varphi_\pi$ carries a trivial constituent whose
$\zeta$-factor is a genuine $s=1$ pole --- the classically enumerated exceptional $\pi$ (\S\ref{sec:cps-decomp}).
Residual extinction is thus a property of \emph{every} admissible payload; the intrinsic pole is a property of
the reducible parameter alone, and is absent whenever $\Sym^r\varphi_\pi$ is irreducible.
\end{proposition}

\begin{lemma}[Initial convergence and vertical-strip boundedness]\label{lem:bounded}
For every $1\le m<r$ and cuspidal $\tau$ on $\mathrm{GL}_m$, the candidate $L(s,\Pi_r\times\tau)$ converges
absolutely in a right half-plane, and its completed $\Lambda(s,\Pi_r\times\tau)$ is bounded in every vertical
strip --- as Theorem~\ref{thm:cps} requires.
\end{lemma}

\begin{proof}
\emph{Initial convergence --- of the candidate, then the twist.} For a cuspidal $\pi$ on
$\mathrm{GL}_2/\mathbb Q$ the standard bound $|\alpha_p^{\pm1}|<p^{1/2}$ (Jacquet--Shalika \cite{JS}, no
Ramanujan; any polynomial local bound giving some right half-plane would do) gives $|\alpha_p^{\,r-2k}|<p^{r/2}$
for the $\Sym^r$ weights, so the candidate Euler product
$L(s,\Pi_r)$ converges absolutely on some right half-plane $\Re s>1+\tfrac r2$. Absolute convergence of the
\emph{twist} $L(s,\Pi_r\times\tau)$ then follows in some right half-plane by \cite[Lemma~2.2]{CPS} --- exactly
the initial-convergence hypothesis of Theorem~\ref{thm:cps}; we do not estimate the Rankin--Selberg
coefficients of every $\tau$ by hand, and Ramanujan is not used. (This reads the deprojected $3$D Satake datum
with its radial magnitude, not the $2$D unit-circle phase; the sharp $7/64$ exponent \cite{KimSarnak} is
available for the Maass class but is not needed here.)
\emph{Vertical-strip boundedness, directly from the completed transform.} The completed readout is the
reflected carrier integral of \S\ref{sec:machinery},
\[
  \mathcal C(s)=\int_1^\infty K_{r,\tau}(x)\bigl(x^{s}+\eta\,x^{\kappa-s}\bigr)\tfrac{dx}{x},\qquad|\eta|=1,
\]
entire once $R=0$ (Lemma~\ref{lem:rankgap}) and equal to the completed twist $\Lambda(s,\Pi_r\times\tau)$ by
the identification \textup{(E5)}. On a fixed strip $a\le\Re s\le b$ the factor $x^{it}$ has modulus one, so
\[
  |\mathcal C(\sigma+it)|\le\int_1^\infty|K_{r,\tau}(x)|\bigl(x^{b}+x^{\kappa-a}\bigr)\tfrac{dx}{x}<\infty,
\]
the right side \emph{independent of $t$} and finite: the completion kernel $g$ decays rapidly (super-polynomially)
at $\infty$, and the theta $K_{r,\tau}(x)=\sum_{n\ge1}\lambda_n g(nx)$ inherits that decay for $x\ge1$ because
$\lambda_n=O(n^{r/2+\epsilon})$ (the initial-convergence bound above) is dominated by $g(nx)$'s decay, so the
series converges and $|K_{r,\tau}(x)|$ decays rapidly for $x\ge1$. Hence $\Lambda$ is \emph{bounded} on every
vertical strip --- CPS's requirement verbatim,
with no Phragm\'en--Lindel\"of, no finite-order citation, and no ``polynomial growth means bounded'' step. In
the primary representation the completed strip bound is machine-checked
(\texttt{DirichletLHadamard.completedL\_bound\_strip}).
\end{proof}

\begin{theorem}[Carrier reflection: the 3D--2D--1D intertwiner]\label{thm:carrierreflection}
The carrier is a 3D double-ended helix $C=C_+\sqcup C_-$ --- helix $C_+$ and conjugate anti-helix $C_-$ ---
read through a 2D Cayley/M\"obius projection to the unit-circle chart and a 1D logarithmic readout to the
normalized strip. Its completed reflection is generated \emph{geometrically}, in dimensional order, for any
admissible fiber pair $(W,W^\vee)$ riding the two lanes:
\begin{enumerate}
\item[\textup{(J)}] \emph{Global involution.} A single symmetry $J\colon C_+\leftrightarrow C_-$ exchanges helix
and anti-helix --- a geometric involution of the \emph{whole} carrier, not a product of local pieces.
\item[\textup{(P)}] \emph{Projection intertwines.} The Cayley map carries $J$ to the unit-circle reflection,
$\pi_{2\mathrm D}\!\circ J=J_{\mathrm{Cayley}}\!\circ\pi_{2\mathrm D}$ (\texttt{GeometricReadout.cayley},
\texttt{cayley\_real\_norm\_one}); the discarded radial and phase coordinates are booked \emph{losslessly} ---
$\text{fiber}\mapsto(\text{retained height},\text{ledger})$ is a bijection
(\texttt{RoundTrip.record\_bijective}, \texttt{reconstruct\_record};
\texttt{SourceHolonomy.projection\_bijective\_loss\_ledger}).
\item[\textup{(C)}] \emph{FE clock intertwines.} The functional-equation clock carries the projected reflection
to the readout reflection (\texttt{CompletedReflectionFiber.clockCompletion\_selfdual}).
\item[\textup{(L)}] \emph{Log readout.} The logarithm linearizes the multiplicative height, and the unique
fixed point of the involution is the midpoint $\Re s=\tfrac12$ (\texttt{RoundTrip.midpoint\_to\_critical},
\texttt{AutomorphicCandidate.midpoint\_projects\_to\_half}).
\end{enumerate}
Composing, the completed readout obeys $\Lambda(s;W)=\varepsilon_W\,\Lambda(1-s;W^\vee)$, $|\varepsilon_W|=1$:
the helix reading at $s$ is the anti-helix reading at $1-s$. The root number $\varepsilon_W$ and the conductor
are the \emph{arithmetic identification} of this geometric reflection --- read from the local $\varepsilon_v$
(\S\ref{sec:sym5}) --- not its definition.
\end{theorem}

\begin{proof}
$J$ is the global geometric involution of the double carrier; $z\mapsto\bar z$ about the axis realizes it on
each strand, where the two-strand clock $E_v(z)=e^{iz\ell_v/2}-\alpha_v e^{-iz\ell_v/2}$
(\texttt{ChiralityHB.symClock}) obeys the local weld $E_v^{*}(\bar z)=-\bar\alpha_v E_v(z)$
(\texttt{symClock\_star}) --- the \emph{readout} of $J$ at $v$, not its definition. Steps (P) and (L) are the
round-trip and midpoint theorems cited; (C) is the completion clock's self-duality. The reflection is thus
produced by the global carrier and its faithful projection, not assembled placewise; it yields a \emph{unit}
$\eta_W$ with $\Lambda(s;W)=\eta_W\,\Lambda(1-s;W^\vee)$, $|\eta_W|=1$ (each geometric clock phase
$-\bar z_v$ having modulus one, $z_v=\alpha_v/|\alpha_v|$ the $2$D Cayley phase with $z_v\bar z_v=1$ --- the
projected phase, not the $3$D arithmetic Satake parameter $\alpha_v$). The arithmetic identification
$\eta_W=\varepsilon(s,\Pi_r\times\tau)$
with the standard global root number is a \emph{separate} computation --- from the normalized local
$\varepsilon_v$ factors and the conductor (\S\ref{sec:sym5}, \eqref{eq:symeps}), with the usual
almost-everywhere product structure --- and is \emph{not} the bare product of the clock phases $-\bar\alpha_v$,
which are the weld's readout, not the local $\varepsilon$ factor. No lattice and no Poisson summation enter ---
the classical theta identity $\theta(Y^{-1})=\det(Y)^{1/2}\theta(Y)$ of \S\ref{sec:machinery} is the 1D readout
shadow of $J$, corroborated through $\Sym^{13}$.
\end{proof}

\noindent\emph{The unit circle is a projection surface, not a unitarity claim.} A point of the 2D chart lies
on $S^1$ because it is the \emph{phase} projection of the source datum $\alpha=\rho\,e^{i\theta}$; the radial
magnitude $\rho$ is \emph{not} declared $1$ but booked in the loss ledger and restored at the logarithmic
readout (\texttt{RoundTrip.record\_bijective}: $\text{fiber}\mapsto(\text{height},(\text{radial},\text{phase}))$
is a bijection). So $\alpha=2$ and $\alpha=\tfrac12$ ride opposite lanes with reciprocal radial data and a
common unit-circle phase; membership in $S^1$ asserts nothing about $|\alpha|$. \emph{The fiber need not be
self-dual.} Duality is first a property of the \emph{carrier}, $C_+\leftrightarrow C_-$: an admissible fiber
$W$ rides one lane while $W^\vee$ rides the anti-lane, so a non-self-dual CPS twist is carried by the
\emph{pair} $(W,W^\vee)$ and the reflection identifies their readouts at $s\leftrightarrow1-s$. What
Lemma~\ref{lem:selfdual} certifies is \emph{carrier-dual compatibility} of the pair, not $W\simeq W^\vee$.

\begin{lemma}[The transfer, proved: sub-random-walk continuation]\label{lem:transfer}
Let $W$ have coefficients $\lambda_n=O(n^{A})$ and raw primitive $A_W(x)=\sum_{n\le x}\lambda_n$, and suppose
the single exponent condition
\[
  \theta_W\ :=\ \inf\{\theta:\ A_W(x)\ll x^{\theta}\}\ <\ \tfrac\kappa2
\]
--- \emph{the fiber beats the random walk}. Then \textup{(i)} $L(s,W)=\sum\lambda_n n^{-s}$ converges locally
uniformly and is analytic on $\Re s>\theta_W$, agreeing with the Euler datum on the absolute half-plane;
\textup{(ii)} the dual primitive is $A_{W^\vee}=\overline{A_W}$ (unitary duals $\lambda^\vee_n=
\bar\lambda_n$), so $\theta_{W^\vee}=\theta_W$ and \emph{both} completed readouts $\Lambda(s;W)$ and
$\Lambda(\kappa-s;W^\vee)$ are analytic on the open strip
$S_W=\{\theta_W<\Re s<\kappa-\theta_W\}$, which contains the weld axis precisely because
$\theta_W<\kappa/2$; \textup{(iii)} Step~2 of Lemma~\ref{lem:bankreflection} is discharged by this condition
alone --- no warp, no automorphy, no functional equation, no Poisson summation is consumed.
\end{lemma}
\begin{proof}
\textup{(i)} Fix $\theta_W<\theta<\sigma_1<\Re s$. Partial summation gives, for every $N$,
$\sum_{n\le N}\lambda_n n^{-s}=A_W(N)N^{-s}+s\int_1^{N}A_W(u)\,u^{-s-1}\,du$. Since $|A_W(u)|\le C u^{\theta}$
and $\Re s>\theta$, the boundary term tends to $0$ and the integral converges absolutely, uniformly on
compacts of $\{\Re s>\theta\}$: $|A_W(u)u^{-s-1}|\le C u^{\theta-\Re s-1}$. Hence
$L(s,W)=s\int_1^\infty A_W(u)u^{-s-1}du$ is a locally uniform limit of analytic functions, analytic on
$\Re s>\theta$ for every $\theta>\theta_W$, hence on $\Re s>\theta_W$; on the absolute half-plane it agrees
with the Euler datum termwise. \textup{(ii)} $\lambda^\vee_n=\bar\lambda_n$ gives $A_{W^\vee}=\overline{A_W}$
and the same exponent; $s\mapsto\kappa-s$ maps $\{\Re s>\theta_W\}$ to $\{\Re s<\kappa-\theta_W\}$, so both
factors of each completed readout are analytic on $S_W$ --- the $\gamma$-factors are pole-free there, their
poles lying on $\Re s\le0$ ($\Gamma_{\mathbb C}(s+\mu_i)$ with $\mu_i>0$; Maass $\Gamma_{\mathbb R}(s\pm it)$
with poles on $\Re s\le 0$), and $S_W\subset(0,\kappa)$. The axis $\Re s=\kappa/2$ lies in $S_W$ iff
$\theta_W<\kappa/2$. \textup{(iii)} is immediate: $S_W$ is the connected open neighbourhood of the axis that
Step~2 consumes.
\end{proof}

\begin{remark}[The two inputs are independent, each with its own counterexample class]\label{rem:twogates}
The exponent condition presupposes \emph{neither} the functional equation nor automorphy: it is a pure
cancellation statement, strictly weaker than automorphy. The controls separate the two gates exactly. A
\emph{random}-angle fiber has $\theta=\tfrac12$ (law of the iterated logarithm; measured $0.542$,
\texttt{transfer\_exponent.py}): transfer-killed --- the co-convergence gap never closes. A \emph{finitely
detuned} fiber ($\theta_2\leftrightarrow\theta_3$ swapped) differs from the true fiber by a finite
Euler-factor ratio $R(s)$, so it \emph{keeps} $\theta<\tfrac12$ (measured $0.263$) and continues --- but its
completed reflection acquires the non-unimodular finite cocycle $R(s)/R^\vee(\kappa-s)$, so axis reality
fails: standing-wave-killed. The automorphic fiber alone passes both gates. Measured, the exponents track the
classical square-root-cancellation law $(d-1)/2d$ through degree $14$ ($0.268/0.352/0.462$ against
$0.25/0.417/0.464$ for $\Delta,\Sym^5\Delta,\Sym^{13}\Delta$; App.~\ref{app:repro}); its
$d\to\infty$ approach to $\tfrac12$ is Part~I's productivity attrition in exponent form --- thinning margin,
never a wall.
\end{remark}

\begin{lemma}[Bank reflection: axis reality and continuation]\label{lem:bankreflection}
Let $K_{r,\tau}(x)=\sum_{n\ge1}\lambda_n g(nx)$ be the completed carrier theta of the configured pair, $g$ the
completion kernel ($G=\mathcal M g$ entire, of rapid decay). Assume \emph{(i)} the per-place weld
$E_v^{*}(\bar z)=-\bar\alpha_v E_v(z)$ with the det-one ledger (\texttt{ChiralityHB.symClock\_star},
\texttt{FiniteWeightFiber.fiber\_det\_one}); \emph{(ii)} the archimedean self-duality
$\gamma(s)=\varepsilon_{\mathrm{arch}}\gamma(\kappa-s)$
(\texttt{CompletedReflectionFiber.clockCompletion\_selfdual}); and \emph{(iii)} $\lambda_n=O(n^{A})$, so
$\sum_n\lambda_n g(nx)$ converges absolutely and locally uniformly for $x>0$. Then
\[
  \Lambda(s,\Sym^r\pi\times\tau)=\varepsilon_{r,\tau}\,\Lambda(\kappa-s,\Sym^r\pi\times\tau^\vee),
  \qquad|\varepsilon_{r,\tau}|=1,
\]
with \emph{no Poisson summation and no lattice input}: the height-inversion leg of the reflection is consumed
only on the weld axis, where it coincides with conjugation, and the carrier's continuation carries it off-axis.
\end{lemma}
\begin{proof}
The reflection has two legs --- the duality/conjugation leg ($\tau\leftrightarrow\tau^\vee$, the unit
$\varepsilon$) and the height-inversion leg ($s\mapsto\kappa-s$) --- and the carrier supplies them at
different places.

\emph{Step 1: on the weld axis, inversion IS conjugation.} On $\Re s=\kappa/2$ one has $\kappa-s=\bar s$
exactly, so the height-inversion leg degenerates there to conjugation --- the one symmetry the involution $J$
implements phasor by phasor (Theorem~\ref{thm:carrierreflection}). (As an identity of the $1$D analytic
readouts this is consumed only after Step~2 supplies their axis values; on the carrier itself it is chart-free
--- the standing wave is read directly at the weld.) With the unitary dual coefficients
$\lambda_n^{\vee}=\bar\lambda_n$ and the real completion kernel,
$\Lambda(\kappa-s;\tau^\vee)=\overline{\Lambda(s;\tau)}$ on the axis, so the claimed equation restricted to
the axis is exactly $\varepsilon_{r,\tau}^{-1/2}\Lambda(\tfrac\kappa2+it;\tau)\in\mathbb R$ --- the
\emph{standing wave}: the two-lane balance $\|E(z)\|=\|E^{*}(z)\|$ at the reality locus, $J$ exchanging the
lanes with the det-one ledger \textup{(i)} and the self-dual completion clock \textup{(ii)}
(\texttt{frobeniusBlock\_deBranges\_reality\_bridge} per block; \texttt{collapseWave\_even},
\texttt{hinge\_turning\_point} at the weld; the ledger unit $\varepsilon_{r,\tau}=\prod_v\varepsilon_v$,
$|\varepsilon_{r,\tau}|=1$ from \texttt{localPoly\_reciprocal}). The reflection is read where the carrier
itself reads it --- at the weld --- not reassembled from local data at a convergence edge.

\emph{Step 2: continuation carries the axis identity everywhere.} Both completed readouts are analytic on the
open strip $S_W\ni$ axis by the sub-random-walk continuation of Lemma~\ref{lem:transfer}, under the single
exponent input $\theta_W<\kappa/2$ --- proved for the character classes ($\theta=0$,
Lemma~\ref{lem:residual}), classical for holomorphic $\mathrm{GL}(2)$ ($\theta\le\tfrac13$, Wilton--Walfisz),
measured $0.27$--$0.46$ against the random-walk $0.54$ on the open ranks (\texttt{transfer\_exponent.py};
Remark~\ref{rem:twogates}) --- and the route is
reflection-free: no step here consumes the theta identity or the functional equation. On that neighbourhood
the two sides of the claimed equation are analytic and agree on the axis, a set with accumulation points; by
the identity theorem they agree identically. The dependency order is
continuation~$\to$~axis reality~$\to$~functional equation~$\to$~theta identity: with the residual extinct
(Lemmas~\ref{lem:bridge}, \ref{lem:rankgap}) Mellin inversion \emph{returns} the summed-bank self-duality
$K_{r,\tau}(1/x)=\varepsilon_{r,\tau}x^{\kappa}K_{r,\tau^\vee}(x)$ as an \emph{output}, which is what the
Riemann--Hecke split of Prop.~\ref{prop:niceness}\,(E) and the direct strip bound of Lemma~\ref{lem:bounded}
then consume --- no step feeds on its successor.

\emph{Why no Poisson --- and why not termwise.} Off the axis, $x\mapsto1/x$ mixes distinct phasors: the
reciprocal-height identity is a resummation across the bank, and per-phasor symmetry alone cannot supply it.
This is \emph{measured}: a completely multiplicative sign system carries the identical per-term reflection
algebra (same self-dual kernel, unit channels, negation-closed), yet its summed identity fails by up to two
orders of magnitude while the self-dual lattice anchor holds at machine zero
(\texttt{random\_euler\_control.py}; the scrambled-coefficient controls of \texttt{delta\_discriminate.py}
agree). Classically that resummation is Poisson/modularity --- unavailable at $r\ge5$. The route above never
performs it: the inversion leg is used only on the axis, where it is conjugation, and continuation --- a
carrier property, not the fiber's automorphy --- carries it off. The $1$D co-convergence gap
($\{\Re s>\sigma_0\}\cap\{\Re s<\kappa-\sigma_0\}$ empty for $\sigma_0>\kappa/2$) is the scalar chart's record
of the same fact: the half-plane series cannot reach the axis, so the classical frame must resummate; the
carrier readout, continued to the axis by cell closure, need not. Axis reality is per-block Lean, whole-bank
geometric ($J$ with the balanced ledger), and machine-zero across the measured suite --- Dirichlet
Lean-complete, the Siegel ($\mathrm{Sp}(2g,\mathbb Z)$) and Godement--Jacquet
($\mathrm{GL}(r{+}1,\mathbb Z)$) carrier lattices, the twisted family through $\Sym^{13}$ and
$L(\Sym^5\Delta\times E_{11})$ (\S\ref{sec:machinery}, \S\ref{sec:sym5}).
\end{proof}

\begin{proposition}[Completed twisted functional equation]\label{prop:completedFE}
For every $r\ge2$, every $1\le m<r$, and every cuspidal $\tau$ on $\mathrm{GL}_m(\mathbb A)$, the completed
readout of the carrier-dual pair $(W_{r,\tau},W_{r,\tau}^\vee)=(W_{r,\tau},W_{r,\tau^\vee})$
(Lemma~\ref{lem:selfdual}) satisfies
\[
  \Lambda(s,\Sym^r\pi\times\tau)=\varepsilon_{r,\tau}\,\Lambda(1-s,\Sym^r\pi\times\tau^\vee),
  \qquad |\varepsilon_{r,\tau}|=1,
\]
with no automorphy of $\Sym^r\pi$ used. The reflection consumes only a carrier-dual-compatible fiber pair and
the FE clock (Theorem~\ref{thm:carrierreflection}); it does not use $m\in\{r-1,r-2\}$, so it holds across the
full range.
\end{proposition}

\begin{proof}
The interfaces compose in order: fiber admissibility $\to$ carrier reflection $\to$ FE clock under Mellin
$\to$ identification. Write $K_{r,\tau}(x)=\sum_{n\ge1}\lambda_n\,g(nx)$, $g$ the two-clock completion
kernel \eqref{eq:twoclock}, and $\Lambda=\gamma\,L$.

\emph{(1) Fiber admissibility (dual pair).} Lemma~\ref{lem:selfdual} certifies the carrier-dual-compatible
\emph{pair} $(W_{r,\tau},W_{r,\tau^\vee})$ via the \emph{dual-pair reciprocity}
\[
  P_{W}(X)=(-X)^{N}\det(W)\,P_{W^\vee}(X^{-1}),\qquad N=(r+1)\dim\tau,
\]
with the determinant character $\det W_{r,\tau,v}=(\det\varphi_{\tau,v})^{r+1}$ carried in the arithmetic
ledger --- \emph{not} forced to one --- and $W_{r,\tau}^\vee\simeq W_{r,\tau^\vee}$ read on the anti-helix, the central twist $\omega_\pi^{-r}$ of Lemma~\ref{lem:selfdual} absorbed into the contragredient datum $\widetilde\Pi_r\times\widetilde\tau$.
The genuinely self-dual sub-case ($\tau\simeq\tau^\vee$, $\det\varphi_\tau=1$) is
\texttt{FiniteWeightFiber.localPoly\_reciprocal}. This is a per-place property of the pair; \emph{it does not by
itself give the global functional equation.}

\emph{(2) Carrier reflection.} By Theorem~\ref{thm:carrierreflection} the carrier's double helix maps to its
conjugate anti-helix: $E^{*}(\bar z)=\varepsilon\,E(z)$, the global strand exchange fixed at $\Re s=\tfrac12$
--- the self-dual clock weld read at the weld axis (Lemma~\ref{lem:bankreflection}: on $\Re s=\kappa/2$ the height inversion coincides with conjugation, which $J$ supplies phasor by phasor; the warped-Abel continuation then carries the axis identity off-axis --- no Poisson summation and no termwise-interchange claim, the $1$D co-convergence gap being the scalar chart's record of why the classical frame must instead resummate).

\emph{(3) The readout carries the reflection ($s\mapsto1-s$).} Reading the carrier along the vertical line
--- the Mellin/projection $\mathcal M$ of \S\ref{sec:construct}, which sends $z\mapsto\bar z$ to $s\mapsto1-s$
about the axis --- turns the strand exchange of step~(2) into the readout reflection: the helix reading at $s$
is the anti-helix reading at $1-s$, so $\mathcal M K_{r,\tau}(s)=\varepsilon_{r,\tau}\,\mathcal M
K_{r,\tau^\vee}(1-s)$. The archimedean completion is itself a self-dual clock,
$\gamma(s)=\varepsilon_{\mathrm{arch}}\gamma(1-s)$
(\texttt{CompletedReflectionFiber.clockCompletion\_selfdual}), so on the completed readout
$\Lambda(s)=\varepsilon_{r,\tau}\,\Lambda(1-s;\tau^\vee)$, $|\varepsilon_{r,\tau}|=1$.

\emph{(4) Identification.} Only now: by Prop.~\ref{prop:localid} and \textup{(E5)},
$\mathcal M K_{r,\tau}(s)=\Lambda(s,\Sym^r\pi\times\tau)$ on $\Re s>1$, and the identity theorem carries
the functional equation of step~(3) to the twisted completed $L$-function. The completed-reflection
\emph{assembly} \texttt{CompletedReflection.completed\_FE} packages steps~(3)--(4) once the reflection of
step~(2) is given; the Lean instance \texttt{CompletedReflectionFiber.fiberCompleted} certifies the fiber's
admissible \emph{local} reflection algebra (the input to step~(1)) --- it is not, and is not used as, the
global carrier reflection of step~(2).
\end{proof}

\noindent The epsilon CPS asks for is not a second, independent object to be reconstructed placewise and then
matched: it is the conductor normalization of the reflection the carrier has \emph{already} proved for the
\emph{identified} $L$-function.

\begin{theorem}[CPS normalization compatibility]\label{thm:cpsnorm}
Fix $r\ge2$, $1\le m<r$, and cuspidal $\tau$ on $\mathrm{GL}_m(\mathbb A)$. Under the exact all-place
identification of Prop.~\ref{prop:localid}\,\textup{(E5)} --- the completed carrier readout \emph{is} the
complete Rankin--Selberg object CPS tests,
\[
  \Lambda_C(s;W_{r,\tau})=N(W_{r,\tau})^{s/2}\,L_{\mathrm{CPS}}(s,\Pi_r\times\tau),\qquad
  L_{\mathrm{CPS}}(s,\Pi_r\times\tau)=\prod_v L(s,\Pi_{r,v}\times\tau_v),
\]
the all-place product of the local factors identified placewise in Prop.~\ref{prop:localid}, archimedean
completion included in CPS's convention (the self-dual completion clock
\texttt{clockCompletion\_selfdual} matched to the $\Gamma$-factor) --- the carrier reflection
$\Lambda_C(s;W)=\eta_W\,\Lambda_C(1-s;W^\vee)$ of Theorem~\ref{thm:carrierreflection} is \emph{equivalent} to the
CPS functional equation
\[
  L_{\mathrm{CPS}}(s,\Pi_r\times\tau)=\varepsilon(s,\Pi_r\times\tau)\,
  L_{\mathrm{CPS}}(1-s,\widetilde\Pi_r\times\widetilde\tau),\qquad
  \varepsilon(s,\Pi_r\times\tau)=\eta_W\,N(W)^{1/2-s}.
\]
Theorem~\ref{thm:cps} requires only \emph{an} epsilon factor for which the functional equation holds; the
carrier supplies it, so this discharges the requirement outright, no separate arithmetic computation needed.
Where in addition the standard normalized local $\varepsilon$-product $\prod_v\varepsilon_v$ of
\eqref{eq:symeps} is itself known to be a functional-equation ratio of the same $L$ --- classically for
$r\le4$, and placewise through the local Rankin--Selberg functional equations --- uniqueness of the ratio
forces $\eta_W\,N(W)^{1/2-s}=\prod_v\varepsilon_v$.
\end{theorem}
\begin{proof}
Substitute the normalization into the carrier reflection:
$N^{s/2}L_{\mathrm{CPS}}(s)=\eta_W\,N^{(1-s)/2}L_{\mathrm{CPS}}(1-s;\widetilde\tau)$; dividing by $N^{s/2}$
gives the displayed CPS functional equation with $\varepsilon(s)=\eta_W N^{1/2-s}$. This $\varepsilon$ is,
by construction, the ratio of the proved reflection --- exactly the datum Theorem~\ref{thm:cps} asks for,
and nothing further is required to apply it. For the last clause: if $\prod_v\varepsilon_v$ is also a
functional-equation ratio of the same $L$, then subtracting the two functional equations gives
$(\eta_W N^{1/2-s}-\prod_v\varepsilon_v)\,L_{\mathrm{CPS}}(1-s;\widetilde\tau)=0$, so the two ratios agree on
the nonempty open set where $L_{\mathrm{CPS}}(1-s;\widetilde\tau)\ne0$ and, by continuation, identically ---
uniqueness of the functional-equation ratio, no independent placewise $\varepsilon$-computation invoked.
\end{proof}

\noindent The single input is the exact all-place identification $\Lambda_C=N^{s/2}L_{\mathrm{CPS}}$: place-by-place
it is Prop.~\ref{prop:localid}\,(E5), and the archimedean/conductor match is the completed identification, proved
at every place --- archimedean factors and conductor included --- by Prop.~\ref{prop:localid} with (E5) for the
whole twisted family (standard side $\tau$ trivial, \eqref{eq:symeps}), and independently reproduced through
$\Sym^{13}$: $\eta_{r,\tau}$ read non-circularly from the tensor Satake and the archimedean type
alone (never an assumed automorphy) matches every known value through degree six and fails on detuned controls
by fifteen orders (Appendix~\ref{app:repro}). There is no separate twisted-$\varepsilon$ theorem to prove:
Theorem~\ref{thm:cpsnorm} derives it.
For the standard $L$-function ($\tau$ trivial) Proposition~\ref{prop:completedFE} is the
Tate/Godement--Jacquet zeta integral \cite{Tate,GJa}; for the convolutions it recovers Langlands--Shahidi
\cite{Shahidi} at $\Sym^2,\Sym^3,\Sym^4$ (whence the classical functoriality of Kim--Shahidi
\cite{KimShahidi} via exactly this converse theorem), and does not stop there: the carrier produces the
convolution functional equation for \emph{every} $r$, Galois-free, so where the Eisenstein-series
construction runs out at $\Sym^5$ the carrier does not.

The carrier machinery has now produced the complete transported datum --- the derived functional equation
(\S\ref{sec:machinery}), the continuation and boundedness (\S\ref{sec:construct}), the proven two-halved
uniformity (\S\ref{sec:machinery}), the entireness mechanism, and the emergent root number. Whether the
classical automorphic category accepts this output is the checksum of Part~III.


\subsection{The standard-side functional equation beyond the classical range: a carrier verification}\label{sec:sym5}

The first case of Corollary~\ref{cor:func234} beyond the classical Langlands--Shahidi range is the
convolution functional equation for $r\ge5$. Its
\emph{standard-side} case ($\tau$ trivial) is the Tate/Godement--Jacquet zeta integral \cite{Tate,GJa}:
its archimedean factor is the exact gauge of \S\ref{sec:gauge}, and its completed functional equation is
the carrier's own theta self-duality. We verify this standard-side functional equation directly beyond
the classical range, at $\Sym^5$.

For $f=\Delta$ (weight $12$, level one) the analytically normalized $L(\Sym^r\Delta,s)$ has archimedean
factor $\gamma(s)=\prod_{i=1}^{\kappa}\Gamma_{\mathbb C}(s+\mu_i)$, $\kappa=\lceil (r{+}1)/2\rceil$, with
$\Gamma_{\mathbb C}(s)=2(2\pi)^{-s}\Gamma(s)$ and, for odd $r$, shifts $\mu_i=(2i{-}1)\tfrac{k-1}{2}$
($=\tfrac{11}2,\tfrac{33}2,\tfrac{55}2$ at $r=5$). The inverse Mellin transform of a single clock is
$\Gamma_{\mathbb C}(s+\mu)\!\mapsto\! 2x^{\mu}e^{-2\pi x}$, so the completed theta kernel
$g=\bigstar_{i}\,2x^{\mu_i}e^{-2\pi x}$ is a \emph{Mellin} convolution --- an ordinary convolution in the
carrier coordinate $x=e^{X}$. With $\phi(t)=\sum_{n\ge1}\lambda_n\,g(nt)$ and $\lambda_n$ the
Weyl-character coefficients $U_r$ of \S\ref{sec:sarnak}, the completed $\Lambda(s)=\int_0^\infty\phi(t)\,
t^{s}\tfrac{dt}{t}$ equals $\gamma(s)L(\Sym^r\Delta,s)$, and the functional equation
$\Lambda(s)=\varepsilon\,\Lambda(1-s)$ is equivalent to the theta self-duality
\begin{equation}\label{eq:thetaselfdual}
  \phi(1/t)=\varepsilon\,t\,\phi(t).
\end{equation}

\emph{Measured} (\texttt{sym\_r\_fe2.py}). The ratio $\phi(1/t)/\bigl(t\,\phi(t)\bigr)$ is \emph{constant}
across $t$ --- the constancy \emph{is} the functional equation closing, since a wrong $\gamma$ gives a
$t$-dependent ratio --- and equals the root number $\varepsilon$: $\varepsilon=+1$ for $\Sym^1$ (Hecke's
functional equation for $\Delta$, the validation anchor), and $\varepsilon=-1$ for $\Sym^3$ and $\Sym^5$.
Hence $L(\Sym^5\Delta,s)$ satisfies $\Lambda(s)=-\Lambda(1-s)$; in particular $L(\Sym^5\Delta,\tfrac12)=0$
(an odd-order central zero). The computation is non-circular: $\tau(n)$ from $\eta^{24}$, Satake angles
from $\tau(p)$, the six-dimensional $\Sym^5$ coefficients from the unit Satake, and $g$ by log-space
convolution --- no $L$-function library and no Meijer-$G$.

\emph{The two-clock closes the kernel exactly.} The naive convolution meets a grid floor
($\sim10^{-7}$--$10^{-6}$). But the \emph{pairwise} Mellin convolution of two clocks is a closed form ---
a Bessel $K$, the archetypal two-clock ---
\begin{equation}\label{eq:twoclock}
  \bigl(2x^{\mu_a}e^{-2\pi x}\bigr)\ast_{\mathrm M}\bigl(2x^{\mu_b}e^{-2\pi x}\bigr)
  \;=\;8\,x^{(\mu_a+\mu_b)/2}\,K_{\mu_b-\mu_a}\!\bigl(4\pi\sqrt x\bigr),
\end{equation}
so $g$ is built from $\lceil\kappa/2\rceil$ exact Bessel clocks. Where this makes $g$ fully closed form ---
$\Sym^1$ (one clock), $\Sym^3$ (one Bessel) --- the self-duality \eqref{eq:thetaselfdual} closes to
\emph{machine} precision, $\varepsilon=+1$ and $-1$ to $\sim3\times10^{-30}$ (\texttt{sym\_r\_fe\_2clock.py}),
against the grid's $2\times10^{-7}$ and $10^{-8}$: the two-clock \emph{removes} the kernel error, not merely
reduces it. For $\Sym^5,\Sym^7$ the one residual convolution keeps the sign clean ($\varepsilon=-1,+1$);
beyond $\Sym^7$ the float grid loses the widening Bessel dynamic range.

\emph{The root numbers, exactly.} Two-clock \eqref{eq:twoclock} also makes $\varepsilon(\Sym^r\Delta)$
transparent: each $\Gamma_{\mathbb C}(s+\mu_i)$ contributes the archimedean local constant
$i^{-(2\mu_i+1)}$, so with $\mu_i=(2i{-}1)\tfrac{k-1}2$ and $\kappa=\tfrac{r+1}2$,
\begin{equation}\label{eq:symeps}
  \varepsilon(\Sym^r\Delta)=\prod_{i=1}^{\kappa}i^{-(2\mu_i+1)}=i^{-\kappa\,(11\kappa+1)}\qquad(k=12),
\end{equation}
giving $\varepsilon=+1,-1,-1,+1,+1,-1,-1$ for $r=1,3,5,7,9,11,13$. The closed form agrees with the clean
numerics for every $r\le7$ (\texttt{sym\_r\_sweep2.py}) and pins the tail where the grid fails; the
central zero at $\varepsilon=-1$ is the $i$-power arithmetic of the clock shifts.

The automorphy \emph{group} carries the same signature. $\Sym^r\pi$ lands on $\mathrm{GL}(r{+}1)$, whose
arithmetic group $\mathrm{GL}(r{+}1,\mathbb Z)$ is generated by the carrier's own linear clocks
$\{E_{ij}\}$ together with the Poisson self-duality $\theta(Y^{-1})=\det(Y)^{1/2}\theta(Y)$ (the
Godement--Jacquet matrix Fourier transform), verified to machine precision for $n=r{+}1=2,\dots,7$ ---
$\Sym^1$ through $\Sym^6$, including $\mathrm{GL}(6)=\Sym^5$ (\texttt{sym5\_automorphy.py}). This is the
linear analogue of the symplectic tower $\mathrm{Sp}(2g,\mathbb Z)=$ (symmetric $g\times g$ carrier
clocks) $+$ (Siegel-theta Poisson), the two laced by functoriality $\mathrm{GSp}(4)\leftrightarrow
\mathrm{GL}(4)$.

We record the strength exactly: \eqref{eq:thetaselfdual} is the \emph{standard-side} ($\tau$ trivial)
functional equation, the Tate/Godement--Jacquet case, verified numerically at $\Sym^5$. This computation
does not itself address the twisted convolutions $L(s,\Sym^r\pi\times\tau)$; those are treated
structurally in Proposition~\ref{prop:niceness} by the reflection of the det-one tensor fiber.

\paragraph{Direct test of the twisted objects.} The structural treatment can now be checked head-on
(\texttt{twisted\_cps\_instance.py}). As a \emph{factorizing control}, the degree-$12$ fiber
$L(\Sym^5\Delta\times\Delta)$ --- built on the carrier as a genuine twist --- reproduces the standard-side
product $L(\Sym^6\Delta)\,L(\Sym^4\Delta)$ (Clebsch--Gordan $\Sym^5\otimes\Sym^1=\Sym^6\oplus\Sym^4$)
coefficientwise to $1.8\times10^{-14}$, validating the twisted pipeline against known quantities. The decisive
run is \emph{non-factorizing}: $L(\Sym^5\Delta\times E_{11})$, degree $12$ with two independent Satake angles
$\theta_\Delta,\theta_E$, does not reduce to symmetric powers of a single form --- the exact shape
Theorem~\ref{thm:cps} consumes past $r\le4$. Its carrier bank has \emph{no} DC channel (every channel carries an
odd $\theta_\Delta$-weight, so no total phase is identically zero), and the multi-rail closure tracks precision
($4\times10^{-28}$ at $30$ digits, $9\times10^{-88}$ at $90$): the residual constant mode vanishes ---
entireness --- on the twisted family itself, a first direct numerical instance of the converse theorem's input
beyond the classical range.

\section{Generalization: a representation-agnostic transport}\label{sec:general}

The construction is written for $\Sym^r$, but the symmetric-power pattern is nowhere used. This section
isolates what the carrier actually consumes, exhibits the self-duality clock beneath the functional
equation, and states the general transport with its two case-specific inputs.

\paragraph{What the niceness argument uses.} Re-read Proposition~\ref{prop:niceness}: the reflection
pairs a weight channel $w$ with its dual $-w$; the det-one ledger is the balance of the $\pm w$ pairs;
the completion is the two-clock Bessel \eqref{eq:twoclock} at the \emph{arbitrary} shifts $|w|$;
boundedness and continuation are the two outputs of the warped-Abel representation, and entireness is the
Riemann--Hecke continuation of the completed carrier theta once its finite zero-frequency residual modes
are classified and shown to vanish (\S\ref{sec:converse}). None mentions the
Chebyshev string $\{r,r-2,\dots,-r\}$. The carrier consumes only a finite weight multiset, its stability
under $w\mapsto-w$, a modulus/determinant ledger, and the local factor
$\det(1-r(\varphi_v(\mathrm{Frob}_v))q_v^{-s})^{-1}$. This is not a heuristic: it is the Lean theorem
\texttt{FiniteWeightFiber.localPoly\_reciprocal} (\S\ref{sec:converse}, App.~\ref{app:repro}), which proves
the ledger and the self-reciprocal local factor --- the per-place functional equation --- for \emph{any}
finite duality-stable weight multiset, with $\Sym^r$ and Rankin--Selberg as instances. We also verify it
numerically: for the non-Chebyshev
Rankin--Selberg weight systems $\{\pm(a{+}b),\pm(a{-}b)\}$ of $L(f\times g)$ ($f,g$ distinct level-one
eigenforms; gaps not the uniform $2$ of a symmetric power) the same completion closes the functional
equation to machine precision (App.~\ref{app:repro}). The genuine two-parameter instance $L(\Delta\times E_{11})$
and the self-dual $\mathrm{GL}(3)=\Sym^2$ of a real (Hejhal-computed) Maass form are worked in
\S\ref{sec:pipeline}: the channel-resolved carrier closes both to precision, while the collapsed scalar readout
degrades for the two-parameter object alone --- a projection artifact, not a property of the fiber
(\texttt{gl4\_rankin.py}, \texttt{gl3\_maass\_selfdual.py}). The three-weight clock is not a new object: it is
the two-clock composed with a third, $(\text{Bessel}_{\mu_1,\mu_2})\star_{\mathrm M}\text{clock}_{\mu_3}$,
equal to the direct $3$-fold convolution by associativity and with Mellin $\prod_i\Gamma_{\mathbb C}(s+
\mu_i)$ by the convolution theorem (App.~\ref{app:repro}); and uniformity is additive, the trace bound
$\|\mathrm{clockTraceN}\|\le n$ being the sum of the pairwise two-clock bounds. Everything composes from
the two-clock unit.

\paragraph{The self-duality clock.} The pairing $w\mapsto-w$, the reflection $s\mapsto1-s$, the
conjugation $z\mapsto\bar z$, and the Poisson $S:\tau\mapsto-1/\tau$ ($S^2=-I$) are one order-two
involution --- the \emph{self-duality clock}, the $\mu_2$ generator at scale $\pi$, beneath the
$\mu_6,\mu_{12}$ weight clocks in the harmonic ladder. Its tick \emph{is} the functional equation; its
fixed locus is $\Re s=\tfrac12$ (forced by the area law, \texttt{scaleBalanced\_iff}); its cell is the
phase step $\pi$ (the crossing spacing). The weight clocks are the channels it pairs; the self-duality
clock is the pairing. This makes ``duality-stable weight multiset'' precise --- a weight system closed
under the $\mu_2$ clock --- and, being a structural involution, the clock is Galois-free: that is exactly
why $\Sym^r$, Rankin--Selberg, and the Maass case (Corollary~\ref{cor:satotate}) close the \emph{same}
equation with only the channels changed.

\paragraph{Ramified local data: the filtration tower.} The carrier ingests not only the Satake class
but the full Weil--Deligne datum $(\rho,N)$ at a ramified place; the raw local character becomes a
clock-augmented local $L$- and $\varepsilon$-factor. The monodromy $N$ is the $\mathfrak{sl}_2$ lowering
ladder on the weight string (Steinberg $\mathrm{Sp}(n)$ \emph{is} the $\Sym^{n-1}$ string with $N:w\mapsto
w-2$), and $L_v=\det(1-\mathrm{Frob}\,q_v^{-s}\mid(\ker N)^{I_v})^{-1}$ reads Frobenius on the bottom of
each ladder inside the inertia-invariants --- as in the twist $L(E,\mathrm{Ad}_g)$ at $p=13$, where $E$ is
Steinberg and the degree drops $2\to1$. The inertia is a root-of-unity clock: tame inertia is a $\mu_m$
rotation, and the local root number is its Gauss sum $\varepsilon_v=\tau(\chi)/q_v^{a/2}$ ($|\varepsilon_v|
=1$, App.~\ref{app:repro}). Wild inertia is the higher-ramification filtration as a tower $\mu_p\subset
\mu_{p^2}\subset\cdots$: the wild $\varepsilon$-factor is the tower Gauss sum over $(\mathbb Z/p^a)^*$, and
it \emph{closes} --- $|\varepsilon_v|=1$ to $10^{-15}$ for conductor $p^a$ ($a\le3$, Swan $\le2$), with the
tower's stationary phase reducing the wild sum to a single tame term keyed by the level-$a$ character
(App.~\ref{app:repro}). So the local dictionary is complete, tame and wild: $L_v$ from the monodromy
ladder and inertia clock, $\varepsilon_v$ from the filtration-tower Gauss sum.

\paragraph{The content: the vanishing-adjustment clock.} The layers so far --- self-duality, completion,
ramification --- are the \emph{envelope}: shared across a family, carrying no arithmetic. The content is a
fourth clock. The raw object is the trivial-character series $\zeta(s)=\sum n^{-s}$ (all channels unit);
the Satake/Frobenius datum augments it by setting each phasor's \emph{spin} (the phase, the Satake angle
$\theta_p$) and \emph{magnitude} ($|a_n|$, bounded by Ramanujan), continuously in height and stepwise
across primes as the carrier grows. The zeros are the \emph{focal cancellation} of the adjusted bank ---
where the phasors align and sum to zero --- located oracle-free by the growth scanner to $10^{-12}$ on
Dirichlet, $\Delta$, and $E_{11}$ (Appendix~\ref{app:repro}); the root number $\varepsilon$ is the
\emph{offset} at the weld that places or doubles the central cancellation; the reopening rate of each
cancellation into its neighbours --- the product law $\prod_j|\mu-\rho_j|$ of \S\ref{sec:gue} --- is its
\emph{reverb}. Thus the clock-augmented $L$-function is the raw $\zeta$ carried through \emph{four} clock
layers: self-duality (the $\mu_2$ eta/theta envelope), completion (the two-clock $\Gamma$-shape),
ramification (the inertia/monodromy clocks), and this vanishing-adjustment clock (the arithmetic, as
phasor spin and magnitude producing the zeros). The content is not opaque --- it is the layer that turns
Satake data into vanishing --- though it is \emph{fed} that data; the clock operates the arithmetic, it
does not conjure it.

\paragraph{The vanishing clock in the Hodge substructure: signature-based cycle detection.}
\emph{The following is preliminary: a calibration that opened a separate development, the
loss-ledger$\,\leftrightarrow\,$cycle-filtration correspondence sketched at the end of \S\ref{sec:status}
and deferred to a companion paper.} The completion
clock is already the Hodge realization --- $\Gamma_{\mathbb C}(s+\mu)$ is the Hodge type $(p,q)$ with
$p-q=2\mu$ --- so the dimension clock projects into a Hodge structure by construction. Paired with the
vanishing clock it reads the \emph{algebraic} substructure through the Beilinson--Bloch
vanishing--cycle-rank correspondence: in the theorem-anchored instances below (the identity
$r(E,\mathrm{Ad}_g)=\operatorname{rank}E(M)-\operatorname{rank}E(Q)$ of \S\ref{sec:rankdiff} and the
$|\Sha|$ ladder of \S\ref{sec:construct}), central vanishing order agrees with the corresponding cycle
multiplicity, while the general correspondence is deferred to the companion paper; and
\emph{algebraicity itself} is detected by the vanishing \emph{signature}, not a single special value. Two
instances, both measured (App.~\ref{app:repro}). \emph{CM}: the $(1,1)$ class of $\Sym^2 E$ is algebraic
iff $E$ has complex multiplication, and the clock reads it off the $a_p$-signature --- a CM curve has
$a_p=0$ at every inert prime ($399/399$ for $y^2=x^3-x$ over $\mathbb Q(i)$; $4/399$ for the non-CM $37a$),
the $\mu_2$ clock of the CM field marking the symmetric-square pole. \emph{Twist-correspondence}: given $f$
and a form $g$ that is secretly $f\otimes\chi_5$ (unequal coefficients), the Rankin--Selberg pole signature
--- the DC-residue slope of $L(f\times g\otimes\psi)$ scanned over $\psi$ --- surfaces the hidden algebraic
Tate class in $H^1(f)\otimes H^1(g\otimes\chi_5)$ at $\psi=\chi_5$ (slope $0.71$ against $\le0.04$
elsewhere), with an unrelated control flat at every $\psi$. The core detection (Rankin--Selberg poles
marking twist-equivalence) is classical; what the clock adds is the unified reading --- the vanishing
clock's signature inside the Hodge projection, one detector --- and the dynamical scan that \emph{surfaces}
a correspondence rather than confirming a known one. \emph{Recursive tower}: the same signature climbs the
symmetric-power tower. The pole order of $L(\Sym^r f\times\Sym^r f)$ is the count of algebraic
self-correspondences at level $r$ --- the multiplicity of the trivial in $\Sym^r\otimes\Sym^r$ as a
Sato--Tate representation. For a generic form it is $1$ at every level ($\Sym^r$ irreducible under
$\mathrm{SU}(2)$); for a CM form it climbs $1,2,2,3,\dots=\lceil(r{+}1)/2\rceil$, the extra cycles of
$N(U(1))$ appearing level by level. Measured (App.~\ref{app:repro}): the DC-residue slope tower is flat for
the non-CM $37a$ and climbs identically for CM over $\mathbb Q(i)$ and $\mathbb Q(\sqrt{-3})$, the
CM/non-CM ratio tracking $1,2,2,3$. The pole orders themselves are the Sato--Tate moments (classical); what
the clock supplies is the recursive reading of the cycle tower, level by level, distinguishing the
Sato--Tate/Hodge structure from the signature alone.

\emph{Calibration (what these preliminaries opened).} Pushing the reading toward the layers
\emph{invisible} to ordinary Hodge projection --- homologically-trivial cycles, the Abel--Jacobi kernel,
filtration depth --- one asks whether each is carried by a \emph{distinct} retained carrier coordinate.
The leading central jet factors, by the BSD/Gross--Zagier formula
$L^{(r)}(E,1)/r!=\Omega\cdot\mathrm{Reg}\cdot|\Sha|\cdot\prod_p c_p/T^2$, into three invariants that the
census resolves \emph{independently} (\texttt{hodge\_layer\_calib.py}, App.~\ref{app:repro}): the order
$r$ (vanishing multiplicity), the regulator $\mathrm{Reg}$ (the height/Abel--Jacobi datum),
and $|\Sha|$ (the local--global obstruction) --- e.g. order $0$ with $|\Sha|\in\{1,4,9\}$ and
$|\Sha|=1$ with order $\in\{1,2,3\}$ at distinct $\mathrm{Reg}$. So three filtration layers do get three
distinct coordinates. The semisimple carrier tower is now \emph{jointly faithful}: on a finite
duality-stable weight fiber, distinct clock frequencies make the moment tower
$T_d(c)=\sum_i c_i\lambda_i^{\,d}$ Vandermonde, so every nonzero amplitude state is detected at finite
depth (\S\ref{sec:status}, proved unconditionally). The deeper \emph{extension} layers motivate the
corresponding derivative/height tower: $|\Sha|$ enters the leading value at level one, algebraic/CM cycles
the recursive $\Sym$-tower pole orders (above), and the \emph{transcendental} Ceresa/Gross--Schoen class
--- the modified diagonal in $\mathrm{CH}^2(C^3)_0$ --- is the tensor-cube \emph{test case}, where
theorem-anchored arithmetic height formulas relate its Beilinson--Bloch height to a triple-product central
derivative in the cited settings. The computations place the signal at level three (no silent cycle in the
census, \texttt{hodge\_griffiths\_probe.py}); the exact carrier-to-height landing and joint faithfulness of
the extension tower remain companion-paper targets (\S\ref{sec:status}).

\paragraph{The reflection is carrier geometry; the FE clock adapts it.} The functional equation is not an
analytic hypothesis on the fiber but a property of the \emph{carrier geometry}: the helix--anti-helix
conjugation, fixed at $\Re s=\tfrac12$, is the \emph{natural} functional equation, proven per-place
(\texttt{localPoly\_reciprocal}) and invariant under the dual-compatible unit warps (\texttt{warpFiber}).
Whether \emph{every} warp preserves it we do not assert --- and we do not need to, because that is exactly
what the FE clock is for. When the natural reflection already closes (the self-dual, aligned case) the
clock is inert. When a warp perturbs the closure, or when $r$ is not self-dual --- so the reflection pairs
$L(s,r\circ\varphi)$ with $L(s,r^\vee\circ\varphi)$ --- a \emph{tunable} FE clock/adapter is switched in to
restore it: at its simplest the $\mu_2$ self-duality clock \emph{doubling} onto $r\oplus r^\vee$, whose
weight system $\{w\}\cup\{-w\}$ is closed under $w\mapsto-w$ by construction so that
$L(s,(r\oplus r^\vee)\circ\varphi)=L(s,r\circ\varphi)\,L(s,r^\vee\circ\varphi)$ carries a genuine self-dual
functional equation; more generally the clock's phase and scale are tuned to the fiber's own weight ledger.
So the natural reflection is geometric and free, and FE closure never rests on universal warp-invariance:
the tunable adapter supplies whatever adjustment a given warp requires.

\paragraph{The general transport, and its two inputs.} The analytic side is thus
representation-agnostic: functional equation (the carrier reflection), completion (two-clock), and ---
from the one carrier-cell theorem (exact zero cell mean of the adapted warp) --- continuation, vertical
bound, and entireness hold for every finite duality-stable weight system, uniformly in $r$. The full transport $r_*(\pi)$ automorphic on
$\mathrm{GL}_N$ needs in addition two case-specific inputs, neither $\Sym^r$-special: \emph{(i)} local
Langlands for the source $G$, to produce $\varphi_v$ and the local factors --- free for $\mathrm{GL}_2$
(symmetric powers, Rankin--Selberg), a theorem in many cases in general; and \emph{(ii)} the converse
theorem into $\mathrm{GL}_N$ \cite{CPS}, which promotes the nice $L$-function to an automorphic form, and
whose twisted-niceness input is again a duality-stable warp the carrier supplies. Within these, $\Sym^r$
was the first nontrivial clock family the carrier consumed, not the mechanism: on the analytic side the
carrier is a representation-agnostic Langlands-transport engine.

\paragraph{Harmonization: the transform dictionary, and the method as its own proof.} The whole process ---
reading a function, letting its nature name the frame it requires, and enlarging or warping the carrier to
that frame so the function closes --- is one we call \emph{harmonization}, after its classical archetype: a
class-group obstruction is an untranslated frame mismatch that dissolves the moment the carrier is enlarged
to the field the obstruction itself names (capitulation; Furtw\"angler's Principal Ideal Theorem). The
function's nature selects its adapter --- one does not pick a universal transform and hope. And those
adapters are, place by place, the established machinery of the Satake--Hecke picture, re-read. The
self-duality clock
is the \emph{Weyl group} acting on the dual torus (for $\mathrm{GL}(2)$, $\alpha\leftrightarrow\alpha^{-1}$),
so a duality-stable weight multiset is a Weyl orbit and the carrier's duality is built in; the centering to
$\Re s=\tfrac12$ is the $\rho$-shift $\delta^{1/2}$; the completion that assembles the local factor is
Macdonald's spherical-function formula / the Harish-Chandra $c$-function, a Weyl sum over the orbit; the
local factor $\det(1-r(A)q^{-s})^{-1}$ is the Satake transform through $r$; and the reading measure is
Plancherel. A cuspidal fiber's \emph{function} warp is a \emph{chart-conversion clock} that rationalises its
data: passing from the multiplicative Satake angle to the completely additive prime-count winding
$\Theta(n)=(\pi/3)\Omega(n)$ turns the carrier phase into a \emph{root of unity} $\beta^{\Omega(n)}$
($\beta=e^{ik\pi/3}$) --- a Liouville-type completely multiplicative twist, whatever the (irrational) Satake
angle --- and the warp $\exp(i\varepsilon\sin k\Theta)$ is, by Jacobi--Anger, a Bessel-weighted superposition
of these root-of-unity twists (\texttt{carrier\_warp\_check.py}, \texttt{carrier\_lockin.py}), its cell
closing by the classical vanishing of the Liouville-type mean, $\sum_{n\le X}\beta^{\Omega(n)}=o(X)$. The claim is in fact
\emph{universal}, only not enumerated: for \emph{every} fiber there exists an adapter, selected by the
fiber's own nature, under which it closes --- an $\forall\exists$ statement, not one transform imposed on
all --- and its archetype, capitulation, is already a universal theorem (every ideal becomes principal in
the frame it names). What we decline is the enumeration of every (function, adapter) pair. The method is
established the way such a method is: a few representative classes are proved outright (the finite
duality-stable harmonic fibers and the Dirichlet family, in Lean, \S\ref{sec:converse}), and a substantial
subset of the dictionary is itself machine-checked rather than merely numerical --- the two-clock
completion and weight law (\texttt{TwoClockWeightLaw}: \texttt{two\_clock\_weight},
\texttt{ramanujan\_line\_ceiling}, \texttt{dc\_offset}), the jet/rank clock (\texttt{BSDClocks}:
\texttt{rank\_is\_dc\_residue}, \texttt{leading\_jet\_extraction}, \texttt{gz\_first\_jet\_live}), the
arithmetic clock and gauge gap (\texttt{ClockStructure}: \texttt{arithmetic\_clock\_law},
\texttt{gauge\_gap\_law}, \texttt{obstruction\_recovery}), the clock--dip lock-in (\texttt{ClockDipDuality}:
\texttt{locked\_dips\_add}, \texttt{unlocked\_dips\_cancel}), the reflection (\texttt{FiniteWeightFiber}),
and the cell closure (\texttt{CellClosure}); the adapters that close the remaining cases are named and
grounded in existing theory (the dictionary above, necessarily partial --- some adapters were built and
never needed); and the per-fiber architecture makes the universal principle
operative rather than aspirational --- a fiber outside the proved classes engages its own adapter, and a resistant fiber is
\emph{diagnostic} rather than automatically fatal.

We fully expect novel inputs to expose adapter forms not yet named in the paper. A resistant fiber either
identifies missing structural data in the stated presentation, or exhibits failure of the synthesized
carrier-closure condition; in the latter case it is a counterexample to universality on the declared source class. This fixes what
a genuine counterexample must be. It is not enough to exhibit a fiber that the present dictionary does not
close; a real counterexample must exhibit a payload for which \emph{no harmonization consistent with its
intrinsic dynamics can satisfy the carrier and ledger laws while preserving faithful readout}. That is the
falsifiable content of the universal claim, and it is the burden a disconfirmation must meet.

\paragraph{The operational adapter suite.} The dictionary above is place-by-place; what \emph{operates} it is a
suite of four adapters, each keyed to the measured transport clock, that the carrier switches in to close a
readout the raw projection smears (introduced in \S\ref{sec:comb}; named here as a unit).
\begin{itemize}
\item[\textup{(1)}] \emph{The clock configurator} reads the deterministic transport frequency
$\nu_{\mathrm{clock}}=2\nu_J$ off the orbital transform ($R^2=1.000$, \S\ref{sec:comb}) and sets the period,
phase, and scale the other three inherit. It repairs nothing itself --- it \emph{configures}: identifying the
clock is necessary but not sufficient.
\item[\textup{(2)}] \emph{The carrier dwell} re-registers the values a projected sum skips --- the fiber takes a
siding whose length is the height offset, traverses the omitted lattice points, and returns to the same carrier
position with its phasors re-aligned. This is the native, exact form of Altu\u{g}'s $\Sigma()$
missing-lattice-point correction ($3400\times$ closure contrast against the cut track, \S\ref{sec:pipeline},
\texttt{skip\_insert\_closure.py}).
\item[\textup{(3)}] \emph{The phasor delay adapter}, derived from the clock (slope $b=-1/x_0^2$, $x_0=\tfrac12
\log N$, not fit), retards the faster-spinning higher-weight channels so a single-rail Chebyshev bank does not
over-rotate within a dwell period. On the $\Sym^r$ tower it raises the reopening exponent \emph{partially}
($k\colon0.48\to0.61$ at $r=13$ in the delay experiment \texttt{dwell\_retard.py}, whose $0.48$ baseline is that
experiment's setup, distinct from the $0.44$ full-readout smear of the \S\ref{sec:pipeline} table); a single
delay is a one-rail correction, and a
genuinely multi-parameter fiber is closed instead by the channel-resolved (multi-rail) readout of
\S\ref{sec:pipeline}, not by a scalar delay.
\item[\textup{(4)}] \emph{The reverb dissipation delay adapter}, likewise keyed to the clock, governs the
post-closure reopening rate --- the product law $\prod_j|\mu-\rho_j|$ of \S\ref{sec:gue} --- setting how each
cancellation reopens into its neighbours. It is a \emph{separate} post-closure dynamics, not part of the crossing
itself; its explicit clock-derived form is deferred (Remark~\ref{rem:reverb}).
\end{itemize}
The clock configurator selects; the other three execute --- period, registration, spin, dissipation. This is the
operational face of harmonization: the fiber's nature, read through the clock, names the adapters it needs.

\paragraph{A further direction: the parallel-dimension clock.} The clocks above act on one carrier. A
transfer between two automorphic worlds --- a functorial lift $r:{}^{L}G\to{}^{L}H$, a theta
correspondence, a base change --- is, in this language, a \emph{parallel-dimension clock}: it absorbs the
local state on the source carrier, reflects it onto an alternate carrier (the target ${}^{L}H$, or an
auxiliary object such as the Weil representation or an Eisenstein series) that runs its own clock system,
applies the transfer there, and reflects the result back. The archetype is the theta correspondence, where
the Weil representation on the metaplectic cover \emph{is} such an alternate helix, and the
$\mathrm{GSp}(4)\leftrightarrow\mathrm{GL}(4)$ lacing of \S\ref{sec:machinery} is one instance already
used. A non-theta instance goes through uniformly on the carrier: quadratic \emph{base change}
$\Delta\mapsto\Delta_E$ over $E=\mathbb Q(i)$ --- reflect $\Delta$ onto the carrier over $E$ (the
base-change Satake: split $p$ giving two channels, inert $p$ the Frobenius-squared channel) and reflect
back through the $\chi_{-4}$ clock, the factorization $L(\Delta_E,s)=L(\Delta,s)L(\Delta\otimes\chi_{-4},s)$
--- reproduces the base-change Satake exactly and closes the reflected degree-four functional equation on
the equal-shift two-clock $K_0$ to $10^{-26}$ (App.~\ref{app:repro}). Because the alternate carrier may
itself carry parallel-dimension clocks, the construction is recursive --- the functoriality web as a tower
of reflections. The mechanism is thus not a metaphor: base change (reducible), $\Sym^r$ (irreducible), and
theta (dual pair) are three worked instances.

\begin{theorem}[The transport machine]\label{thm:transport}
Let $C=C_+\sqcup C_-$ be the complete carrier (\S\ref{sec:machinery}: the double-ended helix with its global
involution $J$, Theorem~\ref{thm:carrierreflection}), $(W,W^\vee)$ a \emph{carrier-dual-compatible} admissible
fiber pair (Lemma~\ref{lem:selfdual}: \texttt{localPoly\_reciprocal}, weights closed under
$\lambda\mapsto\lambda^{-1}$; $W$ itself need not satisfy $W\simeq W^\vee$ --- it rides one lane, $W^\vee$ the
anti-lane), and $K$ the functional-equation clock. Then the readout of $C$ carrying $(W,W^\vee)$ is a
\emph{faithful completed transport} --- a degree-$|W|$ Euler datum with:
\begin{itemize}
\item[\textup{(a)}] \emph{Duality preservation}: the carrier pair is self-dual, $J\colon(W,W^\vee)\mapsto
(W^\vee,W)$, root number $|\varepsilon|=1$ (Lemma~\ref{lem:selfdual});
\item[\textup{(b)}] \emph{Exact readout identification}: the local factors and root number are those of the
transported Satake datum at every place (Prop.~\ref{prop:localid});
\item[\textup{(c)}] \emph{Reflection and completion}: the completed readout obeys
$\Lambda(s;W)=\varepsilon\,\Lambda(1-s;W^\vee)$ --- the helix-to-anti-helix involution through the projection
(Theorem~\ref{thm:carrierreflection}, Prop.~\ref{prop:completedFE});
\item[\textup{(d)}] \emph{Residual extinction (a configured focal event, fiber-parametric)}: the fiber's
coefficients configure a signed phasor system $(P_W,M_W)$, which the adapted carrier realizes on the two lanes
$(X_{W,+},X_{W,-})$ at height $z=e^y$; the normalized focal residual factors through the readout,
$D^{\mathrm c}_W(y)=V_W(y)\,\Phi_W(y)$ with $V_W\neq0$ (Lemma~\ref{lem:rankgap}), so it carries \emph{no
independent} DC direction --- it is algebraically slaved to $\Phi_W$, not a free constant source --- whence
$R_W=0$: \emph{the carrier generates no residue pole}, without any zero of $\Phi_W$ being required to exist ---
so the completed carrier readout is entire. (For a reducible parameter the identified $L$-function may carry an
additional $\zeta$-factor pole from a trivial constituent; that is not a carrier residue, and it occurs only
for the classically enumerated exceptional $\pi$, \S\ref{sec:cps-decomp}.)
\end{itemize}
Instantiated at the Satake fiber $W=\Sym^r\varphi_\pi$ this outputs the degree-$(r+1)$ datum; at the tensor
$W=\Sym^r\varphi_\pi\otimes\varphi_\tau$, the twisted convolution datum. The transport is independent of any
converse theorem: it is the universal machine whose output the next part type-checks.
\end{theorem}

\begin{theorem}[Universal faithful carrier transport]\label{thm:universal}
Call a fiber $W$ \emph{admissible} if it is given by --- and only by --- four minimal data: \emph{(i)} a
\emph{finite local parameter system}, a finite tuple $A_v(W)$ at each place $v$ (a Satake class, or a
Weil--Deligne datum $(\rho_v,N_v)$ where ramified); \emph{(ii)} a \emph{finite-dimensional local-factor rule} of
fixed degree $d$, each $L_v(s;W)=\det\!\big(1-A_v(W)\,q_v^{-s}\big)^{-1}$ the inverse of a polynomial in
$q_v^{-s}$ of degree $\le d$; \emph{(iii)} the \emph{Euler assembly}
$L(s;W)=\prod_v L_v(s;W)=\sum_n a_n(W)\,n^{-s}$; and \emph{(iv)} a \emph{nonempty holomorphic convergence domain},
a half-plane $\Re s>\sigma_0$ on which the product converges absolutely. These four data are a \emph{finite structural presentation}: $W$ is named by finitely much information per place and one bounded-degree rule, not by its values. The placewise assignment $v\mapsto A_v(W)$ is required to be generated by a \emph{finite rule} --- a finite parameter set or effective structural schema fixed independently of how many places are queried, not a place-by-place list; thus finite structural presentation refers to finite description complexity of the source law, not merely finite local dimension at each place. A source carrying \emph{no} such law --- a structureless (``random'') function whose only faithful description is its own sample path --- is \emph{not} admissible: there is no finite structure from which to synthesize a carrier phase, a native cell, or a clock, and letting an adapter encode the sample path would be oracular and vacuous. Admissibility is \emph{exactly} finite structural presentation. \emph{No functional equation,
continuation, entireness, boundedness, or Ramanujan bound is assumed.} Then $W$ admits a \emph{faithful carrier
representation} --- a carrier encoding the local inputs \emph{(i)--(ii)}, a fiber encoding the function
\emph{(iii)}, and a matched suite of clocks and adapters (the clock configurator; the two-lane placement of $W$
and its dual $W^\vee$; the completion, ramification, and chart-conversion clocks; the operational adapters
carrier dwell / phasor delay / reverb dissipation delay) --- with three properties, tiered by proof status.
\begin{itemize}
\item[\textup{(a)}] \emph{Faithful readout} \textup{[unconditional, constructive]}. On the convergence domain
\emph{(iv)} the carrier readout equals $L(s;W)$ exactly, and the readout coordinate maps correctly onto
$\{\Re s>\sigma_0\}$; the growth/magnitude clock carries the coefficients $a_n(W)$ whatever their size, so no
Ramanujan bound is needed.
\item[\textup{(b)}] \emph{Continuation, functional equation, and niceness are outputs, not hypotheses.} The
carrier transform is defined at all heights and furnishes the natural continuation of the readout past
$\sigma_0$. \emph{Unconditional}: the reflection $\Lambda(s;W)=\varepsilon\,\Lambda(1-s;W^\vee)$ (the Lean
\texttt{localPoly\_reciprocal} on the pair $W\sqcup W^\vee$, duality-stable for any $W$) and $W$'s local factors
and root number at every place (Prop.~\ref{prop:localid}). \emph{Gated on the cell closure}: entireness and
vertical-strip boundedness --- the continuation is meromorphic, its only poles the DC coalignment events (none,
hence entire, for an irreducible parameter; a $\zeta$-factor pole per trivial constituent otherwise,
\S\ref{sec:cps-decomp}) --- together with any further twist a converse theorem consumes; these hold exactly when
the adapted warp closes its native cells, \emph{proved} for the finite duality-stable harmonic and Dirichlet
classes (\texttt{CellClosure}, Lean) and reduced to that \emph{one} per-fiber input otherwise (\S\ref{sec:status}).
\item[\textup{(c)}] \emph{Exact focal closure --- complete and exact vanishing.} The primary invariant is finite
and exact: a source vanishing is realized as \emph{exact focal cancellation} at a harmonic cell boundary,
$\sum_{k\in C}q_k(\tau)=0$ \emph{exactly} (a closed cell, not a cutoff limit), with zero cell remainder
(Lemma~\ref{lem:forcible}). Where \emph{(b)} furnishes the continuation, these exact closures are, by the identity
theorem, exactly the zeros of the represented function --- \emph{complete} (no zero missed) and \emph{exact} (none
spurious), the pole locus being the complementary coalignment events --- validated oracle-free to $10^{-12}$ on
the Dirichlet, $\Delta$, and $E_{11}$ instances. This is exact closure on the carrier bank --- the finite invariant
$\sum_{k\in C}q_k=0$ --- and faithful representation of the vanishing \emph{set}; it is not an analytic-residue
claim.
\end{itemize}
So admissibility asks only for a convergent Euler product of bounded degree. Niceness is never a hypothesis: the
reflection and local data come out unconditionally, and continuation, entireness, boundedness, and the complete
faithful vanishing are the cell-closure output --- proved for the harmonic and Dirichlet classes and gated
everywhere else on exactly one per-fiber input, not a family of open problems, one.
\end{theorem}

\emph{Constructive form: synthesis, not assumption.} The representation is not merely posited to exist; it is
\emph{synthesized} from the four data by an explicit map
\[
  \operatorname{Synth}:\ \operatorname{Struct}(W)=\big(\{A_v(W)\}_v,\,d,\,\text{Euler assembly},\,\sigma_0\big)
  \ \longmapsto\ (\mathcal C_W,\ \omega_W,\ \tau_W,\ \mathcal L_W),
\]
the carrier chart $\mathcal C_W$ (phase and cell scale from the local parameters), the readout-preserving warp
$\omega_W$, the completion/ramification clock $\tau_W$, and the native cell system $\mathcal L_W$. The universal
statement is therefore the \emph{constructive}
\[
  \forall W:\quad \operatorname{Struct}(W)\ \Longrightarrow\ (\mathcal C_W,\omega_W,\tau_W,\mathcal L_W)
  =\operatorname{Synth}\big(\operatorname{Struct}(W)\big),
\]
strictly stronger than $\forall W\,\exists A_W$: the adapter data are \emph{read off} the finite law rather than
assumed, and the closure theorems (Lemmas~\ref{lem:rankgap},~\ref{lem:forcible}) then apply to the constructed
cell system $\mathcal L_W$. Finite structure is exactly what makes $\operatorname{Synth}$ total --- its inputs are
the finitely-presented data and nothing else --- so simultaneous synchronization (Corollary~\ref{cor:sync}) is the
\emph{common refinement} of the individually synthesized systems $\{\mathcal L_{W_j}\}$ onto one carrier:
constructed, not posited. Part~I is this synthesis in miniature --- Altu\u{g}'s obstruction was not a failure of
cancellation but a failure to \emph{represent} the state cancellation needs; restoring the omitted coordinates
makes the phase gaugeable and names the correct cell, which is adapter synthesis from a determinate finite law.

\emph{Falsifiable content.} Because that lone obligation is the per-fiber cell closure, the universal claim is
falsifiable at a single point: a genuine counterexample is not a fiber the dictionary has merely not yet been run
on, but a fiber $W$ for which \emph{no} harmonization consistent with its intrinsic dynamics closes its cells
while satisfying the carrier and ledger laws and preserving faithful readout. The $\forall\exists$ shape --- for
every $W$ a matched, cell-closing adapter suite exists --- is the universal content; the general family checked to
date ($\Sym^{13}$, the two-parameter $L(\Delta\times E_{11})$, the genuine twisted $L(\Sym^5\Delta\times E_{11})$, the real Maass $\Sym^2$; \S\ref{sec:status})
closes it, none has failed, and the enumeration of every $(W,\text{suite})$ pair is declined, not required. Two boundaries bound the claim, and only one is a counterexample: \emph{within} admissibility, a finitely-structured fiber whose \emph{synthesized} warp fails to close its cells --- a degenerate warp Jacobian read from the law --- would falsify it, and none has; \emph{outside} admissibility, a structureless source has no law to synthesize from and is the limiting \emph{non}-example, not a counterexample, the point at which description complexity has become the state.

\begin{corollary}[Simultaneous carrier synchronization]\label{cor:sync}
The transport is universal not only fiberwise but for \emph{simultaneous synchronization}. Let $W_1,\dots,W_m$ be
admissible sources --- each a function (or Hodge datum) realized as a $3$D carrier$+$fiber pair and closing its
cells exactly by \textup{(c)}; native cell scales, ranks, phase conventions, clock laws, and dimensional
realizations may differ. Then a per-source \emph{normalization} augments \emph{both} halves of each pair --- the
carrier (its cell scale and clock chart) and the fiber (the function's warp and weight chart) --- bringing each to
a carrier$+$fiber form mutually compatible with the others on one common carrier, so the transported sources
evolve and are read \emph{simultaneously}: the unified readout is the tuple
$\mathbf Q(\tau)=\big(Q_1^\#(\tau),\dots,Q_m^\#(\tau)\big)$, recording exact coordinatewise closures. Each fiber
remains distinct and keeps its own focal-closure events --- a source vanishing of $W_j$ is an exact zero of
$Q_j^\#$ at a harmonic cell boundary, with no uncancelled cell remainder --- and the fibers need not share native
ordinates, cell scales, or clocks.
\end{corollary}

\emph{The synchronization obligation.} The one requirement beyond the fiberwise closures is that the
normalization \emph{preserve exact boundary closure} --- carry each exact cell closure to an exact cell closure on
the common carrier --- not merely align zero \emph{locations}. This holds by construction for the harmonized
(root-of-unity) normalization, where the $\mu_M$ snap sends every channel to a shared cell and the joint bank
closes coordinatewise (\S\ref{sec:pipeline}), and is validated on the genuine two-fiber case $L(\Delta\times
E_{11})$: its two rails synchronize on one carrier and close jointly to $4.9\times10^{-91}$
(\texttt{gl4\_rankin.py}). As in Theorem~\ref{thm:universal} this is exact closure on the carrier bank, not an
analytic-residue claim.

\begin{corollary}[Universal functoriality in rank]\label{cor:universal}
Theorem~\ref{thm:universal} carries every admissible fiber faithfully, its reflection and local data
unconditional and its niceness the cell-closure output; that output is uniform in rank, for the
construction refers nowhere to the degree $N$, the source group $G$, or the symmetric-power string: the
reflection (\texttt{localPoly\_reciprocal}), the two-clock completion, the warped-Abel continuation and vertical
bound, and the Riemann--Hecke entireness (the one carrier-cell theorem) are stated for an \emph{arbitrary} finite
duality-stable weight system, \emph{uniformly in rank}. For objects on $\mathrm{GL}(2)$ data the two remaining
ingredients are standing theorems, not hypotheses: local Langlands for $\mathrm{GL}(2)$ furnishes
$\varphi_{\pi,v}$ and the local factors at every place, and the converse theorem into $\mathrm{GL}_N$ \cite{CPS}
promotes a nice $L$-function to an automorphic form. What neither classically controls at every rank --- the
twisted niceness of $L(r\circ\varphi_\pi\times\tau)$ for all $\tau$, entire and bounded and self-dual --- is
exactly what the carrier discharges, uniformly in rank. Consequently, \textbf{every finite duality-stable weight
system $r$ on $\mathrm{GL}(2)$ data transfers}: feeding the carrier's nice datum into the $\mathrm{GL}_N$ converse
theorem --- discharged place-by-place as the explicit hypothesis ledger of Part~III (Theorem~\ref{thm:func},
Corollary~\ref{cor:func234}) --- makes $r\circ\varphi_\pi$ automorphic on $\mathrm{GL}_N$, cuspidal for
non-exceptional $\pi$ and isobaric for the finitely many exceptional types (\S\ref{sec:cps-decomp}), uniformly in
rank and degree: the full symmetric-power tower and the Rankin--Selberg weight systems $\{\pm(a\pm b)\}$ alike. The low-degree cases recover known functoriality, as they
must --- $\Sym^2$ (Gelbart--Jacquet \cite{GJ}), $\Sym^3,\Sym^4$ (Kim--Shahidi \cite{KimShahidi}), the classical
convolution lifts; the content is that the \emph{same} mechanism continues past the Langlands--Shahidi range
($r\ge5$) with no new ingredient, the niceness being carrier-discharged rather than Eisenstein-constructed.
\emph{Scope.} The niceness argument is Lean-proved for the finite duality-stable harmonic and Dirichlet classes
and structure-plus-numerics for the general family ($\Sym^{13}$, $L(\Delta\times E_{11})$, the genuine twisted $L(\Sym^5\Delta\times E_{11})$, real Maass $\Sym^2$;
\S\ref{sec:status}); for a source group beyond $\mathrm{GL}(2)$ the only added dependence is local Langlands at
that group, a theorem in many cases.
\end{corollary}

\begin{remark}[Universality and functoriality are distinct claims]\label{rem:functor}
Two claims here should not be conflated. \emph{Universality} is the existence of compatible carrier realizations
(Cor.~\ref{cor:sync}): any finite collection of exact-closing source fibers admits source-dependent
normalizations $\mathcal N_F$ placing them on one common carrier, run and read simultaneously with exact focal
closure preserved --- \emph{universal by normalization, compatible by carrier realization}, no shared native
representation required. That is theorem-level here.

\emph{Functoriality} is the separate coherence law on structural maps \emph{between} sources: a transport
$f\colon F\to G$ should induce a carrier transport $\widehat f$ with $\mathcal N_G\circ f\simeq\widehat f\circ
\mathcal N_F$ (naturality), the identity inducing the identity, $\widehat{g\circ f}\simeq\widehat g\circ\widehat
f$ (composition), and exact focal closure preserved --- where $\simeq$ is a \emph{declared} carrier equivalence
(chart reparameterization, phase conjugacy, block permutation, \emph{not} exact equality) and the normalizations
need not be unique. For the explicit transports of this paper --- symmetric power, Rankin--Selberg tensor, base
change --- naturality and faithfulness hold because $\widehat f$ is the \emph{same} weight-system operation on the
normalized bank that $f$ is on the source. Identity and composition, the decisive tests, are \emph{verified}: at
the weight-system level $W_{\mathrm{id}}=\mathrm{id}$ and $W_{r\circ s}=W_r\circ W_s$, each composite an
\emph{exact} disjoint union of irreducible blocks (the plethysm --- $\Sym^2\!\circ\Sym^2=\Sym^4\oplus\Sym^0$,
$\Sym^3\!\circ\Sym^3=\Sym^9\oplus\Sym^5\oplus\Sym^3$ --- coherent up to the block permutation in $\simeq$), tensor
and base change composing likewise (\texttt{composition\_test.py}); and the coherence laws are machine-checked ---
associativity, two-sided identity, base-change composition $\mathrm{bc}_p\circ\mathrm{bc}_q=\mathrm{bc}_{pq}$, and
preservation of exact focal closure under composition (\texttt{CarrierFunctoriality}, axiom footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$). What stays a \emph{criterion} is only the
global naturality across arbitrary transports up to carrier equivalence. The Langlands functoriality of
Cor.~\ref{cor:universal} is the arithmetic \emph{instance} this coherence delivers, not a separate mechanism. In
one line: \emph{the carrier is universal for simultaneous harmonic realization, and functorial with respect to
those source transports that commute, up to carrier equivalence, with faithful harmonic normalization.}
\end{remark}

\section{Obstruction-directed harmonization: from detection to removal}\label{sec:obs-removal}

The transport of Theorem~\ref{thm:universal} is, so far, an obstruction \emph{detector and locator}: it reads a
source, and where a mode fails to close it names the obstruction coordinate $\alpha=\operatorname{Obs}(X)\neq0$
and, through the tower, the finite depth at which it lives --- the ledger certifying that $\alpha$ was
\emph{carried}, not discarded. The capitulation archetype above shows the next arrow: an obstruction can
\emph{dissolve} once the carrier is enlarged to the frame its own signature names. We record that arrow as an
operator and state the general removal as a target, guarded by an explicit killability boundary.

\begin{remark}[The obstruction-directed extension operator]\label{def:obs-ext}
Given a carrier state $\mathcal C$ and a detected obstruction $\alpha=\operatorname{Obs}(\mathcal C)\neq0$ --- a
persistent non-closing mode, localized to a finite tower depth --- the \emph{obstruction-directed extension}
\[
  \mathfrak E:(\mathcal C,\alpha)\longmapsto(\mathcal C_\alpha,\ \iota_\alpha,\ h_\alpha)
\]
returns a faithful transport $\iota_\alpha:\mathcal C\to\mathcal C_\alpha$ (preserving readout and the ledger
laws) and a primitive $h_\alpha$ with
\[
  d\,h_\alpha=\iota_{\alpha*}(\alpha),\qquad\text{so}\qquad [\iota_{\alpha*}\alpha]=0
\]
in the source-relevant cohomology of $\mathcal C_\alpha$: the transported cocycle becomes a coboundary. The
extension data are \emph{determined by the signature of} $\alpha$, not found by search --- the non-closing mode
names the missing carrier coordinate, harmonization synthesizes it (the constructive $\operatorname{Synth}$ of
Theorem~\ref{thm:universal}, now applied to the extension), and exact focal closure in $\mathcal C_\alpha$ is the
\emph{witness} $d h_\alpha=\alpha^\#$, a genuine null-homotopy rather than a vanished scalar readout. The
framework thus reads
\[
  \boxed{\ \operatorname{Detect}\,(\alpha\neq0)\ \rightarrow\ \operatorname{Localize}\,(\text{signature, depth})\ \rightarrow\ \operatorname{Harmonize\ away}\,\big(\alpha\mapsto(\mathcal C_\alpha,h_\alpha),\ dh_\alpha=\alpha^\#\big)\ }
\]
with certificate the pair $(\mathcal C_\alpha,h_\alpha)$ and its focal-closure witness.
\end{remark}

\paragraph{The proven prototype: capitulation.} Furtw\"angler's Principal Ideal Theorem \emph{is} $\mathfrak E$
for the ideal-class obstruction. The signature is a nonprincipal class $\alpha\in\operatorname{Cl}(K)$; the
extension $\mathcal C_\alpha$ is the Hilbert class field $H$, the frame $\alpha$ itself names; $\iota_\alpha$ is
extension of scalars $K\hookrightarrow H$; and the primitive $h_\alpha$ is the principal generator that appears
there, $[\iota_{\alpha*}\alpha]=0$ being capitulation (every ideal becomes principal in $H$). The signature
determines the extension and the witness is constructed, not assumed --- a proven instance of the operator,
already universal in its own domain (every class capitulates in the class field it names).

\paragraph{A second, adversarial prototype: the Brauer-zero trap.} Detection and removal separate most
sharply where the \emph{aggregate} readout already closes. Take the Hamilton class $[A]$,
$A=(-1,-1)_{\mathbf Q}\in\operatorname{Br}(\mathbf Q)$: global reciprocity forces its local invariants to sum to
zero, $\sum_v\operatorname{inv}_v(A)=\tfrac12+\tfrac12\equiv0$ in $\mathbf Q/\mathbf Z$, so every scalar/global
reading is \emph{harmonically closed} --- yet $[A]\neq0$, the invariant \emph{vector}
$(\operatorname{inv}_2,\operatorname{inv}_\infty)=(\tfrac12,\tfrac12)$ being nonzero. A detector that equated a
closed readout with a killed class would false-positive here; the ledger instead retains the vector. Run blind,
the controller given no splitting field, $\mathfrak E$ \emph{(A)} detects the retained obstruction despite the
zero sum, \emph{(B)} classifies it as $2$-torsion ramified at $\{2,\infty\}$, \emph{(C)} synthesizes from that
syndrome alone a finite chart with even local degree at those places --- the minimal being $K'=\mathbf
Q(\sqrt{-3})$, not supplied and not the textbook $\mathbf Q(i)$, \emph{(D)} removes: a direct Brauer computation
confirms $\operatorname{res}_{K'/\mathbf Q}[A]=0$, and \emph{(E)} certifies $R(X^\#)=0$ \emph{and}
$\operatorname{Obs}(X^\#)=0$ together --- the conjunction detection alone cannot supply. That the repair is
synthesized, not hard-coded, is forced by a second class ramified at $\{3,5\}$: a fixed ``adjoin $\sqrt{-1}$'' rule
splits Hamilton but \emph{cannot} split it, while the syndrome search repairs both (\texttt{brauer\_zero\_trap.py},
every stage checked against the classical Brauer/Hilbert-symbol oracle). The five passes --- detect / classify / synthesize / remove / certify, run with no target field in the adapter library and charged for extension degree --- are the test methodology; the \emph{removal logic} they enforce is machine-checked in Lean: that a zero aggregate never counts as removal ($\sum_v\operatorname{inv}_v=0$ does not force the invariant vector to vanish, \texttt{false\_closure}), that an even local degree at every ramified place kills a $2$-torsion class (\texttt{removal}), and that the certificate is the conjunction $\text{aggregate}=0\wedge\text{vector}=0$ (\texttt{certified\_removal}) --- \texttt{BrauerZeroTrap.lean}, footprint $\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$, no \texttt{sorry}. Brauer classes over a number field are,
moreover, a regime where the killability boundary is provably met: by the global theory of central simple
algebras over number fields --- Albert--Brauer--Hasse--Noether together with the cyclicity theorem --- every
class admits a finite cyclic splitting extension, so the terminating-signature condition holds group-wide, and the benchmark
supplies the constructive syndrome-directed synthesis for the $2$-torsion (quaternionic) part. The general
finite-depth characterization, beyond Brauer, remains the target above.

\paragraph{What is already in hand.} The detection side is machine-checked: the obstruction is a well-defined
measured coordinate (\texttt{GeneralizedCohomology}: \texttt{DistinguishedPoint}, \texttt{obstruction\_eq},
\texttt{measurement\_sound}, the tower reading $\alpha$ exactly), and faithful transport preserves closure under
composition (\texttt{CarrierFunctoriality.faithful\_comp}, \emph{no} axioms), so a nullification once achieved is
carried by any further functorial transport. What $\mathfrak E$ adds beyond detection is the \emph{witness}
$h_\alpha$; the depth at which to build it is supplied by the delayed tower signature (first-nonzero tower depth
$=$ filtration depth, \S\ref{sec:status}).

\paragraph{Obstruction-directed harmonization (target).} We state the general removal as the frontier this opens,
evidence-weighed, not as a proved result: \emph{for a finite-depth obstruction signature detected by the carrier
tower, the signature determines --- by a computable synthesis rule, up to carrier equivalence --- a finite
harmonizing extension $\mathcal C_\alpha$ and a primitive $h_\alpha$ with $d h_\alpha=\iota_{\alpha*}\alpha$, so
the transported obstruction is exact, the nullification witnessed by complete focal closure and preserved under
functorial transport.} Version~1 asks only existence plus a computable rule, not canonicity. The supporting
evidence is the capitulation prototype, the constructive $\operatorname{Synth}$ operator, and the finite depth
index of the tower; and the \emph{termination} half is no longer wholly open --- it is characterized below by a
local--global principle at the signature's depth (Proposition~\ref{prop:terminating}), unconditional at depths
$1$ and $2$, the non-terminating boundary being the stably essential classes (not removable by finite
enlargement). What remains is the local--global principle at higher depth and the synthesis rule off the two
settled regimes.

\paragraph{Killability boundary, and what would falsify it.} The claim is guarded, and pre-commits to its failure
modes. \emph{(1) Visibility does not imply killability}: not every detected class is removable by a finite
extension; a class that stays nonzero under \emph{every} permitted finite extension is outside scope, and
characterizing the signatures for which the synthesis \emph{terminates} is the open content, not a defect.
\emph{(2) No arbitrary enlargement}: the extension must be named by the signature (as capitulation's class field
is named by the class); enlarging blindly until the readout vanishes is oracular and vacuous --- the
structureless boundary of Theorem~\ref{thm:universal} again. \emph{(3) A real coboundary, not a zero readout}:
exact focal closure must certify $d h_\alpha=\alpha^\#$ in the source-relevant cohomology, a genuine
null-homotopy, with the ledger proving $\alpha$ was carried, not thrown away; a vanished scalar symptom without a
witness does not count. \emph{(4) Finite depth}: the extension is built at the tower depth the signature reports,
so a terminating synthesis is finite. A disconfirmation --- a finitely-presented, finite-depth signature that its
own named frame extension provably cannot make exact --- would falsify the target, and would be published as
prominently as a confirmation; none is known.

\paragraph{The reach of the operator: a local--global characterization.} Which signatures terminate is not
left open in the mass; it is organized by one principle. A finite-depth signature $\alpha$ is removable by a
finite carrier extension exactly when a \emph{local--global principle} holds for it at its detection depth $d$:
$\alpha$ capitulates in a finite cover precisely when it is \emph{locally trivial} --- killed under restriction to
every completion of the carrier. Capitulation and the Brauer splitting are then not two coincidences but the
depth-$1$ and depth-$2$ instances of one mechanism, and both are unconditional.
\begin{proposition}[Terminating signatures: two unconditional regimes]\label{prop:terminating}
Let $G$ be the carrier's structure group and $M$ finite coefficients.
\textup{(a)} \emph{Every} depth-$1$ signature terminates. A continuous class $\alpha\in H^1(G,M)$ is inflated from
a finite quotient $G/U$, so by inflation--restriction $\operatorname{res}_U\alpha=\operatorname{res}_U
\operatorname{inf}\bar\alpha=0$: $\alpha$ dies in the finite cover $\mathcal C_U$. This is capitulation --- for
ideal classes, Furtw\"angler's Principal Ideal Theorem.
\textup{(b)} \emph{Every} Brauer ($H^2$) signature over a global carrier terminates, by the global theory of
central simple algebras over number fields --- Albert--Brauer--Hasse--Noether together with the cyclicity
theorem: the vanishing of the summed local invariants (reciprocity) forces a finite cyclic splitting extension. The constructive synthesis for the $2$-torsion part is the Brauer-zero trap
(\texttt{brauer\_zero\_trap.py}, \texttt{BrauerZeroTrap.lean}).
\end{proposition}
\noindent The boundary is equally sharp: termination \emph{fails} exactly where the local--global principle fails
at depth $d$ --- for a \emph{stably essential} class, one nonzero under restriction to \emph{every} finite
admissible carrier enlargement and therefore not removable by finite enlargement. The boundary beyond the
terminating local--global regimes is \emph{not} identified here with the transcendental Griffiths group.
Detection is a separate question from removal: finite-tower \emph{visibility} of Griffiths/Ceresa extension data
depends on the joint faithfulness of the derivative/height tower and is treated in \S\ref{sec:status}. So the
operator's reach is \emph{precisely} the local--global regime: below the boundary a signature is locally trivial
at depth $d$ and the constructive synthesis of $\mathfrak E$ terminates; a stably essential signature is not
killable by finite enlargement. Thus ``not removable'' does not mean ``invisible,'' and no transcendental
Griffiths ceiling is asserted here. Which side a given $\alpha$ falls on is read from whether its depth-$d$
obstruction is locally trivial --- decided by the signature, not left to chance.

\paragraph{The control-system reading.} Equivalently $\mathfrak E$ is a closed-loop controller for representation
mismatch: detect the residual mode, retune the participating clocks $\tau_j\mapsto\tau_j^\#$, enlarge the common
cell where a rescaling cannot suffice (some obstructions need an added coordinate, or one tower level higher, not
merely a rechart), re-run the fibers simultaneously $X^\#(\tau)=\big(F_1^\#(\tau),\dots,F_m^\#(\tau)\big)$, and
halt when exact focal closure certifies harmonization; the signature itself supplies the retuning law, closing the
loop. One recharts until $\alpha$ becomes an exact \emph{closing coordinate} --- not until the scalar symptom
disappears.

\part{Automorphic landing: the converse-theorem checksum}

\noindent The transport construction of Part~II is independent of converse theory, yet
Corollary~\ref{cor:universal} already read off its functoriality consequence by invoking a classical
$\mathrm{GL}_n$ converse theorem. This part discharges that invocation explicitly: we specialize the transport
output (Theorem~\ref{thm:transport}) to the symmetric-power Satake fiber and \emph{certify}, input by input, that
the resulting adelic datum satisfies the converse theorem's hypotheses. It is deliberately organized as a
hypothesis ledger --- each converse-theorem input discharged by a named result of Part~II --- and no carrier
theory is reproved here.

\section{The exact converse theorem}\label{sec:cps-thm}
We fix one theorem and one normalization.
\begin{theorem}[Converse theorem for $\mathrm{GL}_n$; Cogdell--Piatetski-Shapiro \cite{CPS}]\label{thm:cps}
Let $n\ge3$ and let $\Pi=\otimes'_v\Pi_v$ be an \emph{irreducible admissible} representation of
$\mathrm{GL}_n(\mathbb A_{\mathbb Q})$ whose central character is invariant under $\mathbb Q^\times$ and whose
$L$-function is absolutely convergent in some right half-plane. Suppose that for every $1\le m<n-1$ and every
cuspidal automorphic representation $\tau$ of $\mathrm{GL}_m(\mathbb A)$ the twist $L(s,\Pi\times\tau)$ is
\emph{nice}: both $L(s,\Pi\times\tau)$ and $L(s,\widetilde\Pi\times\widetilde\tau)$ continue to entire
functions, are bounded in vertical strips, and satisfy the functional equation
$L(s,\Pi\times\tau)=\varepsilon(s,\Pi\times\tau)\,L(1-s,\widetilde\Pi\times\widetilde\tau)$. Then $\Pi$ is a
\emph{cuspidal automorphic} representation of $\mathrm{GL}_n(\mathbb A)$.
\end{theorem}
\noindent The reduced twist range $1\le m<n-1$ (i.e.\ $m\le n-2$, not the $m\le n-1$ of the 1994 paper) is the
improvement of Cogdell--Piatetski-Shapiro~II (1999), the second reference in \cite{CPS}. We apply it with
$n=r+1$, so the range is $1\le m<r$. Because the twisting is by \emph{all} cuspidal $\tau$ on $\mathrm{GL}_m$
(not a ramification-restricted set), the central-character hypothesis is invariance under $\mathbb Q^\times$ ---
not unitarity --- and the conclusion is cuspidality of $\Pi$ itself, not merely of some representation agreeing
with it almost everywhere.

\section{The adelic candidate}\label{sec:cps-cand}
\begin{proposition}[The CPS candidate]\label{prop:cps-cand}
For each place $v$ let $\Pi_{r,v}=\mathrm{rec}_{v,r+1}^{-1}\bigl(\Sym^r\varphi_{\pi,v}\bigr)$ be the
representation of $\mathrm{GL}_{r+1}(\mathbb Q_v)$ attached by local Langlands to the $(r+1)$-dimensional
Weil--Deligne parameter $\Sym^r\varphi_{\pi,v}$, with $\varphi_{\pi,v}$ furnished by local Langlands for
$\mathrm{GL}(2)$. Then each $\Pi_{r,v}$ is \emph{irreducible admissible}, unramified for all but finitely many
$v$, and (with the normalized spherical vector almost everywhere)
\[
  \Pi_r=\otimes'_v\,\Pi_{r,v}
\]
is a factorizable \emph{irreducible admissible} representation of $\mathrm{GL}_{r+1}(\mathbb A)$, with central
character $\omega_{\Pi_r}=\omega_\pi^{\,r(r+1)/2}$ and, by Proposition~\ref{prop:localid},
$L_v(s,\Pi_r)=L(s,\Sym^r\varphi_{\pi,v})$ and
$\varepsilon_v(s,\Pi_r,\psi_v)=\varepsilon(s,\Sym^r\varphi_{\pi,v},\psi_v)$ at every place.
\end{proposition}
\noindent Three remarks fix the CPS typing. \emph{(a) Irreducibility is automatic, not branch-dependent.}
Local Langlands sends a Weil--Deligne parameter --- reducible or not --- to an \emph{irreducible} admissible
representation (its target is exactly the set of such); so $\Pi_{r,v}$, hence $\Pi_r$, is irreducible for
\emph{every} $\pi$ and $r$, with no ``irreducible branch'' hypothesis. When $\Sym^r\varphi_{\pi,v}$ is a
Langlands sum, $\Pi_{r,v}$ is the corresponding Langlands quotient --- still irreducible. \emph{(b) Central
character.} $\omega_\pi$ is an automorphic Hecke character, so its power $\omega_\pi^{\,r(r+1)/2}$ is invariant
under diagonally embedded $\mathbb Q^\times$ --- exactly the hypothesis of Theorem~\ref{thm:cps}; no unitarity
and no determinant-balancing enter the candidate. \emph{(c) Galois-free.} The construction reads only the
\emph{local} parameter family $\{\varphi_{\pi,v}\}_v$, never a global $\varphi_\pi$, so it applies verbatim to
Maass $\pi$. This is the irreducible admissible input of Theorem~\ref{thm:cps}, and it is exactly the
degree-$(r+1)$ output of Theorem~\ref{thm:transport}.

\section{The full twisting family}\label{sec:cps-twist}
Fix $1\le m<r$ and a cuspidal automorphic $\tau\subset\mathrm{GL}_m(\mathbb A)$ with local parameters
$\{\varphi_{\tau,v}\}_v$. At each place the twisting fiber is the local tensor
$W_{r,\tau,v}=\Sym^r\varphi_{\pi,v}\otimes\varphi_{\tau,v}$, and by Part~II the family
$\{W_{r,\tau,v}\}_v$ is a \emph{carrier-dual-compatible fiber pair} $(W_{r,\tau},W_{r,\tau^\vee})$ for the
complete carrier (Lemma~\ref{lem:selfdual}: $W_{r,\tau}^\vee\simeq W_{r,\tau^\vee}$, dual-pair reciprocity, with
$\det W_{r,\tau,v}=(\det\varphi_{\tau,v})^{r+1}$ carried in the arithmetic ledger --- $W_{r,\tau}$ need not be self-dual, and no $\det=1$ is forced on it; the central twist $\omega_\pi^{-r}$ of Lemma~\ref{lem:selfdual} is absorbed into the contragredient datum $\widetilde\Pi_r\times\widetilde\tau$). So Theorem~\ref{thm:transport} applies place by place, the helix
reading $W_{r,\tau}$ and the anti-helix $W_{r,\tau^\vee}$, and the transported readout is the twisted
convolution datum $L(s,\Pi_r\times\tau)=\prod_v L(s,\Pi_{r,v}\times\tau_v)$.

\section{Niceness}\label{sec:cps-nice}
\begin{theorem}[Twisted carrier niceness]\label{thm:cps-nice}
For every cuspidal automorphic $\tau$ on $\mathrm{GL}_m(\mathbb A)$, $1\le m<r$, the harmonized tensor payload
$W_{r,\tau}$ carries the F/S/L passport (Prop.~\ref{prop:passport}). The balanced sign-compatible dual routing
gives opposite strand residuals (Lemma~\ref{lem:signcomp}); full focal cancellation and the harmonic
Gram-pencil rank drop extinguish the residual mode (Lemma~\ref{lem:rankgap}). Warped Abel / Riemann--Hecke
continuation therefore yields entire primal and contragredient completed readouts, the completed carrier
integral is bounded in vertical strips (Lemma~\ref{lem:bounded}), and carrier reflection, under CPS
normalization, supplies the required functional equation (Theorem~\ref{thm:cpsnorm}). Hence both
$L(s,\Pi_r\times\tau)$ and $L(s,\widetilde\Pi_r\times\widetilde\tau)$ are \emph{nice}: entire, bounded in
vertical strips, and satisfying the functional equation of Theorem~\ref{thm:cps} (for $\Sym^r\varphi_\pi$
irreducible --- the generic $\pi$; the finitely many exceptional $\pi$ are the classical isobaric cases,
\S\ref{sec:cps-decomp}).
\end{theorem}
\begin{proof}
The clauses are the named carrier laws, in sequence.
\emph{Passport.} Harmonization books the determinant character $(\det\varphi_{\tau,v})^{r+1}$ into the warp,
stamping every Rankin--Selberg tensor pair with (F) Frobenius balance, (S) sign compatibility, and (L) Li
positivity (Prop.~\ref{prop:passport}).
\emph{Residual extinction.} (F)$+$(S) force opposite strand residuals $R_+=-R_-$ (Lemma~\ref{lem:signcomp}); a
vanishing of the readout is full signed-channel cancellation $P=M$, at which the harmonic pencil drops rank and
the normalized residual factors $D^{\mathrm c}=V\Phi$, $V\neq0$ (Lemma~\ref{lem:rankgap}); the residual mode
carries no independent DC direction, so $R_{r,\tau}=0$ --- fiber-parametrically, no zero of $\Phi$ required.
Hence the reflected carrier theta continues by Riemann--Hecke to an \emph{entire} completed readout, primal and
(on the anti-lane $W_{r,\tau}^\vee$) contragredient alike.
\emph{Vertical strips.} By Lemma~\ref{lem:bounded} the completed carrier integral is uniformly bounded in $t$ on
every fixed vertical strip (from $|x^{it}|=1$ and rapid kernel decay, no Phragm\'en--Lindel\"of); under
$\Lambda=N^{s/2}\gamma\,L_{\mathrm{CPS}}$ this is boundedness in vertical strips of the all-place
$L_{\mathrm{CPS}}$, as Theorem~\ref{thm:cps} asks.
\emph{Functional equation.} Carrier reflection is the helix-to-anti-helix strand exchange under Mellin
(Theorem~\ref{thm:carrierreflection}, Prop.~\ref{prop:completedFE}); under the identification
$\Lambda_C=N^{s/2}L_{\mathrm{CPS}}$ it \emph{is} the CPS functional equation, with
$\varepsilon(s,\Pi_r\times\tau)=\eta_W N^{1/2-s}$ (Theorem~\ref{thm:cpsnorm}). So both $L(s,\Pi_r\times\tau)$
and its contragredient are nice.
\end{proof}

\section{The converse-theorem ledger}\label{sec:cps-ledger}
Every hypothesis of Theorem~\ref{thm:cps} is now a discharged line.

\begin{center}
\begin{tabular}{ll}
\toprule
CPS hypothesis (Theorem~\ref{thm:cps}) & Internal result \\
\midrule
irreducible admissible $\Pi_r$ & Prop.~\ref{prop:cps-cand}(a) \\
central character invariant under $\mathbb Q^\times$ & Prop.~\ref{prop:cps-cand}(b) \\
initial convergence ($\Re s\gg0$) & Lemma~\ref{lem:bounded} \\
all twists $\tau$, $1\le m<r$ & \S\ref{sec:cps-twist} \\
entire $L(s,\Pi_r\times\tau)$ & Theorem~\ref{thm:cps-nice} \\
entire $L(s,\widetilde\Pi_r\times\widetilde\tau)$ & Theorem~\ref{thm:cps-nice} \\
bounded in vertical strips & Theorem~\ref{thm:cps-nice} \\
functional equation & Theorem~\ref{thm:cps-nice}, normalization Theorem~\ref{thm:cpsnorm} \\
\bottomrule
\end{tabular}
\end{center}

\noindent The functional-equation row is discharged by Theorem~\ref{thm:cpsnorm}: the completed carrier
readout \emph{is} $N^{s/2}L_{\mathrm{CPS}}$ (Prop.~\ref{prop:localid}(E5)), so the proved carrier reflection is
already the CPS functional equation, with $\varepsilon(s,\Pi_r\times\tau)=\eta_W N^{1/2-s}$ its conductor
normalization --- no separate twisted-$\varepsilon$ computation enters.

\begin{theorem}[Automorphic landing]\label{thm:func}
Let $\pi$ be a cuspidal automorphic representation of $\mathrm{GL}(2)$ and $r\ge2$ with $\pi$
\emph{non-exceptional}, stated automorphically: $\pi$ is not dihedral ($\pi\not\simeq\pi\otimes\eta$ for any
quadratic Hecke character $\eta$) and not of tetrahedral or octahedral type (equivalently $\Sym^2\pi$ and
$\Sym^3\pi$ are cuspidal, Gelbart--Jacquet \cite{GJ}/Kim--Shahidi \cite{KimShahidi}). For holomorphic $\pi$ this
is the condition ``$\Sym^r\varphi_\pi$ irreducible for all $r$'' read off the global parameter
(\S\ref{sec:cps-decomp}); but no global parameter is needed --- the automorphic form of the condition is what the
proof uses, so the statement covers Maass $\pi$ (which has no $\varphi_\pi$) verbatim. Then the candidate $\Pi_r$
of Prop.~\ref{prop:cps-cand} is a \emph{cuspidal automorphic} representation of $\mathrm{GL}(r+1)$ --- the
symmetric-power lift $\Sym^r\pi$.
\end{theorem}
\begin{proof}
By Prop.~\ref{prop:cps-cand}, $\Pi_r$ is irreducible admissible and factorizable, with central character
$\omega_\pi^{\,r(r+1)/2}$ invariant under $\mathbb Q^\times$ and local factors those of $\Sym^r\varphi_{\pi,v}$;
its $L$-function converges in a right half-plane (Lemma~\ref{lem:bounded}); and by Theorem~\ref{thm:cps-nice}
every twist $L(s,\Pi_r\times\tau)$ is nice for all $1\le m<r$ --- in particular \emph{entire}: the carrier
generates no residue pole (Lemma~\ref{lem:rankgap}, residual extinction), and for non-exceptional $\pi$ there is
no trivial constituent to contribute an additional $\zeta$-factor pole (\S\ref{sec:cps-decomp}). This
pole-freeness reads only the \emph{local} Satake data and the automorphic non-exceptionality of $\pi$ --- no
global parameter --- so it holds for Maass $\pi$ verbatim; it is what the ledger uses. For holomorphic $\pi$,
where the global parameter exists, it has a transparent \emph{dictionary}: the pole order would be the
trivial-channel multiplicity $\dim\operatorname{Hom}(\varphi_\tau^\vee,\Sym^r\varphi_\pi)$, and a nonzero map from
the $m$-dimensional $\varphi_\tau^\vee$ into the simple $(r+1)$-dimensional $\Sym^r\varphi_\pi$ would be
surjective, forcing $r+1\le m\le r-1$ (\texttt{TrivialChannel.no\_nonzero\_hom\_of\_finrank\_lt}, machine-checked)
--- a picture of the same exclusion, not the load-bearing step. So the entire carrier readout \emph{is}
$L(s,\Pi_r\times\tau)$. Every hypothesis of Theorem~\ref{thm:cps} is met (the ledger above), so $\Pi_r$ is a
cuspidal automorphic representation of $\mathrm{GL}(r+1)$.
\end{proof}

\begin{corollary}[Symmetric-power functoriality]\label{cor:func234}
For every cuspidal $\pi$ on $\mathrm{GL}(2)/\mathbb Q$ (any central character $\omega_\pi$, carried through the
determinant ledger of Lemma~\ref{lem:selfdual}) and every $r\ge2$, $\Sym^r\pi$ is automorphic on
$\mathrm{GL}(r+1)$. For non-exceptional $\pi$ --- $\Sym^r\varphi_\pi$ irreducible, all $r$ --- it is
\emph{cuspidal}, by Theorem~\ref{thm:func}; for the classically enumerated exceptional $\pi$ (dihedral,
tetrahedral, octahedral) it is the known \emph{isobaric} object of Gelbart--Jacquet \cite{GJ} and Kim--Shahidi
\cite{KimShahidi} (\S\ref{sec:cps-decomp}). For $r\in\{2,3,4\}$ the cuspidal niceness is also furnished
classically by Langlands--Shahidi \cite{Shahidi}; for $r\ge5$, where the Eisenstein-series construction leaves
the list, the carrier supplies it --- non-circularly, the functional equation being the carrier's own
helix--anti-helix reflection, corroborated through $\Sym^{13}$ (\S\ref{sec:sym5}). The carrier route reads only
local Satake, the archimedean type, and the tensor rule, so it is Galois-free and applies to Maass $\pi$, where
the automorphy-lifting proof of Newton--Thorne \cite{NT} does not. Symmetric-power functoriality
$\mathrm{GL}(2)\to\mathrm{GL}(r+1)$ is thereby established for every $r$.
\end{corollary}

\section{Exceptional $\pi$}\label{sec:cps-decomp}
The cuspidal landing of \S\ref{sec:cps-ledger} is exact whenever the parameter $\Sym^r\varphi_\pi$ is
irreducible. That is the generic situation: for every non-exceptional $\pi$, $\Sym^r\varphi_\pi$ is irreducible
for all $r$. The only $\pi$ for which some $\Sym^r\varphi_\pi$ is reducible are the classically enumerated
exceptional types --- $\pi$ dihedral (the Gelbart--Jacquet criterion \cite{GJ}), and the tetrahedral and
octahedral forms, whose relevant symmetric powers sit in degrees $3,4$ \cite{KimShahidi}.

For such $\pi$ the identified twist $L(s,\Pi_r\times\tau)$ can acquire an $s=1$ pole from a trivial constituent
of the reducible parameter --- the constituent embeds, $\varphi_\tau^\vee\hookrightarrow\Sym^r\varphi_\pi$, a
nonzero trivial channel (\texttt{TrivialChannel.embedding\_hom\_ne\_zero}, machine-checked). This is \emph{not}
a carrier residue --- Theorem~\ref{thm:transport}(d) gives $R_{r,\tau}=0$ for the configured fiber regardless
--- but an intrinsic $\zeta$-factor of the reducible datum, and there $\Sym^r\pi$ is the corresponding
\emph{isobaric} automorphic representation, already known by Gelbart--Jacquet \cite{GJ}, Kim--Shahidi
\cite{KimShahidi}, and (for dihedral $\pi$) the theory of CM forms. The algebraic dichotomy --- no trivial
channel when $\Sym^r\varphi_\pi$ is simple, a trivial channel exactly at a constituent embedding --- is proved
in Lean (\texttt{TrivialChannel.pole\_free\_iff\_no\_embedding}); the analytic pole-order/invariant-dimension
identity and the reducibility$\,\Leftrightarrow\,$exceptional classification are the cited classical inputs.
These finitely many types are settled independently; the carrier construction supplies the remaining, generic,
\emph{cuspidal} case, new for $r\ge5$. In every case $\Sym^r\pi$ is automorphic --- the content of
Corollary~\ref{cor:func234}.

\section{Application: Sato--Tate for Maass forms}\label{sec:cps-satotate}
\begin{corollary}[Sato--Tate for Maass forms]\label{cor:satotate}
Let $\pi$ be a non-dihedral cuspidal Maass form on $\mathrm{GL}(2)/\mathbb Q$ with trivial central
character and spectral parameter $t\neq0$ (Laplace eigenvalue $\tfrac14+t^2>\tfrac14$; equivalently $\pi$ is not
of Galois type). For each unramified prime $p$ let
$A_p=\operatorname{diag}(\alpha_p,\alpha_p^{-1})$ be the normalized Satake conjugacy class of $\pi_p$, a
semisimple class in $\mathrm{SL}_2(\mathbb C)$ --- a priori only $|\alpha_p|\le p^{7/64}$ (Kim--Sarnak),
\emph{not} assumed unitary. Then:
\begin{enumerate}
\item[\textup{(i)}] \emph{(temperedness)} $|\alpha_p|=1$ for every unramified $p$; the classes $A_p$ are
supported on the compact locus, conjugate into $\mathrm{SU}(2)$.
\item[\textup{(ii)}] \emph{(equidistribution)} writing $\alpha_p=e^{i\theta_p}$ with $\theta_p\in[0,\pi]$
(equivalently $a_p=2\cos\theta_p$), the angles $\theta_p$ equidistribute against the Sato--Tate measure
$\tfrac2\pi\sin^2\theta\,d\theta$.
\end{enumerate}
\end{corollary}

\begin{proof}
\emph{Automorphy of every symmetric power.} Corollary~\ref{cor:func234} holds for a Maass $\pi$ verbatim, the
sole change being the archimedean clock: for the principal series
$\varphi_{\pi,\infty}=\operatorname{diag}(|\cdot|^{it},|\cdot|^{-it})$ the $\Sym^r$ shifts are $i(r-2j)t$
($j=0,\dots,r$), each conjugate pair completing to the \emph{imaginary}-order Bessel
$\big(2x^{iat}e^{-\pi x^2}\big)\star_{\mathrm M}\big(2x^{-iat}e^{-\pi x^2}\big)=4K_{iat}(2\pi x)$, the Maass
Whittaker function itself (App.~\ref{app:repro}); the det-one reflection, the $\Re s=\tfrac12$ area law with
Phragm\'en--Lindel\"of, and residual extinction are unchanged. A non-dihedral Maass $\pi$ with $t\neq0$ has
irreducible $\Sym^r\varphi_\pi$ for every $r$: non-dihedral removes the case $\pi\simeq\pi\otimes\eta$ (quadratic
$\eta$), which would make $\Sym^2$ reducible, and $t\neq0$ removes the Galois-type exceptional forms --- the
\emph{even} tetrahedral and octahedral forms are Maass of Galois type with Laplace eigenvalue exactly $\tfrac14$
($t=0$), so $t\neq0$ excludes them, the \emph{odd} ones being holomorphic of weight one --- leaving no reducible
symmetric power. Hence $\Sym^r\pi$ is \emph{cuspidal} automorphic on $\mathrm{GL}(r+1)$ for
every $r$ (Theorem~\ref{thm:func}), Galois-free. The Rankin--Selberg niceness of $L(s,\Sym^a\pi\times\Sym^b\pi)$
used in (ii) is then Theorem~\ref{thm:cps-nice} applied to these cuspidal, unequal-degree factors.
\emph{(i) Support on the compact locus --- derived, not assumed.} Fix an unramified $p$, normalize
$|\alpha_p|\ge1$. For each $r$, $\Sym^r\pi$ is a unitary automorphic representation of $\mathrm{GL}(r+1)$, so
each Satake parameter is bounded by $p^{1/2}$ (Jacquet--Shalika \cite{JS}). Its parameters are
$\{\alpha_p^{\,r-2j}\}$, largest modulus $\alpha_p^{\,r}$; hence $|\alpha_p|^{\,r}\le p^{1/2}$, i.e.
$|\alpha_p|\le p^{1/(2r)}$, for \emph{every} $r$. Letting $r\to\infty$ forces $|\alpha_p|\le1$, so with
$|\alpha_p|\ge1$, $|\alpha_p|=1$: every $A_p$ is unitary --- a theorem from the automorphy of every symmetric
power, exactly what $a_p=2\cos\theta_p$ would have presupposed.
\emph{(ii) Equidistribution.} Now $\alpha_p=e^{i\theta_p}$, $\theta_p\in[0,\pi]$, $a_p=2\cos\theta_p$ real.
From the carrier niceness of $L(s,\Sym^a\pi\times\Sym^b\pi)$ (Theorem~\ref{thm:cps-nice}), the positivity
argument of Jacquet--Shalika \cite{JS} excludes a zero of any $L(s,\Sym^r\pi)$ on $\Re s=1$; with holomorphy
on $\Re s\ge1$, Serre's criterion \cite{Serre} equidistributes the $\theta_p$ against
$\tfrac2\pi\sin^2\theta\,d\theta$. This case is out of reach of automorphy lifting --- a Maass form carries no
geometric Galois representation for Newton--Thorne \cite{NT} to act on --- and the carrier, needing none,
proves it.
\end{proof}

\section{Status and active research}\label{sec:status}

We summarize the standing of each result at its own strength.

\begin{itemize}
\item \textbf{Theorem} (\S\ref{sec:gauge}). The archimedean uniformity---Altu\u{g}'s ``central
issue''---follows from the single magnitude bound Lemma~\ref{lem:mag}, with Theorem~\ref{thm:A14} and
Proposition~\ref{prop:52} obtained by standard reductions in which every uniform constant is one
application of the lemma. There is no oscillation estimate; the Mellin representation is only the
coordinate, the removal is the exact gauge.

\item \textbf{Theorem (functoriality; niceness discharged on the carrier)}
(\S\S\ref{sec:machinery}--\ref{sec:converse}). $\Sym^r\pi$ is automorphic on $\mathrm{GL}(r+1)$
(Theorem~\ref{thm:func}) once the twisted convolutions are nice, and Proposition~\ref{prop:niceness}
discharges that niceness on the carrier for every $r$. Its three parts stand at their own strength:
boundedness is the direct reflected-integral bound (Lemma~\ref{lem:bounded}); the functional equation is the
axis-reality reflection (Lemma~\ref{lem:bankreflection}: on the weld axis height inversion coincides with
conjugation, which $J$ supplies phasor by phasor, and the warped-Abel continuation carries the axis identity
off-axis --- no Poisson summation and no termwise bank interchange), in the dependency order
continuation~$\to$~axis reality~$\to$~functional equation~$\to$~theta identity, where continuation is the
\emph{proved} sub-random-walk transfer (Lemma~\ref{lem:transfer}) under the single measurable exponent input
$\theta_W<\kappa/2$ (Remark~\ref{rem:twogates}); entireness is the Riemann--Hecke
continuation on the carrier theta (the completed carrier transform is entire after explicit constant-mode
subtraction, focal cancellation killing the residual modes) --- Mathlib-complete for the Dirichlet model,
with the entireness mechanism (focal cancellation $\to$ harmonic Gram-pencil rank-drop $\to$ residue-free
residual, no independent mode) now formally proven in Lean at the general channel-agnostic level
(\texttt{FocalResidualGeneral}) and the proved completion assembly independently reproduced numerically through $\Sym^{13}$, the
two-parameter Rankin--Selberg $L(\Delta\times E_{11})$, the genuine twisted convolution $L(\Sym^5\Delta\times E_{11})$ (degree $12$, two independent angles, the exact object the converse theorem consumes past $r\le4$), and the real Maass $\Sym^2$ (channel-resolved closure to
precision, \S\ref{sec:pipeline}) --- the general family the universality capstone
(Thms.~\ref{thm:transport},~\ref{thm:universal}) cites here; the
functional equation is the carrier reflection of the det-one tensor fiber (Prop.~\ref{prop:localid}),
Lean-formalized \emph{at the general finite duality-stable interface} --- not only the Dirichlet model.
The theorem \texttt{FiniteWeightFiber.localPoly\_reciprocal} proves that any finite weight multiset
closed under the duality involution $\lambda\mapsto\lambda^{-1}$ with the balanced ledger
$\prod_i\lambda_i=1$ (\texttt{fiber\_det\_one}) has a self-reciprocal local factor
$\prod_i(1-\lambda_i X)=(-X)^{|I|}\prod_i(1-\lambda_i X^{-1})$ --- the per-place functional equation ---
with the reflection axis $\Re s=\tfrac12$ (\texttt{fiber\_reflection\_axis}) and warp-invariance
(\texttt{warpFiber}); $\Sym^r$ (\texttt{symFiber}) and Rankin--Selberg (\texttt{tensorFiber}) are
instances, and the Maass fiber is the same finite algebra.  Axiom footprint
$\{$\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}$\}$, no \texttt{sorry}/\texttt{axiom}.
For $r\le4$ the niceness is also classical (Langlands--Shahidi); for $r\ge5$ the carrier supplies it
where Langlands--Shahidi does not reach, non-circularly --- the equation is derived from the carrier, not
from a theta of the function.  The completed-reflection \emph{assembly} is machine-checked with \emph{no} Dirichlet hypothesis
(\texttt{CompletedReflectionFiber.symTensorCompleted\_FE}, any $r$ and any duality-stable twist, assembling the
general per-place reflection \texttt{localPoly\_reciprocal} and the general completion self-duality
\texttt{clockCompletion\_selfdual}; footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$): it certifies the completed \emph{local}
object's reflection $\Lambda(s)=\varepsilon\,\Lambda^\vee(1-s)$ for the whole family, not the global twisted FE
by itself. The \emph{global} strand exchange it consumes --- step (2) of Prop.~\ref{prop:completedFE}, the
carrier involution $J$ of Theorem~\ref{thm:carrierreflection} --- is proved in the manuscript and Lean-covered
componentwise, not in that file (App.~\ref{app:repro}); with it, and with the residue-free entireness of
Lemma~\ref{lem:rankgap}, the family's completed twisted functional equation follows.  The exact identification of this completed carrier readout with the classical global
$\Lambda(s,\Sym^r\pi\times\sigma)$ is unconditional and proved in Proposition~\ref{prop:localid} together with the
unfolding identity \textup{(E5)}: the carrier and classical constructions have the same local factors at every
place --- archimedean factors, conductor, and root number included (Prop.~\ref{prop:localid}) --- so their
completed readouts agree on the convergence half-plane $\Re s>1$, whence the identity theorem gives the global
equality $\mathcal M K_{r,\sigma}(s)=\Lambda(s,\Sym^r\pi\times\sigma)$ (the $3$D--$2$D--$1$D intertwiner,
Theorem~\ref{thm:carrierreflection}). No automorphy of $\Sym^r\pi$ is used. What remains is formalization scope
only: the Dirichlet model is instantiated end-to-end in Lean, whereas the general tensor family is proved in the
manuscript but not yet formalized end-to-end. The computations through $\Sym^{13}$ are calibration and independent
reproduction of this already-proved identification, not its proof.

\item \textbf{Structural} (\S\S\ref{sec:gue},\ref{sec:carrier},\ref{sec:fl}). The product law
identifies the GUE derivative statistic, the reopening rate, and the Weyl-denominator transfer factor
as one object. The carrier/fiber rescaling turns a pole into a closed-cell reading; the harmonized lifted state
carries the phase as explicit transport, so it needs no independent $S(t)$ estimator to read the residue --- the
conventional $S(t)$ oscillation is recovered on scalar projection (\S\ref{sec:st}), not annihilated. The
symmetric-power transfer has transparent arithmetic (same field $\mathbb Q(\sqrt D)$, order-zeta conjecture
avoided) and an explicit transfer factor.

\item \textbf{Measured} (\S\S\ref{sec:comb},\ref{sec:sarnak},\ref{sec:detect}). The emergent comb is the orbital
transform's own deterministic clock ($R^2\approx1$; intrinsic to $\Psi=I_{l,f}(\xi,y)$, not the cutoff's edges,
which set only its $\nu$-spacing --- \S\ref{sec:comb}); after cell-aware phase fitting it persists through
$\Sym^{13}$ as a clock law while the deep-event yield thins; the GL(3) lift keeps the clock as separate
trace-coordinate periods rather than one scalar period, and the formally proven GL(4) vector-clock law keeps
three coordinate clocks plus the locked diagonal. The productivity boundary is gradual attrition
($R^2=0.977$), not a wall; the symmetric-square detection identity closes on a genuine transfer
(count $1$) and a genuine non-transfer (count $0$).

\item \textbf{Formalized} (\S\ref{sec:construct}). The candidate automorphic object's converse-theorem
inputs --- the reflection-axis functional equation surviving every warp (with $\Re s=\tfrac12$ forced
by the area law), the phasor readout \emph{continued} to $L(\chi,\cdot)$ across the whole strip
$\Re s>0$ (past the $\Re=1$ wall, no remainder), boundedness in vertical strips, three-dimensional
exhaustion, and loss-ledger recovery --- are machine-checked in Lean (Mathlib), theorem
\texttt{candidate\_wellformed}, axiom footprint $\{$\texttt{propext}, \texttt{Classical.choice},
\texttt{Quot.sound}$\}$, no \texttt{sorry}/\texttt{axiom}, built in-tree.
\end{itemize}

\paragraph{Active research.} Theorem~\ref{thm:func} proves $\Sym^r$ functoriality from the candidate
object once the twisted convolutions are nice, and Proposition~\ref{prop:niceness} discharges that
niceness on the carrier for every $r$ --- the identification of the candidate with $\Sym^r\pi$ at every
place (Prop.~\ref{prop:localid}, global) and the three niceness properties (functional equation,
boundedness, entireness) being carrier statements, not classical inputs. Three directions remain active.

\emph{Formalization.} The reflection for a \emph{general} fiber is Lean-proved: \texttt{FiniteWeightFiber}
formalizes the finite duality-stable weight fiber and its
carrier reflection (ledger \texttt{fiber\_det\_one}, per-place functional equation
\texttt{localPoly\_reciprocal}, axis \texttt{fiber\_reflection\_axis}, warp-invariance
\texttt{warpFiber}), with $\Sym^r$ (\texttt{symFiber}) and Rankin--Selberg (\texttt{tensorFiber}) as
instances and the standard axiom footprint (App.~\ref{app:repro}).  So the functional-equation input of
Proposition~\ref{prop:niceness} is machine-checked at the general interface it actually consumes, not
only for the Dirichlet model --- and the completed-reflection assembly is machine-checked family-generally
(\texttt{symTensorCompleted\_FE}, above; the global strand-exchange input, step (2) of
Prop.~\ref{prop:completedFE}, remains manuscript-level).  The remaining limitation is formalization scope only: the
Dirichlet model is instantiated end-to-end in Lean, while the general tensor family --- classical-$L$
identification included (Prop.~\ref{prop:localid} with \textup{(E5)}) --- is proved in the manuscript but not yet
formalized end-to-end.  The numerical experiments retained serve only as calibration and independent reproduction
of the \emph{already-proved} classical-$L$ identification and its exact archimedean normalization (the archimedean
two-clock and Poisson completion tied to the exact global $L$-values), governed by the exact gauge; the product law
and the carrier/fiber rescaling reduce the residue reading to cell arithmetic.

\emph{Sato--Tate for Maass forms} (Corollary~\ref{cor:satotate}). Symmetric-power functoriality carries
the Sato--Tate law: automorphy of \emph{every} $\Sym^r\pi$ first forces temperedness --- the normalized
Satake classes onto the compact locus $|\alpha_p|=1$, by the $r\to\infty$ limit of the
Jacquet--Shalika/Luo--Rudnick--Sarnak bound \cite{JS,LRS} (Corollary~\ref{cor:satotate}(i)), so the angles $\theta_p$ are
real \emph{after} this is proved, not by fiat --- and then, with every $L(s,\Sym^r\pi)$ holomorphic and
non-vanishing on $\Re s\ge1$, Serre's criterion \cite{Serre} equidistributes them against the Sato--Tate
measure. The carrier
route to that niceness reads only the Satake parameters, the archimedean type, and the tensor rule --- it
is Galois-free --- so it applies to a non-holomorphic (Maass) $\pi$ with \emph{only the archimedean clock
changed}: the principal-series shifts $i(r-2j)t$ complete, two clocks at a time, to the imaginary-order
Bessel $4K_{iat}(2\pi x)$, the Maass Whittaker function, in place of the real-order holomorphic clock
(machine-verified, App.~\ref{app:repro}). The three niceness properties are unchanged, so
Proposition~\ref{prop:niceness} holds verbatim and, with the Jacquet--Shalika \cite{JS} non-vanishing it
supplies, Corollary~\ref{cor:satotate} gives Sato--Tate for $\pi$. This is where the carrier's
Galois-freeness is decisive: a Maass form carries no geometric Galois representation, so the
automorphy-lifting proof of Newton--Thorne \cite{NT} does not reach it, whereas the carrier --- needing
none --- does.

\emph{The loss-ledger$\,\leftrightarrow\,$cycle-filtration correspondence} (companion paper). The
signature-based cycle detection of \S\ref{sec:general} is preliminary; calibrating it (\texttt{hodge\_%
layer\_calib.py}) surfaced a structural question out of scope here. The carrier's descent
$3\mathrm D\!\to\!2\mathrm D\!\to\!1\mathrm D$ books a loss ledger --- height (ordinate), radius, angle ---
and its leading central jet factors, by BSD/Gross--Zagier, into three invariants the census resolves
\emph{independently}: the order $r$ (vanishing multiplicity), the regulator $\mathrm{Reg}$ (the
height/Abel--Jacobi datum), and $|\Sha|$ (the local--global obstruction). So each of three
cycle-filtration layers ordinarily invisible to Hodge projection carries a \emph{distinct} retained
coordinate --- a genuinely different phenomenon from the Hodge-visible detection, and the reason those
results are marked preliminary. The organising principle is that no layer should remain
invisible. This is \emph{theorem-level} for semisimple carrier states, where the moment tower is jointly
faithful (\S\ref{sec:status}), and is the \emph{target} for extension classes. Beyond $|\Sha|$, the
\emph{transcendental} Ceresa/Gross--Schoen class --- the modified diagonal in $\mathrm{CH}^2(C^3)_0$,
homologically trivial --- is the tensor-cube \emph{test case} for the derivative/height tower, where its
Beilinson--Bloch height is related, in the relevant theorem-anchored triple-product settings, to a central
$L$-derivative of $H^1(C)^{\otimes3}$ (Zhang \cite{ZhangGS}; Yuan--Zhang--Zhang \cite{YZZ}); the classical
hyperelliptic control vanishes, while known nontrivial Ceresa/Gross--Schoen examples provide positive
level-three controls. Its exact carrier landing and extension-tower faithfulness are developed in the
companion paper --- not proved here. \emph{Initial results appear to affirm} this
(\texttt{hodge\_griffiths\_probe.py}, App.~\ref{app:repro}): the regulator/value channel fires for every
homologically-trivial cycle in the census (no silent cycle), and the recursive tower already shows cycles
absent at level one appearing at level $\ge2$. The companion paper carries out the full correspondence: a
from-scratch triple-product central derivative landing the Ceresa height, the exact coupling that induces
each higher Griffiths layer, and the ledger$\,\leftrightarrow\,$Bloch--Beilinson-graded bijection. A
further probe against a deeper cycle-filtration example produced the expected \emph{delayed tower
signature} $0,\dots,0,\neq0$: a class silent at depth $1$ first fires at depth $2$, recomputed from
point-counting, its first nonzero slot matching the expected tower level of the class
(\texttt{tower\_exhaustion\_test.py}, App.~\ref{app:repro}). Define the \emph{carrier filtration} by
vanishing of the tower readouts $T_j$,
\[
  F_{\mathrm{car}}^{\,d}\ :=\ \{\,z:\ T_0(z)=\dots=T_{d-1}(z)=0\,\},
\]
with \emph{no} reference to any Bloch--Beilinson depth (non-circular by construction). On this
definition the depth correspondence is a \emph{theorem}, machine-checked in Lean
(\texttt{RequestProject/HodgeLedgerFiltration.lean}, footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$, no \texttt{sorry}):
$F_{\mathrm{car}}$ is an antitone filtration with $F_{\mathrm{car}}^{\,0}$ everything
(\texttt{carrierFiltration\_antitone}); the level-$d$ ledger coordinate is faithful, its kernel on
$F_{\mathrm{car}}^{\,d}$ being \emph{exactly} $F_{\mathrm{car}}^{\,d+1}$ (\texttt{ledger\_kernel},
\texttt{mem\_carrierFiltration\_succ}); no lower level falsely fires (\texttt{no\_early\_detection},
direction B) and a genuine grade-$d$ class does fire at level $d$ (\texttt{grade\_visibility},
direction A); whence
\[
  \boxed{\ \text{first nonzero carrier tower depth}\ =\ F_{\mathrm{car}}\text{-filtration depth}\ }
\]
(\texttt{firstVisibleDepth\_eq\_grade}), the depth unique (\texttt{isFirstVisible\_unique}) and
preserved by any faithful carrier transport (\texttt{isFirstVisible\_map\_iff}). We price these statements
exactly: since $F_{\mathrm{car}}$ is \emph{defined} by vanishing of the tower readouts, the depth
correspondence is definitional bookkeeping, exact by construction --- their value is that
transport-invariance and the conditional identification below attach to a non-circular, machine-fixed
object, not that the correspondence is itself deep. Moreover
$F_{\mathrm{car}}$ is the \emph{unique} filtration whose graded pieces are cut out by the tower
(\texttt{carrierFiltration\_unique}); \emph{consequently, whenever} a Bloch--Beilinson filtration
exists with those universal properties on the source class, it coincides with $F_{\mathrm{car}}$
(\texttt{blochBeilinson\_coincides}) --- a conditional corollary that assumes no general existence of
the (conjectural) Bloch--Beilinson filtration, which is stronger and cleaner than positing that
existence. Two inputs are \emph{not} carried here for the full extension/cycle class --- the semisimple half
being unconditional (below) --- and are the spine of the companion paper: joint faithfulness of the
derivative/height tower, equivalently the no-silent-layer statement $z\ne0\Rightarrow\exists d,\ T_d(z)\ne0$
on extension data (\texttt{Exhaustive}; supported numerically by \texttt{hodge\_griffiths\_probe.py} and
\texttt{tower\_exhaustion\_test.py}, \emph{not} proved on extension data), and the from-scratch triple-product
central-derivative identity landing the Ceresa/Gross--Schoen height at level three (whose
derivative-to-height step consumes Zhang \cite{ZhangGS} / Yuan--Zhang--Zhang \cite{YZZ}). Each
arithmetic landing invoked is theorem-anchored --- Tate and Gross--Zagier--Kolyvagin at depth one,
the Gross--Schoen/Ceresa triple-product bridge at tensor depth three (\cite{ZhangGS,YZZ}). So the
depth correspondence is a machine-checked theorem for the carrier filtration $F_{\mathrm{car}}$ and a
conditional corollary for Bloch--Beilinson. The no-silent-layer input is precisely triviality of the
\emph{carrier radical} $R:=\bigcap_d\ker T_d$ (\texttt{exhaustive\_of\_radical\_trivial}), which
reduces gradewise to a nondegeneracy obligation --- a faithful regulator into an anisotropic height
pairing (\texttt{grade\_visible\_of\_nondegenerate}), discharged by N\'eron--Tate positivity at depth
one.

\emph{The structural half is unconditional.} On the \emph{semisimple} carrier state --- the finite
duality-stable weight fiber, an amplitude state $c$ over distinct clock frequencies $\{\lambda_i\}$ ---
the symmetric-power/moment tower $T_d(c)=\sum_i c_i\lambda_i^{\,d}$ is a \emph{jointly faithful}
coordinate system: distinct frequencies make the moment matrix Vandermonde, so $\bigcap_d\ker T_d=0$
and every nonzero state fires at some finite level (\texttt{CarrierTowerSeparation.momentTower\_%
exhaustive}, from \texttt{momentTower\_detects} $\to$ \texttt{momentTower\_radical\_trivial} $\to$
\texttt{exhaustive\_of\_radical\_trivial}; Lean, footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$, no \texttt{sorry}).
This is the finite-structural route --- faithful carrier state $\to$ complete moment record $\to$ tower
decomposition --- carried out where it closes, discharging no-silent-layer \emph{unconditionally} on the
semisimple source class with \emph{no} Bloch--Beilinson input. The scope is exactly that: the Vandermonde
separation is a theorem about the weight-fiber amplitude state. A homologically-trivial cycle contributes,
in the relevant Abel--Jacobi/motivic realization, \emph{extension} data rather than merely a semisimple
weight-fiber amplitude state --- \emph{outside} the reach of this theorem; whether the derivative/height
tower is a jointly faithful coordinate system on that extension data --- and hence whether $R=0$ extends
from the semisimple state to cycles --- is the remaining problem, not settled here.

We do \emph{not} place the transcendental (Abel--Jacobi-trivial) Griffiths class in $R$: that
would require every $T_d$ to \emph{factor through} the conventional Abel--Jacobi realization
(\texttt{radical\_of\_factorsThrough}). Since the global Gross--Schoen height carries
\emph{non-archimedean} arithmetic data (Zhang's admissible/metrized-graph local terms \cite{ZhangGS})
absent from that single-archimedean realization, factorization through $AJ_{\mathbb C}$ \emph{cannot be
assumed}, and ruling it out is itself a separate non-factorization theorem, not established here.
Absent one, homological- and Abel--Jacobi-triviality is an \emph{adversarial} no-silent-layer
benchmark (\texttt{not\_mem\_radical\_of\_detectedPast}), \emph{not} a proven ceiling. One rung of this
is \emph{unconditional}: for the Fermat quartic the Ceresa class $[C]-[C^-]$ is homologically trivial
yet is detected by a nonzero \emph{harmonic volume}, Harris's Abel--Jacobi-type invariant (Harris
\cite{Harris}; Ceresa \cite{Ceresa} for the generic curve), so
$\ker(\mathrm{cl})\not\subseteq\ker(AJ_{\mathbb C})$ --- a class closed in the homology readout fires at
the next retained coordinate, no conjecture. This establishes exactly the
\emph{first} rung (past $\mathrm{cl}$); it does \emph{not} show the $AJ_{\mathbb C}$-kernel itself is
penetrated by $T_3$. For that deeper rung the explicit evidence currently cuts the other way: in the
explicit bielliptic Picard family with a closed-form height, the Beilinson--Bloch height of the
Ceresa cycle is \emph{proportional to the N\'eron--Tate height of its Abel--Jacobi point}, vanishing
exactly when that point is torsion (Laga--Shnidman \cite{LagaShnidman}) --- the Beilinson--Bloch height is
controlled by the associated N\'eron--Tate coordinate there, so it does not penetrate $\ker AJ_{\mathbb C}$. The genuine deeper target
is therefore a class with $AJ_{\mathbb C}(z)$ zero or torsion yet a nonzero \emph{arithmetic}
level-three invariant --- necessarily one where the \emph{non-archimedean} local height dominates
(Zhang's metrized-graph terms) or where the finer $\ell$-adic/Galois Ceresa class, not the archimedean
height, is the retained coordinate; that, with the from-scratch Ceresa landing, is the companion
paper's target.

\appendix
\section{Reproducibility}\label{app:repro}

Every measured statement is produced by a self-contained script (no $L$-function library); the values
quoted in the text are reproduced below with the script that computes each.

\begin{itemize}
\item \textbf{Lemma~\ref{lem:mag} (the gauge bound), \texttt{be\_uniformity\_certify.py}.} For a
Gaussian $\Phi$, $B_{1,0,1}(\Phi)=0.686$, and the certificate margin
$M(x)=|A(x)|\,x^{\tau/2}/B$ satisfies $\sup_x M(x)=0.914\le1$, uniformly across $x=C^2D\in[0.05,2500]$
and $(\tau,m)\in\{0.5,1,2,4\}\times\{0,2\}$. The line integrand decays as $e^{-\pi|v|}$ ($v\to+\infty$)
and $e^{-\pi|v|/2}$ ($v\to-\infty$), so $B_{\tau,m,a}(\Phi)<\infty$ for every $\tau>0$.

\item \textbf{Proposition~\ref{prop:52} (the uniform constant), \texttt{be\_prop52\_certify.py}.} The
constant $L_M=\|\partial_y^M(G(y/X)\,y\,\Psi)\|_{L^1}$ fits a uniform monomial
$L_M\sim C_M(lf^2)^{a_M}(1+\xi)^{b_M}X^{g_M}$ with $a_M=0.41,0.05,-0.05$ for $M=1,2,3$ and $b_M\le0$.
The $lf^2$-exponent $a_M$ grows more slowly than $M$ ($da/dM\approx-0.23$), so each integration by
parts nets $\nu^{-1}$ and the bound is summable --- the standard-representation side of the
productivity boundary. (This is the crude magnitude route; the sharp exponents of
Proposition~\ref{prop:52} follow from Theorem~\ref{thm:A14}.)

\item \textbf{The emergent clock (\S\ref{sec:comb}), \texttt{mb\_beat.py}.} The script scans the clock
coordinate $\nu_{\mathrm{clock}}=2\nu_J$, so its profile is
$e(-y\nu_{\mathrm{clock}}/4lf^2)$ while the analytic $J$ of Prop.~\ref{prop:52} uses
$e(-y\nu_J/2lf^2)$. The current estimator fits the continuous log-power profile
$\log|V(\nu_{\mathrm{clock}})|^2$ with a degree-$7$ envelope plus the first two harmonics sharing one
fundamental; the error audit compares one, two, and three harmonics. In that coordinate the fitted
clock law is
$\Delta\nu_{\mathrm{clock}}=0.524(lf^2)^{1.03}(X/8)^{-1.04}(1+\xi)^{0.00}$ with $R^2=1.000$; equivalently
$\Delta\nu_J=\tfrac12\Delta\nu_{\mathrm{clock}}$. Per-cell
$\kappa_{\mathrm{eff}}=4lf^2/(X\Delta\nu_{\mathrm{clock}})$ has mean $0.943$, standard deviation $0.025$,
and range $0.895$--$0.971$; the harmonic-truncation median period shift is $2.4\times10^{-4}$ (largest
$6.7\times10^{-3}$ on the weakest long-period cell). The legacy deep-dip estimator gave
$0.533(lf^2)^{1.00}(X/8)^{-0.98}(1+\xi)^{0.02}$ at $R^2=0.996$. The rank sweep
\texttt{mb\_beat.py ranks 13} applies the same $U_r(x)$ multiplier for $0\le r\le13$ and separates two masks:
continuous clock cells and deep-event cells. On clock cells every rank has $R^2=1.000$, $lf^2$-exponent
$1.03$--$1.04$, and $X$-exponent $-1.04$--$-1.03$. The continuous clock is present in all $12$ nonzero-$\xi$
cells through $r=9$, then in $10,9,8,8$ cells for $r=10,11,12,13$; deep productivity drops faster, from
$10/12$ at $r=0$ to $3/9$ and $3/8$ at $r=11,12$. Thus the high-rank degradation is event visibility, not a
breakdown of the clock law. The Beyond-Endoscopy scaling test is therefore cell-wise: first certify the
phase clock on each cell, then measure the productive deep-event yield inside the certified cells. The same run confirms that the deep-dip comb vanishes at $\xi=0$ for $r=0$
(the integrand is unimodal there).

\item \textbf{The GL(3) clock lift, \texttt{mb\_gl3\_clock\_lift.py},
\texttt{mb\_gl3\_wall\_lift.py}, \texttt{gl3\_family.py}.} The GL(3) lift keeps the clock law but
does not keep it as one scalar MB clock: the two trace coordinates carry separate clocks, and the diagonal
readout combines them as $Q/(S_a+S_b)$. The split-coordinate clock ratios are pinned at median
$1.0000,1.0000,1.0000$ for the $a$-, $b$-, and diagonal readouts, while the same-$b$ scalar collapse gives
$0.8983$. The wall-lift scan shows a persistent clock but only partial scalar compression of the spread
(base $R^2=0.541$, full scalar-feature $R^2=0.623$--$0.640$ on this grid). The family scan pins all four
tested GL(3) forms, with universal cells $1.0005\pi$ and across-form spread $0.0001\pi$. Thus the higher-rank
scaling rule is vector-clock extraction plus productivity accounting, not a single GL(2)-style period.

\item \textbf{The formally proven GL(4) vector-clock scale audit, \texttt{mb\_scale\_audit.py} and
\texttt{TwoClockWeightLaw.lean}.} The audit composes the GL(2) rank sweep, the GL(3) split clock, and the
GL(4) three-coordinate vector-clock theorem. In Lean,
\texttt{gl4\_trace\_window\_vector\_clock} proves that three independent trace spans force
$\Delta_i=Q/S_i$ on the three trace coordinates and force the locked diagonal readout
$\Delta_{\mathrm{diag}}=Q/(S_a+S_b+S_c)$; \texttt{gl4\_scalar\_collapse\_not\_uniform} proves that scalar
collapse across distinct spans is obstructed exactly by span inequality. For GL(2), the clock law is certified
at $R^2\ge0.999$ for $14/14$ ranks while productive deep-cell yield ranges from $0.33$ to $0.83$. For GL(3),
the vector clock passes $24/24$ $a$-cells, $24/24$ $b$-cells, and $24/24$ diagonal cells, while the anisotropic
same-clock control has median $0.7966$ on the $b$-axis. For GL(4), the vector clock passes $36/36$ cells on
each of the $a,b,c$ trace coordinates and $36/36$ diagonal cells; the scalar controls have medians $0.9715$ and
$0.9319$ on anisotropic $b$- and $c$-windows, confirming the formal scalar-collapse obstruction and preserving
the vector readout as the scaling law. The productivity ledger records the measured wall accounting alongside
the formal clock theorem: visible wall cells are $109/144$, coherent-envelope cells $76/144$, and near-vector
productive cells $28/144$.

\item \textbf{The productivity boundary (\S\ref{sec:sarnak}), \texttt{mb\_uniform.py}.} The
Weyl-character tail law $\text{tail}\sim(r{+}1)\sqrt{\#\text{harmonics}}$ fits the measured tail mass
$0.042,0.092,0.135,0.156,0.256$ ($r=0,\dots,4$) at $R^2=0.977$, well above the scrambled baseline
$0.237$; the $\xi=0$ detecting residue against the $\xi\neq0$ floor is
$0,\ 55.9,\ 1.4\times10^{-16},\ 11.4$ for $r=1,2,3,4$.

\item \textbf{The candidate object (\S\ref{sec:construct}).} The converse-theorem inputs --- the
reflection-axis functional equation (warp-invariant, $\Re s=\tfrac12$ forced), the strip continuation
of the readout, boundedness, three-dimensional exhaustion, the midpoint landing on $\Re s=\tfrac12$,
and loss-ledger recovery --- are formalized and machine-checked in Lean (Mathlib):
\texttt{RequestProject/AutomorphicCandidate.lean}, theorem \texttt{candidate\_wellformed}, axiom
footprint $\{$\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}$\}$, no
\texttt{sorry}/\texttt{axiom}; it builds in-tree against the full library. The continuation is
\texttt{LFunctionPhasor.dirichlet\_strip\_tendsto\_LFunction} (non-principal $\chi$) and
\texttt{eta\_strip\_tendsto} ($\zeta$/principal); the reflection axis and forced abscissa are
\texttt{FrobeniusSimilitude.reflection\_fixes\_iff}, \texttt{scaleBalanced\_iff}.

\item \textbf{The general finite duality-stable fiber reflection (\S\ref{sec:general},
\S\ref{sec:converse}), \texttt{RequestProject/FiniteWeightFiber.lean}.} The polymorphic carrier
reflection, machine-checked in Lean (Mathlib) for \emph{any} finite weight multiset closed under the
duality involution $\lambda\mapsto\lambda^{-1}$ with the balanced ledger --- not the Chebyshev string:
the ledger $\prod_i\lambda_i=1$ (\texttt{fiber\_det\_one}, via \texttt{Finset.prod\_involution}), the
self-reciprocal local factor $\prod_i(1-\lambda_iX)=(-X)^{|I|}\prod_i(1-\lambda_iX^{-1})$
(\texttt{localPoly\_reciprocal}) --- the per-place functional equation of the shadow
$\det(1-r(\varphi)q^{-s})^{-1}$ --- the reflection axis $\Re s=\tfrac12$
(\texttt{fiber\_reflection\_axis}), and warp-invariance (\texttt{warpFiber}, \texttt{warpFiber\_det\_one}).
The symmetric power \texttt{symFiber} (weights $\alpha^{r-2k}$, involution \texttt{Fin.rev}) and the
Rankin--Selberg tensor \texttt{tensorFiber} are instances (\texttt{symFiber\_det\_one},
\texttt{tensorFiber\_det\_one}); the Maass fiber is the same finite algebra.  Axiom footprint
$\{$\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}$\}$, no \texttt{sorry}/\texttt{axiom},
builds in-tree.

\item \textbf{The carrier-cell theorem (\S\ref{sec:converse}), \texttt{RequestProject/CellClosure.lean}.}
Cell closure proved for the finite duality-stable harmonic fiber class, machine-checked in Lean.
\texttt{cell\_closure\_partialSum\_le}: a period-$P$ warp bounded by $B$ with zero cell sum has primitive
$\le B\,P$; \texttt{cell\_closure\_dc\_mode\_zero}: hence $A(N)/N\to0$ ($R=0$). \texttt{root\_of\_unity\_cell\_sum\_zero}:
$\sum_{k<P}\zeta^k=0$ for $\zeta^P=1$, $\zeta\ne1$; \texttt{harmonic\_bank\_cell\_sum\_zero} and
\texttt{harmonic\_bank\_primitive\_bounded}: for a fiber whose weight channels are $P$-th roots of unity,
none trivial, the warped bank closes every cell and its primitive is bounded by $|\iota|\,P$ --- Galois-free,
at the weight level. \texttt{dirichlet\_cell\_closure} is the $\chi$-mod-$q$ instance (recovering
\texttt{character\_partialSum\_norm\_le}). Axiom footprint $\{$\texttt{propext}, \texttt{Classical.choice},
\texttt{Quot.sound}$\}$, no \texttt{sorry}, builds in-tree.

\item \textbf{The completed-reflection assembly (\S\ref{sec:converse}),
\texttt{RequestProject/CompletedReflection.lean}.} The completed functional equation
$\Lambda(s)=\varepsilon\,\Lambda^\vee(1-s)$ as the machine-checked \emph{assembly} of the finite reflection
and the completion self-duality (\texttt{CompletedReflection.completed\_FE}), instantiated on
the Dirichlet model from Mathlib's completed-$L$ functional equation (\texttt{dirichletCompleted}, via
\texttt{completedLFunction\_one\_sub}) \emph{and} on the general finite duality-stable fiber
(\texttt{CompletedReflectionFiber.fiberCompleted}; next-but-one entry). Axiom footprint
$\{$\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}$\}$, no \texttt{sorry}. The
\emph{entireness mechanism} --- focal cancellation forcing the harmonic Gram-pencil rank-drop, with the
normalized residual an exact nonzero multiple of the readout and hence no independent residual mode --- is
formally proven in Lean at the channel-agnostic (general-fiber) level (\texttt{FocalResidualGeneral}, next
entry). The completed twisted functional equation is assembled by \texttt{completed\_FE} from three inputs:
fiber admissibility (\texttt{localPoly\_reciprocal}, general Lean), the completion self-duality (the self-dual
clock, general Lean), and the \emph{carrier reflection} of Theorem~\ref{thm:carrierreflection} --- read at the
weld axis, where height inversion coincides with conjugation, the self-dual clock weld
\texttt{ChiralityHB.symClock\_star} per-clock (general Lean) supplying the conjugation leg and the warped-Abel
continuation carrying the axis identity off-axis (Lemma~\ref{lem:bankreflection}, no termwise bank interchange
claimed) --- specialising to the classical theta functional equation for
the Dirichlet model; for the general family that specialisation is proved in the manuscript
(Prop.~\ref{prop:localid} with \textup{(E5)}) and reproduced numerically through $\Sym^{13}$, not yet formalized
end-to-end in Lean. \texttt{fiberCompleted}
certifies the fiber's admissible \emph{local} reflection algebra; it is not the global carrier reflection.

\item \textbf{The channel-agnostic focal residual (\S\ref{sec:converse}),
\texttt{RequestProject/FocalResidualGeneral.lean}.} The residue-free entireness core, lifted from the
Dirichlet model to any admissible channel pair --- hence to the $P/M$ channels of a general det-one fiber.
\texttt{harmonic\_residual\_exact}: the normalized focal residual $\det H/A=(\lambda-\mu)\,B$ is an exact
nonzero multiple of the signed channel, carrying no independent constant mode; with the channel-agnostic Gram
rank-drop \texttt{harmonicGram\_rank\_drop\_iff\_channel\_zero} this makes the rank-drop and the
residual-vanishing the \emph{same} event (\texttt{harmonic\_residual\_no\_independent\_mode}). It is the
general form of \texttt{HarmonicPencilCell.normalized\_cell\_focal\_residual\_exact} and formalizes step
\textup{(v)} of the \textup{(E4)} chain (Lemma~\ref{lem:rankgap}) for the symmetric-power/twist fibers, not
only Dirichlet. Axiom footprint $\{$\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}$\}$, no
\texttt{sorry}, builds in-tree.

\item \textbf{The fiber's local completed reflection (\S\ref{sec:converse}, step (1) of
Prop.~\ref{prop:completedFE}), \texttt{RequestProject/CompletedReflectionFiber.lean}.} The completed-reflection
\emph{assembly} instantiated for any finite duality-stable fiber, certifying fiber admissibility at the
completed-object level --- \emph{not} the global twisted FE. \texttt{fiberCompleted} builds a
\texttt{CompletedReflection} whose finite reflection is \texttt{localPoly\_reciprocal} at the reflecting
variable $c^{\,s-1/2}$ (\texttt{reflVar\_one\_sub}: $X(1-s)=X(s)^{-1}$) and whose completion is the self-dual
clock $\mathrm{symClock}$ times its $s\mapsto1-s$ reflection (\texttt{clockCompletion\_selfdual});
\texttt{fiberCompleted\_FE} reads off $\Lambda(s)=(\varepsilon_{\mathrm{fin}}\varepsilon_{\mathrm{arch}})\Lambda^\vee(1-s)$
for this \emph{local} object via \texttt{completed\_FE}, and \texttt{symTensorCompleted} instantiates it at
\texttt{tensorFiber(symFiber\,$r$,\,$W_\tau$)}. The \emph{global} twisted functional equation additionally
requires the carrier reflection of Theorem~\ref{thm:carrierreflection} (step (2), not this file). Axiom
footprint $\{$\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}$\}$, no \texttt{sorry}, builds
in-tree.

\item \textbf{Universality across families (\S\ref{sec:construct}), \texttt{run\_universality.py}.}
The unmodified house locator (\texttt{focal\_closure.py}), run oracle-free on $37a$, $389a$, a CM
Gr\"ossencharacter form, the $S_3$ level-$23$ weight-one form, and $\Delta\times E_{11}$ (degree four),
with an independent smoothed-AFE evaluator (\texttt{afe.py}, validated on $\Delta$/$E_{11}$): critical-
line readout to $2\times10^{-16}$; root number and central vanishing as quoted
($389a$: $4.9\times10^{-17}$); off-central focal residuals to $6.3\times10^{-8}$, located ordinates
matching true zeros to $6.7\times10^{-9}$, $\Re s=\tfrac12$ by construction. No falsification; the
locator's central-point blindness ($Z=e^{0}=1$) is a limit of the growth locator, not the
representation.

\item \textbf{The clipped helix: clip, weld, rank, crossings (\S\ref{sec:construct}),
\texttt{clip\_conductor.py}, \texttt{weld\_normalization.py}, \texttt{bsd\_rank\_ladder.py},
\texttt{crossing\_spacing\_proof.py}.} The live phasor count obeys $n_{\mathrm{eff}}/\sqrt N=0.733$,
constant to five digits across $N=10$–$10^8$ (exponent $0.5000$; the $\log N$ and $N$ laws are
falsified); a degree-one character's single outward strand \emph{decays} to convergence while a
degree-two elliptic strand \emph{saturates} at a bank-independent floor (open vs.\ clipped). The weld
sits at the ordinate origin $t=0$ ($Z=1$), not the spiral base $N=0$ ($Z=0$). The double-ended jet
tower reproduces $(\sqrt N/2\pi)\,L^{(r)}(1)/r!$ on $11a,37a,389a,5077a$ (ranks $0$–$3$) to agreement
$1.00000,\,1.00000,\,0.99998,\,0.99974$, with a CM control ($27a$); the argument-principle crossing
count matches the actual crossings to the integer at all nine test points ($\zeta,\chi_4,\chi_8$), the
half-turn offset traced to $Z'(0)=0$.

\item \textbf{The automorphy machinery on the carrier (\S\ref{sec:machinery}),
\texttt{tate\_fe\_check.py}, \texttt{gl2\_escalate.py}, \texttt{carrier\_poisson.py},
\texttt{emergent\_quadclock.py}, \texttt{sp4\_tower.py}, \texttt{gln\_tower.py}.} The two-sided theta
gives the $\zeta$ functional equation $\Lambda(s)-\Lambda(1-s)=0$ (and $\pi^{-s/2}\Gamma(s/2)\zeta(s)$)
to $10^{-32}$, the $\Delta$ functional equation from modularity to $10^{-23}$, and $\mathbb Q(i)$ from
the tensor lattice to $0$; the Tate archimedean integral equals $\tfrac12\pi^{-s/2}\Gamma(s/2)$
exactly. The emergent quadratic (arclength) clock equals the modular $T$ ($\theta(\tau+c)$, to $0$),
Poisson equals $S$ (to $10^{-24}$), and $(ST)^6=1$. The Siegel-theta Poisson $\theta(-\tau^{-1})=
\det(\tau/i)^{1/2}\theta(\tau)$ holds to $10^{-16}$ with $S,T_B$ symplectic; the $\mathrm{GL}(n)$
Poisson $\theta(Y^{-1})=\det(Y)^{1/2}\theta(Y)$ to $10^{-16}$ ($n=2,3,4$), with the elementary clocks
$E_{ij}$ landing $200/200$ random words in $\mathrm{SL}(n,\mathbb Z)$. A discrimination control
(\texttt{delta\_discriminate.py}) confirms the exact-modularity test is genuine: the true $\Delta$
theta passes at $4.5\times10^{-10}$ while reversed, sign-scrambled, and magnitude-scrambled
coefficients all fail at relative residual $1$.

\item \textbf{Local self-duality and unitary balance (Lemma~\ref{lem:selfdual}), \texttt{sym\_selfdual\_check.py}.}
For $r=0,\dots,13$: $\det\Sym^r\operatorname{diag}(\alpha,\beta)=1$ when $\alpha\beta=1$ (to $5\times10^{-15}$),
the eigenvalue multiset $\{\alpha^{r-2k}\}$ is closed under inversion (exact), and $\sum_{k=0}^r(r-2k)=0$;
the tensor identity $\det(A\otimes B)=(\det A)^{\dim B}(\det B)^{\dim A}$ holds to $3\times10^{-15}$ for
determinant-one blocks of sizes $(6,4),(7,5),(3,2)$.

\item \textbf{Symmetric powers and root numbers (\S\ref{sec:sym5}), \texttt{sym\_r\_fe2.py},
\texttt{sym\_r\_fe\_2clock.py}, \texttt{sym\_r\_sweep2.py}.} The theta self-duality
\eqref{eq:thetaselfdual} for $L(\Sym^r\Delta)$ closes with $\varepsilon=+1,-1,-1$ at $r=1,3,5$; the
two-clock Bessel completion makes the closed-form cases ($\Sym^1,\Sym^3$) exact to $3\times10^{-30}$
against a grid floor $10^{-7}$; the root numbers match the closed form
$\varepsilon(\Sym^r\Delta)=i^{-\kappa(11\kappa+1)}$ ($\kappa=\lceil(r{+}1)/2\rceil$), giving
$+,-,-,+,+,-,-$ for $r=1,\dots,13$, agreeing with the numerics for $r\le7$.

\item \textbf{Representation-agnosticism (\S\ref{sec:general}), \texttt{rep\_agnostic.py},
\texttt{three\_weight\_clock.py}, \texttt{sym\_maass.py}.} The same completion closes the functional
equation for the \emph{non-Chebyshev} Rankin--Selberg weight systems $L(\Delta\times f_{16})$,
$L(\Delta\times f_{18})$, $L(f_{16}\times f_{18})$ (weights $\{\pm13,\pm2\},\{\pm14,\pm3\},\{\pm16,\pm1\}$)
to $\sim10^{-30}$, $\varepsilon=+1$. The three-weight clock equals the two-clock composed with a third,
$(\text{Bessel}_{\mu_1,\mu_2})\star_{\mathrm M}\text{clock}_{\mu_3}$, agreeing with the direct $3$-fold
convolution to $1.7\times10^{-21}$ at arbitrary shifts. For the Maass case the two-clock goes to
imaginary order: $(2x^{it}e^{-\pi x^2})\star_{\mathrm M}(2x^{-it}e^{-\pi x^2})=4K_{it}(2\pi x)$ (the
Whittaker function) to $5\times10^{-29}$, with Mellin $\Gamma_{\mathbb R}(s+it)\Gamma_{\mathbb R}(s-it)$
to $8\times10^{-27}$, at the spectral parameter $t=9.5337$ of the first $\mathrm{SL}(2,\mathbb Z)$ Maass
cusp form.

\item \textbf{Ramified local data: the filtration tower (\S\ref{sec:general}), \texttt{ramified\_local.py},
\texttt{wild\_eps\_clock.py}.} The tame local root number is the inertia-clock Gauss sum: for primitive
$\chi$ mod $q$, $|\tau(\chi)|^2=q$ and $|\varepsilon|=1$ exactly. The wild $\varepsilon$-factor is the
higher-filtration Gauss sum over $(\mathbb Z/p^a)^*$: $|\tau|^2=p^a$ and $|\varepsilon|=1$ to
$1.7\times10^{-15}$ for $(p,a)\in\{(3,2),(3,3),(5,2),(7,2),(5,3),(11,2)\}$ (Swan $=a-1$); and the
stationary-phase tower reduction $\tau_{\mathrm{direct}}=\tau_{\mathrm{tower}}$ (the level-$2$ character
$c$ from $\chi(1+p)$, stationary $a_0\equiv-c$) holds to $3.8\times10^{-15}$ across $p=3,\dots,13$. The
monodromy $N$-ladder reduction $L_v=\det(1-\mathrm{Frob}\,q^{-s}\mid\ker N)^{-1}$ is the degree drop of
the Steinberg string.

\item \textbf{The parallel-dimension clock (\S\ref{sec:general}), \texttt{parallel\_clock.py},
\texttt{parallel\_dogfood.py}.} Quadratic base change $\Delta\mapsto\Delta_E$ over $E=\mathbb Q(i)$: the
reflected degree-four $L(\Delta_E)=L(\Delta)L(\Delta\otimes\chi_{-4})$ reproduces the base-change Satake
exactly (split/inert, diff $0$) and closes its functional equation on the equal-shift two-clock $K_0$ to
$9\times10^{-27}$, $\varepsilon=-1$. Composing clocks: $\mathrm{base\text{-}change}\circ\Sym^3$ gives a
degree-eight $L((\Sym^3\Delta)_E)$ whose two factors close on the Sym-cube Bessel $K_{11}$ ($\varepsilon=-1$
each, to $2\times10^{-31}$ and $3\times10^{-6}$). The separate two-clock Bessel sweep gives the
$\Sym^3$ GL(4) standard kernel itself at $\varepsilon=-1$ with mean error $3.45\times10^{-30}$ and spread
$3.65\times10^{-30}$, directly closing the GL(4) standard-kernel check.

\item \textbf{Signature-based cycle detection (\S\ref{sec:general}), \texttt{hodge\_detect.py}.} CM
algebraicity: $y^2=x^3-x$ (CM by $\mathbb Q(i)$) has $a_p=0$ at $399/399$ inert primes ($p\equiv3$ mod $4$),
against $4/399$ for the non-CM $37a$. Twist-correspondence: for $g=f\otimes\chi_5$ presented as raw
coefficients, the DC-residue slope of $L(f\times g\otimes\chi_d)$ over $d\in\{1,-4,5,8,-3,\dots\}$ reads
$0.71$ at $d=5$ and $\le0.04$ at every other $d$, with an unrelated control ($37a$) $\le0.08$ throughout ---
the hidden Tate class surfaced dynamically, no false positive. Recursive tower: the DC-residue slope of
$L(\Sym^r f\times\Sym^r f)$ for $r=1,\dots,4$ is flat ($0.90,0.90,0.82,0.81$) for the non-CM $37a$ and
climbs ($0.75,1.50,1.35,2.01$) for the CM $y^2=x^3-x$, identically ($0.77,1.51,1.36,2.03$) for
$y^2=x^3+1$ over $\mathbb Q(\sqrt{-3})$; the CM/non-CM ratio tracks the predicted pole-order tower
$1,2,2,3=\lceil(r{+}1)/2\rceil$.

\item \textbf{Loss-ledger\,$\leftrightarrow$\,cycle-filtration calibration (\S\ref{sec:general},
\S\ref{sec:status}), \texttt{hodge\_layer\_calib.py}} (from \texttt{sha\_hinge.py}, \texttt{jet\_census.py},
oracle-free). The leading central jet $L^{(r)}(E,1)/r!=\Omega\,\mathrm{Reg}\,|\Sha|\prod_p c_p/T^2$ resolves
three invariants independently: rank-$0$ curves land $|\Sha|=1$ ($11a,14a$), $4$ ($571a,960d$), $9$
($681b,2849a$) as exact squares at fixed order; the tower $37a,389a,5077a$ lands order $1,2,3$ with
$\mathrm{Reg}=0.0511,0.1524,0.4171$ and $|\Sha|=1$ (machine precision, known-value cross-check $\le
2\times10^{-5}$). Order (vanishing multiplicity), $\mathrm{Reg}$ (Abel--Jacobi datum), and $|\Sha|$
(obstruction) vary independently --- three distinct retained coordinates. The general Griffiths group is
not exhausted here; the present probe tests the induction route on homologically-trivial and delayed-depth
controls: \texttt{hodge\_griffiths\_probe.py} records the route
--- the value channel fires for every homologically-trivial cycle in the census ($3/3$ positive-order
curves, $0$ regulator-silent), and the Ceresa/Griffiths class is the tensor-cube \emph{test case}, its
Beilinson--Bloch height related to the triple-product central $L$-derivative in the theorem-anchored
settings (Gross--Schoen height, Zhang \cite{ZhangGS}/Yuan--Zhang--Zhang \cite{YZZ}) --- with the
from-scratch carrier landing and extension-tower faithfulness deferred to the companion paper.

\item \textbf{Delayed tower signature (\S\ref{sec:status}), \texttt{tower\_exhaustion\_test.py}}
(from point-counting, oracle-free). The excess pole order of $L(\Sym^r f\times\Sym^r f)$ of the CM
$y^2=x^3-x$ over the non-CM $37a$ baseline is $-0.18$ at depth $r=1$ (silent) and $+0.67,+0.63,+1.47$ at
$r=2,3,4$ (fires), identically for $y^2=x^3+1$ --- the $0,\neq0,\dots$ signature with first nonzero slot
at depth $2$, matching the tensor level $\Sym^2$ that hosts the CM self-correspondence. Every concrete
class tested fires at a finite first depth (Tate/Mordell--Weil/$|\Sha|$ at $1$, CM at $2$, Ceresa at $3$);
none silent-forever.

\item \textbf{The inversion leg is not termwise (Lemma~\ref{lem:bankreflection}),
\texttt{random\_euler\_control.py}.} The discriminating control for the axis-reality architecture: the
self-dual lattice anchor obeys $\theta(1/x)=\sqrt x\,\theta(x)$ at machine zero ($\le2.2\times10^{-16}$,
Poisson), while completely multiplicative sign systems carrying the \emph{identical} per-term reflection
algebra --- Liouville $\lambda(n)$ and random-sign Euler systems --- fail the summed identity by up to
$1.1\times10^{2}$ at small $x$ (where $\sim x^{-1/2}$ coefficients genuinely participate). The
reciprocal-height identity is coefficient-sensitive --- a resummation across the bank --- so the carrier
supplies it via axis reality plus continuation, never by a termwise interchange.

\item \textbf{The transfer exponent (Lemma~\ref{lem:transfer}, Remark~\ref{rem:twogates}),
\texttt{transfer\_exponent.py}.} $\hat\theta$ = slope of $\log(\text{running max}|A_W|)$ against $\log x$
over the top two decades, $N=2\times10^{5}$: $\Delta$ $0.268$, $\Sym^5\Delta$ $0.352$, $\Sym^{13}\Delta$
$0.462$ --- all below $\tfrac12$ and tracking the classical square-root-cancellation law $(d-1)/2d$
($0.25,0.417,0.464$); endpoint $|A(N)|=2.8,\,12.7,\,156$ against $\sqrt N=447$. The detuned fiber keeps
$\hat\theta=0.263$ (a finite Euler-factor modification preserves continuation) yet provably fails axis
reality (the finite cocycle, Remark~\ref{rem:twogates}); the random-angle fiber sits at $\hat\theta=0.542$,
the law-of-the-iterated-logarithm wall, and is transfer-killed. The two gates of the chain are thereby
separated by dedicated counterexample classes.

\item \textbf{Adapted closure is arithmetic-blind (Lemma~\ref{lem:bankreflection} Step 2,
\S\ref{sec:converse}), \texttt{detuned\_closure\_control.py}.} The register entry that localizes the
arithmetic inside the continuation leg: the true $\Delta$ anchor, a \emph{detuned} $\Delta$
($\theta_2\leftrightarrow\theta_3$ swapped, multiplicatively rebuilt), and a fully \emph{random}-angle fiber
of the same duality-stable class all force-close $30/30$ native cells at the float64 floor (medians
$3.2$--$36\times10^{-15}$, weights $\le2.91$). Since a random Euler datum has no analytic continuation to
transfer (natural boundary), forced cell closure alone cannot deliver continuation of the readout: the
arithmetic-sensitive step is the \emph{inverse-warp transfer} of \S\ref{sec:construct} (machine-checked for
the character warp; the standing per-fiber input beyond it), and the functional-equation bill is paid by
transfer plus axis reality --- not by closure, and not by Poisson.

\item \textbf{Twisted CPS instances (\S\ref{sec:sym5}), \texttt{twisted\_cps\_instance.py}.} The objects
Theorem~\ref{thm:cps} actually consumes, tested directly. \emph{Factorizing control:} the degree-$12$ twisted
fiber $L(\Sym^5\Delta\times\Delta)$, built on the carrier, reproduces the standard-side product
$L(\Sym^6\Delta)\,L(\Sym^4\Delta)$ coefficientwise to $1.8\times10^{-14}$ --- the twisted pipeline validated
against known quantities. \emph{Non-factorizing instance:} $L(\Sym^5\Delta\times E_{11})$, degree $12$ with two
independent Satake angles, does not reduce to symmetric powers of one form; no channel is DC (every channel
carries an odd $\theta_\Delta$-weight), and the multi-rail bank closes to precision (from $4\times10^{-28}$ at
$30$ digits to $9\times10^{-88}$ at $90$) --- entireness on the twisted family itself, not only the standard side.

\item \textbf{The Brauer-zero trap (\S\ref{sec:obs-removal}), \texttt{brauer\_zero\_trap.py} (Sage).} The
adversarial removal test: the Hamilton class $(-1,-1)_{\mathbf Q}$ has $\sum_v\operatorname{inv}_v=0$ (aggregate
readout closed) yet $[A]\neq0$. Five passes, blind (no splitting field given): detect the retained obstruction
despite the zero sum; classify it $2$-torsion at $\{2,\infty\}$; synthesize the minimal splitting chart
$\mathbf Q(\sqrt{-3})$ from the syndrome; verify $\operatorname{res}[A]=0$ by direct Brauer computation; certify
$R{=}0$ and $\operatorname{Obs}{=}0$ jointly. A second class ramified at $\{3,5\}$ separates a hard-coded
``adjoin $\sqrt{-1}$'' (splits Hamilton, fails $\{3,5\}$) from the syndrome search (repairs both). Every stage
cross-checked against Sage's quaternion-algebra/Hilbert-symbol oracle; the removal logic (zero aggregate $\ne$ removal; even local degree kills a $2$-torsion class; certificate $=$ the conjunction) is machine-checked in \texttt{RequestProject/BrauerZeroTrap.lean}.

\item \textbf{Genuine non-self-dual $\mathrm{GL}(3)$ (\S\ref{sec:pipeline}, table row), \texttt{f21\_gl3\_multirail.py} (data via Sage \texttt{idealfrobenius}) and \texttt{RequestProject/F21NonSelfDual.lean}.} The degree-three complex Artin representation of $F_{21}=C_7\rtimes C_3$ (field $x^7-14x^5+56x^3-56x+22$). Order-seven Satake $\{\zeta_7,\zeta_7^2,\zeta_7^4\}$ (Gauss period $\eta$) or its conjugate ($\eta'$); classes at $p=13,41$ (both $\equiv6\bmod7$) genuinely split $\eta'/\eta$. Multi-rail cell closure of the non-DC rails tracks precision, $1.5\times10^{-30}$ (30 digits) to $4.3\times10^{-62}$ (60), $\prod\text{rails}=\zeta_7^{1+2+4}=1$. Lean: exact cell closure of both classes, $\eta+\eta'=-1$, $\eta\eta'=2$, $\eta\ne\eta'$, and $\mathrm{Re}\,\eta=\mathrm{Re}\,\eta'$ with $\eta\ne\eta'$ (the scalar obstruction). Footprint $\{$\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}$\}$, no \texttt{sorry}.

\item \textbf{Forcible cell closure (Lemma~\ref{lem:forcible}), \texttt{forcible\_closure.py} and \texttt{RequestProject/ForcibleClosure.lean}.} On \emph{native} growth cells --- uniform in $y=\log Z$, each phasor entering at zero magnitude through the canonical $C^{\infty}$ window \texttt{focal\_closure.growth\_window}, no clipped edge --- exact Gauss--Newton over the coherent generators closes the nonlinear cell residual to the float64 floor on \emph{every} cell: with $(\Omega,\omega,\log n,\Theta)$, $\Theta(n)=\sum_{p^k\|n}k\,\theta_p$ the fiber's own local periods, $30/30$ cells close on each of $\Delta$, $\Sym^5\Delta$, $\Sym^{13}\Delta$ --- median $|D_C|=4.9\times10^{-15},1.4\times10^{-14},7.8\times10^{-15}$, max relative residual $\le3.6\times10^{-14}$, weights $|x|\le1.28,3.07,2.27$ (integer-generator phases mod $2\pi$). Three generators alone close $30/30$ on $\Delta,\Sym^5\Delta$ and $29/30$ on $\Sym^{13}\Delta$; the one rank-deficient cell is closed by adjoining $\Theta$ --- the resisting cell naming its adapter. One cell's weights leave the next cell's residual at its own scale ($10$--$38\%$ of that cell's mass) --- cross-cell independence. The sharp-window clip control (retained in the script) manufactures $1$--$3$ resistant cells per fiber with exploding weights: the never-clip method law made measurable. Lean \texttt{residual\_forcible}: two $\mathbb R$-independent directions span $\mathbb C$, so any residual is forcible to zero; \texttt{CarrierReachability.reachable\_independent\_stage}: a continuous non-constant lane phase attains $\sin(2\phi)\neq0$ (a connected image cannot lie in the discrete lock $\tfrac{\pi}{2}\mathbb Z$), supplying the pair --- the two are composed by direct application, no further Lean theorem claimed. Footprint $\{$\texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}$\}$, no \texttt{sorry}.

\item \textbf{Carrier-transport functoriality (\S\ref{sec:general}), \texttt{RequestProject/CarrierFunctoriality.lean} and \texttt{composition\_test.py}.} \texttt{faithful\_comp} (the composite of closure-preserving transports preserves closure, \emph{no} axioms) with associativity, two-sided identity, and base change $\mathrm{bc}_p\circ\mathrm{bc}_q=\mathrm{bc}_{pq}$; the script verifies exact plethysm splitting $\Sym^2\!\circ\Sym^2=\Sym^4\oplus\Sym^0$, $\Sym^3\!\circ\Sym^3=\Sym^9\oplus\Sym^5\oplus\Sym^3$.

\item \textbf{Tensor-induction residual (functorial preservation, \S\ref{sec:converse}), \texttt{tensor\_induction\_check.py}.} On real $\Delta$ Satake: the Clebsch--Gordan factorization $a_{\pi\times\Sym^4}=a_{\Sym^5}\!\star a_{\Sym^3}$ holds coefficientwise to $1.4\times10^{-14}$; $\mathrm{mean}(a_{\Sym^5})\to6\times10^{-5}$ while $L(\Sym^3)(1)=0.652\ne0$ (the trivial-rep control gives mean $0.652$, so the deduction is non-vacuous).
\end{itemize}

\begin{thebibliography}{99}
\bibitem{AltI} S.~A.~Altu\u{g}, \emph{Beyond endoscopy via the trace formula, I}, Compositio Math.
\textbf{151} (2015).
\bibitem{AltII} S.~A.~Altu\u{g}, \emph{Beyond endoscopy via the trace formula, II}, Amer.\ J.\ Math.
\textbf{139} (2017).
\bibitem{AltIII} S.~A.~Altu\u{g}, \emph{Beyond endoscopy via the trace formula, III}, J.\ Inst.\
Math.\ Jussieu \textbf{19} (2020).
\bibitem{GJ} S.~Gelbart and H.~Jacquet, \emph{A relation between automorphic representations of
$\mathrm{GL}(2)$ and $\mathrm{GL}(3)$}, Ann.\ Sci.\ \'ENS \textbf{11} (1978).
\bibitem{Sar} P.~Sarnak, \emph{Comments on Robert Langlands' lecture ``Endoscopy and Beyond''}, notes
(2001), \texttt{publications.ias.edu/sarnak}.
\bibitem{Hormander} L.~H\"ormander, \emph{The Analysis of Linear Partial Differential Operators I},
2nd ed., Grundlehren \textbf{256}, Springer (1990); Thm.~7.7.1 (non-stationary phase).
\bibitem{Wong} R.~Wong, \emph{Asymptotic Approximations of Integrals}, Classics in Applied
Mathematics \textbf{34}, SIAM (2001); Ch.~3 (Watson's lemma and the Mellin method).
\bibitem{Tate} J.~Tate, \emph{Fourier analysis in number fields and Hecke's zeta-functions}, thesis
(1950), in J.~W.~S.~Cassels and A.~Fr\"ohlich (eds.), \emph{Algebraic Number Theory}, Academic Press
(1967), 305--347.
\bibitem{GJa} R.~Godement and H.~Jacquet, \emph{Zeta Functions of Simple Algebras}, Lecture Notes in
Mathematics \textbf{260}, Springer (1972).
\bibitem{CPS} J.~W.~Cogdell and I.~I.~Piatetski-Shapiro, \emph{Converse theorems for
$\mathrm{GL}_n$}, Publ.\ Math.\ IH\'ES \textbf{79} (1994), 157--214; \emph{II}, J.\ reine angew.\
Math.\ \textbf{507} (1999), 165--188.
\bibitem{Shahidi} F.~Shahidi, \emph{Eisenstein Series and Automorphic $L$-functions}, Amer.\ Math.\
Soc.\ Colloquium Publications \textbf{58}, AMS (2010); and \emph{A proof of Langlands' conjecture on
Plancherel measures; complementary series for $p$-adic groups}, Ann.\ of Math.\ \textbf{132} (1990),
273--330.
\bibitem{KimSarnak} H.~Kim, \emph{Functoriality for the exterior square of $\mathrm{GL}_4$ and the symmetric
fourth of $\mathrm{GL}_2$}, with Appendix~2 by H.~Kim and P.~Sarnak, J.\ Amer.\ Math.\ Soc.\ \textbf{16}
(2003), 139--183 (the bound $|\alpha_p|\le p^{7/64}$).
\bibitem{KimShahidi} H.~Kim and F.~Shahidi, \emph{Functorial products for
$\mathrm{GL}(2)\times\mathrm{GL}(3)$ and the symmetric cube for $\mathrm{GL}(2)$}, Ann.\ of Math.\
\textbf{155} (2002), 837--893 (for the symmetric fourth, see \cite{KimSarnak}).
\bibitem{NT} J.~Newton and J.~A.~Thorne, \emph{Symmetric power functoriality for holomorphic modular
forms, I \& II}, Publ.\ Math.\ IH\'ES \textbf{134} (2021), 1--116, 117--152.
\bibitem{Serre} J.-P.~Serre, \emph{Abelian $\ell$-adic Representations and Elliptic Curves}, Benjamin
(1968); Ch.~I, the equidistribution criterion for the Sato--Tate law from the analyticity and
non-vanishing of the symmetric-power $L$-functions.
\bibitem{JS} H.~Jacquet and J.~A.~Shalika, \emph{A non-vanishing theorem for zeta functions of
$\mathrm{GL}_n$}, Invent.\ Math.\ \textbf{38} (1976), 1--16; non-vanishing on $\Re s=1$ from the
positivity of the Rankin--Selberg convolution; and \emph{On Euler products and the classification of
automorphic representations}, Amer.\ J.\ Math.\ \textbf{103} (1981), the local bound $|\alpha|<p^{1/2}$.
\bibitem{LRS} W.~Luo, Z.~Rudnick, and P.~Sarnak, \emph{On the generalized Ramanujan conjecture for
$\mathrm{GL}(n)$}, in \emph{Automorphic Forms, Automorphic Representations, and Arithmetic}, Proc.\
Sympos.\ Pure Math.\ \textbf{66}, Part 2, AMS (1999), 301--310; the bound
$|\alpha|\le p^{1/2-1/(n^2+1)}$ toward Ramanujan.
\bibitem{Titchmarsh} E.~C.~Titchmarsh, \emph{The Theory of Functions}, 2nd ed., Oxford University
Press (1939), \S\S5.6--5.65 (Phragm\'en--Lindel\"of).
\bibitem{ZhangGS} S.~Zhang, \emph{Gross--Schoen cycles and dualizing sheaves}, Invent.\ Math.\
\textbf{179} (2010), 1--73; the Beilinson--Bloch height of the modified diagonal.
\bibitem{YZZ} X.~Yuan, S.~Zhang, and W.~Zhang, \emph{Triple product $L$-series and Gross--Schoen
cycles}, book manuscript; the central derivative of the triple-product $L$-function as a
Gross--Schoen/Ceresa height.
\bibitem{Ceresa} G.~Ceresa, \emph{$C$ is not algebraically equivalent to $C^-$ in its Jacobian},
Ann.\ of Math.\ (2) \textbf{117} (1983), 285--291.
\bibitem{Harris} B.~Harris, \emph{Harmonic volumes}, Acta Math.\ \textbf{150} (1983), 91--123, and
\emph{Homological versus algebraic equivalence in a Jacobian}, Proc.\ Natl.\ Acad.\ Sci.\ USA
\textbf{80} (1983), 1157--1158 --- the Fermat-quartic Ceresa cycle detected by a nonzero harmonic volume.
\bibitem{LagaShnidman} J.~Laga and A.~Shnidman, \emph{Ceresa cycles of bielliptic Picard curves},
arXiv:2312.12965 (2024); the Beilinson--Bloch height proportional to the N\'eron--Tate height of an
explicit elliptic point.
\end{thebibliography}

\end{document}
