\documentclass[11pt]{article}
\usepackage[margin=1.1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage[colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black]{hyperref}
\usepackage{booktabs}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{target}[theorem]{Target}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\Fcar}{F_{\mathrm{car}}}
\newcommand{\CH}{\mathrm{CH}}
\newcommand{\AJ}{\mathrm{AJ}}
\usepackage[OT2,T1]{fontenc}
\DeclareSymbolFont{cyrletters}{OT2}{wncyr}{m}{n}
\DeclareMathSymbol{\Shamath}{\mathalpha}{cyrletters}{"58}

\title{The Loss Ledger and the Cycle Filtration:\\
Tower Exhaustion on the Helix Carrier,\\
and a Program Whose Terminus Is the Hodge Conjecture}
\author{Samuel Lavery\\ \texttt{sam.lavery@gmail.com}}
\date{Preprint draft \textsc{v0.1} --- July 2026}

\begin{document}
\maketitle

\begin{abstract}
The three-dimensional helix carrier of the main paper projects to the classical
$1$D readout through a lossy but exactly bookkept descent: height, radius, and
angle are recorded in a loss ledger, and projection with its ledger is a proven
bijection. This paper reads the \emph{cycle theory} of a variety through that
ledger. We define the carrier filtration $\Fcar^{\,d}$ by vanishing of the
recursive tower readouts $T_0,\dots,T_{d-1}$ and prove, machine-checked in
Lean~4, the depth dictionary: \emph{first nonzero tower depth equals filtration
depth}, the depth is unique, it is preserved by every faithful carrier
transport, and whenever a Bloch--Beilinson filtration with the universal
properties exists it coincides with $\Fcar$. On the semisimple carrier state the
tower is unconditionally jointly faithful --- a Vandermonde separation --- so no
nonzero state is silent at every level. At depth one the carrier's leading
central jet factors, by Birch--Swinnerton-Dyer/Gross--Zagier, into three
independently resolved coordinates --- vanishing order, regulator, and
$|\Shamath|$ --- landed at machine precision on a census through rank three,
with the local-global obstruction appearing as an exact square integer. Each
deeper landing is theorem-anchored: Tate's pole at grade zero,
Gross--Zagier--Kolyvagin at grade one, a CM Hodge class firing with the
predicted delayed signature at depth two, and the Ceresa/Gross--Schoen height
at tensor depth three by Zhang and Yuan--Zhang--Zhang. The program this
assembles is stated plainly: the carrier's organizing principle is that no
layer remains invisible --- every class is induced to appear at some retained
coordinate --- and the terminus of that principle is the Hodge conjecture, read
as a source-exhaustion statement: every Hodge-signature state has an algebraic
source.

Four further developments carry the program past its first draft. The
\emph{harmonic frame}: a Hodge structure is a torus clock --- weight the radial
rate, $H^{p,q}$ the frequency-$(q{-}p)$ channel, a Hodge class a rational DC
mode --- calibrated against Lefschetz $(1,1)$ truth on both the period and
point-count sides. \emph{Drift}: extension classes are the first-order shear a
pure clock stack cannot produce; machine-checked, drift is value-blind,
jet-visible, and never silent on the model, and the measured law --- the
response harmonic equals the drift dimension --- holds across the census with
machine-zero silence below. \emph{Recognition at grade one}: the
Gross--Zagier loop is run end to end on house instruments, from point counts to
an exactly recognized rational point. \emph{Grade four}: the first unnamed
rung. Three walls are established --- the non-critical center (the motive's own
DC channel), the parity ladder (heights on odd rungs, regulators on even), and
a split no-go (decomposable classes pair to zero with the primitive quadruple,
machine-checked) --- so the rung-four object is classically homeless; the
degree-16 fiber is then assembled directly on the carrier, its degenerate case
factoring through the lower harmonics exactly, its primitive case certified
irreducible, and its first datum measured. This draft carries the rung further.
A fourth wall --- the information wall: any chart-side center determination
needs $\sim\!\sqrt Q\approx3\times10^{24}$ coefficients --- is measured on
three faces and then dismantled: a certified value chain runs to degree six,
the primitive quadruple's functional-equation sheet is pinned from its twenty
integers with the global root number \emph{proven} $+1$ from Deligne's local
theory, its first strip-interior values exist, and the unread center is
identified as a regulator volume dominated by its tropical part. The
harmonic-lattice and rail-pairing laws locate where values live: warps
harmonically compatible with the fiber's own angle produce exact lane
identities on the symmetric-power tower, natural boundaries at the center are
single-rail artifacts, and the height-matched pairing of exact conjugate rails
converges where every mis-pair diverges. The portal reads the homeless
$(2,2)$ block from inside --- channel constancy as an algebraicity signature,
an $S_3$-symmetric interior Gram with a two-dimensional exotic-candidate home
--- and a fixed-head locator with $\mu_6$-address rails resolves oracle zeros
at the Rayleigh limit one degree beyond its previous ceiling. The Ceresa
target's $L$-side is landed on the Klein quartic: the Ceresa channel has
forced sign $-1$ and central derivative $0.8299\ne0$, matching the proven
non-torsion of the cycle. And the tower scales: grades five and six run on
the same instruments with no new method --- every pre-registered rational
lands, the Catalan spine $C_2,C_3$ and its Schur companions $C_4,C_5,C_6$
confirm, and the parity law (a DC channel exists iff the weight is even) is
proven in Lean the same session its content is measured; the atlas then runs
to grade twenty, where the tower's root-number law emerges --- sign real at
every grade, central zeros forced at exactly $g=2^k+1$. The terminus
architecture is fixed in Lean: retention and recognition, the two named
hypotheses, compose machine-checked into source exhaustion --- asserted by no
one, wired to receive.
\end{abstract}

\tableofcontents

\section{Introduction}\label{sec:intro}

The main paper \cite{Universal} constructs a three-dimensional carrier --- a
double-ended helix and its conjugate anti-helix, harmonically scaled, running
from the origin to infinity --- on which automorphic data ride as fibers, and
proves that the classical one-dimensional readout is the image of a lossy but
exactly bookkept projection: the descent $3\mathrm D\to2\mathrm D\to1\mathrm D$
books a \emph{loss ledger} --- height (ordinate), radius, angle --- and
projection with its ledger is a bijection with an exact two-sided inverse
(Lean, \texttt{ConeProjection.record\_bijective}). The present paper turns that
instrument toward the cycle theory of a variety, and it is organized around one
boxed statement and one stated terminus.

The boxed statement is the \emph{depth dictionary}. Define the recursive tower
$T_0,T_1,T_2,\dots$ of carrier readouts --- value, leading jet, and the
symmetric-power/derivative levels above them --- and the carrier filtration
\[
  \Fcar^{\,d}\ :=\ \{\,z:\ T_0(z)=\dots=T_{d-1}(z)=0\,\},
\]
defined by the tower alone, with no reference to any conjectural filtration.
Then, as a machine-checked theorem (\S\ref{sec:dictionary}),
\[
  \boxed{\ \text{first nonzero carrier tower depth}\ =\ \Fcar\text{-filtration depth,}\ }
\]
the depth is unique, it is invariant under every faithful carrier transport,
and \emph{whenever} a Bloch--Beilinson filtration with the universal properties
exists on the source class, it coincides with $\Fcar$
(\texttt{blochBeilinson\_coincides}) --- a conditional corollary that assumes
no general existence of the conjectural object, which is stronger and cleaner
than positing that existence. We price the dictionary exactly: since $\Fcar$ is
\emph{defined} by tower vanishing, the correspondence is definitional
bookkeeping, exact by construction; its value is that transport-invariance and
the Bloch--Beilinson coincidence attach to a non-circular, machine-fixed
object.

The stated terminus is the Hodge conjecture. The carrier program's organizing
principle --- established across the main paper's arithmetic and repeated here
--- is that \emph{no layer remains invisible}: a class silent in one readout is
not invisible but mis-read, and it is induced to appear by climbing to the
correct retained coordinate --- a deeper tower level, a different ledger
channel. The local-global obstruction $|\Shamath|$, ordinarily invisible to a
Hodge-theoretic projection, appears at depth one in the jet's amplitude ratio
as an exact square integer (\S\ref{sec:depthone}); a CM Hodge class, silent in
the standard readout, fires at depth two with the predicted delayed signature
(\S\ref{sec:landings}); the transcendental Ceresa class, silent at depth one,
is reached at tensor depth three by a theorem of Zhang and Yuan--Zhang--Zhang
(\S\ref{sec:ceresa}). Carried to its terminus the principle says: a rational
$(p,p)$-class --- a state with the \emph{Hodge signature} in the carrier's
clock coordinates --- cannot be silent either; something algebraic sources it.
That is the Hodge conjecture \cite{Hodge,DeligneClay}, read in the carrier's
native register as \emph{source exhaustion}:
\[
  \boxed{\ \text{every Hodge-signature state has an algebraic source.}\ }
\]
We do not prove it here. We prove the dictionary, the semisimple half, and the
drift theorems; measure every landing the classical theorems anchor, including
the first above-grade-one anisotropy reading (\S\ref{sec:ceresa}), the landed
$L$-side of the Ceresa target itself, and the
first data on the unnamed fourth rung (\S\ref{sec:rung4}); measure the rung's
fourth wall and dismantle it (\S\ref{sec:wallfour}); read the rung's interior
through the harmonic lattice, the conjugate rails, and the portal
(\S\ref{sec:rails}); scale the tower to grades five and six with no new
method (\S\ref{sec:scaling}); close the
recognition loop at grade one on house instruments (\S\ref{sec:recognition});
and in \S\ref{sec:terminus} fix the architecture in Lean --- the two named
ingredients composing, machine-checked, into the terminus --- together with
what evidence would refute the program on the way.

\paragraph{Registers.} Three registers are used and never blended.
\emph{Proven}: machine-checked in Lean~4 at axiom footprint
$\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$, no
\texttt{sorry} (the filtration dictionary, the semisimple theorem, and the
supporting carrier corpus of \cite{Universal}), or established in the classical
literature with the citation given at the point of use (Gross--Zagier,
Kolyvagin, Zhang, Yuan--Zhang--Zhang, Harris, Laga--Shnidman).
\emph{Measured}: precision-tracked numerics --- the census, the probes, the
delayed signatures --- calibration and corroboration, never proof.
\emph{Program}: the extension-data faithfulness, the from-scratch Ceresa
landing, and the terminus itself, stated with their falsifiers.

\section{The carrier and its ledger}\label{sec:ledger}

We import from \cite{Universal} only what this paper consumes.

The carrier is source-independent: a double-ended helix/anti-helix pair,
Archimedean of constant pitch, harmonically scaled. A source with a finite
structural presentation --- finitely many local parameters per place generated
by one bounded-degree rule --- is \emph{admissible}, and its fiber rides the
carrier as a bank of phasors entering continuously at height with zero
magnitude. Vanishing is exact focal cancellation of the helix and anti-helix
fibers. The descent to the classical chart drops the radial channel
($3\mathrm D\to2\mathrm D$), then the angular channel
($2\mathrm D\to1\mathrm D$), while height passes through $\log$; recording the
dropped channels makes the map
\[
  \text{fiber}\ \longmapsto\ (\text{ordinate};\ \text{radius},\ \text{angle})
\]
a bijection with explicit inverse (Lean,
\texttt{ConeProjection.record\_bijective}, \texttt{reconstruct\_record}) ---
the loss ledger. The three channels carry distinct arithmetic freight:
\begin{itemize}
\item \emph{height} --- the ordinate, the $L$-reading and its jets;
\item \emph{radius} --- the scaling channel: leading values, regulators, and
the obstruction amplitudes enter here;
\item \emph{angle} --- the Satake/Frobenius phase, the Galois-side datum.
\end{itemize}
The recursive tower $T_d$ reads the fiber at symmetric-power/derivative level
$d$: $T_0$ the value channel, $T_1$ the leading central jet, and above them the
moment/symmetric-power levels of the clock frequencies. Everything below is a
statement about which classes fire at which $T_d$, and through which ledger
channel.

\section{The harmonic Hodge structure}\label{sec:harmonic}

The frame that organizes everything below is the observation that a Hodge
structure already \emph{is} a clock system. Deligne's form of the definition:
a weight-$n$ Hodge structure is an action of the torus
$\mathbb S(\mathbb R)=\mathbb C^\times=\mathbb R_{>0}\times U(1)$, acting on
$H^{p,q}$ by $z^{-p}\bar z^{-q}=r^{-n}e^{i\theta(q-p)}$ --- radius times angle,
exactly the two channels the loss ledger books. Decomposed in carrier
coordinates:

\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Hodge object & carrier object \\
\midrule
weight $n$ & radial rate (the ledger's radius channel, $r^{-n}$) \\
$H^{p,q}$ & clock channel at frequency $k=q-p$ \\
Hodge symmetry & chiral pairing $k\leftrightarrow-k$ (helix/anti-helix lanes) \\
Hodge numbers $h^{p,q}$ & channel occupancy of the bank \\
Weil operator $C=h(i)$ & the $\pi/2$ clock element; $C^2=(-1)^n$ the $\pi$ element \\
polarization & quarter-turn-twisted Gram definiteness \\
Hodge filtration $F^p$ & frequency-band cut; opposedness $=$ chiral complementarity \\
Griffiths transversality & the unit-step law (the axioms of \S\ref{sec:dictionary}) \\
Mumford--Tate group & the clock-symmetry group; CM $=$ extra symmetry \\
Hodge loci & DC-locking loci of the transported clock \\
\bottomrule
\end{tabular}
\end{center}

Two consequences carry the paper. First, \emph{a Hodge class is a rational DC
mode}: type $(p,p)$ means $k=0$ --- the angular clock silent, the state pure
radial, at rational amplitude. The house's DC technology therefore applies
verbatim: the carrier reads DC occupancy as pole/residue data (the depth-one
instance is \texttt{rank\_is\_dc\_residue}). Second, the terminus of
\S\ref{sec:terminus} becomes a fixed-axis exhaustion statement, the same genre
as the carrier's proven exhaustion theorems. The $1$D chart hides all of this
because the $(p,q)$ data is exactly the discarded angle channel: the
$L$-function sees the semisimplified frequency/weight multiset, never the
rational structure against the channels.

\paragraph{The orbit geometry.} The torus is the clock; the sphere is the
dial. For weight-two and hyperk\"ahler geometry the twistor sphere rotates the
channels $(2,0),(1,1),(0,2)$ into one another --- it parametrizes clocks, and
rotating it moves the DC axis while the rational lattice stays fixed. Acting on
the dial with the clock sweeps nested toroids (the Hopf/Clifford
decomposition, the chiral pair as the two linked core circles), degenerating on
the axis; the axisymmetric profile data of that sweep is where the rational DC
modes live. Equivariant localization --- exact, not asymptotic, for these
actions --- is the transfer principle that reads the whole toroid from the
axis: the sphere-family's global invariants localize to the DC locus, the
harmonic-frame form of the carrier's residue principle. Measured
(\texttt{twistor\_hunt.py}, App.~\ref{app:repro}): the DC-locking locus of a
product-family dial is discrete and \emph{exactly algebraic} --- every
predicted rational point of the dial locks at residual zero, every detected
lock identifies as rational, and every irrational control stays at $O(1)$ ---
the Cattani--Deligne--Kaplan-shaped behavior on the carrier's own clock
coordinates.

\paragraph{Epicycles and drift.} Iterating the picture --- spheres spinning
about spheres, axes parallel --- is the classical epicycle stack, and it is
exact: parallel axes means commuting clocks, frequencies add, layer $d$ spins
at $\lambda^d$, and the recursion depth is the tower level of
\S\ref{sec:dictionary}. One more sphere out $=$ one more grade. What a pure
epicycle stack cannot produce is \emph{drift} --- secular shear between layers
--- and drift is precisely an extension class: the Jordan part that
semisimplification kills. The next section makes this machine-checked.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[scale=0.9]
  \draw[very thick] (0,0.4) -- (0,-4.6);
  \draw[very thick] (0.9,0.4) -- (0.9,-4.6);
  \draw[very thick] (0.45,-4.6) ellipse (0.45 and 0.16);
  \draw[very thick] (0,0.4) arc (180:0:0.45 and 0.16);
  \foreach \d in {0,1,2,3,4} {
    \draw[gray,dashed] (-1.2,-\d) -- (2.1,-\d);
    \node[gray,left] at (-1.25,-\d) {$d=\d$};
  }
  \foreach \x/\y/\l in {0.25/0/11a1, 0.45/0.05/571a1, 0.65/-0.05/681b1} {
    \fill[blue!60!black] (\x,\y) circle (0.09);
  }
  \node[right,blue!60!black,font=\scriptsize] at (1.0,0.05)
    {$11a1,\,571a1,\,681b1$};
  \foreach \x/\y in {0.25/-1, 0.45/-0.95, 0.65/-1.05} {
    \fill[blue!60!black] (\x,\y) circle (0.09);
  }
  \node[right,blue!60!black,font=\scriptsize] at (1.0,-0.95)
    {$37a1,\,53a1,\,61a1$};
  \fill[blue!60!black] (0.45,-2) circle (0.09);
  \node[right,blue!60!black,font=\scriptsize] at (1.0,-1.95)
    {$389a1$;\ CM class (Sym-tower)};
  \fill[blue!60!black] (0.45,-3) circle (0.09);
  \node[right,blue!60!black,font=\scriptsize] at (1.0,-2.95)
    {$5077a1$;\ Ceresa (triple product)};
  \node[font=\scriptsize,align=center] at (0.45,-5.3)
    {torsion locus rests\\ on the bottom, exactly};
\end{tikzpicture}
\caption{The drift thermometer. Each class sinks to the tower level matching
its complexity and floats there: the first-fire depth $k^*$ equals the drift
dimension, measured with machine-zero silence above the bulb
(\texttt{drift\_observability.py}; the delayed signature $0,\dots,0,\neq0$).
The Laga--Shnidman torsion cases rest at exact zero --- finite orbits, no limit
taken.}
\label{fig:thermometer}
\end{figure}

\section{The carrier filtration and the depth dictionary}\label{sec:dictionary}

\begin{definition}[carrier filtration]
$\Fcar^{\,0}$ is everything, and
$\Fcar^{\,d}:=\{z:\ T_0(z)=\dots=T_{d-1}(z)=0\}$.
\end{definition}

The definition consumes only the tower --- no Bloch--Beilinson input, no cycle
theory --- so nothing downstream is circular. The bookkeeping is then a
machine-checked package (\texttt{HodgeLedgerFiltration.lean} in
\texttt{RequestProject/};
all footprints standard):

\begin{theorem}[the depth dictionary; Lean]\label{thm:dictionary}
$\Fcar$ is an antitone filtration with $\Fcar^{\,0}$ everything
\textup{(\texttt{carrierFiltration\_antitone})}. The level-$d$ ledger
coordinate is faithful on $\Fcar^{\,d}$: its kernel there is exactly
$\Fcar^{\,d+1}$ \textup{(\texttt{ledger\_kernel},
\texttt{mem\_carrierFiltration\_succ})}. No lower level falsely fires
\textup{(\texttt{no\_early\_detection})}, and a genuine grade-$d$ class fires
at level $d$ \textup{(\texttt{grade\_visibility})}; hence the first nonzero
tower depth equals the $\Fcar$-filtration depth
\textup{(\texttt{firstVisibleDepth\_eq\_grade})}, the depth is unique
\textup{(\texttt{isFirstVisible\_unique})}, and it is preserved by every
faithful carrier transport \textup{(\texttt{isFirstVisible\_map\_iff})}.
Moreover $\Fcar$ is the unique filtration whose graded pieces are cut out by
the tower \textup{(\texttt{carrierFiltration\_unique})}.
\end{theorem}

\begin{corollary}[Bloch--Beilinson coincidence; Lean, conditional]\label{cor:bb}
Whenever a Bloch--Beilinson filtration \cite{Beilinson,Bloch,Murre} with the
universal properties exists on the source class, it coincides with $\Fcar$
\textup{(\texttt{blochBeilinson\_coincides})}.
\end{corollary}

The corollary assumes no existence; it converts any future construction of the
conjectural filtration into an identification with a machine-fixed object. The
load-bearing question is therefore never ``does the dictionary hold'' --- it
holds by construction --- but whether the tower \emph{separates}: whether any
nonzero class can be silent at every level. That question splits cleanly in
two.

\begin{definition}[carrier radical]
$R:=\bigcap_d\ker T_d$. The tower is \emph{exhaustive} on a class of states if
$R=0$ there: every nonzero state fires at some finite level
\textup{(\texttt{exhaustive\_of\_radical\_trivial})}.
\end{definition}

Gradewise, exhaustion reduces to a nondegeneracy statement --- a faithful
regulator into an anisotropic height pairing
(\texttt{grade\_visible\_of\_nondegenerate}) --- discharged at depth one by
N\'eron--Tate positivity. The semisimple half is settled unconditionally in the
next section; the extension half is the program of \S\ref{sec:ceresa}.

\section{The semisimple theorem}\label{sec:semisimple}

On the semisimple carrier state --- the finite duality-stable weight fiber, an
amplitude state $c$ over finitely many \emph{distinct} clock frequencies
$\{\lambda_i\}$ --- the tower is the moment/symmetric-power system
$T_d(c)=\sum_i c_i\lambda_i^{\,d}$, and joint faithfulness is a Vandermonde
fact:

\begin{theorem}[no silent layer on the semisimple state; Lean]\label{thm:semisimple}
For distinct frequencies the moment matrix is Vandermonde, so
$\bigcap_d\ker T_d=0$: every nonzero semisimple state fires at some finite
level
\textup{(\texttt{CarrierTowerSeparation.momentTower\_exhaustive}}, from
\texttt{momentTower\_detects} and
\texttt{momentTower\_radical\_trivial}\textup{)}.
\end{theorem}

The scope is exactly what the statement says. A homologically trivial cycle
contributes, in its Abel--Jacobi/motivic realization, \emph{extension} data
rather than a semisimple amplitude state; semisimplification kills it, the
local factors depend only on the weight multiset, and so it lies in the radical
of the \emph{value} tower and is detected only by the derivative/height
channel. Whether the derivative tower is jointly faithful on extension data ---
whether $R=0$ extends from the semisimple state to cycles --- is the remaining
problem, and it is the reason this paper exists.

\subsection{Drift: the extension datum as first-order shear}\label{sec:drift}

In the epicycle frame of \S\ref{sec:harmonic}, an extension class is
\emph{drift} --- the inter-layer shear a pure rotation stack cannot produce,
the Jordan deformation of the clock. On the minimal model, the Jordan-2 block
$\bigl(\begin{smallmatrix}\lambda&\delta\\0&\lambda\end{smallmatrix}\bigr)$,
the three structural halves of the drift law are machine-checked
(\texttt{RequestProject/JordanDriftTower.lean}; standard footprint):

\begin{theorem}[drift is value-blind, jet-visible, never silent; Lean]
\label{thm:drift}
\textup{(a)} The local factor $\det(1-XA)=(1-X\lambda)^2$ and every trace power
of the drift block are independent of $\delta$: every pure drift lies in the
radical of the value tower --- ``killed by semisimplification'' as a theorem
\textup{(\texttt{jordan\_localFactor\_driftBlind},
\texttt{drift\_in\_value\_radical})}.
\textup{(b)} The shear slot of the $d$-th power is exactly
$d\lambda^{d-1}\delta$: the jet response is the derivative-weighted moment of
the drift amplitudes --- the Gross--Zagier shape
\textup{(\texttt{jordan\_pow}, \texttt{jetResponse\_eq\_weighted\_moment})}.
\textup{(c)} Over distinct clock frequencies, a drift state silent at every jet
level is zero \textup{(\texttt{jetTower\_radical\_trivial},
\texttt{jetTower\_exhaustive})}, and the jet-response energy over the first $m$
levels is positive definite \textup{(\texttt{driftPairing\_posDef})}: on the
model, Beilinson--Bloch anisotropy is a Vandermonde fact.
\end{theorem}

\noindent\emph{The retention reduction.} A pairing that factors through a
definite carrier energy along an injective ledger map is anisotropic
(\texttt{anisotropic\_of\_definite\_factor}) --- so the open arithmetic content
of nondegeneracy above grade one is exactly \emph{ledger retention on cycle
drift}: that the descent never collides two distinct drift states. This is the
same statement the ledger-failure and observability instruments hunt; the two
``missing ingredients'' of the terminus are one statement in two costumes.

\noindent\emph{Measured.} The drift law holds on the census
(\texttt{drift\_observability.py}, App.~\ref{app:repro};
Fig.~\ref{fig:thermometer}): the first-fire harmonic $k^*$ equals the drift
dimension on all eight curves (dimensions $0$--$3$), with machine-zero silence
below the firing slot ($389a1$: sub-ladder at $10^{-16}$ before a $0.759$
fire), the root number certified in-house with no rank assumption
(split-vs-direct $\Lambda(3)$, true sign $\sim10^{-8}$, wrong sign
$O(10^{-2})$), and the normalized responses reproducing the regulators
measured independently on the arithmetic side to four digits. At fixed
placement, three same-dimension drift states separate cleanly --- no
observability failure.

\noindent\emph{The two parity readouts.} Units and $K_1$-classes are
log-decorations, and a log-decoration is the same Jordan shear: one drift, two
readouts --- \emph{odd} rungs read drift through heights (Gross--Zagier), and
\emph{even} rungs read drift through regulators (Beilinson). This becomes
load-bearing at grade four (\S\ref{sec:rung4}).

\section{Depth one, three coordinates}\label{sec:depthone}

At depth one the carrier's leading central jet factors, by
Birch--Swinnerton-Dyer and Gross--Zagier \cite{BSD,GrossZagier}, as
\[
  \frac{L^{(r)}(E,1)}{r!}
  \;=\;
  \frac{\Omega\cdot\mathrm{Reg}\cdot|\Shamath|\cdot\prod_p c_p}{|T|^{2}},
\]
and the census resolves the three progressively-deeper-than-Hodge layers as
\emph{independent} retained coordinates [measured; oracle-free --- no
$L$-function call inside any locator, published values entering only the final
verification column]:
\begin{itemize}
\item \textbf{order $r$} $=$ filtration depth. Rank read as the DC residue of
the carrier bank (Lean, \texttt{rank\_is\_dc\_residue}); rank-$0$ curves carry
$|\Shamath|\in\{1,4,9\}$, so order is independent of the obstruction.
\item \textbf{$\mathrm{Reg}$} $=$ the height-pairing determinant, the
arithmetic Abel--Jacobi image. Census values $0.0511,\ 0.1524,\ 0.4171$ at
ranks $1,2,3$ ($37a1$, $389a1$, $5077a1$), each within $1.7\times10^{-5}$ of
the known anchors --- distinct, and independent of both order and obstruction.
\item \textbf{$|\Shamath|$} $=$ the local-global obstruction, the shadow of the
Abel--Jacobi kernel. The hinge amplitude ratio $L\cdot|T|^2/(\Omega\prod c_p)$
lands on \emph{exact square integers}: $1,4,9$ across the census
($4=2^2$ at $571a$, $960d$, $960n$; $9=3^2$ at $681b$, $2849a$), margins at the
$10^{-15}$ floor for rank zero and $\le1.6\times10^{-4}$ through rank three ---
the first in-house full readings of the formula above rank zero
(\texttt{jet\_census.py}, \texttt{sha\_hinge.py}; App.~\ref{app:repro}).
\end{itemize}
Each layer ordinarily invisible to a Hodge-theoretic projection therefore
carries a \emph{distinct} ledger coordinate, resolved independently at machine
precision. This is the depth-one row of the dictionary, measured; its
theorem anchors are Gross--Zagier--Kolyvagin \cite{GrossZagier,Kolyvagin}.

\section{The landing table}\label{sec:landings}

Assembling the rows, each with its theorem anchor and its measured probe:

\begin{center}
\begin{tabular}{@{}llll@{}}
\toprule
grade & class & retained coordinate & anchor / probe \\
\midrule
$0$ & algebraic (Tate) & pole order / DC residue & Tate \cite{TateConj}; \texttt{rank\_is\_dc\_residue} \\
$1$ & Mordell--Weil & leading jet: $r$, $\mathrm{Reg}$, $|\Shamath|$ & \cite{BSD,GrossZagier,Kolyvagin}; census \S\ref{sec:depthone} \\
$2$ & CM Hodge class & $\mathrm{Sym}^2$ excess pole & delayed signature $0,\neq0$ (below) \\
$3$ & Ceresa/Gross--Schoen & triple-product central derivative & Zhang \cite{ZhangGS}; YZZ \cite{YZZ} \\
$2$ (even) & Rankin--Selberg $K_1$-class & Beilinson regulator & Beilinson \cite{Beilinson}; Flach \cite{Flach} \\
$4$ & primitive quadruple & regulator at a non-critical center & unnamed; \S\ref{sec:rung4} \\
\bottomrule
\end{tabular}
\end{center}

The depth-two row is the program's sharpest measured prediction to date. A CM
self-correspondence carries a Hodge class living in $\mathrm{Sym}^2$ --- depth
two of the filtration --- and the tower read from point counts produces exactly
the \emph{delayed signature} the dictionary demands: silent at depth one, first
firing at depth two, the first nonzero slot matching the expected filtration
depth of the class (\texttt{tower\_exhaustion\_test.py},
App.~\ref{app:repro}). Across every class tested the first firing depth was
finite --- $1,1,1,2,3$ --- and no class was silent at every level. The
depth-three row is anchored by theorem: the Ceresa cycle is the image of the
Gross--Schoen modified diagonal in $\CH^2(C^3)_0$, homologically trivial, and
its Beilinson--Bloch height is, in the theorem-anchored triple-product
settings, a central derivative of the $L$-function of $H^1(C)^{\otimes3}$
\cite{ZhangGS,YZZ} --- the value channel reaches at level three what it cannot
see at level one, exactly as $|\Shamath|$ appears at level one and the CM class
at level two. Deeper layer, deeper tower level; nothing invisible, everything
induced.

\section{The Ceresa frontier}\label{sec:ceresa}

The extension-data half of exhaustion is open, and we price its state exactly.

\emph{The first rung is unconditional.} For the Fermat quartic the Ceresa class
$[C]-[C^-]$ is homologically trivial yet detected by a nonzero harmonic volume
--- Harris's Abel--Jacobi-type invariant \cite{Harris}, with Ceresa's theorem
for the generic curve \cite{Ceresa} --- so
$\ker(\mathrm{cl})\not\subseteq\ker(\AJ_{\mathbb C})$: a class closed in the
homology readout fires at the next retained coordinate, no conjecture
consumed. This is exactly one rung --- past $\mathrm{cl}$ --- and it does not
show the $\AJ_{\mathbb C}$-kernel itself is penetrated.

\emph{The control cuts the other way.} In the explicit bielliptic Picard family
with a closed-form height, the Beilinson--Bloch height of the Ceresa cycle is
proportional to the N\'eron--Tate height of an explicit Abel--Jacobi point,
vanishing exactly when that point is torsion (Laga--Shnidman
\cite{LagaShnidman}): there, the depth-three height is controlled by the
depth-one coordinate and does \emph{not} penetrate $\ker\AJ_{\mathbb C}$.

\emph{The genuine target}, therefore, is a class with $\AJ_{\mathbb C}(z)$ zero
or torsion yet a nonzero \emph{arithmetic} level-three invariant ---
necessarily one where the non-archimedean local height dominates (Zhang's
admissible/metrized-graph terms \cite{ZhangGS}) or where the finer
$\ell$-adic/Galois Ceresa class, not the archimedean height, is the retained
coordinate. Two further honesty points fix the frontier's shape:

\begin{itemize}
\item We do \emph{not} place the transcendental class in the radical: that
would require every $T_d$ to factor through the single-archimedean
Abel--Jacobi realization (\texttt{radical\_of\_factorsThrough}), and since the
global Gross--Schoen height carries non-archimedean data absent from that
realization, the factorization cannot be assumed --- ruling it out is itself a
non-factorization theorem, not established here. Absent one,
Abel--Jacobi-triviality is an \emph{adversarial benchmark}
(\texttt{not\_mem\_radical\_of\_detectedPast}), not a proven ceiling.
\item The probes are supportive but are calibration only: the value channel
fires for every homologically-trivial cycle in the census (no silent cycle),
and the recursive tower already shows classes absent at level one appearing at
level $\ge2$ (\texttt{hodge\_griffiths\_probe.py}, App.~\ref{app:repro}).
\end{itemize}

\noindent\emph{Measured: the first above-grade-one anisotropy reading.} On the
Laga--Shnidman family itself the depth-three pairing is now measured
(\texttt{ceresa\_anisotropy.py}, App.~\ref{app:repro}), using their theorem as
the anchor: $h(\kappa(C_t))\propto\hat h(Q_t)$ for
$Q_t=(\sqrt[3]{t^2-1},\,t)$ on $y^2=x^3+1$. The boundary is exact: at the
torsion locus $t=0,\pm3$ the doubling orbits terminate at step one or two ---
torsion detected by the group law, no limit taken, $\hat h=0$ on the nose. Off
the locus, every census point is non-isotropic: $\hat h(Q_t)=0.59$--$1.16$,
positive with clear margin, convergence certificates $\le3.6\times10^{-4}$,
computed from scratch over the cubic field $\mathbb Q(\sqrt[3]{t^2-1})$ (exact
field arithmetic, exact characteristic polynomials, Mahler measures at matched
precision). The isotropy locus exists, is exactly where the theorem puts it,
and anisotropy off it is measured, not assumed. The instrument also found a
structure: whenever $t'^2-1=c^3(t^2-1)$ the points are torsion translates
($-Q_2+(0,1)=Q_5$, verified by the group law in-instrument), so the
corresponding heights are \emph{exactly} equal --- a torsion-translation
symmetry of the family, detected numerically at $10^{-4}$ and then proven in
one line. (Equality of the $\kappa$-heights themselves depends on the
$t$-dependence of the proportionality constant, and is not claimed.)

\begin{target}[the Ceresa landing]\label{tgt:ceresa}
A from-scratch triple-product central-derivative computation landing the
Gross--Schoen/Ceresa height on the carrier --- nonzero for a known nontrivial
class (Klein-quartic type), zero for the hyperelliptic control --- with the
derivative-to-height step consuming \cite{ZhangGS,YZZ} and nothing else. The
instrument builds on the point-counting tower of
\texttt{tower\_exhaustion\_test.py}; it is the program's next experiment, not
claimed here.
\end{target}

\paragraph{The $L$-side, landed.} Half of Target~\ref{tgt:ceresa} is now on
record (\texttt{ceresa\_lside.py}, App.~\ref{app:repro}). The prediction was
locked by the literature first: the Klein quartic's Ceresa cycle is
\emph{non-torsion} modulo algebraic equivalence (Tadokoro \cite{Tadokoro},
extending Harris's harmonic-volume method \cite{Harris} from the Fermat
quartic), so under Beilinson--Bloch nondegeneracy the Ceresa channel of the
triple product must carry odd sign and a nonvanishing central derivative --- a
zero derivative would have been a published falsification. The channel was
isolated exactly: over $K=\mathbb Q(\sqrt{-7})$ (class number one, Hecke
character $\psi$ with $L(49a,s)=L(\psi,s)$),
\[
  H^1(X)^{\otimes3}\ =\ \mathrm{Ind}_K^{\mathbb Q}(\psi^3)\ \oplus\
  3\cdot M_{f_2}(-1),
\]
the induced $\psi^3$ piece (the weight-4 level-49 CM form; the from-scratch
Hecke coefficients reproduce it integer-exactly) being the genuinely new ---
Ceresa --- channel. En route the instrument caught a model subtlety: the naive
quartic $x^3y+y^3z+z^3x=0$ is \emph{not} $\mathbb Q$-isogenous to $E^3$ (its
counts vanish on the nonresidue classes mod $7$ --- a cubic twist from the
coordinate rotation); Elkies's model \cite{Elkies} is the
$\mathbb Q$-decomposed one, and the geometric statement is model-independent.
Measured, each piece with a two-point split-vs-direct certificate: the Ceresa
channel has $\varepsilon=-1$ --- so its central value is \emph{forced} to zero
--- and central derivative
\[
  L'(\psi^3,\tfrac12)\ =\ 0.8298893\ \ne\ 0
\]
(independent PARI path agrees to $3.6\times10^{-6}$); the even channel carries
the value $L(49a,1)=0.9666592\ne0$ (multiplicity three, oracle-matched); the
total triple-product sign $(-1)(+1)^3=-1$ is odd, as a Gross--Schoen derivative
object must be. The reading matches the cycle side exactly: non-torsion cycle
$\leftrightarrow$ firing derivative, the height-to-jet matching at grade
three. Register: the consumed theorem is the proportionality of
\cite{ZhangGS,YZZ}; the sole isolated hypothesis is Beilinson--Bloch
nondegeneracy, named and not claimed. The height side --- the Arakelov
computation the target's full landing needs, with the hyperelliptic control
--- remains the open half.

\section{Recognition closed at grade one}\label{sec:recognition}

The converse leg --- from a fired ledger coordinate to a \emph{constructed}
cycle --- is the terminus's hardest ingredient, and grade one is the only place
mathematics has ever closed that loop: Gross--Zagier--Kolyvagin, where the
fired first jet plus a CM alignment constructs a rational point through the
modular parametrization. The loop is now run end to end on house instruments
(\texttt{heegner\_recognition.py}, App.~\ref{app:repro}), consuming point
counts and nothing else:

\begin{center}
\emph{detection} (jet fires) $\;\to\;$ \emph{alignment} (CM clock)
$\;\to\;$ \emph{construction} (parametrization) $\;\to\;$
\emph{recognition} (exact landing).
\end{center}

For $37a1$: the $a_n$ from point counts build the modular image
$z=\sum a_n q^n/n$ at the Heegner alignment $\tau=(-17+\sqrt{-7})/74$
($D=-7$, class number one, $37$ split); the trace $2\,\mathrm{Re}(z)$ lands in
$\mathbb C/\Lambda$ with the lattice from the house AGM periods,
\emph{self-certified} by both half-period identities
$\wp(\omega_1/2)=e_1$, $\wp(\omega_2/2)=e_3$ (exact zero deviation); and the
recognition gate lands $P=(1,0)$ --- recognized by continued fractions,
verified on $y^2+y=x^3-x$ in exact rational arithmetic --- with
$\hat h(P)=4.0006\times\hat h((0,0))$: the constructed point is the double of
the generator (Heegner index $2$, integer landing at $5.7\times10^{-4}$),
realizing the fired jet $L'(37a1,1)=0.306$ as an actual cycle, per
Gross--Zagier. Two normalization errors en route were caught by the gates
before any claim (the BSD period covers both real components; the reduced
modulus fixes the lattice shape only up to generator assignment) --- the gates,
not the operator, decide. This is the operational template the terminus needs
at every grade; what changes above is only which arm plays the
parametrization.

\paragraph{The loop closed at grade four, clock-relation regime.} The same
four arms now run end to end one floor below the frontier
(\texttt{recognition\_loop\_g4.py}, App.~\ref{app:repro}), oracle-free, on
quadruples where truth is known but never consulted until grading.
\emph{Detection}: the portal's folded pair-directions inside the $(2,2)$
block, with the zero-variance freeze as certificate. \emph{Alignment}: the
freeze pattern inverts to the relation lattice --- with a measured law the
pre-registration had backwards: an isogeny lock $\theta_i=\theta_j$ freezes
the two directions carrying $(+,-)$ on each locked pair, so two disjoint
locked pairs freeze exactly two of the three directions and \emph{the single
live direction names the locked partition} --- then the period-clock
machinery certifies each implicated pair independently of the counts.
\emph{Construction}: the isogeny is \emph{found}, not assumed --- degrees
$5$ and $2$ with kernels $\mathbb Z/5$, $\mathbb Z/2$, $j$-residuals
$2.5\times10^{-15}$ and $8.3\times10^{-16}$ --- and the grade-four class is
the product graph. \emph{Recognition}: occupancy lands on the
invariant-theory count ($0.996\to1$) and the class's predicted channel
profile matches the measured portal exactly ($22/10/1$, within
$0.5\sigma$). The falsifier column is reading-scale (the fiber untouched,
only the reading harmonic grid varied), and it resolves two facts at once:
the \emph{qualitative} lock is scale-invariant (an isogeny lock is an exact
zero, so it survives every winding --- the genuine-algebraicity control),
while the \emph{quantitative} integer certificate is $\mu_6$-locked --- on
the $\mu_6$ grid every case lands its truth integer clean ($2/1/0$);
mod-$12$ over-splits the relations ($2\to6$, $1\to4$) \emph{and
manufactures a class in the scrambled null} ($0\to1$ --- the mis-scaling
phantom, the register's mis-clocking clause surfacing at recognition
level); an off-lattice winding lands no integer anywhere. The scrambled
control nulls at every arm, and a deliberately
false alignment is \emph{rejected by the construction arm} --- no integer
isogeny degree exists, the residual never leaves $O(1)$ --- the loop's
arms police each other, as at grade one. Register-exact boundary: this
closes recognition for classes sourced by pairwise clock relations (the
Lefschetz/isogeny, Tate-for-products regime); the exotic/Weil-type classes
--- occupancy with \emph{no} frozen pair-direction, the two-plane of
\S\ref{sec:rails} --- are a strictly different object, and this template
does not reach them.

\paragraph{The even rung's loop: grade two, and the state of the art.}
Between the two closed rungs sits the even-parity template, where the
construction arm exists in the literature: Beilinson's Siegel-unit classes
on products of modular curves, whose regulator is the Rankin--Selberg value
at the non-critical point \cite{Beilinson1985,LLZ,BDR,BrunaultChida}. Run
in-house (\texttt{bf\_loop\_g2.py}, App.~\ref{app:repro}): the degree-4
Rankin--Selberg motive has \emph{no critical points} --- the same even-rung
regulator geometry as grade four --- with a trivial zero forced at the edge
and the exact bridge $L'(f\otimes g,1)=\varepsilon\,(N_fN_g/4\pi^2)\,
L(f\otimes g,2)$ derived and numerically confirmed. The detection arm is
certified ($L(11a1\times37a1,2)=3.46319093$; the derivative through the
trivial zero confirmed independently), and the construction arm
\emph{closes on the Eisenstein corner}: the Rogers--Zudilin identity
\cite{RogersZudilin} is verified from scratch --- a two-dimensional Mahler
integral against the evaluator's $L(E_{24},2)$, relative difference
$1.55\times10^{-5}$, with the rational landing $m\cdot\pi^2/L=23.9996\to24$.
For the \emph{genuine} two-cuspform product the construction arm remains
open --- and the honest finding is that this is the literature's own state:
no from-scratch regulator number for a genuine degree-4 product of distinct
cuspforms exists in print (the published numerics are all the degenerate
corner). The carrier translation, which is the rung's real yield: even rungs
read a Gram \emph{volume} of paired drift channels --- two units' log
channels paired against the test form, never a self-pairing --- the
$\pi$-power is fixed by the Tate twist through the functional equation, and
\emph{the rational is a lane count of the conjugate-closed re-weld, not a
period}. Grade four's staked matching law (\S\ref{sec:wallfour}) is the
exact structural successor: a higher drift determinant in place of the
single pairing, the same tropical-plus-archimedean split, the same
integer-landing discipline, and no height anywhere.

\section{Rung four: the walls, and the far side}\label{sec:rung4}

The ladder of named landings --- grade $0$ Tate/Lefschetz; grade $1$
Birch--Swinnerton-Dyer/Gross--Zagier/Kolyvagin; grade $2$
Gan--Gross--Prasad/Kudla/W.~Zhang \cite{GGP,WZhangAFL}; grade $3$
Gross--Kudla/Gross--Schoen/Zhang/Yuan--Zhang--Zhang \cite{ZhangGS,YZZ} ---
ends at grade four: the quadruple product $L(f_1\times f_2\times f_3\times
f_4,s)$ and the fourth modified diagonal carry no name, no integral
representation (Garrett's construction is the last of its line), no general
functional equation, no height formula. Three walls explain why, each proven
or measured here.

\paragraph{Wall one: the non-critical center.} The motive $\otimes^4H^1$ has
weight $4$ and Hodge types $(4,0)+4(3,1)+6(2,2)+4(1,3)+(0,4)$: the
six-dimensional $(2,2)$ block is a $k=0$ channel --- \emph{grade four is the
first rung whose motive has a DC channel} (even weight $\Leftrightarrow$ DC
present --- now machine-checked:
\texttt{RequestProject/EvenWeightDC.lean},
\texttt{dc\_channel\_iff\_even\_weight}, with the instantiated corollaries
\texttt{grade4\_dc\_channel} and \texttt{grade5\_no\_dc\_channel}), and a
$(w/2,w/2)$ block makes the center non-critical. Heights die;
the named ladder lives entirely in critical-center territory. Any rung-four
central-derivative identity must be Beilinson-shaped --- and indeed the even
ladder already exists one rung down: Beilinson(--Flach) at grade two,
regulators where grade one had heights. One drift, two parity readouts
(\S\ref{sec:drift}).

\paragraph{Wall two: the diagonal was never the right object.} The
codimension bookkeeping matches the $\otimes^n$ motive's pairing only at
$n=3$, and the higher modified diagonals vanish outright for low genus
(Voisin \cite{VoisinMD}: $\Gamma^{g+2}(X,x)=0$). The rung-four cycle theory cannot be ``grade
three but larger.''

\paragraph{Wall three: the split no-go, and homelessness.} The natural even-rung
candidates on $X_0(N)^4$ are surfaces with units, and both are forced split:
units on a product split (Rosenlicht), so the regulator integrand splits as
$\log|u_1|+\log|u_2|$, each term carrying one unit-free Petersson block, and
distinct newforms are orthogonal. \emph{Every decomposable class pairs to zero
with the primitive quadruple} --- machine-checked in model form
(\texttt{RequestProject/Rung4SplitNoGo.lean}:
\texttt{split\_unit\_pairing\_vanishes}, \texttt{product\_pairing\_factors};
standard footprint). Combined with the measured occupancy zero (four distinct
non-isogenous curves have \emph{no} algebraic $(1,1,1,1)$-classes,
\texttt{quadruple\_rung.py}), the rung-four recognition object has no naive
home on $X_0(N)^4$ at all. The rung is unnamed because it is classically
homeless.

\paragraph{The detection row, measured.} The DC occupancy of the
$16$-dimensional channel, read from point counts, lands on the
invariant-theory predictions exactly: $0.029\to0$ for four non-isogenous
curves; $0.958\to1$ for two pairs from distinct classes; $1.974\to$
\textbf{Catalan $2$} --- non-crossing pairings, not three --- for the double
self-pair, the rung's first measured structure constant; $2.918\to3$ for the
CM quadruple; odd-parity controls at zero throughout
(\texttt{quadruple\_rung.py}). The Weil mechanism --- rational classes
assembled from irrational cycles, the shape of the open Hodge classes --- is
likewise measured as occupancy \emph{excess}: quadruples of pairwise
non-isogenous twists carry zero $\mathbb Q$-pairing count yet full
$\overline{\mathbb Q}$ occupancy exactly when the twist product is a square
(\texttt{weil\_detection.py}), calibrating exotic-class detection where truth
is known.

\paragraph{The far side: the fiber assembled.} The carrier does not need the
missing variety: the degree-16 tensor fiber is admissible by construction, and
it is now assembled and measured (\texttt{farside\_quadruple.py}). The
degenerate case $f^{\otimes4}$ factors through the lower harmonics
\emph{exactly}: the sixteen eigenphases match
$\mathrm{Sym}^4\oplus3\,\mathrm{Sym}^2\oplus2\cdot\mathbf 1$ at
$3.3\times10^{-16}$ per prime, and the coefficient identity
$\lambda(f^{\otimes4})=\zeta^2*\mathrm{Sym}^2{}^{*3}*\mathrm{Sym}^4$ holds to
$3.6\times10^{-14}$ across five thousand coefficients --- the rung-four
Clebsch--Gordan identity, both sides from the same point counts. The primitive
case (four distinct curves) is certified \emph{irreducible} by the Schur
second moment: $\sum m_i^2=0.930\to1$, against $13.703\to14=1^2+3^2+2^2$ for
the degenerate control --- no direct-sum decomposition, hence no factorization
into lower $L$-functions, ever. And the first quantitative datum: the
primitive fiber's partial-sum growth exponent, $0.577$ over the top measured
decade (degenerate control $1.081$, exactly the double-edge-pole behavior its
occupancy predicts) --- a finite-window value, expected to equilibrate with
$x$, and the first measurement ever taken of this object.

\paragraph{The rung-four program, staked.} Conditionally, in the register of
\S\ref{sec:terminus}: the rung-four recognition object is a \emph{non-split,
carrier-native regulator reading} of the primitive degree-16 fiber's drift
channel at the non-critical center --- the log-shear datum of the fiber read at
the DC slot of its completed reflection, against the fiber's first log-channel
jet. Its consistency degenerations are already theorems of the instrument
suite: the single-form case must and does factor through
$\mathrm{Sym}^4/\mathrm{Sym}^2/\zeta$, and the Tate obstruction is the
measured occupancy. Nothing classical constrains the primitive reading; every
number it produces is a prediction.

\section{Wall four: the information wall, measured and dismantled}\label{sec:wallfour}

The three walls of \S\ref{sec:rung4} explain why the rung is unnamed. A fourth
wall, discovered here, explains why it would have stayed unnamed: the one
number the rung guards --- $L(\mathrm{quad},\tfrac12)$ --- is
\emph{chart-unreachable even numerically}. This section measures the wall on
three independent faces and then strips the guarded number of everything
readable around it.

\paragraph{The certified value chain.} The house evaluator computes completed
values by one contour pass through the split identity
$\Lambda(s_0)=\sum_n\lambda_n[H(s_0,n)+\varepsilon H(1-s_0,n)]$, and
\emph{self-certifies} each functional-equation shape by a two-point
split-vs-direct comparison at $s_0=2.2,2.5$ (a wrong sign or wrong
$\Gamma$-shape misses at $10^{-2}$; the true shape matches at $10^{-5}$ or
better). Gates: $\zeta(\tfrac12)$ to $3\times10^{-7}$ and $L(11a1,\tfrac12)$
to $2\times10^{-7}$. The chain is then oracle-validated on a fully independent
code path (\textsc{pari} \texttt{lfunsympow}, plus Dokchitser at degree four):
$L(\mathrm{Sym}^2 11a1,\tfrac12)=0.8933980$,
$L(\mathrm{Sym}^4 11a1,\tfrac12)=0.6058010$,
$L(\mathrm{Sym}^3 11a1,\tfrac12)=1.1402380$ (oracle $1.1402309$), both $s=1$
values, and the degenerate assembly
$\zeta(\tfrac12)^2L(\mathrm{Sym}^2,\tfrac12)^3L(\mathrm{Sym}^4,\tfrac12)
=0.921258569$ at $7\times10^{-6}$ --- the classical side of the rung-four
calibration, from scratch. Two values are new to the record:
$L(11a1\times37a1,\tfrac12)=5.0227652$ (degree four, Dokchitser-confirmed at
$1.2\times10^{-5}$) and the degree-six center
\[
  L(\mathrm{Sym}^2(11a1)\otimes37a1,\tfrac12)\ =\ 0.61570486
\]
($\varepsilon=+1$, $Q=11^4\cdot37^3$, two-point certificates
$7.5\times10^{-5}/6.1\times10^{-5}$; twelve megabytes where the standard route
wanted gigabytes) --- the deepest certified truth, one rung below the triple
product.

\paragraph{The wall, measured on three faces.} \emph{Linear:} the windowed
center protocol is provably sound --- its fitted leading-pole coefficient on
the degenerate case lands on the analytic prediction
$A=\sqrt\pi\,L(\mathrm{Sym}^2,1)^3L(\mathrm{Sym}^4,1)=1.5323$ at
$5\times10^{-4}$ --- but the primitive is absolutely blocked: the analytic
conductor $(11\cdot37\cdot53\cdot61)^8\approx10^{49}$ prices any chart-side
center determination at $\sim\!\sqrt Q\approx3\times10^{24}$ coefficients, and
the measured reading climbs as a pure transient ($X^{0.19}$; the carrier
window's ladder shows the same physics, converging on RS4 at $1.5\%$ as it
crosses $\sqrt Q=407$ while the quadruple climbs $14.5\to32.1$ with no
plateau at any reachable height) --- exactly as the information bound demands
for \emph{any} linear reader. \emph{Fitted warps:} Gauss--Newton-solved warp
weights close the primitive cells (median $|D|$ $4.98\to0.21$ --- the first
forcible-closure datum above degree fourteen, overfit-caveated) but fail the
value gates on both certified truths ($F_w(\tfrac12)\ne L(\tfrac12)$, ratios
$1.35$ and $0.78$, no common registration): \emph{solved warps buy
summability, not values} --- the measured gap between
continuation-\emph{exists} and value-\emph{computable}. \emph{Lane surgery:}
the half-lane objects that would decompose the read are of
Estermann--Kurokawa class \cite{Estermann,Kurokawa} --- incomplete Euler
products with a natural boundary at the center (window ladders diverge,
growth exponent $+0.43$) --- so no decomposition into complete readables
exists. The falsifier fired in public and is recorded as such: the corpus
never claimed a value recipe, and the finding has a name (below).

\paragraph{The sheet from twenty integers.} Everything around the guarded
number is readable from the four curves' local data alone.
The functional-equation sheet:
\[
  Q=(11\cdot37\cdot53\cdot61)^8,\qquad
  G(s)=Q^{s/2}\,\Gamma_{\mathbb C}(s+2)\,\Gamma_{\mathbb C}(s+1)^4\,
  \Gamma_{\mathbb R}(s)^3\,\Gamma_{\mathbb R}(s+1)^3,
\]
the $3/3$ split of the $(2,2)$ block \emph{forced} --- $F_\infty$ maps each
balanced lane to its complement, pairing the six lanes into three swap-pairs,
each contributing one $+1$ and one $-1$ eigenvalue --- so the shape carries no
free parameter. First values of the primitive quadruple ever taken:
$L(2)=1.67012705$, $L(2.5)=1.37508344$, $L(3)=1.22583059$ (Euler product on
the convergent axis --- the toll is a strip phenomenon, not a function
phenomenon), reflected exactly to the mirror axis ($L(-1)=L(-2)=0$, trivial
zeros; $L(-1.5)=2.878\times10^{72}$). The center's vanishing order is read as
zero --- rank $=$ DC-residue (the house law, validated across
$122$ determinations at grades $0$--$3$) plus the portal's measured occupancy
zero --- so $L(\mathrm{quad},\tfrac12)\ne0$ in the framework register,
falsifiable. And the center is \emph{non-critical with no critical points
anywhere} (the $(2,2)$ $\Gamma_{\mathbb R}$ poles kill $s=2,3$; the motivic
center is half-integral): the unread number has no Deligne-rational part.
What the wall guards is a \emph{regulator volume} --- nothing else.

\paragraph{The sign, proven.} The sheet's root number is not provisional: it
is computed unconditionally from Deligne's local theory
\cite{DeligneEps,TateNTB}. At each bad prime exactly one tensor leg is special
($\mathrm{sp}(2)$, conductor exponent one) and the other three legs are
unramified of total dimension eight, so the unramified-twist formula gives
sign $\varepsilon_p(\mathrm{sp}(2)\otimes W)
=\varepsilon_p(\mathrm{sp}(2))^{8}\cdot\mathrm{sgn}\,\det W(\mathrm{Frob}_p)
=(\pm1)^8\cdot\mathrm{sgn}(p^{12})=+1$ --- independent of split versus
non-split \cite{Rohrlich} --- while the conductor exponent
$a_p=8\cdot1$ postdicts $Q=(\prod N_j)^8$ independently. At infinity, Deligne's
recipe on the Hodge diamond gives
$i^{\,5h^{0,4}+3h^{1,3}+\#\{F_\infty=-1\ \text{on}\ (2,2)\}}=i^{17+3}=i^{20}=+1$,
with the middle-block rule pinned uniquely (not a free convention) by
demanding real signs on $\mathrm{Sym}^2$ and $\mathrm{Sym}^4$ simultaneously.
Calibration: the same component rules postdict all nine known signs --- the
four curves (matching rank parity), $\mathrm{Sym}^2$, $\mathrm{Sym}^3$,
$\mathrm{Sym}^4$, the Rankin--Selberg pair, and the degree-six object, whose
odd-dimensional unramified factor at $37$ genuinely exercises the finite rule.
Hence
\[
  \varepsilon(\mathrm{quad})\ =\ \varepsilon_\infty\cdot\prod_p\varepsilon_p
  \ =\ +1,
\]
a theorem of the local data (\texttt{eps\_quadruple\_notes.md},
App.~\ref{app:repro}). Register: what is proven is the motive's global root
number; that the completed product satisfies the sheet's reflection is the
carrier-side transport statement, exactly as everywhere else in the program.

\paragraph{The tropical layer, and what the number is.} The four curves'
reduction graphs are computed and exact: $11a1$ is $I_5$
($\Delta=-11^5$, cycle graph $C_5$), the other three are $I_1$. The graph
invariants are exact rationals --- $\tau(C_n)=n/12$, so
$\sum\tau=\tfrac{2}{3}$ baseline, and the $C_5$ Green's function has moments
$m_1=0$, $m_2=5/36$. The portal (\S\ref{sec:rails}) shows every $(2,2)$ lane
of the primitive fluctuating --- the classes penetrate
$\ker\mathrm{AJ}_{\mathbb C}$ --- which in Zhang's admissible-pairing
decomposition \cite{ZhangGS} is the regime where the height is carried by the
tropical part: \emph{the wall's remainder is tropical-dominated, mostly
rational}. The named theorem-target this stakes (program register): the
\textbf{grade-four matching law}, the unnamed rung's Gross--Kudla/Ichino
analogue --- ledger-side drift determinant $=$ tropical admissible pairing
(graphs) $+$ archimedean remainder --- with both sides' computable pieces now
in hand. And the wall itself, after tonight, guards nothing else: not
existence (sheet pinned), not sign (proven), not vanishing order, not
non-vanishing, not occupancy, not interior geometry, not off-strip values ---
one transcendental volume. The residual obstruction has a name, the
\textbf{value-registration law} (the value-level analogue of the
$S(t)$-compensation theorem): the single theorem-target through which any
carrier-native center \emph{value} must pass, at every grade at once. Its
measured content is now on record (\texttt{value\_registration.py},
App.~\ref{app:repro}): across a $24$-row census over the six certified
truths, the registration defect \emph{decomposes} --- a finite-$Y$ transient
living on the lattice point itself (the honest unwarped window; decaying as
$Y/\sqrt Q$ grows, functional form not yet pinned) plus a warp-induced
defect governed by \emph{off-lattice distance} (correlation $+0.89$,
cross-validated out-of-object) and removed exactly by snapping to the
integer-$m$ harmonic lattice. Cross-validation kills the alternatives: the
cell-closure-improvement ratio has \emph{zero} predictive power for
registration --- the quantitative form of ``solved warps buy summability,
not values'' --- and no degree/conductor law survives held-out testing.
Since every nontrivial integer-$m$ warp reads a \emph{different}
$L$-function (\S\ref{sec:rails}), the only registering lattice reading of
the object's own $L$ is the unwarped window, where the full $\sqrt Q$
transient must be paid: registration is lane-side and free; cost is
radial-side and irreducible in every form tested tonight.

\paragraph{The fiber's formal home.} The degree-16 object of
\S\ref{sec:rung4} now exists in Lean
(\texttt{RequestProject/QuadrupleFiber.lean}; standard footprint, thirteen
theorems): the four-fold tensor fiber composes from the two-fold construction
with determinant one preserved, per-place functional equation with the
$(-X)^{16}$ reflection explicit, completed local reflection
$\Lambda(s)=\varepsilon(s)\Lambda^{\vee}(1-s)$, and strand exchange over the
sixteen weight channels; the concrete curve instance
(\texttt{curveQuadFiber}) carries all of it. The composition was, as
predicted, nearly free --- the carrier's constructions are degree-agnostic,
which is the point of \S\ref{sec:scaling}.

\section{The lattice, the rails, and the portal}\label{sec:rails}

How the instruments got inside the rung is itself a law, and it was measured
before it was named: \emph{the helix admits only harmonically self-compatible
readings}. Three independently falsified conditions make the phrase precise:
warps must be integer multiples of the fiber's own local angle (the lattice),
lanes pair only with their exact conjugates (the rails), and addresses live on
the $\mu_6$ cells (the carrier's own lattice). Everything in this section
consumes point counts and the certified chain of \S\ref{sec:wallfour}, nothing
else.

\paragraph{The harmonic lattice.} Warping the fiber's local eigenvalues
$\{e^{\pm i\theta_p}\}$ by $e^{im\theta_p}$ with \emph{integer} $m$ produces
exact lane identities on the symmetric-power tower:
$F_2F_{-2}=L(\mathrm{Sym}^3f,s)\,C_2(s)$ and
$F_3F_{-3}=\bigl(L(\mathrm{Sym}^4f,s)/\zeta(s)\bigr)C_3(s)$, with elementary
bad-prime factors $C_2=(1-\alpha^3q)/(1-\alpha q)^2$,
$C_3=(1-\alpha^4q)(1-q)/(1-\alpha q)^2$ --- machine zero
($10^{-9}$--$10^{-13}$) in the absolute region, certified centers on the
right-hand sides. The incommensurate control $m=\sqrt2$ has \emph{no} partner
identity ($O(1)$ mismatch). Lattice warps are parameter-free: closure is
structural on every cell or absent --- nothing to train, nothing to overfit.
The base unit is the fiber's own $\theta_p$; the tower is its integer
multiples; that is what ``harmonically compatible'' means, measured.

\paragraph{The two-rail pairing, and where values live.} The individual
half-lane objects $F_m$ have natural boundaries at the center
(\S\ref{sec:wallfour}); the three-dimensional question --- ground rule of the
program --- is whether that boundary is a carrier fact or a chart artifact.
Measured, on the same phasor data, three ways at $\tfrac12$: the single rail
$F_2$ \emph{diverges} ($|F_2|^2$ marching $6.4\to25.1$, growth exponent
$+0.43$); the height-matched Hermitian pairing of exact conjugate rails ---
the Dirichlet convolution $(F_2\ast F_{-2})[n]=\sum_{d|n}\lambda_2[d]
\lambda_{-2}[n/d]$, phasor at height $\log d$ on one rail against phasor at
height $\log(n/d)$ on the other, a geometric operation performed before any
chart reads anything --- \emph{converges} to the certified
$L(\mathrm{Sym}^3,\tfrac12)\,C_2(\tfrac12)=1.368286$ at $9.7\times10^{-5}$
(growth exponent $+0.018$); and \emph{both} mis-pairs ($F_2\ast F_{-3}$,
$F_3\ast F_{-2}$) diverge like the single rail. The rail-matching law ---
exact conjugates only --- extends the non-self-dual GL(3) precedent past
natural boundaries: \emph{the boundary lives in the single-rail scalar chart,
not on the carrier, and values live at the pairing level}. The primitive
quadruple is itself a two-rail pairing ($G\ast\bar G$, $G$ the plus-half of
$f_1$ tensored with the full triple), so its carrier representation exists
--- verified numerically on the carrier: $G\ast\bar G$ reproduces the full
degree-16 tensor to $2.4\times10^{-13}$ with real (conjugate-closed)
coefficients (\texttt{helix\_tower.py}); the pairing read keeps the
quadruple's own transient scale, so the
\emph{value} wall of \S\ref{sec:wallfour} stands --- and the height run
locates it exactly: on the carrier the $\mathrm{Sym}^3$ pair converges at a
radial head of tens while the quadruple needs $\sim\!\sqrt Q\approx10^{24}$,
so the wall is the carrier's \emph{radial scale}, not any lane defect ---
the $\sqrt Q$ toll made geometric. (A unit-scale window on the
\emph{readable} $\mathrm{Sym}^3$ pairing reads $1.0000$ against the true
$1.3683$: the never-unit-scale law's first height-side instance.) The door
this opens is spectral, and it is walked through below.

\paragraph{The portal: reading the homeless block from inside.} Per prime, the
sixteen lanes of the quadruple fiber are the sign vectors
$\epsilon\in\{\pm1\}^4$, and the diagonal frequency $k=\sum\epsilon_i$ sorts
them into the Hodge channels: $k=4$ the $(4,0)$ lane, $k=2$ the four $(3,1)$
lanes, $k=0$ the six $(2,2)$ lanes. The scalar chart reads only
$\lambda_p=\sum_kT_k(p)$ --- the channels summed, unmixable; with the fiber's
angles alongside, the portal
$T_k(p)=\sum_{\epsilon:\,\Sigma\epsilon=k}e^{i\epsilon\cdot\theta(p)}$ reads
each channel separately at every prime ($148{,}929$ primes to $2\times10^6$).
Measured against exact product--Sato--Tate predictions: primitive moments
$\langle|T_0|^2\rangle=12.3818$ vs $99/8=12.375$,
$\langle|T_2|^2\rangle=7.004$ vs $7$, $\langle|T_4|^2\rangle=1$ (all
$\le0.4\sigma$); degenerate control $(36,16,1)$ \emph{with zero variance} ---
when the clocks coincide every balanced lane freezes, and \textbf{channel
constancy is the portal's algebraicity signature}: the degenerate block's six
frozen lanes are its six algebraic classes, seen live, while every primitive
lane fluctuates (the homeless fiber, $\mathbb Q$-count zero). Inside the
$(2,2)$ block the six lanes fold into three pair-directions
$\{12|34\},\{13|24\},\{14|23\}$ whose interior Gram is exactly
$\mathrm{diag}\ 17/32$, off-diagonal $1/4$ (measured to $\pm0.0007$) ---
an $S_3$-symmetric $\mathbf 1\oplus\mathbf 2$ eigensplit, $33/32$ on the
symmetric line and $9/32$ on the two-dimensional complement: \emph{the
two-plane is where a grade-four exotic class would live}. The wrong-harmonic
falsifier ($\theta_1\to2\theta_1$) leaves the predictions by $144\sigma$.
This is the first channel-resolved interior map of a Hodge structure with no
classical home.

\paragraph{The spectral door.} Values pay the $\sqrt Q$ toll; zeros are $local$
focal events and pay none --- but they need the right head and the right
address. The house diagonal schedule $Z=e^y$ is the conductor-one special
case (it starves higher conductor at low ordinate); parking the head at
maximum data and scanning the ordinate --- the horizontal slice of the same
geometry --- with rails addressed on the $\mu_6$ lattice
(key $=$ sign $\times\,n\bmod6$, twelve rails) gates \textbf{12/12} against
the \textsc{pari} oracle zeros of $\mathrm{Sym}^3(11a1)$ (median
$|\Delta t|=5.8\times10^{-4}$), including the close pair $7.75/8.01$ split at
the Rayleigh limit --- the first locator validation beyond degree two ---
while mod-$12$ addressing over-splits ($11/12$): $\mu_6$ is \emph{the}
lattice, as the method law says. On the primitive quadruple the same
instrument returns a clean null (a marginal $t=2.68$ event in the pre-rail
pass was killed by hostile checks --- it wandered with the head while the
gate zero stayed fixed --- and removed entirely by the rails: textbook
falsification). The toll structure, measured: individual zeros need heads at
conductor scale; values and zeros pay chart tolls, \emph{shape pays none} ---
which is why the portal and the sheet read the rung the chart cannot.

\section{Scaling: grades five and six}\label{sec:scaling}

The obvious question --- Sam's, verbatim: does this scale beyond grade four,
does it constantly require new inventions, or does it plateau --- has a
measured answer at the structure tier. The design was frozen, two more
prime-conductor semistable curves were added ($79a1$, $83a1$; twenty-five,
then thirty integers), every prediction was pre-registered as an exact
rational \emph{before} measurement, and the deliverable was the
\emph{design-change log}: every point where grade five or six forced anything
beyond changing $g$ and the curve list.

\paragraph{The verdict: compute only.} All pre-registered rationals land
within $1.2\sigma$ over $148{,}927$ primes. Grade five primitive channel
moments $1,\ 10,\ 215/8$ --- measured $1.0000,\ 10.0081,\ 26.9110$; grade six
$1,\ 27/2,\ 405/8,\ 1225/16$ --- measured $1.0000,\ 13.5197,\ 50.7632,\
76.8083$; every degenerate control exact with zero variance ($1,25,100$;
$1,36,225,400$). The moment law itself is closed-form,
$\langle|T_k|^2\rangle=\binom{g}{m}\sum_i\binom{m}{i}\binom{g-m}{i}4^{-i}$
with $m=(g-k)/2$, verified against the brute lane-pair sum at every grade.
The one genuine code addition: the odd-weight $\Gamma$-assembly branch
(grade four's script hard-coded the even middle block) --- the odd case of
the same Serre recipe, no new mathematical idea; grade six reuses the even
branch verbatim. No other change of any kind.

\paragraph{The Catalan spine.} The degenerate DC occupancy marches on the
Catalan numbers: $C_2=2$ at grade four (\S\ref{sec:rung4}),
$\mathbf{C_3=5}$ at grade six (measured $4.9847$) --- and the degenerate
Schur second moments march with them: $C_4=14$, $C_5=42$, $C_6=132$ (measured
$13.94$, $41.75$, $130.99$; the primitive Schur moment stays at $1$ ---
irreducible --- at both new grades). The non-crossing/Temperley--Lieb
structure constants are not a grade-four curiosity; they are the tower's
spine.

\paragraph{The parity law, measured and proven in the same session.} Grade
five (odd weight) has \emph{no} DC channel --- there is nothing to occupy;
its sheet is all-$\Gamma_{\mathbb C}$,
$Q=(11\cdot37\cdot53\cdot61\cdot79)^{16}$, and the component rules give
$\varepsilon=-1$: \emph{a central zero is forced on the sheet} --- the
pre-committed falsifiable statement that replaces the missing DC reading on
odd rungs. Grade six restores the DC channel ($20$ balanced lanes of $64$;
middle split $10/10$ forced; $\varepsilon=+1$; non-critical center exactly as
grade four). The same fact is a theorem the same day
(\texttt{EvenWeightDC.lean}, \S\ref{sec:rung4}). Falsifiers at both grades:
wrong-harmonic $139\sigma/132\sigma$; scrambling the \emph{degenerate}
alignment lifts the frozen channels by $437\sigma$ (channel constancy is
genuine per-prime alignment, not a moment coincidence), while scrambling the
primitive changes nothing (the moments are marginal--Sato--Tate facts, as
they must be).

\paragraph{The tower to grade twenty, and the root-number law.} The atlas was
then run to grade twenty (the first twenty prime-conductor curves; the
$2^g$-lane enumeration replaced by an exact $O(g^2)$-per-prime polynomial
convolution --- an algorithm, not a method), and the empirical field produced
a theorem-shaped law. The archimedean assembly closes to
$\varepsilon(g)=i^{A(g)}$ with
\[
  A(g)\ =\ 2^{g-1}\ +\ g\binom{g-1}{\lfloor (g-1)/2\rfloor},
\]
always even --- so the tower is self-dual with a real sign at \emph{every}
grade --- and the sign is $-1$ exactly when $g=2^k+1$: by Kummer's theorem
the $2$-adic valuation of the central binomial is the binary digit sum, so
among odd grades only $m=(g-1)/2$ a power of two survives. \emph{Forced
central zeros at exactly $g=3,5,9,17,33,\dots$} --- reproducing grade three
(the Ceresa channel's forced zero, \S\ref{sec:ceresa}) and grade five
(\S\ref{sec:scaling}), while $g=7,11,13,15,19$ are odd with $\varepsilon=+1$,
so ``odd forces a zero'' is false and the law is sharper; grades nine and
seventeen stand as new pre-committed forced-vanishing predictions. Alongside
it, three more measured laws: the Catalan spine holds exactly to
$C_{10}=16796$ and $C_{20}=6.56\times10^9$; the DC lane fraction falls as
$\binom{g}{g/2}/2^g\sim\sqrt{2/\pi g}$ (the homelessness curve,
$.500\to.176$); and the interior Gram of the middle block continues the
grade-four $\mathbf 1\oplus\mathbf 2$ split as
\emph{trivial $\oplus$ nontrivial $S_g$-irreps} at every even grade mapped
($\mathbf 1\oplus\mathbf 9$ at six, $\mathbf 1\oplus\mathbf{20}
\oplus\mathbf{14}$ at eight; the balanced-bipartition object, the faithful
continuation of grade four's pair-directions) --- one simple common mode, and
an exotic-candidate complement of known representation type. Resolution
itself obeys a three-tier law at fixed prime count: bounded channel moments
stay flat ($<1.5\sigma$ through grade twenty); single-clock power moments
degrade polynomially; $g$-clock product readouts (the Schur/primitivity
trace) die exponentially at $g\approx17$ --- \emph{the cliff is a property of
the readout, not the object}, and the channel decomposition still reads
cleanly where the global trace is blind. Finally the falsifier column
returned a method law of its own: a probe of fixed support dilutes
($145\sigma\to83\sigma$ up the tower, \emph{including} a single leg warped to
the top harmonic $m=g$ --- the dilution axis is the corrupted-leg
\emph{count}, not the multiplier), while constant-fraction support holds and
grows ($145\sigma\to493\sigma$). Two lessons, one per axis: within the
warp-based falsifier family the dilution law is a \emph{support} law (the
corrupted-leg count, not the multiplier), while the carrier-side harmonic
\emph{scale} (the $\mu_6$ cells) stays grade-invariant. Method correction,
adopted after these runs: falsifier probes belong on the \emph{reading
scale} --- hold the fiber untouched and move the instrument off the $\mu_6$
grid, on which the object closes and off which it fails --- and the
warp-based family used here is deprecated for future instruments (its
measurements stand as the family's characterization). The corrected family
already has a height-side instance on record: the unit-scale window misread
of \S\ref{sec:rails}. Conductor toll at grade twenty: $\log_{10}Q\approx2.15\times10^7$
--- the value chart is twenty-one million digits deep while the structure
tier reads on. The symmetric-power side supplies the companion sign law and
a constituent-level validation of the same component rules: for semistable
$E$ the known closed form \cite{DMW,SaitoEps} --- $w_m=+1$ for even $m$;
$w_m=\bigl(\tfrac{-2}{m}\bigr)w(E)$ for odd $m$ --- is re-derived honestly
from Tate's twisted-Steinberg factor
($\varepsilon_p(\mathrm{Sym}^k)=w_1(p)^k$; no even-power shortcut exists on
the Sym side) and confirmed against the \textsc{pari} oracle on all eighteen
signs of $\mathrm{Sym}^{1..9}$ of $11a1$ and $37a1$, with the forced
vanishings verified as actual central zeros where values are reachable. And
the grade-nine consistency identity closes: the degenerate
$V^{\otimes9}=\bigoplus_k m_k\,\mathrm{Sym}^k$ sheet's diamond sign equals
the constituent product $\prod_k\varepsilon(\mathrm{Sym}^k)^{m_k}=-1$
(with $\sum_k m_kA(\mathrm{Sym}^k)=886=A$ exactly and Tate twists
sign-neutral) --- the degenerate shadow of the $g=2^3+1$ forced zero, the
two towers' $2$-adic sign laws (binary digit sum; Kronecker
$(\tfrac{-2}{m})$) imaging each other. The atlas's harmonic compatibility
was then audited rather than assumed (\texttt{harmonic\_compat.py}): the bank is conjugate-closed to
machine zero at grades $6$, $12$, and $20$, and every channel moment is
\emph{affine} in the single-clock closure value $c(w)=\mathbb E[\cos2w\theta]$
--- at the fiber's own fundamental, $c=-\tfrac12$ and the motive's exact
rationals close; at any other rational multiplier, $c=0$ and the reading is a
different, decoupled object ($>100\sigma$ from the motive); at an
incommensurate multiplier, $c$ is irrational and every moment goes
transcendental --- the false-null mechanism of the standing method law, now
measured in quantitative form. (One certification pitfall caught in-run:
best-fit rational approximation ``certifies'' fake rationality for
incommensurate $c$; the honest discriminator is lattice membership
$c\in\{-\tfrac12,0\}$.)

\paragraph{The tiered picture.} What scales freely is \emph{structure}: sheet,
sign, channels, interior geometry, primitivity, occupancy --- cost
$2^g$ per prime, method fixed. What recedes doubly-exponentially is the
\emph{chart}: $Q=(\prod N)^{2^{g-1}}$ prices center values out at every grade
past the degree-six rung, and individual zeros with them --- which is why the
value-registration law (\S\ref{sec:wallfour}) is the single named gate, at
every grade at once, rather than one wall per grade. The classical pattern
--- one new integral representation per grade, supply exhausted at three ---
was a chart artifact; the carrier needs two parity templates (heights on odd
rungs, regulators on even), and grades one through six now instantiate both.

\paragraph{The pairing law, staked.} Program register, with its falsifiers.
The session's results assemble into one candidate law: \emph{the central data
of $\Lambda$ is the Gram data of a single Hermitian pairing on the double
helix}. Its analytic face is the rail-matching law (only conjugate-closed ---
admissible --- objects pair; natural boundaries are single-rail artifacts);
its arithmetic face is the drift pairing (jets $=$ pairing determinants:
heights on odd rungs, regulators on even --- the parity alternation, DC-level
Lean-proven); its local decomposition is tropical (reduction-graph Green's
functions) $+$ archimedean, per Zhang's admissible theory. Named instances:
Tate at grade zero, Birch--Swinnerton-Dyer/Gross--Zagier at one,
Beilinson--Flach at two, Gross--Schoen/Zhang/Yuan--Zhang--Zhang at three ---
certified here on the Klein quartic (\S\ref{sec:ceresa}) --- the pinned sheet
at four, the structure tier at five and six. Falsifiers, pre-committed: a
grade-five central non-vanishing (the sheet forces zero); a grade-one
place-by-place height decomposition that fails to close on the certified
regulators; a grade-four matching-law assembly whose ledger and tropical
sides disagree beyond the archimedean remainder. The law is stated to be
shot at --- and the grade-one shot has already been fired and missed: on the
certified census the canonical height decomposes place-by-place exactly ---
$\hat h(P)=2\bigl(\lambda_\infty+\sum_p\tfrac{n_p}{2}
B_2(\{m/n_p\})\log p\bigr)$, the single calibrated constant being the
classical factor two between the canonical height and the N\'eron sum ---
blind on $53a1$/$61a1$ to $10^{-7}$ (the house $4^{-n}$ limit converges
\emph{upward to} the prediction, so the residual is truncation, not error),
non-circularly against the incomplete-$\Gamma$ jet to $3.5\times10^{-13}$,
with the rank-two pairing matrix decomposing \emph{entrywise} (regulator
$=$ determinant to $4.3\times10^{-11}$) and the wrong-graph control missing
by exactly $\tfrac23\log37$. Every $I_1$ tropical share is $\tfrac16\log p$
on the nose (\texttt{matching\_law\_g1.py}, App.~\ref{app:repro}).

\section{The terminus: the Hodge conjecture as source exhaustion}\label{sec:terminus}

The program's end goal is stated plainly, with its logic and its price.

In the carrier's coordinates a rational $(p,p)$-class is a state with the
\emph{Hodge signature}: its clock/weight datum sits in the self-paired,
phase-balanced position the ledger assigns to type $(p,p)$. The Hodge
conjecture \cite{Hodge,DeligneClay} asserts such a class is algebraic --- in
the register of this program:
\[
  \boxed{\ \text{every Hodge-signature state has an algebraic source.}\ }
\]
This is a source-exhaustion statement, the same genre as the carrier's proven
exhaustion theorems --- every vanishing event has a source; no layer is silent
--- now asserted at the top of the cycle tower. The two-question test the
program applies to every target passes: nothing here assumes the conjecture
(the towers, poles, and heights are read unconditionally from point counts and
completed values), and nothing is circular (the falsifiers below are concrete).
Three facts give the terminus its footing:

\begin{enumerate}
\item \emph{The divisor case is the template.} Lefschetz $(1,1)$
\cite{Lefschetz} is the classical grade-one instance: the Hodge-signature
condition detects exactly the algebraic classes, and the carrier's depth-one
row (\S\ref{sec:depthone}) reads that grade's full arithmetic --- order,
regulator, obstruction --- as ledger coordinates.
\item \emph{The pole reading is Tate-shaped.} The carrier reads algebraic-cycle
count as DC/pole data natively (\texttt{rank\_is\_dc\_residue}; the
$\mathrm{Sym}^2$ excess-pole detection of the CM Hodge class is a measured
instance of exactly the pole-order reading Tate's conjecture \cite{TateConj}
assigns to algebraic classes). The program's detection direction --- Hodge
signature $\Rightarrow$ some $T_d$ fires --- is thus already exercised.
\item \emph{The exhaustion principle has never failed a test.} Every class
put to it has appeared at finite depth ($1,1,1,2,3$), with the predicted
delayed signatures; deliberate search for a phantom has so far produced none.
\end{enumerate}

\noindent\emph{What the terminus still needs} --- named exactly, the honest
spine of the program:

\begin{enumerate}
\item \emph{The transcendental retained coordinate.} Two varieties can share
their zeta/Satake data yet differ in Chow and Griffiths groups, so the Satake
ledger alone cannot separate the transcendental layer in general. The program
must exhibit the additional retained coordinate --- the non-archimedean height
channel or the $\ell$-adic Ceresa class of \S\ref{sec:ceresa}, carried on the
ledger's radial/angle channels beyond the weight multiset --- and prove it is
genuinely retained by the descent, not synthesized after the fact. This is the
crux, and we state it as the program's hardest single obligation.
\item \emph{The converse leg: from firing coordinate to cycle.} Detection is
half the conjecture; the other half constructs the algebraic source from the
fired coordinate --- the cycle-theoretic analogue of the converse theorem that
turns the main paper's nice $L$-functions into automorphic representations.
The functoriality program of \cite{Universal} supplies the model: identify the
complete invariant package (there: functional equation, continuation,
boundedness, exhaustion; here: the graded tower record with its ledger), then
invoke or build the recognition theorem that says the package has a unique
source. No such recognition theorem exists yet at cycle level; building its
carrier form is the program's constructive arm.
\end{enumerate}

\noindent\emph{The architecture, machine-checked.} The reduction is now
kernel-fixed (\texttt{RequestProject/HodgeDial.lean}; standard footprint): a
\texttt{HodgeDial} carries the DC condition, rationality, an algebraic-source
predicate, and the tower readouts; \textsc{Retention} (no silent rational DC
mode) and \textsc{Recognition} (fired $\Rightarrow$ sourced) are the two named
hypotheses --- \emph{asserted by no one} --- and
\texttt{hodge\_of\_retention\_recognition} composes them, unconditionally, into
\textsc{SourceExhaustion}. On the semisimple model dial, retention is already a
theorem (\texttt{model\_sourceExhaustion\_of\_recognition} consumes the
Vandermonde separation), so there the terminus needs recognition alone. Any
future landing of either ingredient, by anyone, assembles into the terminus in
the kernel with no further argument; the sentence itself never needs to be
said in the author's voice.

\noindent\emph{Falsifiability register.} Pre-committed, in print: the program
dies at (a) a \emph{phantom} --- a nonzero class silent at every tower depth
(one suffices; the carrier radical would be nontrivial on cycles); (b) a
\emph{false source} --- a Hodge-signature state whose firing coordinates
provably admit no algebraic cycle beneath them; (c) a \emph{ledger failure} ---
a pair of varieties whose full retained ledger (not merely Satake) coincides
while their cycle theories differ. The register also demands that the reading
procedures fail when mis-clocked, and this has been exercised deliberately:
the wrong root of unity, the wrong tower harmonic, and the wrong harmonic rate
each break their readings by orders of magnitude
(\texttt{harmonic\_falsifier.py}), and the root-of-unity ladder
$\mu_3$--$\mu_{12}$ reconstructs integer point counts exactly with its own
roots while missing at the integer level with wrong ones
(\texttt{mu\_ladder.py}). Any hit will be published as prominently as
a confirmation. Current count after deliberate searching: zero. The first
adversarial instance of (c) has been run and survived: across an isogeny class
the $1$D readout is provably blind --- identical $a_p$, certified in-house ---
while the retained ledger separates every pair and redistributes in the exact
Cassels-invariant combination (App.~\ref{app:repro}). A second instance has
now been run where no shield protects the reading: non-diagonal quartic K3s
--- the Dwork pencil, genuinely coupled, plus block-separable generics with no
symmetry at all, hence no twist characters and no Faltings isogeny shield.
All forty-four non-isomorphic pairs separate in exact integer point counts
(minimum separation $3992$, growing with $p$); the one forced-isomorphic
control pair is identical, as required; and the hardest pair (Dwork $c=2$ vs
$c=1/2$) collides in its coarse fingerprints and even at individual primes,
yet the full trace sequence separates it cleanly --- the clause-(c) stress
scenario in miniature, and the ledger holds (\texttt{k3\_nondiag.py},
App.~\ref{app:repro}).

\section*{Conclusion}

What stands, and at what strength. The depth dictionary is a machine-checked
theorem about a non-circular, machine-fixed filtration, transport-invariant,
coinciding with Bloch--Beilinson whenever the latter exists. No-silent-layer is
unconditional on the semisimple carrier state, and on drift in the model: drift
is value-blind, jet-visible, and never silent, with positive-definite response
energy --- the model form of Beilinson--Bloch anisotropy --- and the measured
law $k^*=$ drift dimension holds across the census with machine-zero silence.
Depth one is measured at machine precision with all three coordinates
independently resolved and the obstruction landing on exact squares; depth two
fired on schedule; depth three is measured on the Laga--Shnidman family with an
exact isotropy boundary and a discovered torsion-translation symmetry, and
awaits its from-scratch landing --- whose $L$-side is now on record: the Klein
quartic's Ceresa channel carries forced sign $-1$ and central derivative
$0.8299\ne0$, matching the proven non-torsion of the cycle
(Target~\ref{tgt:ceresa}, half landed). Recognition is
closed at grade one on house instruments, gate-certified. Grade four --- the
first unnamed rung --- is mapped to its three walls (non-critical center,
parity ladder, split no-go) and crossed: the homeless degree-16 fiber is
assembled on the carrier, its degenerate case factoring through the lower
harmonics exactly, its primitive case certified irreducible, its first datum
on record --- and its fourth wall, the information wall, is measured on three
faces and dismantled: the functional-equation sheet is pinned from the twenty
integers with the root number proven $+1$, the strip-interior values exist,
the center is read non-vanishing in the framework register, the unread number
is identified as a tropical-dominated regulator volume, and the fiber's
formal home is a Lean theorem. The instruments that got inside --- the
harmonic lattice, the conjugate-rail pairing, the portal, the $\mu_6$-address
locator --- obey one measured admissibility criterion, harmonic
self-compatibility, and they scale: grades five and six run with no new
method, the Catalan spine and the parity law confirm across the ladder, and
the residual obstruction at every grade is one named theorem-target, the
value-registration law. The terminus architecture is kernel-fixed with its two
hypotheses named and asserted by no one. The end goal is the Hodge conjecture
as source exhaustion, and the route to it is the same route the main paper
walked for functoriality: build the object, keep the ledger, induce every
layer to appear, and let the recognition theorem finish.

\appendix

\section{Reproducibility}\label{app:repro}

All instruments are oracle-free --- no $L$-function call inside a locator;
published values enter only final verification columns. Lean footprints are
uniformly $\{\texttt{propext},\texttt{Classical.choice},\texttt{Quot.sound}\}$,
no \texttt{sorry}, audited by \texttt{\#print axioms}.

\begin{itemize}
\item \textbf{The filtration dictionary},
\texttt{RequestProject/HodgeLedgerFiltration.lean}:
\texttt{carrierFiltration\_antitone}, \texttt{ledger\_kernel},
\texttt{mem\_carrierFiltration\_succ}, \texttt{no\_early\_detection},
\texttt{grade\_visibility}, \texttt{firstVisibleDepth\_eq\_grade},
\texttt{isFirstVisible\_unique}, \texttt{isFirstVisible\_map\_iff},
\texttt{carrierFiltration\_unique}, \texttt{blochBeilinson\_coincides},
\texttt{exhaustive\_of\_radical\_trivial},
\texttt{grade\_visible\_of\_nondegenerate},
\texttt{radical\_of\_factorsThrough},
\texttt{not\_mem\_radical\_of\_detectedPast}.
\item \textbf{The semisimple theorem},
\texttt{RequestProject/CarrierTowerSeparation.lean}:
\texttt{radical\_trivial\_of\_tower\_injective},
\texttt{momentTower\_detects}, \texttt{momentTower\_radical\_trivial},
\texttt{momentTower\_exhaustive}.
\item \textbf{The depth-one census}, \texttt{tmp/jet\_census.py} and
\texttt{tmp/sha\_hinge.py}: full BSD readings at ranks $0$--$3$; $|\Shamath|$
landed as exact squares $1,4,9$ (margins $\le3.6\times10^{-15}$ at rank zero,
$\le1.6\times10^{-4}$ through rank three); $L^{(r)}/r!$ via incomplete-Gamma
Taylor; heights by $x$-only $4^{-n}$ doubling; Tate $c_p$ and group-law torsion
in-house; Sage-oracle validated once, then run oracle-free.
\item \textbf{The layer calibration}, \texttt{tmp/hodge\_layer\_calib.py}:
order/regulator/obstruction resolved as independent coordinates across the
census.
\item \textbf{The delayed-signature test},
\texttt{tmp/tower\_exhaustion\_test.py}: point-counting tower; CM
self-correspondence silent at depth one, first firing at depth two; first
nonzero slot matches expected filtration depth for every tested class
($1,1,1,2,3$); no class silent at every level.
\item \textbf{The Griffiths probe}, \texttt{tmp/hodge\_griffiths\_probe.py}:
value channel fires for every homologically-trivial cycle in the census; the
recursive tower shows classes absent at level one appearing at level $\ge2$.
\item \textbf{The ledger-failure search, v1},
\texttt{tmp/hodge\_fast\_tests.py}: the $11a$ isogeny class. Identical $a_p$ at
every good $p<400$, certified by point counts --- so the $1$D readout provably
cannot separate the members (Faltings) --- while the retained channels separate
every pair ($\Omega$, $T$, $c_p$, each computed from the curve, never from
$L$), and the Cassels combination $\Omega\prod c_p/|T|^{2}$ is invariant across
the class to $2.2\times10^{-16}$; $|\Shamath|$ landed $=1$ on every member. No
ledger failure found. The v2 escalation --- a pair with equal \emph{full}
ledger and different $\Shamath$ or, in higher dimension, equal zeta and
different Chow data --- is the genuine clause-(c) falsifier hunt.
\item \textbf{The drift model and terminus spine},
\texttt{RequestProject/JordanDriftTower.lean} (drift value-blind / jet-visible
/ never silent; \texttt{driftPairing\_posDef};
\texttt{anisotropic\_of\_definite\_factor}),
\texttt{RequestProject/HodgeDial.lean} (\textsc{Retention},
\textsc{Recognition}, \texttt{hodge\_of\_retention\_recognition},
\texttt{model\_sourceExhaustion\_of\_recognition}),
\texttt{RequestProject/Rung4SplitNoGo.lean}
(\texttt{split\_unit\_pairing\_vanishes}). All standard footprint, no
\texttt{sorry}.
\item \textbf{The harmonic frame, calibrated}, \texttt{tmp/hodge\_clock\_demo.py}:
$E_1\times E_2$ Picard numbers read two ways --- period-clock alignments
(Hecke scan certified against the exact $j=c_4^3/\Delta$) and count-side
moments --- $6/6$ cases matching Lefschetz $(1,1)$ truth; CM discs $-3,-4$
recovered; the two-CM-fields control correctly refuses to align.
\item \textbf{The drift ladder}, \texttt{tmp/drift\_observability.py}: jet
ladders $k=0..4$ for eight curves, root numbers certified in-house
(split-vs-direct $\Lambda(3)$); $k^*=$ drift dimension throughout; responses
$=\mathrm{Reg}\cdot|\Shamath|$; three same-placement falsifier curves
(certified by prime discriminant and exhibited integral points) separate
cleanly.
\item \textbf{The dial}, \texttt{tmp/twistor\_hunt.py}: DC-locking on the
product-family twistor dial is discrete and exactly algebraic; irrational
controls at $O(1)$; locks are local minima (the base point is a critical point
of $j$ --- quadratic shoulders).
\item \textbf{The mis-clocking battery}, \texttt{tmp/harmonic\_falsifier.py}
and \texttt{tmp/mu\_ladder.py}: wrong root / wrong harmonic / wrong rate each
break their readings (separations $10^{3}$--$10^{7}$); rungs
$\mu_3$--$\mu_{12}$ reconstruct integer counts exactly with their own roots
(purity at $10^{-15}$, DC slots as predicted, sphere-lock at inert primes) and
miss at the integer level with wrong ones.
\item \textbf{Recognition at grade one}, \texttt{tmp/heegner\_recognition.py}:
point counts $\to$ modular image $\to$ Heegner alignment ($D=-7$) $\to$
self-certified lattice (both half-period identities exact) $\to$ $P=(1,0)$
recognized and verified in exact arithmetic; $\hat h(P)/\hat h(\text{gen})
=4.0006$.
\item \textbf{Depth-three anisotropy}, \texttt{tmp/ceresa\_anisotropy.py}:
$\hat h(Q_t)$ over $\mathbb Q(\sqrt[3]{t^2-1})$ from scratch; exact torsion
boundary at $t=0,\pm3$; census non-isotropic $0.59$--$1.16$; the
torsion-translation symmetry discovered and group-law-verified in-instrument.
\item \textbf{Rung four}, \texttt{tmp/quadruple\_rung.py} (occupancies
$0/1/\text{Catalan }2/3$ with parity controls), \texttt{tmp/weil\_detection.py}
(the Weil-assembly excess, $\mathbb Q$-count $0$ vs $\overline{\mathbb Q}$
occupancy, orthogonality controls), \texttt{tmp/farside\_quadruple.py} (the
degree-16 fiber: degenerate channel split at $3.3\times10^{-16}$, coefficient
factorization $\zeta^2*\mathrm{Sym}^2{}^{*3}*\mathrm{Sym}^4$ to
$3.6\times10^{-14}$, Schur irreducibility $0.930\to1$ vs $13.703\to14$, window
growth exponent $0.577$).
\item \textbf{The certified evaluator and value chain},
\texttt{tmp/center\_reading.py}, \texttt{tmp/deg6\_center.py},
\texttt{tmp/theta\_cache.py}: one-contour-pass split identity with two-point
split-vs-direct self-certification; gates $\zeta(\tfrac12)$, $L(11a1,\tfrac12)$;
oracle validation \textsc{pari} \texttt{lfunsympow} (degrees $3$--$5$) and
Dokchitser (degree $4$); the new degree-4 and degree-6 centers; $O(1)$
$\theta_p$ caches ($148{,}933$ primes to $2\times10^6$).
\item \textbf{Wall four, three faces}, \texttt{tmp/farside\_center.py},
\texttt{tmp/carrier\_center.py}, \texttt{tmp/adapted\_center.py}: windowed
protocol soundness ($A=1.5315$ vs analytic $1.5323$); the information bound
measured (primitive transient $X^{0.19}$, no plateau at any reachable
height); solved warps close cells but fail both value gates ---
summability, not values.
\item \textbf{The dismantling}, \texttt{tmp/wall\_dissolve.py}: the sheet from
twenty integers (forced $3/3$ split), first strip-interior values, mirror
zeros, center order zero in the framework register, the tropical layer
($\tau(C_n)=n/12$, $\sum\tau=2/3$, $C_5$ moments $m_1=0,m_2=5/36$).
\item \textbf{The root number, proven}, \texttt{tmp/eps\_quadruple.py} and
\texttt{tmp/eps\_quadruple\_notes.md}: the Deligne/Tate local computation,
nine-for-nine postdiction battery (reduction types recomputed via Tate's
algorithm, non-circular), conductor-exponent consistency, Sage oracle
cross-checks.
\item \textbf{The lattice, the rails, the portal, the door},
\texttt{tmp/harmonic\_lattice.py} (exact lane identities, incommensurate
falsifier), \texttt{tmp/helix\_pairing.py} (single rail diverges / conjugate
pair converges to the certified value / both mis-pairs diverge),
\texttt{tmp/hodge\_portal.py} (channel moments, zero-variance degenerate
constancy, interior Gram $17/32$--$1/4$, $144\sigma$ falsifier),
\texttt{tmp/spectral\_door.py} and \texttt{tmp/spectral\_door2.py} (fixed-head
$\mu_6$-rail locator, 12/12 oracle gate, Rayleigh-limit pair split, quadruple
clean null with hostile checks);
\texttt{tmp/helix\_tower.py} spectral half: the growth-window rerun of the
gate (11/12 bare rails; the diagonal schedule starves at tensor conductor,
as diagnosed) and of the quadruple (pre-registered null; the recurrent
$t=2.68$ dip killed a second time by Z-wander and both scrambles); the
arrow-scale falsifier shown to be gauge in fixed-head scans (sign-scramble
is the honest falsifier there, $0/12$); and the growth-vs-flat resolution
comparison --- a bounded null: at reachable head the grown and
equal-magnitude reads resolve the close pair at the same data volume;
\texttt{tmp/helix\_toll.py} and \texttt{tmp/helix\_spectral.py}: the $g=6$
follow-up with two pre-registered predictions falsified and one first-run
claim retracted (the transient growth exponent tracks \emph{degree} through
phase cancellation, not conductor --- a third independent confirmation that
cheap descriptors carry no value information; the carrier-representation
identity holds at both grades), and the $\mathrm{Sym}^4$ escalation: $8/19$
oracle zeros located at degree five, the detected subset head-stable and
dying under both scrambles --- the locator's first degree-five focal events.
\item \textbf{The Ceresa $L$-side}, \texttt{tmp/ceresa\_lside.py}: from-scratch
Hecke $L$-series over $\mathbb Q(\sqrt{-7})$; integer-exact match to the
weight-4 level-49 CM form; two-point sign certificates; central derivative
$0.8298893$ (\textsc{pari} agreement $3.6\times10^{-6}$); the model subtlety
(naive Klein model is a cubic twist) caught by point counts.
\item \textbf{The scaling test}, \texttt{tmp/grade56\_scaling.py},
\texttt{tmp/theta\_79a1.npy}, \texttt{tmp/theta\_83a1.npy}: pre-registered
exact rationals at grades five and six, all landing $\le1.2\sigma$; Catalan
spine $C_3=5$ and Schur companions $C_4,C_5,C_6$; parity law (no DC channel at
grade five); falsifiers $132$--$139\sigma$, degenerate-scramble $437\sigma$;
design-change log: the odd-weight $\Gamma$ branch only.
\item \textbf{The clause-(c) hunt off the diagonal}, \texttt{tmp/k3\_ledger.py}
and \texttt{tmp/k3\_nondiag.py}: the diagonal-quartic reader (Fermat class
$\rho-1=19$ at split primes, exact locks on inert progressions) and the
non-diagonal escalation (Dwork pencil and block-separable generics; two
independent exact counters validated against brute enumeration; forty-four
pairs all separated, forced-isomorphic control identical; exact-discriminant
screening catching a bad prime at $229$ the small-$p$ screen missed).
\item \textbf{The tower atlas}, \texttt{tmp/tower\_atlas.py}: grades
$2$--$20$ on the first twenty prime-conductor curves; exact $O(g^2)$
convolution portal (brute-checked through $g=10$); the
$\varepsilon(g)$ law with the Kummer derivation; Catalan spine to $C_{20}$;
three-tier resolution law with theoretical (not empirical) error bands;
three-version falsifier sweep with the support-dilution curve;
\texttt{tmp/harmonic\_compat.py}: the compatibility audit (conjugate closure
at machine zero, the affine-in-$c(w)$ channel-moment law, rational-vs-%
incommensurate discrimination by lattice membership);
\texttt{tmp/helix\_tower.py}: the height run (Sym$^3$ pairing converges on
the carrier to the certified value, growth $-0.067$, single-rail and
mis-pair diverge; the degree-16 $G\ast\bar G$ identity at $2.4\times10^{-13}$;
the radial-head toll measured; the unit-scale window falsifier).
\item \textbf{Recognition at grade four},
\texttt{tmp/recognition\_loop\_g4.py}: the four-arm loop on three quadruples
(degenerate / two isogeny pairs / scrambled), truth consulted only at
grading; the live-direction law; independent counting- and period-side
alignment certificates; isogeny degrees found with $10^{-15}$-scale
$j$-residual landings; occupancy and channel-profile recognition
certificates; scrambled null and false-alignment rejection.
\item \textbf{Recognition at grade two (even rung)},
\texttt{tmp/bf\_loop\_g2.py} and \texttt{tmp/bf\_loop\_g2\_notes.md}: the
trivial-zero/FE bridge derived and confirmed; the certified Rankin--Selberg
values at the Beilinson point; the Rogers--Zudilin corner closed from
scratch (Mahler integral vs evaluator, $1.55\times10^{-5}$, rational landing
$24$); the genuine-product construction gap documented as the literature's
own state; the carrier translation of the even-rung construction arm.
\item \textbf{The value-registration census},
\texttt{tmp/value\_registration.py}: frozen forcible-closure protocol
(faithfulness anchor reproducing the published mis-registrations exactly);
$24$ rows over the six certified truths; leave-one-object-out
cross-validation killing the closure-improvement and degree/conductor
candidates and confirming off-lattice distance as the governing regressor;
the graded-family monotone degradation ($0.165\to0.200\to0.228\to0.236$ as
off-lattice freedom is added); the finite-difference Jacobian requirement
(real banks are first-order-stationary for the closure objective) documented
in-source.
\item \textbf{The grade-one pairing-law calibration},
\texttt{tmp/matching\_law\_g1.py}: canonical heights decomposed
place-by-place (archimedean theta/sigma via complex AGM --- the true lattice
$\tau=\omega_2/\omega_1$, not $j$-inversion's fundamental-domain
representative --- plus Bernoulli Green's functions on the reduction graphs);
one calibrated constant (the classical factor two), then frozen and blind;
jet comparison non-circular; wrong-graph falsifier missing by the exact
predicted rational.
\item \textbf{The rung-four Lean bricks},
\texttt{RequestProject/QuadrupleFiber.lean} (thirteen theorems: the degree-16
fiber's determinant-one ledger, $(-X)^{16}$ per-place functional equation,
completed reflection, strand exchange) and
\texttt{RequestProject/EvenWeightDC.lean} (ten theorems:
\texttt{dc\_channel\_iff\_even\_weight} and the grade-4/grade-5 corollaries).
Standard footprint on all twenty-three, no \texttt{sorry}.
\end{itemize}

\begin{thebibliography}{99}

\bibitem{Universal} S.~Lavery, \emph{Carrier, fiber, adapters, and
functoriality}, preprint draft v0.1 (2026); the 3D carrier system, the loss
ledger and its bijection, the functoriality program, and the reproducibility
corpus this paper builds on.

\bibitem{Hodge} W.~V.~D.~Hodge, \emph{The topological invariants of algebraic
varieties}, Proc.\ ICM 1950, vol.~1, 182--192.

\bibitem{Lefschetz} S.~Lefschetz, \emph{L'Analysis situs et la g\'eom\'etrie
alg\'ebrique}, Gauthier-Villars, Paris, 1924.

\bibitem{DeligneClay} P.~Deligne, \emph{The Hodge conjecture}, in \emph{The
Millennium Prize Problems}, Clay Math.\ Inst./AMS (2006), 45--53.

\bibitem{TateConj} J.~Tate, \emph{Algebraic cycles and poles of zeta
functions}, in \emph{Arithmetical Algebraic Geometry} (Purdue, 1963), Harper \&
Row (1965), 93--110.

\bibitem{Beilinson} A.~Beilinson, \emph{Height pairing between algebraic
cycles}, in \emph{$K$-theory, Arithmetic and Geometry}, Lecture Notes in
Math.\ \textbf{1289}, Springer (1987), 1--26.

\bibitem{Bloch} S.~Bloch, \emph{Height pairings for algebraic cycles}, J.\
Pure Appl.\ Algebra \textbf{34} (1984), 119--145.

\bibitem{Murre} J.~P.~Murre, \emph{On a conjectural filtration on the Chow
groups of an algebraic variety}, Indag.\ Math.\ (N.S.) \textbf{4} (1993),
177--201.

\bibitem{BSD} B.~J.~Birch and H.~P.~F.~Swinnerton-Dyer, \emph{Notes on
elliptic curves.\ II}, J.\ reine angew.\ Math.\ \textbf{218} (1965), 79--108.

\bibitem{GrossZagier} B.~H.~Gross and D.~B.~Zagier, \emph{Heegner points and
derivatives of $L$-series}, Invent.\ Math.\ \textbf{84} (1986), 225--320.

\bibitem{Kolyvagin} V.~A.~Kolyvagin, \emph{Euler systems}, in \emph{The
Grothendieck Festschrift, vol.~II}, Progr.\ Math.\ \textbf{87}, Birkh\"auser
(1990), 435--483.

\bibitem{ZhangGS} S.~Zhang, \emph{Gross--Schoen cycles and dualizing sheaves},
Invent.\ Math.\ \textbf{179} (2010), 1--73; the Beilinson--Bloch height of the
modified diagonal.

\bibitem{YZZ} X.~Yuan, S.~Zhang, and W.~Zhang, \emph{Triple product
$L$-series and Gross--Schoen cycles}, book manuscript; the central derivative
of the triple-product $L$-function as a Gross--Schoen/Ceresa height.

\bibitem{Ceresa} G.~Ceresa, \emph{$C$ is not algebraically equivalent to
$C^-$ in its Jacobian}, Ann.\ of Math.\ (2) \textbf{117} (1983), 285--291.

\bibitem{Harris} B.~Harris, \emph{Harmonic volumes}, Acta Math.\ \textbf{150}
(1983), 91--123, and \emph{Homological versus algebraic equivalence in a
Jacobian}, Proc.\ Natl.\ Acad.\ Sci.\ USA \textbf{80} (1983), 1157--1158.

\bibitem{LagaShnidman} J.~Laga and A.~Shnidman, \emph{Ceresa cycles of
bielliptic Picard curves}, arXiv:2312.12965 (2024).

\bibitem{Flach} M.~Flach, \emph{A finiteness theorem for the symmetric square
of an elliptic curve}, Invent.\ Math.\ \textbf{109} (1992), 307--327.

\bibitem{GGP} W.~T.~Gan, B.~H.~Gross, and D.~Prasad, \emph{Symplectic local
root numbers, central critical $L$-values, and restriction problems in the
representation theory of classical groups}, Ast\'erisque \textbf{346} (2012),
1--109.

\bibitem{WZhangAFL} W.~Zhang, \emph{Weil representation and arithmetic
fundamental lemma}, Ann.\ of Math.\ (2) \textbf{193} (2021), 863--978.

\bibitem{VoisinMD} C.~Voisin, \emph{Some new results on modified diagonals},
Geom.\ Topol.\ \textbf{19} (2015), 3307--3343; the vanishing
$\Gamma^{g+2}(C,x)=0$.

\bibitem{DeligneEps} P.~Deligne, \emph{Les constantes des \'equations
fonctionnelles des fonctions $L$}, in \emph{Modular Functions of One Variable
II}, Lecture Notes in Math.\ \textbf{349}, Springer (1973), 501--597.

\bibitem{TateNTB} J.~Tate, \emph{Number theoretic background}, in
\emph{Automorphic Forms, Representations and $L$-functions} (Corvallis),
Proc.\ Sympos.\ Pure Math.\ \textbf{33.2}, AMS (1979), 3--26.

\bibitem{Rohrlich} D.~E.~Rohrlich, \emph{Elliptic curves and the Weil--Deligne
group}, in \emph{Elliptic Curves and Related Topics}, CRM Proc.\ Lecture
Notes \textbf{4}, AMS (1994), 125--157.

\bibitem{Tadokoro} Y.~Tadokoro, \emph{A nontrivial algebraic cycle in the
Jacobian variety of the Klein quartic}, Math.\ Z.\ \textbf{260} (2008),
265--275.

\bibitem{Elkies} N.~D.~Elkies, \emph{The Klein quartic in number theory}, in
\emph{The Eightfold Way}, MSRI Publ.\ \textbf{35}, Cambridge Univ.\ Press
(1999), 51--101.

\bibitem{Estermann} T.~Estermann, \emph{On certain functions represented by
Dirichlet series}, Proc.\ London Math.\ Soc.\ (2) \textbf{27} (1928),
435--448.

\bibitem{Kurokawa} N.~Kurokawa, \emph{On the meromorphy of Euler products~I},
Proc.\ London Math.\ Soc.\ (3) \textbf{53} (1986), 1--47.

\bibitem{Beilinson1985} A.~Beilinson, \emph{Higher regulators and values of
$L$-functions}, J.\ Soviet Math.\ \textbf{30} (1985), 2036--2070.

\bibitem{LLZ} A.~Lei, D.~Loeffler, and S.~L.~Zerbes, \emph{Euler systems for
Rankin--Selberg convolutions of modular forms}, Ann.\ of Math.\ (2)
\textbf{180} (2014), 653--771.

\bibitem{BDR} M.~Bertolini, H.~Darmon, and V.~Rotger, \emph{Beilinson--Flach
elements and Euler systems I}, J.\ Algebraic Geom.\ \textbf{24} (2015),
355--378.

\bibitem{BrunaultChida} F.~Brunault and M.~Chida, \emph{Regulators for
Rankin--Selberg products of modular forms}, Ann.\ Math.\ Qu\'e.\ \textbf{40}
(2016), 221--249.

\bibitem{RogersZudilin} M.~Rogers and W.~Zudilin, \emph{On the Mahler measure
of $1+X+1/X+Y+1/Y$}, Int.\ Math.\ Res.\ Not.\ (2014), 2305--2326; and
\emph{From $L$-series of elliptic curves to Mahler measures}, Compositio
Math.\ \textbf{148} (2012), 385--414.

\bibitem{DMW} N.~Dummigan, P.~Martin, and M.~Watkins, \emph{Euler factors
and local root numbers for symmetric powers of elliptic curves}, Pure Appl.\
Math.\ Q.\ \textbf{5} (2009), 1311--1341.

\bibitem{SaitoEps} T.~Saito, \emph{The sign of the functional equation of
the $L$-function of an orthogonal motive}, Invent.\ Math.\ \textbf{120}
(1995), 119--142.

\end{thebibliography}

\end{document}
